### 2017-02-03 PensionAge.Rmd
Initial commit

---
title: "Forecasting the population age structure to determine the best pension age"
author: "Rob J Hyndman, Yijun Zeng and Han Lin Shang"
date: "`r format(Sys.time(), '%-d %B %Y')`"
fontsize: 11pt
papersize: a4
fontfamily: kpfonts
bibliography: pensionage.bib
biblio-style: authoryear-comp
subparagraph: true
toc: false
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
# Make sure you have the latest version of rmarkdown and bookdown
#devtools::install_github("rstudio/rmarkdown")
#devtools::install_github("rstudio/bookdown")
library(demography)
library(addb)
library(ggplot2)
source("Rcode/functions-v4.R")
```

\begin{abstract}
We forecast the old-aged dependency ratio for Australia, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.

We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%.

This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
\end{abstract}

\begin{keywords}
?????
\end{keywords}

\newpage

#Introduction

Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the last twenty or so years [@Fehr2008].  Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Similar demographic challenges face many other countries. One way of measuring this problem is via the old-age dependency ratio (OADP): the number of people post-retirement to the number of people of working age [@Walker1982]. The OADP has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age\footnote{The \textit{pension age} is defined as the age at which eligible residents can access the age pension for the first time.}. In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010]. In May 2014, the Federal Treasurer proposed to further increase the pension age to 70 by 2035. This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014. In this paper, we investigate the effect of these changes to the pension age on the forecast OADP.

The research presented in this paper contributes to the discussion by forecasting the age structure of the population, quantifying the effects of changing the pension age on financial burdens, and hence finding an appropriate pension age scheme which is economically viable for Australia. The analysis of economic impact of increasing pension age can be complicated. In this paper, we will focus on only one aspect: the impact on the burden of future working age generations.

In this paper, we use the old aged dependency ratio (OADR\footnote{All abbreviations have been summarized in Appendix A.}) as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].  The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07]. This can be expressed using the formula below:
\begin{equation}
  OADR=\frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100%
\end{equation}
The research presented here forecasts future population age structures over the next 50 years. We then use those projections to compute the OADR associated with pension age both before and after the adjustments. One major contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.  Forecasts of population structure have been built on forecasts of age and gender-specific mortality rates, fertility rates and net migration using this method. These forecasts presuppose that the historical trends of past years will continue. Historical data of those rates have thus been used as input to simulate future paths of age and gender-specific population structure.

Using these predicted population paths, we can calculate the average of OADR and predict the levels of old age dependency that correspond to different pension age schemes. By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome. Therefore, other main contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2)\ to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future. It should be noted that the desired level has been set at 21%, which is the estimated current level of OADR in 2014. This level was chosen because, while the current financial burden on tax payers is affordable, it is approaching the limits of affordability. However, whether or not the current level is the most appropriate level to Australia remains to be examined and it is not the focus of this paper. This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.

Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation. However, 80% of Australians over pension age fully or partly rely on the age pension [@Power14]. Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.  Nevertheless, it should be aware that using OADR as a single measurement of financial burden might overlook some important economic factors. Some have suggested to use adjusted OADR that considers those important factors in analyzing pension finance [@HY12]. This paper emphasizes how to undertake a better forecasting of economic burden for a given policy rather than the better choice of measurements. Therefore, the simple version of OADR was chosen to illustrate my approach (i.e., without adjustment). There is a ground to extend the approach to incorporate more complex measurement which takes into account of other important economic factors.

Furthermore, choosing the right model to forecast population age structure was another important step involved in the quantification process. I chose to combine the Hyndman-Ullah method and product-ratio method for the forecast. The combination of those two methods overcomes some of shortcomings of other popular demographic forecasting methods such as the Lee-Carter method [@LC92] or the deterministic methods used by the Australian Bureau of Statistics [@ABS06; @ABS12]. More details on forecasting methods are given in later sections.

The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at current OADR-21%. However, it has been argued that a one-time adjustment is not sufficient to ensure a stable OADR in the long term. Therefore, this paper recommends consistently reviewing the pension age according to the presented statistical approach. This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval. The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058. This generates a stable OADR of around 21%. The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.

The remainder of this paper proceeds as follows. Section 2 reviews key literature on population forecasting and background works on the pension age. Section 3 describes the data and methods used in this study. Section 4 discusses the empirical results of this research, and outlines accuracy tests performed on the empirical results. Finally, Section 6 gives concluding remarks as well as identifies the scope for future research.

# Background and Literature Review

## Background on Australian Age Pension

Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing. For example, it provides single home-owners with a real income of \$13653 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}. The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases. The age pension in Australia is very generous, even with the means test. For instance, a couple holding assets of more than one million dollars is still eligible for a partial age pension.

Currently, the age pension is the primary source of income for 70% -80% of Australian residents over 64 years [@ABS06]. Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the current average less than \$100,000 at retirement [@ASFA07].  It has been estimated by @PT08 that a retiree will need to have \$450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.  The required wealth to comply with personal-funded retirement savings requirements is too high for most Australians, suggesting that retirees will continue to rely on the age pension in the coming decades.

The ageing trend in Australia, along with retirees' dependence on the age pension, has dramatically increased the fiscal cost of the age pension. For instance, the fiscal cost of the age pension is currently around at 2.5% of Gross Domestic Profit (GDP), but is expected to increase to 4.4% by the 2050s (Australian Government, 2007). The @PC13 also indicates the government will need to raise taxes by 21% to pay for extra aged care and health costs, which is caused by longer life expectancies in newer generations.

The issue is not only a problem for the government, but also for future retirees. Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65). They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}. This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR03].

```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE, messages=FALSE}
year <- 2065-2007
proposed <- ts(pmin(70,
         c(rep(65,2017-2008), 65 + cumsum(rep(c(0.5,0),55))))[1:50],
         start=2008)
approved <- pmin(proposed,67)
current <- pmin(proposed,65)
cols <- c(current='#1b9e77',approved='#d95f02',proposed='#7570b3')
ggplot() +
  autolayer(proposed, series='proposed') +
  autolayer(approved, series='approved') +
  autolayer(current, series='current') +
  xlab("Year") + ylab("Age of retirement") +
  scale_color_manual(values=cols, name=" ",
                     breaks=c("current","approved","proposed"),
                     labels=c("Pension age at 65","Approved change","Proposed further change"))
```

The Australian government is trying to take early intervention in relation to the pension age to balance between providing social support and fiscal cost. The pension age for males has been set at 65 for over a century. While the pension age for females was 60 years until 1994, it has steadily increased to 65 years, in line with that of males. The previous Labor government announced in 2009 that the pension age will increase six months every two years until 2017, capping at 67 in July 2023. This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because pension age is regarded as a normal age for retirement in Australia. However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and elderly people are capable of continuing work. The National Commission of Audit (NCOA)(2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053. The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government. Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme. This announcement received overwhelmingly negative responses in the media. @Guest14 argues from an economic prospective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is  less than half of the OECD average. He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time. Further, @Power14 contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more a complex social problem.

In fact, all supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age. No justification on the pace or degree of the change has been provided. Also, the government has not disclosed the method it used to determine the new pension age. It is therefore not surprising that the adjustment of the pension age has been questioned by the public. A consistent method to determine the appropriate pension age would be more persuasive in general. For example, it is preferred by OECD countries that pension age should be linked to life expectancy [@OECD12]. There is a practical issue as to how to link life expectancy with pension ages given that there is no information on future mortality rates [@PC13]. @CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50% of any increase in life expectancy''. However, using a ‘rule of thumb’ approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term. My study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates. My approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.

## Mathematical Preliminaries

### Principal Component Analysis

Principal component analysis (PCA) is the main estimation method used in population forecasting. It is essential for understanding the models introduced in the following sub-section. Therefore, a brief introduction of PCA is given here.

Principal components analysis reorients multivariate data in a way that ensures that the first few dimensions (called components) summarize as much of the available information as possible [@LCG03]. More precisely, it uses an orthogonal transformation  to convert a set of possibly correlated variables into a set of linearly uncorrelated variables called \textit{principal components}. It is possible to reduce the dimensions (new uncorrelated variables) if substantial redundancy is present in the data set. The rearrangement of data allows researchers to decide ``how many principal components to retain for subsequent analysis, trading off simplicity (i.e., a small number of dimensions is easier to manage) against completeness (i.e., a large number of dimensions captures a greater amount of available information)'' [@LCG03, p83].

The mathematical derivation of PCA is explained in detail by @LCG03. I have summarized the main ideas here. In PCA, the objective is to find a linear combination of original data with maximum variance, because the aim is to derive the component (which is the new variable after linear transformation) that summarizes as much information as possible. Suppose we have an $m\times n$ matrix $\bm{X}$ that contains $m$ observations of $n$ variables (dimensions) with a rank of $k$. If we denote linear combinations by the matrix $\bm{U}=[\bm{u_1},\bm{u_2},\bm{u_3},\dots,\bm{u_k}]$ where $\bm{u_i}=(u_{1i},u_{2i},u_{3i},\dots,u_{ni})'$ and denote the matrix of principal component scores by $\bm{Z}=[\bm{z_1},\bm{z_2},\bm{z_3},\dots,\bm{z_k}]$ where $\bm{z_i}=(z_{1i},z_{2i},z_{3i},\dots,z_{mi})'$
, then our goal is to choose $\bm{u_i}$ to maximize the variance of the elements of $\bm{z_i}=\bm{X}\bm{u_i}$, which can be written as:
\begin{equation} 
  var(\bm{z_i})=\frac{1}{m-1}\bm{u_i}' \bm{X}' \bm{X}\bm{u_i}.
\end{equation}
This maximization will ensure that first principal component $\bm{z_1}$ captures the most information (variance) in the original data and every subsequent principal component captures the most information in the remaining variance. However, this maximization does not have a unique solution because the magnitude of $\bm{u}$ is arbitrary, thereby making $var(\bm{z_i})$ infinity. To achieve the maximization, we impose a constraint of unit magnitude on the vector $\bm{u_i} ~\forall i$. Thus, the completed maximization problem is as follows:
\begin{equation}
  \text{choose~} \bm{u} \text{~to maximize~} \frac{1}{m-1}\bm{u}' \bm{X}' \bm{X}\bm{u}
\end{equation}
subject to the constraint $\bm{u}'\bm{u} =1$.

We can solve this constrained optimization problem using the Lagrangian multiplier method (see @LCG03 for a detailed mathematical proof). These authors demonstrate that the solved vectors $\bm{z_i}$ and $\bm{u_i}$ are eigenvectors of the matrices $\bm{X}\bm{X}'$ and $\bm{X}'\bm{X}$ respectively, and the corresponding Lagrangian multiplier $\lambda_i$ is the eigenvalue of $\bm{X}\bm{X}'$. The numbers $\lambda_1,\lambda_2,\dots\lambda_k$ are singular values of $\bm{X}$ and vectors $\bm{z_1},\bm{z_2},\dots,\bm{z_k}$ and $\bm{u_1},\bm{u_2},\dots,\bm{u_k}$ are right and left singular vectors. Also, it can be shown that $\lambda_i$ is equal to $var(\bm{z_i})$, which  implies that variance-covariance matrix of $\bm{Z}$ (denoted by $\Sigma$) is  a diagonal matrix with $\Sigma_{ii}=\lambda_i$. Therefore, the vector $\bm{z}$ associated with largest $\lambda$ is the first principal component, which capture the most variance in original data.

The relationship $\bm{z_i}=\bm{X}\bm{u_i}$ can be written in matrix form as follows:
\begin{equation}
  \bm{Z}=\bm{X}\bm{U}
\end{equation}
With a little algebra, we can rearrange the above equation to express $\bm{X}$ as a function of $\bm{Z}$. We post multiplying $\bm{U}'$ of both sides (note that we have $\bm{U}\bm{U}'=\bm{I}$ because of the mutual orthogonality of eigenvectors) and the new equation is as follows:
\begin{equation}
  \bm{X}=\bm{Z}\bm{U}'
\end{equation}
Further, we can express $\bm{X}$ as a function of standardized matrix of principal components (denoted $\bm{Z_s}$) by decomposing $\bm{Z}$ into $\bm{Z^s}\Sigma^{1/2}$. Then, the equation becomes:
\begin{equation}
  \bm{X}=\bm{Z^s}\Sigma^{1/2}\bm{U}'
\end{equation}
Alternatively, it can be expressed as:
\begin{equation}
  \bm{X}=\bm{z^s_1}\sqrt{\lambda_1}\bm{u_1}'+\bm{z^s_2}\sqrt{\lambda_2}\bm{u_2}'+\dots+\bm{z^s_k}\sqrt{\lambda_k}\bm{u_k}'
\end{equation}
This way of expressing $\bm{X}$ is known as a singular value decomposition (SVD). It indicates that any data matrix $\bm{X}$ can be decomposed into three simpler matrices. $\bm{Z^s}$ is a standardized matrix of uncorrelated variables (each with unit variance), $\Sigma^{1/2}$ is a diagonal matrix which perform a stretching transformation of $\bm{Z^s}$ and $\bm{U}'$ performs an orthogonal rotation. Therefore, we can use singular value decomposition to undertake a PCA.

### ARIMA and ARFIMA Model

ARIMA and ARIFMA are essential mathematical models that is required to understand to perform the population forecasting method. I give a brief introduction of them based on the work of @fpp.

\subparagraph{AR($p$) model}
Autoregression models forecast the dependent variable using a linear combination of its past values. An autoregression model the order of $p$ (referred as AR$(p)$ model) can be written as:
\begin{equation}
y_t=c+\phi_1y_{t-1}+\phi_2y_{t-2}+\dots+\phi_py_{p-1}+e_t
\end{equation}
where $c$ is a constant and $e_t$ is white noise.

\subparagraph{MA(q) model}
A moving average model supposes that the variable of interest can be explained by past forecast errors. It can be written as:
\begin{equation}
y_t=c+e_t+\theta_1e_{t-1}+\theta_2e_{t-2}+\dots+\theta_qe_{t-q}
\end{equation}
where $e_t$ is white noise.

\subparagraph{Non-seasonal ARIMA models}  A non-seasonal ARIMA model is a combination of differencing, autoregression and moveing average models. ARIMA is an acronym for AutoRegressive Integrated Moving Average model. An ARIMA model can be written as:
\begin{equation}
  y_t' = c + \phi_1y_{t-1}' + \dots + \phi_py_{t-p}' + \theta_1e_{t-1} + \dots + \theta_qe_{t-q} + e_t
\end{equation}
where $y_t'$ is the differenced series, which is differenced $d$ times. This regression is referred to as an ARIMA($p,d,q$) model, where $p$ is the order of the auotoregression part; $d$ is the degree of first differencing and $q$ is the order of the moving average part.

In fact, the AR($p$) and MA($q$) models are ARIMA ($p$,0,0) and ARIMA (0,0,$q$) models respectively.
ARIMA models can be written in backshift notation (i.e.$By_t=y_{t-1}$) as follows:
\begin{equation}
  (1-\phi_1B-\dots-\phi_pB^p)(1-B)^dy_t=c+(1+\theta_1B+\dots+\theta_qB^q)e_t
\end{equation}
\subparagraph{ARFIMA model}
We can allow $d$ in the ARIMA model to be fractional in order to capture the long-memory property of some series. The ARIMA model with fractional differencing (i.e., $-\frac{1}{2}<d<\frac{1}{2}$) is called the ARFIMA model. The range $0<d<\frac{1}{2}$ gives long-memory process [@CM09].

\subparagraph{Akaike's Information Criterion}

AIC is a model-selection procedure which is useful to determine the order of an ARIMA model.
It can be written as:
\begin{equation}
  AIC=-2log(L)+2(p+q+k+1)
\end{equation}
where $L$ is the likelihood of the data, $k=1$ if $c\neq0$ and $k=0$ if $c=0$.

For ARIMA models, the corrected AIC [@fpp] can be written as
\begin{equation}
  AIC_c=\frac{AIC+2(p+q+k+1)(p+q+k+2)}{T-p-q-k-2}
\end{equation}
where the correction is to reduce small sample bias.
The ARIMA model with minimum AIC or minimum $AIC_c$ is the optimal model. I prefer to use $AIC_c$ to reduce sample bias in this research.

## Literature Review on Population forecasting methods

In population forecasting, two very different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used. For instance, the Australian Bureau of Statistics is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau. In the deterministic approach, experts project future demographic changes using judgement-based scenarios. It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour [@PC13]. In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method. Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates [@PC13].

Therefore, some official agencies decide to mix the two approaches in their forecasts in order to provide a supplement to both approaches. For instance, the most recent forecast of population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture. The approach of forecasting used in this study is very similar to the @PC13. The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of Lee-Carter method. In addition, an adapted product-ratio method is used to eliminate the potential long-term divergence between female and male mortality rates. A more detailed review of forecasting methods is given below.

### Deterministic Methods Used by the ABS

The deterministic method is judgment-based. The Australian Bureau of Statistics formulates assumptions on the basis of demographic trends, in conjunction with advice from individual experts or government departments. The projections are not predictions or forecasts, ``but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period'' [@ABS12, p.2]. In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes. Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for variety of population projections.

### Lee-Carter Method

The Lee-Carter method [@LC92] is a significant milestone in demographic forecasting. It has been widely used to forecast mortality rates across various countries, including Australia.

The model proposed by @LC92 is as follows:
\begin{equation}
  \log(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
\end{equation}
where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section.3} for age $x$ in year $t$. This model involves fitting a matrix of log central rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
$b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$. $k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

The model is under-determined in terms of estimation of parameters. For example, if the vector $a,b,k$ is one solution, then for any scalar $c, a-bc, b, k+bc$ also must be one solution. Therefore, Lee and Carter (1992) impose the following constraints:
\begin{equation}
\sum_{t=1}^{n}k_t=0, \sum_{x=x_1}^{x_m}b_x=1
\end{equation}
Also, we normally seek the least squares solution when estimating parameters. However, in this case, the model cannot be estimated using ordinary regression methods because there is no regressor on the right side of the equation. @LC92 choose a singular value decomposition (SVD) method to undertake PCA, and hence find the least squares solution. It has been shown that applying SVD methods to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969). Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\log(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\log(m_{x,t})-a_x$).
However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the log transformation. To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to ARIMA ($0,1,0$) model with $c\neq0$.

### Hyndman-Ullah Method

@HU07 proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
First, the rates are smoothed using penalized regression splines [@BHT14] before modeling.
Second, it uses functional principal components analysis, which is a continuous version of PCA.
Further, it uses more than one principal component, which address the main weakness of the LC method.
Finally, the forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.

The model proposed by @HU07 is as follows:
\begin{align}
y_t(x)&=s_t(x)+\sigma_t(x)\epsilon_{t,x}\\
s_t(x)&=\mu(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)
\end{align}
The first equation describes the smoothing process. $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [BHT14]. $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms. The second equation has a similar structure to the LC method, except that it incorporates more than one principal component and score. It describes the dynamics of $s_t(x)$ over time. The $\beta_{t,j}$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\phi_j(x)$ for every $j$ is a time-varying index. The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation. The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$. The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively. In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then equation (7) now becomes
\begin{equation}
s_t(x)-\mu(x)=\phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
\end{equation}
We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.

In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\ $ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
\begin{equation}
\hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x)=E[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}]=\hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
\end{equation}
where $\hat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$. Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process. For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an $ARIMA(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process as follows:
\begin{equation}
(1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2..,J
\end{equation}
where the parameters are estimated using maximum likelihood estimation.

# Data and Methodology

## Data

We use the same notation and similar procedures to construct data as [@HB08], because the fundamental model for forecasting population for this study is the Hyndman and Ullah method. The data used to construct population age structure included: age and gender-specific birth and death numbers of each calendar year, age and gender-specific population members on 1\ January of each year, and age and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year. The notations are as follows:
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
\end{align*}
where $x$ denotes age and $x=0,1,2,\dots,m^+$. $m^+$ is the open-ended upper age group, which is 100 in this study. $t$ denotes year and $t=1,2,\dots,n$, where $n$ is the horizon of historical data used. Therefore, all of those data points can be recorded in an $m\times n$ matrix.  The super-scripts $M$ and $F$ denote male and female respectively.

We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
\begin{align*}
m_t(x)&=\frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
f_t(x)&=B_t(x)/E^F_t(x)=\text{age-specific fertility rates in calendar year t}
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths. The equation is:
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
\end{align*}
where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$. The deaths are estimated using the standard life table approach of population projection. It should be noted that the estimated net migration includes errors in data recording.

Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2009. The start-year population for 2010 is also used to estimate net migration. Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2009 was obtained from the @ABS12. Even though annual mortality rates are available from 1921 to 2009, only data collected after 1950 is used for two reasons. First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08]. Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them. Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.

## Methodology

### Forecasting Population Age Structure and OADR

In this study, three steps were taken to simulate OADR associated with a specific pension age scheme. A stochastic functional model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study). Age and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation. The Monte Carlo simulation method was used consistently in this research. Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula. Even though the process seems complicated, it is relatively resy to implement using \textit{R}. The detailed explanation of each step is as follows. The corresponding R code is attached in Appendix B.

\subparagraph{Step 1}The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast. The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently. Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data. However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13]. In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
\begin{align*}
  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
\end{align*}
Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
\begin{align*}
  log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$). It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19).
From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
\begin{align*}
m_{n+h\mid n,M}(x)&=p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
m_{n+h\mid n,F}(x)&=p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
\end{align*}
The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration. A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.

\subparagraph{Step 2} After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon. The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions). Hence, we can simulate $h$-step-ahead age and gender-specific births and deaths based on simulated mortality and fertility rates. According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age. This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population. The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research). It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in equation (17)), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution. It should be noted that the simulated population will be an array with 3 dimensions: age, year and simulation.

\subparagraph{Step 3} Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time. To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations. Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend. I will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age. The same method can be applied to all years over the prediction horizon, given their corresponding pension age. Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers. I will also show how this issue was handled in the example below.

Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age. Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
\begin{equation}
\bm{p}_{n+1}=[p_{mi}]=
\left[
\begin{array}{ccc}
 p_{1,1} & \cdots\cdots & p_{1,1000} \\
\vdots & \ddots & \vdots \\
p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
\end{array}
\right]
\end{equation}
When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
\begin{equation}
\left[
\begin{array}{ccc}
 p_{15,1} & \cdots\cdots & p_{15,1000} \\
\vdots & \ddots & \vdots \\
p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
\end{array}
\right]
\end{equation}
To calculate the total number of working age, we take a column sum of the trimmed matrix (22). The simulations of total number of work age become a vector:
\begin{equation}
\bm{p}^{work}_{n+1}=[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]
\end{equation}
Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
\begin{equation}
\bm{p}^{aged}_{n+1}=[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]
\end{equation}

When $r\neq0$, the vector of total number of work age (23) is added, and the vecor of total number of aged population is subtracted with an adjustment:
\begin{equation}
\text{adjustment}=0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
\end{equation}
This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year. Then, $r\times100\%$ of population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age. In other words,$(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population. The simulation vectors of total work age population and total aged population should then be:
\begin{align*}
\bm{p}^{work}_{n+1}&=[p^{work}_{n+1,1},p^{work}_{n+1,2},\dots,p^{work}_{n+1,1000}]\\
&=[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]+0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]   \\
\bm{p}^{aged}_{n+1}&=[p^{aged}_{n+1,1},p^{aged}_{n+1,2},\dots,p^{aged}_{n+1,1000}]\\
&=[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]-0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
\end{align*}

After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{work}_{n+1}$ by the corresponding element of $\bm{p}^{aged}_{n+1}$, i.e.:
\begin{align*}
\bm{OADR}_{n+1}&=[OADR_{n+1,1},OADR_{n+1,2},\dots,OADR_{n+1,1000}]\\
&=\left[\frac{p^{work}_{n+1,1}}{p^{aged}_{n+1,1}},\dots,\frac{p^{work}_{n+1,1000}}{p^{aged}_{n+1,1000}}\right]
\end{align*}
The average value of elements of $\bm{OADR}_{n+1}$ is the mean prediction of one-step-ahead OADR (i.e mean forecast of OADR in 2011).

The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2011 to 2060). Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
\begin{equation}
\bm{OADR}^{forecast}=[OADR_{h,i}]=
\left[
\begin{array}{ccc}
 OADR_{n+1,1} & \cdots\cdots & OADR_{n+50,1000} \\
\vdots & \ddots & \vdots \\
OADR_{n+50,1} & \cdots\cdots &OADR_{n+50,1000}
\end{array}
\right]
\end{equation}

### Finding the Target Pension Age Scheme

The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level. According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given. Suppose we denote pension age schemes over the prediction horizon by $\bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}]$. The OADR function of pension age over the prediction horizon is denoted as $OADR_h(PA_{n+h})$ for $h=1,2,3,\dots,H$. There is a negative relationship between pension age and OADR. The negative relationship implies that the higher the pension age, the lower the OADR. Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level. Several practical issues need to be considered to achieve this goal. First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR. Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications. Therefore, the target pension age scheme $\bm{PA}^{target}$ can be defined in the following way:
for $h=1,2,\dots,H$
\begin{equation}
\text{minimise~} PA_{n+h}  \text{~such that~} OADR_h(PA_{n+h})\leq OADR^{desired}
\end{equation}
\begin{align*}
\text{subject to the constraint~} 0\leq PA_{n+h}-PA_{n+h-1}\leq 1
\end{align*}
In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience. It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65 and 64.5 respectively. The same pension age for males and females was set to simplify the calculations. This simplification is reasonable because the pension age will be same in 2017 onward.}, which is:
\begin{align*}
  \bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}] = [65,65,\dots,65]
\end{align*}
We take the following algorithm:
For $h=1,2,\dots,H$,
we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
\begin{align}
 OADR^{mean}_h(PA_{n+h})> OADR^{desired} \text{~or~} PA_{n+h}-PA_{n+h-1}\geq 1
\end{align}
where $OADR^{mean}_h(PA_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $PA_{n+h}$.

In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level. To be more specific, ``plausible'', means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR. Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level. Hence, any pension age scheme within those two boundaries is plausible. The range of plausible pension age schemes can be thought of as 80% confidence interval of pension age scheme where we are 80% sure that there will be a desired outcome. In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.

The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR in equation (28) is replaced by the boundary of the 80% prediction interval. Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.

# Empirical Results

## Forecast in Population Age Structure and OADR

```{r getdata}
############################
## GET ALL THE DATA
############################

# Get population data for 1 Jan 2010
# Store data locally ????????????
#pop2010 <- hmd.pop("AUS",username,password,"Australia")
#pop2010 <- extract.ages(pop2010, age=0:100)

# Get mortality data
# Store data locally ????????????
#aus.mort <- hmd.mx("AUS",username,password,"Australia")
#aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
#                    combine.upper=FALSE), 
#                    year=1950:max(aus.mort$year))

##### FERTILITY

# Get fertility data:
# Need to install addb package from http://robjhyndman.com/software/addb/
#library(addb) # Contains fertility data for 1921-2006
#aus.fert <- aus.fertility

# Update fertility data to 2009
# Store data locally ?????????
#ausfertility <- read.csv("http://robjhyndman.com/data/ausfertility.csv",header=TRUE,colClasses="numeric")
#aus.fert$rate$female <- as.matrix(cbind(aus.fert$rate$female[,30:54], ausfertility[,2:36]))
#aus.fert$pop$female <- cbind(aus.fert$pop$female[,30:86], aus.mort$pop$female[16:50,58:60])
#colnames(aus.fert$rate$female) <- colnames(aus.fert$pop$female) <- aus.fert$year <- 1950:2009
#rm(ausfertility)

##### MIGRATION

#aus.mig <- netmigration(aus.mort, aus.fert, mfratio = 1.05)

#save(pop2010,aus.mort,aus.fert,aus.mig,file='ausdata.rda')
load("ausdata.rda")
```

```{r smoothing}
################################################
################ SMOOTHING STEP ################
################################################

ausmort.sm <- smooth.demogdata(aus.mort, obs.var="theoretical")
ausfert.sm <- smooth.demogdata(aus.fert, obs.var="theoretical")
ausmig.sm <- smooth.demogdata(aus.mig)
```

```{r models}
################################################
################ MODELLING STEP ################
################################################

# MORTALITY
mort.fit <- coherentfdm(ausmort.sm)
mortf <- forecast(mort.fit, h=50)

# FERTILITY
fert.fit <- fdm(ausfert.sm)
fertf <- forecast(fert.fit, h=50)

# MIGRATION
mig.fit <- coherentfdm(ausmig.sm)
migf <- forecast(mig.fit, h=50)
```

I use the fitted model of fertility rates as an example to interpret the results of fitted models. It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense. Figure \ref{fig:componentsfertility} above shows the mean age pattern ($\mu(x)$), the first two basis functions ($\phi_1(x)$ and $\phi_2(x)$) and first two coefficients (i.e., principal component scores $\beta_{t,1}$ and $\beta_{t,2}$) for fertility rates. The first term ($\phi_1(x)*\beta_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term. In the plot of coefficient 1,
estimated historical first principal component scores $\beta_{t,1}$ are shown in black for 1950-2009. It captures the general trend of fertility change over time. It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961. This increase of fertility is linked to the Post-World War II baby boom\footnote{between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}. The dramatic decrease from 1960 was due to the availability of contraception pills in Australia. A  noticeable further reduction of fertility rates in late 1960s may be due to a change in the law allowing abortion in some states in Australia.

```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates."}
par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
plot(fertf, 'c', comp=2)
```

The first basis function $\phi_1(x)$ measures the different effects of the trend over time across ages. It indicates the general pattern of fertility has very little effect on females of age 15. This makes intuitive sense because most early pregnancies are accidental, therefore, any of previously discussed events has no effect on early pregnancies. In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s. Furthermore, the blue line is the fitted value of future coefficients (i.e., $\beta_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% prediction interval according to the fitted ARIMA model of first coefficients $\left\{\beta_{t,1}\right\}$. Other terms further explain variation that has not been captured by first term, but less economic explanations can be given for them.

```{r simulation}
############### SIMULATION STEP #################
# This takes a while!
#aus.sim <- pop.sim(mortf, fertf, migf, firstyearpop=pop2010, N=2000)
#save(aus.sim,file='aussim.rda')
load("aussim.rda")

## Means and intervals
popm.mean <- apply(aus.sim$male,c(1,2),mean)
popm.lo <- apply(aus.sim$male,c(1,2),quantile,p=.1)
popm.hi <- apply(aus.sim$male,c(1,2),quantile,p=.9)
popf.mean <- apply(aus.sim$female,c(1,2),mean)
popf.lo <- apply(aus.sim$female,c(1,2),quantile,p=.1)
popf.hi <- apply(aus.sim$female,c(1,2),quantile,p=.9)

## TOTAL POPULATION COMPARISONS
totfpop <- apply(aus.sim$female,c(2,3),sum)
totmpop <- apply(aus.sim$male,c(2,3),sum)
totfpop.q <- apply(totfpop,1,quantile,p=c(0.025,.1,.5,.9,.975),na.rm=TRUE)/1e6
totmpop.q <- apply(totmpop,1,quantile,p=c(0.025,.1,.5,.9,.975),na.rm=TRUE)/1e6
```

```{r totalpopulationbyyears, fig.cap="Fifth-year forecasts of total population for each sex, along with 80% prediction intervals. The actually population from 1950 to 2010 is shown using circles.", fig.height=4}
par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
par(mfrow=c(1,2))
fy <- 2012+(1:50)
plot(1921:2012, colSums(pop2010$pop$female)/1e6,
     xlim=c(1975,2030),
     ylim=range(c(7,17),na.rm=TRUE),
     xlab="Year",
     ylab="Population (millions)",
     main="Total females")
polygon(c(fy,rev(fy)),
        c(totfpop.q[2,],rev(totfpop.q[4,])),
        col="yellow",border=FALSE)
lines(fy,totfpop.q[3,],lwd=2,col="blue")

plot(1921:2012, colSums(pop2010$pop$male)/1e6,
     xlim=c(1975,2030),
     ylim=range(c(7,17),na.rm=TRUE),
     xlab="Year",
     ylab="Population (millions)",
     main="Total males")
polygon(c(fy,rev(fy)),
        c(totmpop.q[2,],rev(totmpop.q[4,])),
        col="yellow",border=FALSE)
lines(fy,totmpop.q[3,],lwd=2,col="blue")
```

```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals. The actual pyramid for 2010 is shown using dashed lines."}
par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(4.3,3.6,3.0,3.3))
plot(c(0,100),c(0,100),type="n", main="Forecast population: 2028",yaxt="n",
    xlab="Population ('000)",ylab="Age",xaxt="n",xlim=c(-1,1)*max(abs(popm.hi[,20]),abs(popf.hi[,20]))/1e3)
mtext("Male                       Female")
abline(v=0)
axis(1,at=seq(-300,0,by=50),labels=rev(seq(0,300,by=50)))
axis(1,at=seq(50,300,by=50))
axis(2,at=seq(0,100,by=10),labels=seq(0,100,by=10))
axis(4,at=seq(0,100,by=10),labels=seq(0,100,by=10))
axis(2,at=seq(0,100,by=20),labels=seq(0,100,by=20))
axis(4,at=seq(0,100,by=20),labels=seq(0,100,by=20))
axis(4,at=50,line=1.5,labels="Age",col=2,tick=FALSE)
polygon(c(-popm.lo[,20],rev(-popm.hi[,20]))/1000,c(0:100,100:0),col="yellow",border=FALSE)
polygon(c(popf.lo[,20],rev(popf.hi[,20]))/1000,c(0:100,100:0),col="yellow",border=FALSE)
lines(-pop2010$pop$male[,ncol(pop2010$pop$male)]/1000,0:100,col=1,lty=2)
lines(pop2010$pop$female[,ncol(pop2010$pop$female)]/1000,0:100,col=1,lty=2)
text(100,60,"2010")
text(-100,60,"2010")
lines(-popm.mean[,20]/1000,0:100,col="blue",lwd=2)
lines(popf.mean[,20]/1000,0:100,col="blue",lwd=2)
```

Both \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2028} show the forecast results of population.  \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2028.
\ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to 18 million by 2060. Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration. We can also observe that the further the projected year is, the bigger the forecast variation of population. This increase in variation shows that we have less relevant information for further apart prediction horizons.

Figure \ref{fig:totalpopulationin2028} shows the mean and the 80% prediction interval of simulated population paths for year 2028, along with the 2010 base population. It can be observed that overall population size is expected to increase substantially.  The uncertainty of population of infant is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates. The uncertainty of the young age population is mainly due to migration [@HB08].

```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval."}
oadp.f <- oadr(pop2010,aus.sim,current)
autoplot(oadp.f) + xlab("year") + ylab("ratio") + 
    ggtitle("Old age dependency ratio forecasts with pension age=65")
```

```{r OADRcurrent, fig.cap="Fifty-year forecasts of the old aged dependency ratio associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014). The actual OADRs for 1950-2010 are shown in black."}
oadp.f.67 <- oadr(pop2010, aus.sim, pension.age=approved)
oadp.f <- oadr(pop2010,aus.sim,pension.age=current)
oadp.f.prop <- oadr(pop2010,aus.sim,pension.age=proposed)
autoplot(oadp.f$x) +
  geom_hline(yintercept=0.21, col="gray") +
  autolayer(oadp.f, series="current", alpha=0.5) +
  autolayer(oadp.f.67, series="approved", alpha=0.5) +
  autolayer(oadp.f.prop, series="proposed", alpha=0.5) +
  ylab("ratio") + xlab("Year") +
  ggtitle("Old-age dependency ratio forecasts") +
  scale_color_manual(values=cols, name=" ",
                     breaks=c("current","approved","proposed"),
                     labels=c("Pension age at 65","Approved change","Proposed further change"))
```

Analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with approved change, gradually increasing the pension age from 65 to 67 by mid-2023. Even though the government might further increase the pension age in future, I kept the pension age at 67 from 2024 to see what would happen if no further action was taken. Figure \ref{fig:OADRat65} shows the mean forecast and prediction interval of the old aged dependency ratio with a pension age of 65, along with the historical OADR for 1920-2010. A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65. This is consistent with the prediction by inter-generation reports in 2002 [@IGR02] and in 2007 [@IGR07].  According to former Australian Treasurer @Costello04, this could be a result of better health care and low fertility rates. These two reasons could be regarded as permanent change and therefore a persistent trend. In addition, there is a big jump from actual data to predicted data. This jump is possibly a result of the Baby Boomers’ retirement. Those born in 1946, the start of the baby boom, would begin retiring in 2011 when the pension age was 65.

Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21%. It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment. However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at nearly same rate as the OADR of a pension age equal of 65. This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care. Therefore, \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term. However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered. This answer will allow us to respond to the recent proposal of further increasing pension age to 70 by 2035.

## Plausible Pension Age Schemes

```{r pension}
###find the optimal scheme of pension.age based on mean forecast
target <- oadp.f$mean[4]

pension.age <- proposed
for(i in 6:50)
{
  current <- oadr(pop2010,aus.sim,
                  pension.age=pension.age)$mean[i]
  while ((current > target) &
         (max(diff(pension.age[(i-1):50]))<=(1-1/12)))
  {
    pension.age[i:50] <- pension.age[i:50] + 1/12
    current <- oadr(pop2010,aus.sim,
                    pension.age=pension.age)$mean[i]
  }
}
oadp.f.optimal <- oadr(pop2010,
                    aus.sim,pension.age=pension.age)
```

```{r pensionupper}
###find the upper boundary of pension ages whose prediction interval contains target    
pension.age.upper <- proposed
for(i in 6:50)
{
  current.upper <- oadr(pop2010,aus.sim,
                    pension.age=pension.age.upper)$upper[i]
  while ((current.upper > target) &
         (max(diff(pension.age.upper[(i-1):50]))<=(1-1/12)))   {
    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1/12
    current.upper <- oadr(pop2010,aus.sim,
                    pension.age=pension.age.upper)$upper[i]
  }
}
oadp.f.upper<- oadr(pop2010,
                    aus.sim,pension.age=pension.age.upper)
```

```{r pensionlower}
#####find the lower boundary of pension ages whose prediction interval contains target
pension.age.lower <- proposed
for(i in 6:20)
{
  current.lower <- oadr(pop2010,aus.sim,
                    pension.age=pension.age.lower)$lower[i]
  while ((current.lower > target) &
         (max(diff(pension.age.lower[(i-1):20]))<=(1-1/12)))   {
    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1/12
    current.lower <- oadr(pop2010,aus.sim,
                  pension.age=pension.age.lower)$lower[i]
  }
}
oadp.f.lower<- oadr(pop2010, aus.sim,pension.age=pension.age.lower)
```

```{r pension forecast}
pension.fc <- structure(list(
  mean=ts(pension.age, start=2011),
  upper=pension.age.upper,
  lower=pension.age.lower,
  level=80,
  x=ts(rep(65,50),end=2010)),class='forecast')
```

Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2. It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years. \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age. Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.

```{r pensionagetables}
year <- time(oadp.f$mean)
yr <- trunc(pension.age)
mth <- trunc((pension.age - trunc(pension.age)) * 12)
agechar <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")

tab <- matrix("",nrow=5,ncol=8)
for(i in 1:4)
{
  tab[,(i-1)*2+1] <- as.character(year[(5*(i-1))+(1:5)])
  tab[,(i-1)*2+2] <- agechar[(5*(i-1))+(1:5)]
}
colnames(tab) <- rep(c("Year","Age"),4)
knitr::kable(format(tab), booktabs=TRUE, 
             caption="Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.")
```

```{r pensionagetables2}
year <- time(oadp.f$mean)
yr <- trunc(pension.age.lower)
mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
age.lo <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
yr <- trunc(pension.age.upper)
mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
age.up <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")

tab <- matrix("",nrow=5,ncol=12)
for(i in 1:4)
{
  tab[,(i-1)*3+1] <- as.character(year[(5*(i-1))+(1:5)])
  tab[,(i-1)*3+2] <- age.lo[(5*(i-1))+(1:5)]
  tab[,(i-1)*3+3] <- age.up[(5*(i-1))+(1:5)]
}
colnames(tab) <- rep(c("Year","Lo","Hi"),4)
knitr::kable(format(tab), booktabs=TRUE, 
             caption="Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months.")
```

\begin{table}
\centering
\begin{tabular}{rrrrrrrrr}
\hline
Year & 2011   & 2012     & 2013   & 2014  & 2015   & 2016   & 2017   & 2018  \\
Age  & 65Y    & 65Y      & 65Y    & 65Y   & 65Y    & 65Y7M  & 65Y10M & 66Y2M \\
\hline
Year & 2019   & 2020     & 2021   & 2022  & 2023   & 2024   & 2025   & 2026  \\
Age  & 66Y5M  & 66Y8M    & 67Y    & 67Y3M & 67Y7M  & 67Y10M & 68Y2M  & 68Y5M \\
\hline
Year & 2027   & 2028     & 2029   & 2030  & 2031   & 2032   & 2033   & 2034  \\
Age  & 68Y8M  & 69Y      & 69Y3M  & 69Y7M & 69Y10M & 70Y2M  & 70Y5M  & 70Y8M \\
\hline
Year & 2035   & 2036     & 2037   & 2038  & 2039   & 2040   & 2041   & 2042  \\
Age  & 70Y11M & 71Y2M    & 71Y3M  & 71Y6M & 71Y8M  & 71Y10M & 72Y    & 72Y2M \\
\hline
Year & 2043   & 2044     & 2045   & 2046  & 2047   & 2048   & 2049   & 2050  \\
Age  & 72Y5M  & 72Y8M    & 72Y11M & 73Y1M & 73Y3M  & 73Y5M  & 73Y7M  & 73Y8M \\
\hline
Year & 2051   & 2052     & 2053   & 2054  & 2055   & 2056   & 2057   & 2058  \\
Age  & 73Y10M & 73Y11M   & 74Y1M  & 74Y3M & 74Y5M  & 74Y7M  & 74Y9M  & 75Y   \\
\hline
Year & 2059   & 2060  \\
Age  & 75Y3M  & 75Y4M \\
\hline
\end{tabular}

\caption{Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}

\vspace{0.6cm}

\begin{tabular}{rrrrrrrrr}
\hline
Year  & 2011  & 2012      & 2013   & 2014   & 2015   & 2016   & 2017   & 2018   \\
Lower & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y5M  & 65Y8M  & 66Y11M \\
Upper & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y9M  & 66Y    & 66Y4M  \\
\hline
Year  & 2019  & 2020      & 2021   & 2022   & 2023   & 2024   & 2025   & 2026   \\
Lower & 66Y2M & 66Y5M     & 66Y8M  & 66Y11M & 67Y2M  & 67Y5M  & 67Y8M  & 67Y11M \\
Upper & 66Y8M & 67Y       & 67Y4M  & 67Y8M  & 67Y11M & 68Y4M  & 68Y7M  & 68Y11M \\
\hline
Year  & 2027  & 2028      & 2029   & 2030   & 2031   & 2032   & 2033   & 2034   \\
Lower & 68Y2M & 68Y5M     & 68Y8M  & 68Y11M & 69Y4M  & 69Y5M  & 69Y8M  & 69Y11M \\
Upper & 69Y4M & 69Y6M     & 69Y10M & 70Y2M  & 70Y6M  & 70Y9M  & 71Y1M  & 71Y4M  \\
\hline
Year  & 2035  & 2036      & 2037   & 2038   & 2039   & 2040   & 2041   & 2042   \\
Lower & 70Y1M & 70Y4M     & 70Y5M  & 70Y6M  & 70Y8M  & 70Y10M & 71Y    & 71Y4M  \\
Upper & 71Y8M & 71Y11M    & 72Y2M  & 72Y4M  & 72Y7M  & 72Y9M  & 73Y    & 73Y4M  \\
\hline
Year  & 2043  & 2044      & 2045   & 2046   & 2047   & 2048   & 2049   & 2050   \\
Lower & 71Y5M & 71Y8M     & 71Y10M & 71Y11M & 72Y    & 72Y2M  & 72Y3M  & 72Y4M  \\
Upper & 73Y5M & 73Y8M     & 74Y    & 74Y3M  & 74Y5M  & 74M8M  & 74Y10M & 75Y    \\
\hline
Year  & 2051  & 2052      & 2053   & 2054   & 2055   & 2056   & 2057   & 2058   \\
Lower & 72Y5M & 72Y7M     & 72Y8M  & 72Y10M & 73Y    & 73Y2M  & 73Y4M  & 73Y7M  \\
Upper & 75Y2M & 75Y4M     & 75Y6M  & 75Y8M  & 75Y10M & 76Y    & 76Y3M  & 76Y5M  \\
\hline
Year  & 2059  & 2060 \\
Lower & 73Y9M & 73Y11M \\
Upper & 76Y8M & 76Y10M \\
\hline
\end{tabular}

\caption{Fifth-years lower and higher boundary of pension age scheme with one boundary of 80\% OADR around desired OADR. Y denotes years and M denotes months.}
\end{table}

```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as blue shading."}
##plots of OADR with plausible pension age schemes 
autoplot(oadp.f.optimal$x) + 
  geom_hline(yintercept=oadp.f$mean[4], col='red') +
  autolayer(oadp.f.optimal) +
  ggtitle("OADR forecast estimates for optimal pension ages") + 
  xlab("year") + ylab("ratio") 
```

```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red)."}
p1 <- autoplot(oadp.f.upper$x) + 
  geom_hline(yintercept=oadp.f$mean[4], col='red') +
  #autolayer(oadp.f.upper) +
  ggtitle("OADR for upper boundary pension ages") + 
  xlab("Year") + ylab("ratio")  +
  ylim(0.07,0.27)
p2 <- autoplot(oadp.f.lower$x) + 
  geom_hline(yintercept=oadp.f$mean[4], col='red') +
  #autolayer(oadp.f.lower) +
  ggtitle("OADR for lower boundary pension ages") + 
  xlab("Year") + ylab("ratio") +
  ylim(0.07,0.27)
gridExtra::grid.arrange(p1,p2, ncol=2)
```

```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade. The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009."}
ggplot() +
  autolayer(pension.fc, series="Pension age to give OADR=0.21") +
#  geom_hline(yintercept=65, color='black') +
  autolayer(ts(c(rep(65,7),c(65.5,65.5,66.5,66.5,67,67),rep(67,37))[1:50],
  start=2013), series="Approved change") +
  autolayer(ts(c(rep(65,50)),start=1990), series="Pension age at 65") +
  xlab("Year") + ylab("Age of retirement")
```

```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade."}
```

```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014). The 80% prediction interval of the forecast of OADR is shown as shading."}
```

The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRatboundaries}. It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level. Note the negative relationship between OADR and pension age. It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged. On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.

\ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change. It was found that the target pension age increases at higher rate than the proposed new pension age scheme. Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035. Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than desired level. From this result, it is concluded that government will need to adjust  pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21%.

However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR. Therefore, it is worth performing a sensitivity test on the desired level here.
Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found. We have shown the comparison of it and its 80% confidence level with real pension age scheme in Figure \ref{ComparisonwithOADR22}. When we allow 1% more in desired OADR, the real pension age becomes plausible. Figure \ref{OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}. It confirms that OADR is stable around a level higher than current level of OADR before 2035. This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.

## Evaluating Forecast Accuracy

Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast. It is not valid to assess the model's fit in terms of historical data. We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model. Therefore, we will use a Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to evaluate the accuracy of the models used in this paper.

The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test. Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $F$ prediction horizon. Then we are allowed to repeat the test $n-F-k+1$ times, where $n$ is the number of total years of observation. The procedure is as follows:

Let $i=1$, we first select historical data for a time interval of $[i,i+1,\dots,i+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{the OADR is generated based on a pension age equal to 65 for the purpose of test}. Then, we can calculate the difference of forecasted OADR over the period $[i+k,i+k+1,\dots,i+k+H-1]$ from the real OADR for the same period, which is known as absolute error. We repeat the following steps for $i=1,2,\dots,n-k-H+1$. Then, we can summary the information into a matrix as follows:
\begin{equation}
  \text{\textbf{Absolute Error}} = [\text{AE}_{h,i}] = 
    \left[
      \begin{array}{ccc}
      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,n-k-H+1} \\
      \vdots          & \ddots       & \vdots \\
      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,n-k-H+1}
      \end{array}
    \right]
\end{equation}
where $h$ denotes for the forecast horizon and $\text{AE}_{h,i}=|OADR^{mean}_{h,i}-OADR^{real}_{h,i}|$. This process is also known as "rolling forecasting origin", because the "origin" ($k+i-1$) at which the forecast is based rolls forward in time. We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR  where $h=1,2,\dots,H$.

```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$."}
########Run a rolling forecast origin 
t <- 2010-1950+1 
H <- 25 ##forecast horizon for test
k <- 25  ##years of data required to make a forecast
oadrtest <- matrix(0,25,t-k-H)
for (i in 1:(t-k-H))
{
  ausmort.short <- extract.years(ausmort.sm, years=1949+i+(0:(k-1))) 
  ausfert.short <- extract.years(ausfert.sm, years=1949+i+(0:(k-1)))
  ausmig.short <- extract.years(ausmig.sm, years=1949+i+(0:(k-1)))
  pop.short <- extract.years(pop2010, years=1949+i+(0:k))
  mort.fit.s <- coherentfdm(ausmort.short)
  mortfs <- forecast(mort.fit.s , H)
  fert.fit.s <- fdm(ausfert.short)
  # Fix problem
#  miss <- is.na(fert.fit.s$residuals$y)
#  fert.fit.s$residuals$y[miss] <- 0
  # End fix
  fertfs <- forecast( fert.fit.s, H)
  mig.fit.s <- coherentfdm(ausmig.short)
  migfs <- forecast(mig.fit.s, H)
  aus.sim.s <- pop.sim(mortfs, fertfs, migfs, firstyearpop=pop.short, N=3)
  oadp.fs <- oadr(pop.short,aus.sim.s)
  oadrtest[,i] <- oadp.fs$mean
}
oadrtest
oadr.real<- oadr(pop2010,aus.sim)$x
oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
for(i in 1:25)
  oadr.real.mat[i,] <- oadr.real[(i+59):(59+21+i)]

oadr.error <- abs(oadrtest-oadr.real.mat)
oadrave <- apply(oadr.error,1,mean)
oadrave

plot(oadrave,xlab="forecast horizon",ylab="mean ")

```

In our sample, $n=2010-1950+1=61$ and we set $k=25$ and $H=25$ to perform the test. The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in \ref{fig:rollingtest}. From this figure, we observe that the absolute mean error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR. Overall, the mean absolute error is very small. For example, the mean absolute error for 25-step-ahead forecast is 1.5%, which is very small if compared to the desired level of OADR, which is at 21%.

It would normally be ideal to compare the mean absolute error of the forecast from my model to other available models to measure the accuracy. For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years. However, we are not able to actually perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.

# Conclusions

The ageing of population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers. The fiscal cost of the age pension is projected to sharply increase as a result. For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden on society.

In this paper, I have suggested a statistical and demographic approach to address the issue. I attempt to quantify the effects of changes in the pension age on financial burdens using an old aged dependency ratio as a measure of financial burden on Australian society. The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable old age dependency ratio around the desired level. To forecast population age structure, three demographic components of population were modelled separately using @HU07 functional time series method, with an extension of the product-ratio method [@HBY13]. Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the old age dependency ratio no greater than desired level. This approach is proposed to find target pension age scheme based on a given desired level of OADR.

I undertake the approach based on assuming the desired level of OADR is at current level of 21%. Using the historical data from 1950 to 2010, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend. It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable old aged dependency ratio at a level which can be affordable to Australians of working age. Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval. It was concluded that the pension age set by government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.

Although my results are promising, there are still grounds for further research. First, my research results are based on forecasts from one particular model. Further studies can apply the same approach but with different models of population forecasting, which allows for enhanced credibility of results. Moreover, my research addresses the issue from a purely demographic perspective. It is possible to include an economic perspective. For example, the economic implications of retaining older workers in workforce can be considered. Second, my research uses an old age dependency ratio as a single measurement of financial burden. Further research should allow the effect of other economic factors to be taken into account. For instance,
the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.

### 2017-02-03 make.R

@@ -1,0 +1,1 @@
+bookdown::render_book("PensionAge.Rmd","bookdown::pdf_document2",quiet=FALSE)

### 2017-02-03 functions-v4.R
Added external R code

@@ -1,0 +1,52 @@
+
+# Function to produce old age dependency ratio
+oadr <- function(x, sim, pension.age=65, historical.pension.age=65, level=80)
+{  
+  adjustment<-(historical.pension.age%%1)*colSums(extract.ages(x,as.integer(historical.pension.age)+1,FALSE)$pop$total,na.rm=TRUE)
+  workers <-colSums(extract.ages(x,15:as.integer(historical.pension.age),FALSE)$pop$total,na.rm=TRUE)+adjustment
+  aged <- colSums(extract.ages(x,as.integer(historical.pension.age):max(x$age),TRUE)$pop$total,na.rm=TRUE)-adjustment
+  
+  xhistory <- ts(aged/workers,s=x$year[1],f=1) 
+
+  ##ts is "time series" s is starting f is frequency
+  
+  h <- dim(sim[[1]])[2]
+  N <- dim(sim[[1]])[3]
+  if(length(pension.age)==1)
+    pension.age <- rep(pension.age, h)
+  if(length(pension.age) != h)
+    stop("length of pension.age should be equal to forecast horizon")
+  # Check that pension.age does not decrease
+  if(max(diff(pension.age)) < 0)
+    stop("Pension ages should not decrease")
+  # Check that pension.age does not increase too quickly
+  if(max(diff(pension.age)) > 1)
+    stop("Pension age should not rise more than 1 year at a time")
+  
+  simages <- as.numeric(dimnames(sim[[1]])[[1]]) # Ages vector from sim
+  # Set up matrices to store populations from each forecast horizon and each simulation
+  male.workers <- female.workers <- male.aged <- female.aged <- matrix(NA,nrow=h,ncol=N)
+  
+  for (i in (1:h))
+  {
+    worker.rows <- (simages >= 15 & simages < as.integer(pension.age[i]))
+    pension.rows <- (simages >= as.integer(pension.age[i]))
+    adjustment.male<-(pension.age[i]%%1)*sim$male[as.integer(pension.age[i]),i,]
+    adjustment.female<-(pension.age[i]%%1)*sim$female[as.integer(pension.age[i]),i,]
+    male.workers[i,] <- colSums(sim$male[worker.rows,i,])+adjustment.male
+    female.workers[i,] <- colSums(sim$female[worker.rows,i,])+adjustment.female
[…]

### 2017-02-03 PensionAge.Rmd
work on plane to Perth

@@
 ---
-title: "Forecasting the population age structure to determine the best pension age"
+title: "Forecasting the old age dependency ratio to determine the best pension age"
 author: "Rob J Hyndman, Yijun Zeng and Han Lin Shang"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache=TRUE, messages=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = FALSE, messages=FALSE, warning=FALSE)
 # Make sure you have the latest version of rmarkdown and bookdown
@@
 library(ggplot2)
-source("Rcode/functions-v4.R")
+source("functions-v4.R")
 ```
@@
 \end{equation}
-The research presented here forecasts future population age structures over the next 50 years.
+We provide forecasts of future population age structures over the next 50 years.
 We then use those projections to compute the OADR associated with pension age both before and after the adjustments.
-One major contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
+One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
 Forecasts of population structure have been built on forecasts of age and gender-specific mortality rates, fertility rates and net migration using this method.
@@
 By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
-Therefore, other main contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2)\ to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
+Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
 It should be noted that the desired level has been set at 21%, which is the estimated current level of OADR in 2014.
@@
 Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.
-Nevertheless, it should be aware that using OADR as a single measurement of financial burden might overlook some important economic factors.
-Some have suggested to use adjusted OADR that considers those important factors in analyzing pension finance [@HY12].
+Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors.
+@HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance [@HY12].
 This paper emphasizes how to undertake a better forecasting of economic burden for a given policy rather than the better choice of measurements.
@@
 
-```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE, messages=FALSE}
+```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE, cache=TRUE}
 year <- 2065-2007
@@
 
-```{r getdata}
+```{r getdata, cache=TRUE}
 ############################
@@
 
-```{r smoothing}
+```{r smoothing, cache=TRUE}
 ################################################
@@
 
-```{r models}
+```{r models, cache=TRUE}
 ################################################
@@
 
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates."}
+```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates.", cache=TRUE}
 par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
@@
 
-```{r simulation}
+```{r simulation, cache=TRUE}
 ############### SIMULATION STEP #################
@@
 ```{r totalpopulationbyyears, fig.cap="Fifth-year forecasts of total population for each sex, along with 80% prediction intervals.
-The actually population from 1950 to 2010 is shown using circles.", fig.height=4}
+The actually population from 1950 to 2010 is shown using circles.", fig.height=4, cache=TRUE}
 par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
@@
 
-```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals. The actual pyramid for 2010 is shown using dashed lines."}
+```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals. The actual pyramid for 2010 is shown using dashed lines.", cache=TRUE}
 par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(4.3,3.6,3.0,3.3))
@@
 
-```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval."}
+```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", cache=TRUE}
 oadp.f <- oadr(pop2010,aus.sim,current)
@@
 ```{r OADRcurrent, fig.cap="Fifty-year forecasts of the old aged dependency ratio associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The actual OADRs for 1950-2010 are shown in black."}
+The actual OADRs for 1950-2010 are shown in black.", cache=TRUE}
 oadp.f.67 <- oadr(pop2010, aus.sim, pension.age=approved)
@@
 
-```{r pension}
+```{r pension, cache=TRUE}
 ###find the optimal scheme of pension.age based on mean forecast
@@
 
-```{r pensionupper}
+```{r pensionupper, cache=TRUE}
 ###find the upper boundary of pension ages whose prediction interval contains target    
@@
 
-```{r pensionlower}
+```{r pensionlower, cache=TRUE}
 #####find the lower boundary of pension ages whose prediction interval contains target
@@
 
-```{r pension forecast}
+```{r pension forecast, cache=TRUE}
 pension.fc <- structure(list(
@@
 
-```{r pensionagetables}
+```{r pensionagetables, cache=TRUE}
 year <- time(oadp.f$mean)
@@
 
-```{r pensionagetables2}
+```{r pensionagetables2, cache=TRUE}
 year <- time(oadp.f$mean)
@@
 ```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as blue shading."}
+The 80% prediction interval of the forecast of OADR is shown as blue shading.", cache=TRUE}
 ##plots of OADR with plausible pension age schemes 
@@
 
-```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red)."}
+```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", cache=TRUE}
 p1 <- autoplot(oadp.f.upper$x) + 
@@
 ```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
-The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009."}
+The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", cache=TRUE}
 ggplot() +
@@
 
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade."}
+```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", cache=TRUE}
 ```
@@
 ```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading."}
+The 80% prediction interval of the forecast of OADR is shown as shading.", cache=TRUE}
 ```
@@
 
-```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$."}
+```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, cache=TRUE}
 ########Run a rolling forecast origin 
@@
 for(i in 1:25)
-  oadr.real.mat[i,] <- oadr.real[(i+59):(59+21+i)]
-
-oadr.error <- abs(oadrtest-oadr.real.mat)
+  oadr.real.mat[i,] <- oadr.real[(i+59):(59+11+i)]
+
+oadr.error <- abs(oadrtest-oadr.real.mat[,1:11])
 oadrave <- apply(oadr.error,1,mean)

### 2017-02-08 PensionAge.Rmd
Return trip from Perth

@@
 \begin{abstract}
-We forecast the old-aged dependency ratio for Australia, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level.
+We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level.
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
@@
 
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the last twenty or so years [@Fehr2008].
+Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
@@
 This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations.
-To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age\footnote{The \textit{pension age} is defined as the age at which eligible residents can access the age pension for the first time.}.
+To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
 In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010].
-In May 2014, the Federal Treasurer proposed to further increase the pension age to 70 by 2035.
+In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035.
 This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014.
-In this paper, we investigate the effect of these changes to the pension age on the forecast OADP.
+In this paper, we investigate the effect of these changes in the pension age on the forecast OADP.
 
@@
 
-In this paper, we use the old aged dependency ratio (OADR\footnote{All abbreviations have been summarized in Appendix A.}) as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
+In this paper, we use the old aged dependency ratio as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
 The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07].
@@
 We provide forecasts of future population age structures over the next 50 years.
-We then use those projections to compute the OADR associated with pension age both before and after the adjustments.
+We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments.
 One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
@@
 
-Using these predicted population paths, we can calculate the average of OADR and predict the levels of old age dependency that correspond to different pension age schemes.
+Using these predicted population paths, we can calculate the average OADR and predict the levels of old age dependency that correspond to different pension age schemes.
 By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
 Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
-It should be noted that the desired level has been set at 21%, which is the estimated current level of OADR in 2014.
-This level was chosen because, while the current financial burden on tax payers is affordable, it is approaching the limits of affordability.
-However, whether or not the current level is the most appropriate level to Australia remains to be examined and it is not the focus of this paper.
+It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2014.
+Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
 This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.
@@
 Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80% of Australians over pension age fully or partly rely on the age pension [@Power14].
+However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14].
 Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.
-Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors.
-@HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance [@HY12].
-This paper emphasizes how to undertake a better forecasting of economic burden for a given policy rather than the better choice of measurements.
-Therefore, the simple version of OADR was chosen to illustrate my approach (i.e., without adjustment).
-There is a ground to extend the approach to incorporate more complex measurement which takes into account of other important economic factors.
-
-Furthermore, choosing the right model to forecast population age structure was another important step involved in the quantification process.
-I chose to combine the Hyndman-Ullah method and product-ratio method for the forecast.
-The combination of those two methods overcomes some of shortcomings of other popular demographic forecasting methods such as the Lee-Carter method [@LC92] or the deterministic methods used by the Australian Bureau of Statistics [@ABS06; @ABS12].
-More details on forecasting methods are given in later sections.
-
-The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at current OADR-21%.
-However, it has been argued that a one-time adjustment is not sufficient to ensure a stable OADR in the long term.
-Therefore, this paper recommends consistently reviewing the pension age according to the presented statistical approach.
-This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
-This generates a stable OADR of around 21%.
-The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
+Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
+We do not consider these here.
+Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables.
 
 The remainder of this paper proceeds as follows.
-Section 2 reviews key literature on population forecasting and background works on the pension age.
-Section 3 describes the data and methods used in this study.
-Section 4 discusses the empirical results of this research, and outlines accuracy tests performed on the empirical results.
-Finally, Section 6 gives concluding remarks as well as identifies the scope for future research.
-
-# Background and Literature Review
-
-## Background on Australian Age Pension
+Section \@ref(sec:litreview) reviews key literature on population forecasting and the pension age in Australia.
+Section \@ref(sec:data) describes the data and modelling framework we use in this study.
+We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \@ref(sec:target).
+Finally, Section \@ref(sec:conclusions) gives concluding remarks as well as identifies the scope for future research.
+
+# Background and Literature Review {#sec:litreview}
+
+## The age pension in Australia
 
@@
 
-## Mathematical Preliminaries
-
-### Principal Component Analysis
-
-Principal component analysis (PCA) is the main estimation method used in population forecasting.
-It is essential for understanding the models introduced in the following sub-section.
-Therefore, a brief introduction of PCA is given here.
-
-Principal components analysis reorients multivariate data in a way that ensures that the first few dimensions (called components) summarize as much of the available information as possible [@LCG03].
-More precisely, it uses an orthogonal transformation  to convert a set of possibly correlated variables into a set of linearly uncorrelated variables called \textit{principal components}.
-It is possible to reduce the dimensions (new uncorrelated variables) if substantial redundancy is present in the data set.
-The rearrangement of data allows researchers to decide ``how many principal components to retain for subsequent analysis, trading off simplicity (i.e., a small number of dimensions is easier to manage) against completeness (i.e., a large number of dimensions captures a greater amount of available information)'' [@LCG03, p83].
-
-The mathematical derivation of PCA is explained in detail by @LCG03.
-I have summarized the main ideas here.
-In PCA, the objective is to find a linear combination of original data with maximum variance, because the aim is to derive the component (which is the new variable after linear transformation) that summarizes as much information as possible.
-Suppose we have an $m\times n$ matrix $\bm{X}$ that contains $m$ observations of $n$ variables (dimensions) with a rank of $k$.
-If we denote linear combinations by the matrix $\bm{U}=[\bm{u_1},\bm{u_2},\bm{u_3},\dots,\bm{u_k}]$ where $\bm{u_i}=(u_{1i},u_{2i},u_{3i},\dots,u_{ni})'$ and denote the matrix of principal component scores by $\bm{Z}=[\bm{z_1},\bm{z_2},\bm{z_3},\dots,\bm{z_k}]$ where $\bm{z_i}=(z_{1i},z_{2i},z_{3i},\dots,z_{mi})'$
-, then our goal is to choose $\bm{u_i}$ to maximize the variance of the elements of $\bm{z_i}=\bm{X}\bm{u_i}$, which can be written as:
-\begin{equation} 
-  var(\bm{z_i})=\frac{1}{m-1}\bm{u_i}' \bm{X}' \bm{X}\bm{u_i}.
-\end{equation}
-This maximization will ensure that first principal component $\bm{z_1}$ captures the most information (variance) in the original data and every subsequent principal component captures the most information in the remaining variance.
-However, this maximization does not have a unique solution because the magnitude of $\bm{u}$ is arbitrary, thereby making $var(\bm{z_i})$ infinity.
-To achieve the maximization, we impose a constraint of unit magnitude on the vector $\bm{u_i} ~\forall i$.
-Thus, the completed maximization problem is as follows:
-\begin{equation}
-  \text{choose~} \bm{u} \text{~to maximize~} \frac{1}{m-1}\bm{u}' \bm{X}' \bm{X}\bm{u}
-\end{equation}
-subject to the constraint $\bm{u}'\bm{u} =1$.
-
-We can solve this constrained optimization problem using the Lagrangian multiplier method (see @LCG03 for a detailed mathematical proof).
-These authors demonstrate that the solved vectors $\bm{z_i}$ and $\bm{u_i}$ are eigenvectors of the matrices $\bm{X}\bm{X}'$ and $\bm{X}'\bm{X}$ respectively, and the corresponding Lagrangian multiplier $\lambda_i$ is the eigenvalue of $\bm{X}\bm{X}'$.
-The numbers $\lambda_1,\lambda_2,\dots\lambda_k$ are singular values of $\bm{X}$ and vectors $\bm{z_1},\bm{z_2},\dots,\bm{z_k}$ and $\bm{u_1},\bm{u_2},\dots,\bm{u_k}$ are right and left singular vectors.
-Also, it can be shown that $\lambda_i$ is equal to $var(\bm{z_i})$, which  implies that variance-covariance matrix of $\bm{Z}$ (denoted by $\Sigma$) is  a diagonal matrix with $\Sigma_{ii}=\lambda_i$.
-Therefore, the vector $\bm{z}$ associated with largest $\lambda$ is the first principal component, which capture the most variance in original data.
-
-The relationship $\bm{z_i}=\bm{X}\bm{u_i}$ can be written in matrix form as follows:
-\begin{equation}
-  \bm{Z}=\bm{X}\bm{U}
-\end{equation}
-With a little algebra, we can rearrange the above equation to express $\bm{X}$ as a function of $\bm{Z}$.
-We post multiplying $\bm{U}'$ of both sides (note that we have $\bm{U}\bm{U}'=\bm{I}$ because of the mutual orthogonality of eigenvectors) and the new equation is as follows:
-\begin{equation}
-  \bm{X}=\bm{Z}\bm{U}'
-\end{equation}
-Further, we can express $\bm{X}$ as a function of standardized matrix of principal components (denoted $\bm{Z_s}$) by decomposing $\bm{Z}$ into $\bm{Z^s}\Sigma^{1/2}$. Then, the equation becomes:
-\begin{equation}
-  \bm{X}=\bm{Z^s}\Sigma^{1/2}\bm{U}'
-\end{equation}
-Alternatively, it can be expressed as:
-\begin{equation}
-  \bm{X}=\bm{z^s_1}\sqrt{\lambda_1}\bm{u_1}'+\bm{z^s_2}\sqrt{\lambda_2}\bm{u_2}'+\dots+\bm{z^s_k}\sqrt{\lambda_k}\bm{u_k}'
-\end{equation}
-This way of expressing $\bm{X}$ is known as a singular value decomposition (SVD).
-It indicates that any data matrix $\bm{X}$ can be decomposed into three simpler matrices.
-$\bm{Z^s}$ is a standardized matrix of uncorrelated variables (each with unit variance), $\Sigma^{1/2}$ is a diagonal matrix which perform a stretching transformation of $\bm{Z^s}$ and $\bm{U}'$ performs an orthogonal rotation.
-Therefore, we can use singular value decomposition to undertake a PCA.
-
-### ARIMA and ARFIMA Model
-
-ARIMA and ARIFMA are essential mathematical models that is required to understand to perform the population forecasting method. I give a brief introduction of them based on the work of @fpp.
-
-\subparagraph{AR($p$) model}
-Autoregression models forecast the dependent variable using a linear combination of its past values. An autoregression model the order of $p$ (referred as AR$(p)$ model) can be written as:
-\begin{equation}
-y_t=c+\phi_1y_{t-1}+\phi_2y_{t-2}+\dots+\phi_py_{p-1}+e_t
-\end{equation}
-where $c$ is a constant and $e_t$ is white noise.
-
-\subparagraph{MA(q) model}
-A moving average model supposes that the variable of interest can be explained by past forecast errors. It can be written as:
-\begin{equation}
-y_t=c+e_t+\theta_1e_{t-1}+\theta_2e_{t-2}+\dots+\theta_qe_{t-q}
-\end{equation}
-where $e_t$ is white noise.
-
-\subparagraph{Non-seasonal ARIMA models}  A non-seasonal ARIMA model is a combination of differencing, autoregression and moveing average models.
-ARIMA is an acronym for AutoRegressive Integrated Moving Average model.
-An ARIMA model can be written as:
-\begin{equation}
-  y_t' = c + \phi_1y_{t-1}' + \dots + \phi_py_{t-p}' + \theta_1e_{t-1} + \dots + \theta_qe_{t-q} + e_t
-\end{equation}
-where $y_t'$ is the differenced series, which is differenced $d$ times.
-This regression is referred to as an ARIMA($p,d,q$) model, where $p$ is the order of the auotoregression part; $d$ is the degree of first differencing and $q$ is the order of the moving average part.
-
-In fact, the AR($p$) and MA($q$) models are ARIMA ($p$,0,0) and ARIMA (0,0,$q$) models respectively.
-ARIMA models can be written in backshift notation (i.e.$By_t=y_{t-1}$) as follows:
-\begin{equation}
-  (1-\phi_1B-\dots-\phi_pB^p)(1-B)^dy_t=c+(1+\theta_1B+\dots+\theta_qB^q)e_t
-\end{equation}
-\subparagraph{ARFIMA model}
-We can allow $d$ in the ARIMA model to be fractional in order to capture the long-memory property of some series.
-The ARIMA model with fractional differencing (i.e., $-\frac{1}{2}<d<\frac{1}{2}$) is called the ARFIMA model.
-The range $0<d<\frac{1}{2}$ gives long-memory process [@CM09].
-
-\subparagraph{Akaike's Information Criterion}
-
-AIC is a model-selection procedure which is useful to determine the order of an ARIMA model.
-It can be written as:
-\begin{equation}
-  AIC=-2log(L)+2(p+q+k+1)
-\end{equation}
-where $L$ is the likelihood of the data, $k=1$ if $c\neq0$ and $k=0$ if $c=0$.
-
-For ARIMA models, the corrected AIC [@fpp] can be written as
-\begin{equation}
-  AIC_c=\frac{AIC+2(p+q+k+1)(p+q+k+2)}{T-p-q-k-2}
-\end{equation}
-where the correction is to reduce small sample bias.
-The ARIMA model with minimum AIC or minimum $AIC_c$ is the optimal model. I prefer to use $AIC_c$ to reduce sample bias in this research.
-
-## Literature Review on Population forecasting methods
+## Population forecasting
 
@@
 
-# Data and Methodology
-
-## Data
+# Data {#sec:data}
 
@@
 
-## Methodology
-
-### Forecasting Population Age Structure and OADR
+## Forecasting Population Age Structure and OADR {#sec:forecasting}
 
@@
 
-\subparagraph{Step 1}The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
+###Step 1 {-}
+
+The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
 The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
@@
 
-\subparagraph{Step 2} After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
+### Step 2 {-}
+
+After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
 The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
@@
 
-\subparagraph{Step 3} Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time.
+### Step 3 {-}
+
+Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time.
 To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations.
@@
 
-### Finding the Target Pension Age Scheme
-
-The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level.
-According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
-Suppose we denote pension age schemes over the prediction horizon by $\bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}]$.
-The OADR function of pension age over the prediction horizon is denoted as $OADR_h(PA_{n+h})$ for $h=1,2,3,\dots,H$.
-There is a negative relationship between pension age and OADR.
-The negative relationship implies that the higher the pension age, the lower the OADR.
-Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level.
-Several practical issues need to be considered to achieve this goal.
-First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR.
-Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
-Therefore, the target pension age scheme $\bm{PA}^{target}$ can be defined in the following way:
-for $h=1,2,\dots,H$
-\begin{equation}
-\text{minimise~} PA_{n+h}  \text{~such that~} OADR_h(PA_{n+h})\leq OADR^{desired}
-\end{equation}
-\begin{align*}
-\text{subject to the constraint~} 0\leq PA_{n+h}-PA_{n+h-1}\leq 1
-\end{align*}
-In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
-It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
-The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in 2017 onward.}, which is:
-\begin{align*}
-  \bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}] = [65,65,\dots,65]
-\end{align*}
-We take the following algorithm:
-For $h=1,2,\dots,H$,
-we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
-\begin{align}
- OADR^{mean}_h(PA_{n+h})> OADR^{desired} \text{~or~} PA_{n+h}-PA_{n+h-1}\geq 1
-\end{align}
-where $OADR^{mean}_h(PA_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $PA_{n+h}$.
-
-In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
-To be more specific, ``plausible'', means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
-Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
-Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as 80% confidence interval of pension age scheme where we are 80% sure that there will be a desired outcome.
-In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.
-
-The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR in equation (28) is replaced by the boundary of the 80% prediction interval.
-Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.
-
-# Empirical Results
-
-## Forecast in Population Age Structure and OADR
+## Results
 
@@
 
-## Plausible Pension Age Schemes
-
-```{r pension, cache=TRUE}
-###find the optimal scheme of pension.age based on mean forecast
-target <- oadp.f$mean[4]
-
-pension.age <- proposed
-for(i in 6:50)
-{
-  current <- oadr(pop2010,aus.sim,
-                  pension.age=pension.age)$mean[i]
-  while ((current > target) &
-         (max(diff(pension.age[(i-1):50]))<=(1-1/12)))
-  {
-    pension.age[i:50] <- pension.age[i:50] + 1/12
-    current <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age)$mean[i]
-  }
-}
-oadp.f.optimal <- oadr(pop2010,
-                    aus.sim,pension.age=pension.age)
-```
-
-```{r pensionupper, cache=TRUE}
-###find the upper boundary of pension ages whose prediction interval contains target    
-pension.age.upper <- proposed
-for(i in 6:50)
-{
-  current.upper <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.upper)$upper[i]
-  while ((current.upper > target) &
-         (max(diff(pension.age.upper[(i-1):50]))<=(1-1/12)))   {
-    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1/12
-    current.upper <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.upper)$upper[i]
-  }
-}
-oadp.f.upper<- oadr(pop2010,
-                    aus.sim,pension.age=pension.age.upper)
-```
-
-```{r pensionlower, cache=TRUE}
-#####find the lower boundary of pension ages whose prediction interval contains target
-pension.age.lower <- proposed
-for(i in 6:20)
-{
-  current.lower <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.lower)$lower[i]
-  while ((current.lower > target) &
-         (max(diff(pension.age.lower[(i-1):20]))<=(1-1/12)))   {
-    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1/12
-    current.lower <- oadr(pop2010,aus.sim,
-                  pension.age=pension.age.lower)$lower[i]
-  }
-}
-oadp.f.lower<- oadr(pop2010, aus.sim,pension.age=pension.age.lower)
-```
-
-```{r pension forecast, cache=TRUE}
-pension.fc <- structure(list(
-  mean=ts(pension.age, start=2011),
-  upper=pension.age.upper,
-  lower=pension.age.lower,
-  level=80,
-  x=ts(rep(65,50),end=2010)),class='forecast')
-```
-
-Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
-It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years.
-\ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
-
-```{r pensionagetables, cache=TRUE}
-year <- time(oadp.f$mean)
-yr <- trunc(pension.age)
-mth <- trunc((pension.age - trunc(pension.age)) * 12)
-agechar <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
-
-tab <- matrix("",nrow=5,ncol=8)
-for(i in 1:4)
-{
-  tab[,(i-1)*2+1] <- as.character(year[(5*(i-1))+(1:5)])
-  tab[,(i-1)*2+2] <- agechar[(5*(i-1))+(1:5)]
-}
-colnames(tab) <- rep(c("Year","Age"),4)
-knitr::kable(format(tab), booktabs=TRUE, 
-             caption="Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.")
-```
-
-```{r pensionagetables2, cache=TRUE}
-year <- time(oadp.f$mean)
-yr <- trunc(pension.age.lower)
-mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
-age.lo <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
-yr <- trunc(pension.age.upper)
-mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
-age.up <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
-
-tab <- matrix("",nrow=5,ncol=12)
-for(i in 1:4)
-{
-  tab[,(i-1)*3+1] <- as.character(year[(5*(i-1))+(1:5)])
-  tab[,(i-1)*3+2] <- age.lo[(5*(i-1))+(1:5)]
-  tab[,(i-1)*3+3] <- age.up[(5*(i-1))+(1:5)]
-}
-colnames(tab) <- rep(c("Year","Lo","Hi"),4)
-knitr::kable(format(tab), booktabs=TRUE, 
-             caption="Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months.")
-```
-
-\begin{table}
-\centering
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year & 2011   & 2012     & 2013   & 2014  & 2015   & 2016   & 2017   & 2018  \\
-Age  & 65Y    & 65Y      & 65Y    & 65Y   & 65Y    & 65Y7M  & 65Y10M & 66Y2M \\
-\hline
-Year & 2019   & 2020     & 2021   & 2022  & 2023   & 2024   & 2025   & 2026  \\
-Age  & 66Y5M  & 66Y8M    & 67Y    & 67Y3M & 67Y7M  & 67Y10M & 68Y2M  & 68Y5M \\
-\hline
-Year & 2027   & 2028     & 2029   & 2030  & 2031   & 2032   & 2033   & 2034  \\
-Age  & 68Y8M  & 69Y      & 69Y3M  & 69Y7M & 69Y10M & 70Y2M  & 70Y5M  & 70Y8M \\
-\hline
-Year & 2035   & 2036     & 2037   & 2038  & 2039   & 2040   & 2041   & 2042  \\
-Age  & 70Y11M & 71Y2M    & 71Y3M  & 71Y6M & 71Y8M  & 71Y10M & 72Y    & 72Y2M \\
-\hline
-Year & 2043   & 2044     & 2045   & 2046  & 2047   & 2048   & 2049   & 2050  \\
-Age  & 72Y5M  & 72Y8M    & 72Y11M & 73Y1M & 73Y3M  & 73Y5M  & 73Y7M  & 73Y8M \\
-\hline
-Year & 2051   & 2052     & 2053   & 2054  & 2055   & 2056   & 2057   & 2058  \\
-Age  & 73Y10M & 73Y11M   & 74Y1M  & 74Y3M & 74Y5M  & 74Y7M  & 74Y9M  & 75Y   \\
-\hline
-Year & 2059   & 2060  \\
-Age  & 75Y3M  & 75Y4M \\
-\hline
-\end{tabular}
-
-\caption{Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}
-
-\vspace{0.6cm}
-
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year  & 2011  & 2012      & 2013   & 2014   & 2015   & 2016   & 2017   & 2018   \\
-Lower & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y5M  & 65Y8M  & 66Y11M \\
-Upper & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y9M  & 66Y    & 66Y4M  \\
-\hline
-Year  & 2019  & 2020      & 2021   & 2022   & 2023   & 2024   & 2025   & 2026   \\
-Lower & 66Y2M & 66Y5M     & 66Y8M  & 66Y11M & 67Y2M  & 67Y5M  & 67Y8M  & 67Y11M \\
-Upper & 66Y8M & 67Y       & 67Y4M  & 67Y8M  & 67Y11M & 68Y4M  & 68Y7M  & 68Y11M \\
-\hline
-Year  & 2027  & 2028      & 2029   & 2030   & 2031   & 2032   & 2033   & 2034   \\
-Lower & 68Y2M & 68Y5M     & 68Y8M  & 68Y11M & 69Y4M  & 69Y5M  & 69Y8M  & 69Y11M \\
-Upper & 69Y4M & 69Y6M     & 69Y10M & 70Y2M  & 70Y6M  & 70Y9M  & 71Y1M  & 71Y4M  \\
-\hline
-Year  & 2035  & 2036      & 2037   & 2038   & 2039   & 2040   & 2041   & 2042   \\
-Lower & 70Y1M & 70Y4M     & 70Y5M  & 70Y6M  & 70Y8M  & 70Y10M & 71Y    & 71Y4M  \\
-Upper & 71Y8M & 71Y11M    & 72Y2M  & 72Y4M  & 72Y7M  & 72Y9M  & 73Y    & 73Y4M  \\
-\hline
-Year  & 2043  & 2044      & 2045   & 2046   & 2047   & 2048   & 2049   & 2050   \\
-Lower & 71Y5M & 71Y8M     & 71Y10M & 71Y11M & 72Y    & 72Y2M  & 72Y3M  & 72Y4M  \\
-Upper & 73Y5M & 73Y8M     & 74Y    & 74Y3M  & 74Y5M  & 74M8M  & 74Y10M & 75Y    \\
-\hline
-Year  & 2051  & 2052      & 2053   & 2054   & 2055   & 2056   & 2057   & 2058   \\
-Lower & 72Y5M & 72Y7M     & 72Y8M  & 72Y10M & 73Y    & 73Y2M  & 73Y4M  & 73Y7M  \\
-Upper & 75Y2M & 75Y4M     & 75Y6M  & 75Y8M  & 75Y10M & 76Y    & 76Y3M  & 76Y5M  \\
-\hline
-Year  & 2059  & 2060 \\
-Lower & 73Y9M & 73Y11M \\
-Upper & 76Y8M & 76Y10M \\
-\hline
-\end{tabular}
-
-\caption{Fifth-years lower and higher boundary of pension age scheme with one boundary of 80\% OADR around desired OADR. Y denotes years and M denotes months.}
-\end{table}
-
-```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as blue shading.", cache=TRUE}
-##plots of OADR with plausible pension age schemes 
-autoplot(oadp.f.optimal$x) + 
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
-  autolayer(oadp.f.optimal) +
-  ggtitle("OADR forecast estimates for optimal pension ages") + 
-  xlab("year") + ylab("ratio") 
-```
-
-```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", cache=TRUE}
-p1 <- autoplot(oadp.f.upper$x) + 
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
-  #autolayer(oadp.f.upper) +
-  ggtitle("OADR for upper boundary pension ages") + 
-  xlab("Year") + ylab("ratio")  +
-  ylim(0.07,0.27)
-p2 <- autoplot(oadp.f.lower$x) + 
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
-  #autolayer(oadp.f.lower) +
-  ggtitle("OADR for lower boundary pension ages") + 
-  xlab("Year") + ylab("ratio") +
-  ylim(0.07,0.27)
-gridExtra::grid.arrange(p1,p2, ncol=2)
-```
-
-```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
-The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", cache=TRUE}
-ggplot() +
-  autolayer(pension.fc, series="Pension age to give OADR=0.21") +
-#  geom_hline(yintercept=65, color='black') +
-  autolayer(ts(c(rep(65,7),c(65.5,65.5,66.5,66.5,67,67),rep(67,37))[1:50],
-  start=2013), series="Approved change") +
-  autolayer(ts(c(rep(65,50)),start=1990), series="Pension age at 65") +
-  xlab("Year") + ylab("Age of retirement")
-```
-
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", cache=TRUE}
-```
-
-```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading.", cache=TRUE}
-```
-
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRatboundaries}.
-It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
-Note the negative relationship between OADR and pension age.
-It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
-On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
-
-\ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
-It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
-Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
-Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than desired level.
-From this result, it is concluded that government will need to adjust  pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21%.
-
-However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
-Therefore, it is worth performing a sensitivity test on the desired level here.
-Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it and its 80% confidence level with real pension age scheme in Figure \ref{ComparisonwithOADR22}.
-When we allow 1% more in desired OADR, the real pension age becomes plausible.
-Figure \ref{OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
-It confirms that OADR is stable around a level higher than current level of OADR before 2035.
-This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
-
-## Evaluating Forecast Accuracy
+## Evaluating Forecast Accuracy {#sec:accuracy}
 
@@
 
-# Conclusions
+# Finding the Target Pension Age Scheme {#sec:target}
+
+The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level.
+According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
+Suppose we denote pension age schemes over the prediction horizon by $\bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}]$.
+The OADR function of pension age over the prediction horizon is denoted as $OADR_h(PA_{n+h})$ for $h=1,2,3,\dots,H$.
+There is a negative relationship between pension age and OADR.
+The negative relationship implies that the higher the pension age, the lower the OADR.
+Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level.
+Several practical issues need to be considered to achieve this goal.
+First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR.
+Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
+Therefore, the target pension age scheme $\bm{PA}^{target}$ can be defined in the following way:
+for $h=1,2,\dots,H$
+\begin{equation}
+\text{minimise~} PA_{n+h}  \text{~such that~} OADR_h(PA_{n+h})\leq OADR^{desired}
+\end{equation}
+\begin{align*}
+\text{subject to the constraint~} 0\leq PA_{n+h}-PA_{n+h-1}\leq 1
+\end{align*}
+In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
+It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
+The same pension age for males and females was set to simplify the calculations.
+This simplification is reasonable because the pension age will be same in 2017 onward.}, which is:
+\begin{align*}
+  \bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}] = [65,65,\dots,65]
+\end{align*}
+We take the following algorithm:
+For $h=1,2,\dots,H$,
+we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
+\begin{align}
+ OADR^{mean}_h(PA_{n+h})> OADR^{desired} \text{~or~} PA_{n+h}-PA_{n+h-1}\geq 1
+\end{align}
+where $OADR^{mean}_h(PA_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $PA_{n+h}$.
+
+In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
+To be more specific, ``plausible'', means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
+Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
+Hence, any pension age scheme within those two boundaries is plausible.
+The range of plausible pension age schemes can be thought of as 80% confidence interval of pension age scheme where we are 80% sure that there will be a desired outcome.
+In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.
+
+The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR in equation (28) is replaced by the boundary of the 80% prediction interval.
+Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.
+
+## Plausible Pension Age Schemes
+
+```{r pension, cache=TRUE}
+###find the optimal scheme of pension.age based on mean forecast
+target <- oadp.f$mean[4]
+
+pension.age <- proposed
+for(i in 6:50)
+{
+  current <- oadr(pop2010,aus.sim,
+                  pension.age=pension.age)$mean[i]
+  while ((current > target) &
+         (max(diff(pension.age[(i-1):50]))<=(1-1/12)))
+  {
+    pension.age[i:50] <- pension.age[i:50] + 1/12
+    current <- oadr(pop2010,aus.sim,
+                    pension.age=pension.age)$mean[i]
+  }
+}
+oadp.f.optimal <- oadr(pop2010,
+                    aus.sim,pension.age=pension.age)
+```
+
+```{r pensionupper, cache=TRUE}
+###find the upper boundary of pension ages whose prediction interval contains target    
+pension.age.upper <- proposed
+for(i in 6:50)
+{
+  current.upper <- oadr(pop2010,aus.sim,
+                    pension.age=pension.age.upper)$upper[i]
+  while ((current.upper > target) &
+         (max(diff(pension.age.upper[(i-1):50]))<=(1-1/12)))   {
+    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1/12
+    current.upper <- oadr(pop2010,aus.sim,
+                    pension.age=pension.age.upper)$upper[i]
+  }
+}
+oadp.f.upper<- oadr(pop2010,
+                    aus.sim,pension.age=pension.age.upper)
+```
+
+```{r pensionlower, cache=TRUE}
+#####find the lower boundary of pension ages whose prediction interval contains target
+pension.age.lower <- proposed
+for(i in 6:20)
+{
+  current.lower <- oadr(pop2010,aus.sim,
+                    pension.age=pension.age.lower)$lower[i]
+  while ((current.lower > target) &
+         (max(diff(pension.age.lower[(i-1):20]))<=(1-1/12)))   {
+    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1/12
+    current.lower <- oadr(pop2010,aus.sim,
+                  pension.age=pension.age.lower)$lower[i]
+  }
+}
+oadp.f.lower<- oadr(pop2010, aus.sim,pension.age=pension.age.lower)
+```
+
+```{r pension forecast, cache=TRUE}
+pension.fc <- structure(list(
+  mean=ts(pension.age, start=2011),
+  upper=pension.age.upper,
+  lower=pension.age.lower,
+  level=80,
+  x=ts(rep(65,50),end=2010)),class='forecast')
+```
+
+Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
+It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years.
+\ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
+Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
+
+```{r pensionagetables, cache=TRUE}
+year <- time(oadp.f$mean)
+yr <- trunc(pension.age)
+mth <- trunc((pension.age - trunc(pension.age)) * 12)
+agechar <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
+
+tab <- matrix("",nrow=5,ncol=8)
+for(i in 1:4)
+{
+  tab[,(i-1)*2+1] <- as.character(year[(5*(i-1))+(1:5)])
+  tab[,(i-1)*2+2] <- agechar[(5*(i-1))+(1:5)]
+}
+colnames(tab) <- rep(c("Year","Age"),4)
+knitr::kable(format(tab), booktabs=TRUE, 
+             caption="Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.")
+```
+
+```{r pensionagetables2, cache=TRUE}
+year <- time(oadp.f$mean)
+yr <- trunc(pension.age.lower)
+mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
+age.lo <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
+yr <- trunc(pension.age.upper)
+mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
+age.up <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
+
+tab <- matrix("",nrow=5,ncol=12)
+for(i in 1:4)
+{
+  tab[,(i-1)*3+1] <- as.character(year[(5*(i-1))+(1:5)])
+  tab[,(i-1)*3+2] <- age.lo[(5*(i-1))+(1:5)]
+  tab[,(i-1)*3+3] <- age.up[(5*(i-1))+(1:5)]
+}
+colnames(tab) <- rep(c("Year","Lo","Hi"),4)
+knitr::kable(format(tab), booktabs=TRUE, 
+             caption="Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months.")
+```
+
+\begin{table}
+\centering
+\begin{tabular}{rrrrrrrrr}
+\hline
+Year & 2011   & 2012     & 2013   & 2014  & 2015   & 2016   & 2017   & 2018  \\
+Age  & 65Y    & 65Y      & 65Y    & 65Y   & 65Y    & 65Y7M  & 65Y10M & 66Y2M \\
+\hline
+Year & 2019   & 2020     & 2021   & 2022  & 2023   & 2024   & 2025   & 2026  \\
+Age  & 66Y5M  & 66Y8M    & 67Y    & 67Y3M & 67Y7M  & 67Y10M & 68Y2M  & 68Y5M \\
+\hline
+Year & 2027   & 2028     & 2029   & 2030  & 2031   & 2032   & 2033   & 2034  \\
+Age  & 68Y8M  & 69Y      & 69Y3M  & 69Y7M & 69Y10M & 70Y2M  & 70Y5M  & 70Y8M \\
+\hline
+Year & 2035   & 2036     & 2037   & 2038  & 2039   & 2040   & 2041   & 2042  \\
+Age  & 70Y11M & 71Y2M    & 71Y3M  & 71Y6M & 71Y8M  & 71Y10M & 72Y    & 72Y2M \\
+\hline
+Year & 2043   & 2044     & 2045   & 2046  & 2047   & 2048   & 2049   & 2050  \\
+Age  & 72Y5M  & 72Y8M    & 72Y11M & 73Y1M & 73Y3M  & 73Y5M  & 73Y7M  & 73Y8M \\
+\hline
+Year & 2051   & 2052     & 2053   & 2054  & 2055   & 2056   & 2057   & 2058  \\
+Age  & 73Y10M & 73Y11M   & 74Y1M  & 74Y3M & 74Y5M  & 74Y7M  & 74Y9M  & 75Y   \\
+\hline
+Year & 2059   & 2060  \\
+Age  & 75Y3M  & 75Y4M \\
+\hline
+\end{tabular}
+
+\caption{Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}
+
+\vspace{0.6cm}
+
+\begin{tabular}{rrrrrrrrr}
+\hline
+Year  & 2011  & 2012      & 2013   & 2014   & 2015   & 2016   & 2017   & 2018   \\
+Lower & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y5M  & 65Y8M  & 66Y11M \\
+Upper & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y9M  & 66Y    & 66Y4M  \\
+\hline
+Year  & 2019  & 2020      & 2021   & 2022   & 2023   & 2024   & 2025   & 2026   \\
+Lower & 66Y2M & 66Y5M     & 66Y8M  & 66Y11M & 67Y2M  & 67Y5M  & 67Y8M  & 67Y11M \\
+Upper & 66Y8M & 67Y       & 67Y4M  & 67Y8M  & 67Y11M & 68Y4M  & 68Y7M  & 68Y11M \\
+\hline
+Year  & 2027  & 2028      & 2029   & 2030   & 2031   & 2032   & 2033   & 2034   \\
+Lower & 68Y2M & 68Y5M     & 68Y8M  & 68Y11M & 69Y4M  & 69Y5M  & 69Y8M  & 69Y11M \\
+Upper & 69Y4M & 69Y6M     & 69Y10M & 70Y2M  & 70Y6M  & 70Y9M  & 71Y1M  & 71Y4M  \\
+\hline
+Year  & 2035  & 2036      & 2037   & 2038   & 2039   & 2040   & 2041   & 2042   \\
+Lower & 70Y1M & 70Y4M     & 70Y5M  & 70Y6M  & 70Y8M  & 70Y10M & 71Y    & 71Y4M  \\
+Upper & 71Y8M & 71Y11M    & 72Y2M  & 72Y4M  & 72Y7M  & 72Y9M  & 73Y    & 73Y4M  \\
+\hline
+Year  & 2043  & 2044      & 2045   & 2046   & 2047   & 2048   & 2049   & 2050   \\
+Lower & 71Y5M & 71Y8M     & 71Y10M & 71Y11M & 72Y    & 72Y2M  & 72Y3M  & 72Y4M  \\
+Upper & 73Y5M & 73Y8M     & 74Y    & 74Y3M  & 74Y5M  & 74M8M  & 74Y10M & 75Y    \\
+\hline
+Year  & 2051  & 2052      & 2053   & 2054   & 2055   & 2056   & 2057   & 2058   \\
+Lower & 72Y5M & 72Y7M     & 72Y8M  & 72Y10M & 73Y    & 73Y2M  & 73Y4M  & 73Y7M  \\
+Upper & 75Y2M & 75Y4M     & 75Y6M  & 75Y8M  & 75Y10M & 76Y    & 76Y3M  & 76Y5M  \\
+\hline
+Year  & 2059  & 2060 \\
+Lower & 73Y9M & 73Y11M \\
+Upper & 76Y8M & 76Y10M \\
+\hline
+\end{tabular}
+
+\caption{Fifth-years lower and higher boundary of pension age scheme with one boundary of 80\% OADR around desired OADR. Y denotes years and M denotes months.}
+\end{table}
+
+```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
+The 80% prediction interval of the forecast of OADR is shown as blue shading.", cache=TRUE}
+##plots of OADR with plausible pension age schemes 
+autoplot(oadp.f.optimal$x) + 
+  geom_hline(yintercept=oadp.f$mean[4], col='red') +
+  autolayer(oadp.f.optimal) +
+  ggtitle("OADR forecast estimates for optimal pension ages") + 
+  xlab("year") + ylab("ratio") 
+```
+
+```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", cache=TRUE}
+p1 <- autoplot(oadp.f.upper$x) + 
+  geom_hline(yintercept=oadp.f$mean[4], col='red') +
+  #autolayer(oadp.f.upper) +
+  ggtitle("OADR for upper boundary pension ages") + 
+  xlab("Year") + ylab("ratio")  +
+  ylim(0.07,0.27)
+p2 <- autoplot(oadp.f.lower$x) + 
+  geom_hline(yintercept=oadp.f$mean[4], col='red') +
+  #autolayer(oadp.f.lower) +
+  ggtitle("OADR for lower boundary pension ages") + 
+  xlab("Year") + ylab("ratio") +
+  ylim(0.07,0.27)
+gridExtra::grid.arrange(p1,p2, ncol=2)
+```
+
+```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
+The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", cache=TRUE}
+ggplot() +
+  autolayer(pension.fc, series="Pension age to give OADR=0.21") +
+#  geom_hline(yintercept=65, color='black') +
+  autolayer(ts(c(rep(65,7),c(65.5,65.5,66.5,66.5,67,67),rep(67,37))[1:50],
+  start=2013), series="Approved change") +
+  autolayer(ts(c(rep(65,50)),start=1990), series="Pension age at 65") +
+  xlab("Year") + ylab("Age of retirement")
+```
+
+```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", cache=TRUE}
+```
+
+```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
+The 80% prediction interval of the forecast of OADR is shown as shading.", cache=TRUE}
+```
+
+The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRatboundaries}.
+It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
+Note the negative relationship between OADR and pension age.
+It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
+On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
+
+\ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
+It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
+Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
+Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than desired level.
+From this result, it is concluded that government will need to adjust  pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21%.
+
+However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
+Therefore, it is worth performing a sensitivity test on the desired level here.
+Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
+We have shown the comparison of it and its 80% confidence level with real pension age scheme in Figure \ref{ComparisonwithOADR22}.
+When we allow 1% more in desired OADR, the real pension age becomes plausible.
+Figure \ref{OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+It confirms that OADR is stable around a level higher than current level of OADR before 2035.
+This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
+
+# Conclusions {#sec:conclusions}
 
@@
 It was concluded that the pension age set by government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.
+
+The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at 21%.
+However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
+T
+
+herefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
+This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval.
+The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
+This generates a stable OADR of around 21%.
+The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
 

### 2019-01-04 PensionAge.Rmd
Converted to monashebstemplates

@@
 title: "Forecasting the old age dependency ratio to determine the best pension age"
-author: "Rob J Hyndman, Yijun Zeng and Han Lin Shang"
-date: "`r format(Sys.time(), '%-d %B %Y')`"
-fontsize: 11pt
-papersize: a4
-fontfamily: kpfonts
+author:
+- familyname: Hyndman
+  othernames: Rob J
+  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
+  email: Rob.Hyndman@monash.edu
+  correspondingauthor: true
+- familyname: Zeng
+  othernames: Yijun
+  address: Monash University
+- familyname: Shang
+  othernames: Hanlin
+  address: Australian National University
+abstract: "We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level.
+Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%.
+This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
+keywords: "blah, blah"
+wpnumber: no/yr
+jelcodes: C10,C14,C22
+blind: false
+cover: true
+toc: false
 bibliography: pensionage.bib
 biblio-style: authoryear-comp
-subparagraph: true
-toc: false
 output:
-  bookdown::pdf_document2:
+  MonashEBSTemplates::workingpaper:
     fig_caption: yes
@@
     fig_width: 8
-    includes:
-      in_header: preamble.tex
     keep_tex: yes
@@
     citation_package: biblatex
+    includes:
+      in_header: preamble.tex
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages=FALSE, warning=FALSE)
+knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
 # Make sure you have the latest version of rmarkdown and bookdown
-#devtools::install_github("rstudio/rmarkdown")
-#devtools::install_github("rstudio/bookdown")
+# devtools::install_github("rstudio/rmarkdown")
+# devtools::install_github("rstudio/bookdown")
+# And the latest versions of my packages
+# devtools::install_github("robjhyndman/forecast")
+# devtools::install_github("robjhyndman/demography")
+# devtools::install_github("robjhyndman/addb")
 library(demography)
@@
 
-\begin{abstract}
-We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%.
-
-This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
-\end{abstract}
-
-\begin{keywords}
-?????
-\end{keywords}
-
-\newpage
-
-#Introduction
-
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].
+# Introduction
+
+Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
@@
 \begin{equation}
-  OADR=\frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100%
+  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
 \end{equation}
@@
 
-```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE, cache=TRUE}
-year <- 2065-2007
-proposed <- ts(pmin(70,
-         c(rep(65,2017-2008), 65 + cumsum(rep(c(0.5,0),55))))[1:50],
-         start=2008)
-approved <- pmin(proposed,67)
-current <- pmin(proposed,65)
-cols <- c(current='#1b9e77',approved='#d95f02',proposed='#7570b3')
+```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
+year <- 2065 - 2007
+proposed <- ts(pmin(
+  70,
+  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
+)[1:50],
+start = 2008
+)
+approved <- pmin(proposed, 67)
+current <- pmin(proposed, 65)
+cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
 ggplot() +
-  autolayer(proposed, series='proposed') +
-  autolayer(approved, series='approved') +
-  autolayer(current, series='current') +
+  forecast::autolayer(proposed, series = "proposed") +
+  forecast::autolayer(approved, series = "approved") +
+  forecast::autolayer(current, series = "current") +
   xlab("Year") + ylab("Age of retirement") +
-  scale_color_manual(values=cols, name=" ",
-                     breaks=c("current","approved","proposed"),
-                     labels=c("Pension age at 65","Approved change","Proposed further change"))
+  scale_color_manual(
+    values = cols, name = " ",
+    breaks = c("current", "approved", "proposed"),
+    labels = c("Pension age at 65", "Approved change", "Proposed further change")
+  )
 ```
@@
 There is a practical issue as to how to link life expectancy with pension ages given that there is no information on future mortality rates [@PC13].
-@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50% of any increase in life expectancy''.
-However, using a ‘rule of thumb’ approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
+@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that "pension age should increase by approximately 50% of any increase in life expectancy".
+However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
 My study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
@@
 The Australian Bureau of Statistics formulates assumptions on the basis of demographic trends, in conjunction with advice from individual experts or government departments.
-The projections are not predictions or forecasts, ``but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period'' [@ABS12, p.2].
+The projections are not predictions or forecasts, "but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period" [@ABS12, p.2].
 In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
@@
 \begin{align}
-y_t(x)&=s_t(x)+\sigma_t(x)\epsilon_{t,x}\\
-s_t(x)&=\mu(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)
+  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\\
+  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)
 \end{align}
@@
 \begin{equation}
-s_t(x)-\mu(x)=\phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
+  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
 \end{equation}
@@
 
-In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\ $ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
-\begin{equation}
-\hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x)=E[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}]=\hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
+In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
+\begin{equation}
+  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \E[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
 \end{equation}
@@
 Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process.
-For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an $ARIMA(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
+For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
 The fitted process as follows:
 \begin{equation}
-(1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2..,J
+  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2,\dots,J,
 \end{equation}
@@
 \begin{align*}
-m_t(x)&=\frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-f_t(x)&=B_t(x)/E^F_t(x)=\text{age-specific fertility rates in calendar year t}
+  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
+  f_t(x) & = B_t(x)/E^F_t(x)=\text{age-specific fertility rates in calendar year t}
 \end{align*}
@@
 
-###Step 1 {-}
+### Step 1 {-}
 
@@
 \begin{align*}
-m_{n+h\mid n,M}(x)&=p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
-m_{n+h\mid n,F}(x)&=p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
+  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
+  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
 \end{align*}
@@
 \begin{equation}
-\bm{p}_{n+1}=[p_{mi}]=
-\left[
-\begin{array}{ccc}
+  \bm{p}_{n+1}=[p_{mi}] =
+    \begin{bmatrix}
        p_{1,1} & \cdots\cdots & p_{1,1000} \\
@@
       p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
-\end{array}
-\right]
+      \end{bmatrix}.
 \end{equation}
@@
 \begin{equation}
-\left[
-\begin{array}{ccc}
+  \begin{bmatrix}
     p_{15,1} & \cdots\cdots & p_{15,1000} \\
@@
     p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
-\end{array}
-\right]
+  \end{bmatrix}.
 \end{equation}
@@
 \begin{equation}
-\bm{p}^{work}_{n+1}=[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]
+  \bm{p}^{work}_{n+1} = [\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]
 \end{equation}
@@
 \begin{align*}
-\bm{p}^{work}_{n+1}&=[p^{work}_{n+1,1},p^{work}_{n+1,2},\dots,p^{work}_{n+1,1000}]\\
-&=[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]+0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]   \\
-\bm{p}^{aged}_{n+1}&=[p^{aged}_{n+1,1},p^{aged}_{n+1,2},\dots,p^{aged}_{n+1,1000}]\\
-&=[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]-0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
+  \bm{p}^{work}_{n+1}
+    & = [p^{work}_{n+1,1},p^{work}_{n+1,2},\dots,p^{work}_{n+1,1000}]\\
+    & = [\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]+0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]   \\
+  \bm{p}^{aged}_{n+1}
+    & = [p^{aged}_{n+1,1},p^{aged}_{n+1,2},\dots,p^{aged}_{n+1,1000}]\\
+    & = [\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]-0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
 \end{align*}
@@
 \begin{align*}
-\bm{OADR}_{n+1}&=[OADR_{n+1,1},OADR_{n+1,2},\dots,OADR_{n+1,1000}]\\
-&=\left[\frac{p^{work}_{n+1,1}}{p^{aged}_{n+1,1}},\dots,\frac{p^{work}_{n+1,1000}}{p^{aged}_{n+1,1000}}\right]
+  \bm{OADR}_{n+1} & = [OADR_{n+1,1},OADR_{n+1,2},\dots,OADR_{n+1,1000}]\\
+                  & = \left[\frac{p^{work}_{n+1,1}}{p^{aged}_{n+1,1}},\dots,\frac{p^{work}_{n+1,1000}}{p^{aged}_{n+1,1000}}\right]
 \end{align*}
@@
 \begin{equation}
-\bm{OADR}^{forecast}=[OADR_{h,i}]=
-\left[
-\begin{array}{ccc}
+  \bm{OADR}^{forecast}=[OADR_{h,i}] =
+  \begin{bmatrix}
     OADR_{n+1,1} & \cdots\cdots & OADR_{n+50,1000} \\
@@
     OADR_{n+50,1} & \cdots\cdots &OADR_{n+50,1000}
-\end{array}
-\right]
+  \end{bmatrix}.
 \end{equation}
@@
 
-```{r getdata, cache=TRUE}
+```{r getdata, include=FALSE}
 ############################
@@
 
-# Get population data for 1 Jan 2010
-# Store data locally ????????????
-#pop2010 <- hmd.pop("AUS",username,password,"Australia")
-#pop2010 <- extract.ages(pop2010, age=0:100)
+# HMD credentials
+username <- "rob.hyndman@buseco.monash.edu.au"
+password <- "Q234.,mnb"
+
+# Get population data for 1 Jan 2015
+auspop <- hmd.pop("AUS", username, password, "Australia")
+auspop <- extract.ages(auspop, age = 0:100)
 
 # Get mortality data
-# Store data locally ????????????
-#aus.mort <- hmd.mx("AUS",username,password,"Australia")
-#aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
-#                    combine.upper=FALSE), 
-#                    year=1950:max(aus.mort$year))
-
-##### FERTILITY
+aus.mort <- hmd.mx("AUS", username, password, "Australia")
+aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
+  combine.upper = FALSE
+),
+year = 1950:max(aus.mort$year)
+)
 
@@
 # Need to install addb package from http://robjhyndman.com/software/addb/
-#library(addb) # Contains fertility data for 1921-2006
-#aus.fert <- aus.fertility
-
-# Update fertility data to 2009
-# Store data locally ?????????
-#ausfertility <- read.csv("http://robjhyndman.com/data/ausfertility.csv",header=TRUE,colClasses="numeric")
-#aus.fert$rate$female <- as.matrix(cbind(aus.fert$rate$female[,30:54], ausfertility[,2:36]))
-#aus.fert$pop$female <- cbind(aus.fert$pop$female[,30:86], aus.mort$pop$female[16:50,58:60])
-#colnames(aus.fert$rate$female) <- colnames(aus.fert$pop$female) <- aus.fert$year <- 1950:2009
-#rm(ausfertility)
+library(addb) # Contains fertility data for 1921-2006
+aus.fert <- aus.fertility
+births <- aus.fert$rate$female * aus.fert$pop$female
+# Update fertility data to 2015
+ausf <- read.csv("FERTILITY_AGE_STATE_16062017173020984.csv",
+  header = TRUE,
+  stringsAsFactors = FALSE
+)
+# National births only
+ausf <- ausf[ausf$Region == "Australia", ]
+# Remove age aggregations
+ausf <- ausf[ausf$Age %in% paste(15:49), ]
+ausf[, "Age"] <- as.numeric(ausf[, "Age"])
+# Extract births and population values
+newbirths <- matrix(ausf[ausf$Measure == "Births", "Value"],
+  nrow = nrow(births), byrow = TRUE
+) * 1000
+newpop <- matrix(ausf[ausf$Measure == "Female population", "Value"],
+  nrow = nrow(births), byrow = TRUE
+) * 1000
+rownames(newbirths) <- rownames(newpop) <- 15:49
+colnames(newbirths) <- colnames(newpop) <- 2004:2015
+births <- cbind(births[, 1:83], newbirths)
+fpop <- cbind(aus.fert$pop$female[, 1:83], newpop / 1000)
+# Use populations in ausf rather than auspop to get the same rates
+aus.fert$rate$female <- births / fpop
+aus.fert$pop$female <- fpop
+aus.fert$year <- 1921:2015
 
 ##### MIGRATION
-
-#aus.mig <- netmigration(aus.mort, aus.fert, mfratio = 1.05)
-
-#save(pop2010,aus.mort,aus.fert,aus.mig,file='ausdata.rda')
-load("ausdata.rda")
-```
-
-```{r smoothing, cache=TRUE}
+aus.mig <- netmigration(aus.mort, aus.fert, startyearpop = auspop, mfratio = 1.05)
+```
+
+```{r smoothing, dependson='getdata'}
 ################################################
@@
 
-ausmort.sm <- smooth.demogdata(aus.mort, obs.var="theoretical")
-ausfert.sm <- smooth.demogdata(aus.fert, obs.var="theoretical")
+ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
+ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
 ausmig.sm <- smooth.demogdata(aus.mig)
@@
 
-```{r models, cache=TRUE}
+```{r models, dependson='smoothing'}
 ################################################
@@
 mort.fit <- coherentfdm(ausmort.sm)
-mortf <- forecast(mort.fit, h=50)
+mortf <- forecast(mort.fit, h = 50)
 
@@
 fert.fit <- fdm(ausfert.sm)
-fertf <- forecast(fert.fit, h=50)
+fertf <- forecast(fert.fit, h = 50)
 
@@
 mig.fit <- coherentfdm(ausmig.sm)
-migf <- forecast(mig.fit, h=50)
+migf <- forecast(mig.fit, h = 50)
 ```
@@
 
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates.", cache=TRUE}
-par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
-plot(fertf, 'c', comp=2)
+```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates.", dependson='models'}
+par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
+plot(fertf, "c", comp = 2)
 ```
@@
 
-```{r simulation, cache=TRUE}
+```{r simulation, dependson='models'}
 ############### SIMULATION STEP #################
 # This takes a while!
-#aus.sim <- pop.sim(mortf, fertf, migf, firstyearpop=pop2010, N=2000)
-#save(aus.sim,file='aussim.rda')
-load("aussim.rda")
-
+set.seed(2019-01-04)
+nsim <- 20 # Change to 2000 or higher to get better estimates
+aus.sim <- pop.sim(mortf, fertf, migf, firstyearpop = auspop, N = nsim)
+```
+
+```{r simulationresults}
 ## Means and intervals
-popm.mean <- apply(aus.sim$male,c(1,2),mean)
-popm.lo <- apply(aus.sim$male,c(1,2),quantile,p=.1)
-popm.hi <- apply(aus.sim$male,c(1,2),quantile,p=.9)
-popf.mean <- apply(aus.sim$female,c(1,2),mean)
-popf.lo <- apply(aus.sim$female,c(1,2),quantile,p=.1)
-popf.hi <- apply(aus.sim$female,c(1,2),quantile,p=.9)
+popm.mean <- apply(aus.sim$male, c(1, 2), mean, na.rm = TRUE)
+popm.lo <- apply(aus.sim$male, c(1, 2), quantile, p = .1, na.rm = TRUE)
+popm.hi <- apply(aus.sim$male, c(1, 2), quantile, p = .9, na.rm = TRUE)
+popf.mean <- apply(aus.sim$female, c(1, 2), mean, na.rm = TRUE)
+popf.lo <- apply(aus.sim$female, c(1, 2), quantile, p = .1, na.rm = TRUE)
+popf.hi <- apply(aus.sim$female, c(1, 2), quantile, p = .9, na.rm = TRUE)
 
 ## TOTAL POPULATION COMPARISONS
-totfpop <- apply(aus.sim$female,c(2,3),sum)
-totmpop <- apply(aus.sim$male,c(2,3),sum)
-totfpop.q <- apply(totfpop,1,quantile,p=c(0.025,.1,.5,.9,.975),na.rm=TRUE)/1e6
-totmpop.q <- apply(totmpop,1,quantile,p=c(0.025,.1,.5,.9,.975),na.rm=TRUE)/1e6
+totfpop <- apply(aus.sim$female, c(2, 3), sum, na.rm = TRUE)
+totmpop <- apply(aus.sim$male, c(2, 3), sum, na.rm = TRUE)
+totfpop.q <- apply(totfpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
+totmpop.q <- apply(totmpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
 ```
@@
 ```{r totalpopulationbyyears, fig.cap="Fifth-year forecasts of total population for each sex, along with 80% prediction intervals.
-The actually population from 1950 to 2010 is shown using circles.", fig.height=4, cache=TRUE}
-par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(3.3,3.6,1.1,1.1))
-par(mfrow=c(1,2))
-fy <- 2012+(1:50)
-plot(1921:2012, colSums(pop2010$pop$female)/1e6,
-     xlim=c(1975,2030),
-     ylim=range(c(7,17),na.rm=TRUE),
-     xlab="Year",
-     ylab="Population (millions)",
-     main="Total females")
-polygon(c(fy,rev(fy)),
-        c(totfpop.q[2,],rev(totfpop.q[4,])),
-        col="yellow",border=FALSE)
-lines(fy,totfpop.q[3,],lwd=2,col="blue")
-
-plot(1921:2012, colSums(pop2010$pop$male)/1e6,
-     xlim=c(1975,2030),
-     ylim=range(c(7,17),na.rm=TRUE),
-     xlab="Year",
-     ylab="Population (millions)",
-     main="Total males")
-polygon(c(fy,rev(fy)),
-        c(totmpop.q[2,],rev(totmpop.q[4,])),
-        col="yellow",border=FALSE)
-lines(fy,totmpop.q[3,],lwd=2,col="blue")
-```
-
-```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals. The actual pyramid for 2010 is shown using dashed lines.", cache=TRUE}
-par(mgp=c(2.2,0.45,0), tcl=-0.4, mar=c(4.3,3.6,3.0,3.3))
-plot(c(0,100),c(0,100),type="n", main="Forecast population: 2028",yaxt="n",
-    xlab="Population ('000)",ylab="Age",xaxt="n",xlim=c(-1,1)*max(abs(popm.hi[,20]),abs(popf.hi[,20]))/1e3)
+The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
+par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
+par(mfrow = c(1, 2))
+fy <- fertf$year
+plot(auspop$year, colSums(auspop$pop$female) / 1e6,
+  xlim = c(1975, 2030),
+  ylim = range(c(7, 17), na.rm = TRUE),
+  xlab = "Year",
+  ylab = "Population (millions)",
+  main = "Total females"
+)
+polygon(c(fy, rev(fy)),
+  c(totfpop.q[2, ], rev(totfpop.q[4, ])),
+  col = "yellow", border = FALSE
+)
+lines(fy, totfpop.q[3, ], lwd = 2, col = "blue")
+
+plot(auspop$year, colSums(auspop$pop$male) / 1e6,
+  xlim = c(1975, 2030),
+  ylim = range(c(7, 17), na.rm = TRUE),
+  xlab = "Year",
+  ylab = "Population (millions)",
+  main = "Total males"
+)
+polygon(c(fy, rev(fy)),
+  c(totmpop.q[2, ], rev(totmpop.q[4, ])),
+  col = "yellow", border = FALSE
+)
+lines(fy, totmpop.q[3, ], lwd = 2, col = "blue")
+```
+
+```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals.
+The actual pyramid for 2010 is shown using dashed lines.", , dependson='simulationresults'}
+par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(4.3, 3.6, 3.0, 3.3))
+plot(c(0, 100), c(0, 100),
+  type = "n", main = "Forecast population: 2028", yaxt = "n",
+  xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
+)
 mtext("Male                       Female")
-abline(v=0)
-axis(1,at=seq(-300,0,by=50),labels=rev(seq(0,300,by=50)))
-axis(1,at=seq(50,300,by=50))
-axis(2,at=seq(0,100,by=10),labels=seq(0,100,by=10))
-axis(4,at=seq(0,100,by=10),labels=seq(0,100,by=10))
-axis(2,at=seq(0,100,by=20),labels=seq(0,100,by=20))
-axis(4,at=seq(0,100,by=20),labels=seq(0,100,by=20))
-axis(4,at=50,line=1.5,labels="Age",col=2,tick=FALSE)
-polygon(c(-popm.lo[,20],rev(-popm.hi[,20]))/1000,c(0:100,100:0),col="yellow",border=FALSE)
-polygon(c(popf.lo[,20],rev(popf.hi[,20]))/1000,c(0:100,100:0),col="yellow",border=FALSE)
-lines(-pop2010$pop$male[,ncol(pop2010$pop$male)]/1000,0:100,col=1,lty=2)
-lines(pop2010$pop$female[,ncol(pop2010$pop$female)]/1000,0:100,col=1,lty=2)
-text(100,60,"2010")
-text(-100,60,"2010")
-lines(-popm.mean[,20]/1000,0:100,col="blue",lwd=2)
-lines(popf.mean[,20]/1000,0:100,col="blue",lwd=2)
+abline(v = 0)
+axis(1, at = seq(-300, 0, by = 50), labels = rev(seq(0, 300, by = 50)))
+axis(1, at = seq(50, 300, by = 50))
+axis(2, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
+axis(4, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
+axis(2, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
+axis(4, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
+axis(4, at = 50, line = 1.5, labels = "Age", col = 2, tick = FALSE)
+polygon(c(-popm.lo[, 20], rev(-popm.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
+polygon(c(popf.lo[, 20], rev(popf.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
+lines(-auspop$pop$male[, ncol(auspop$pop$male)] / 1000, 0:100, col = 1, lty = 2)
+lines(auspop$pop$female[, ncol(auspop$pop$female)] / 1000, 0:100, col = 1, lty = 2)
+text(100, 60, "2010")
+text(-100, 60, "2010")
+lines(-popm.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
+lines(popf.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
 ```
@@
 
-```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", cache=TRUE}
-oadp.f <- oadr(pop2010,aus.sim,current)
+```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", dependson='simulationresults'}
+oadp.f <- oadr(auspop, aus.sim, pension.age = current)
 autoplot(oadp.f) + xlab("year") + ylab("ratio") +
@@
 ```{r OADRcurrent, fig.cap="Fifty-year forecasts of the old aged dependency ratio associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The actual OADRs for 1950-2010 are shown in black.", cache=TRUE}
-oadp.f.67 <- oadr(pop2010, aus.sim, pension.age=approved)
-oadp.f <- oadr(pop2010,aus.sim,pension.age=current)
-oadp.f.prop <- oadr(pop2010,aus.sim,pension.age=proposed)
+The actual OADRs for 1950-2010 are shown in black.", dependson='OADRat65'}
+oadp.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
+oadp.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
 autoplot(oadp.f$x) +
-  geom_hline(yintercept=0.21, col="gray") +
-  autolayer(oadp.f, series="current", alpha=0.5) +
-  autolayer(oadp.f.67, series="approved", alpha=0.5) +
-  autolayer(oadp.f.prop, series="proposed", alpha=0.5) +
+  geom_hline(yintercept = 0.21, col = "gray") +
+  autolayer(oadp.f, series = "current", alpha = 0.5) +
+  autolayer(oadp.f.67, series = "approved", alpha = 0.5) +
+  autolayer(oadp.f.prop, series = "proposed", alpha = 0.5) +
   ylab("ratio") + xlab("Year") +
   ggtitle("Old-age dependency ratio forecasts") +
-  scale_color_manual(values=cols, name=" ",
-                     breaks=c("current","approved","proposed"),
-                     labels=c("Pension age at 65","Approved change","Proposed further change"))
+  scale_color_manual(
+    values = cols, name = " ",
+    breaks = c("current", "approved", "proposed"),
+    labels = c("Pension age at 65", "Approved change", "Proposed further change")
+  )
 ```
@@
   \text{\textbf{Absolute Error}} = [\text{AE}_{h,i}] =
-    \left[
-      \begin{array}{ccc}
+    \begin{bmatrix}
       \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,n-k-H+1} \\
@@
       \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,n-k-H+1}
-      \end{array}
-    \right]
+    \end{bmatrix}
 \end{equation}
@@
 
-```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, cache=TRUE}
-########Run a rolling forecast origin 
-t <- 2010-1950+1 
-H <- 25 ##forecast horizon for test
-k <- 25  ##years of data required to make a forecast
-oadrtest <- matrix(0,25,t-k-H)
-for (i in 1:(t-k-H))
+```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
+######## Run a rolling forecast origin
+t <- 2010 - 1950 + 1
+H <- 25 ## forecast horizon for test
+k <- 25 ## years of data required to make a forecast
+oadrtest <- matrix(0, 25, t - k - H)
+for (i in 1:(t - k - H))
 {
-  ausmort.short <- extract.years(ausmort.sm, years=1949+i+(0:(k-1))) 
-  ausfert.short <- extract.years(ausfert.sm, years=1949+i+(0:(k-1)))
-  ausmig.short <- extract.years(ausmig.sm, years=1949+i+(0:(k-1)))
-  pop.short <- extract.years(pop2010, years=1949+i+(0:k))
+  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
+  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
+  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
+  pop.short <- extract.years(auspop, years = 1949 + i + (0:k))
   mort.fit.s <- coherentfdm(ausmort.short)
-  mortfs <- forecast(mort.fit.s , H)
+  mortfs <- forecast(mort.fit.s, H)
   fert.fit.s <- fdm(ausfert.short)
@@
   # End fix
-  fertfs <- forecast( fert.fit.s, H)
+  fertfs <- forecast(fert.fit.s, H)
   mig.fit.s <- coherentfdm(ausmig.short)
   migfs <- forecast(mig.fit.s, H)
-  aus.sim.s <- pop.sim(mortfs, fertfs, migfs, firstyearpop=pop.short, N=3)
-  oadp.fs <- oadr(pop.short,aus.sim.s)
-  oadrtest[,i] <- oadp.fs$mean
+  aus.sim.s <- pop.sim(mortfs, fertfs, migfs, firstyearpop = pop.short, N = 3)
+  oadp.fs <- oadr(pop.short, aus.sim.s)
+  oadrtest[, i] <- oadp.fs$mean
 }
 oadrtest
-oadr.real<- oadr(pop2010,aus.sim)$x
+oadr.real <- oadr(auspop, aus.sim)$x
 oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
-for(i in 1:25)
-  oadr.real.mat[i,] <- oadr.real[(i+59):(59+11+i)]
-
-oadr.error <- abs(oadrtest-oadr.real.mat[,1:11])
-oadrave <- apply(oadr.error,1,mean)
+for (i in 1:25)
+  oadr.real.mat[i, ] <- oadr.real[(i + 59):(59 + 11 + i)]
+
+oadr.error <- abs(oadrtest - oadr.real.mat[, 1:11])
+oadrave <- apply(oadr.error, 1, mean)
 oadrave
 
-plot(oadrave,xlab="forecast horizon",ylab="mean ")
-
+plot(oadrave, xlab = "forecast horizon", ylab = "mean ")
 ```
@@
 We take the following algorithm:
-For $h=1,2,\dots,H$,
-we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
+For $h=1,2,\dots,H$, we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
 \begin{align}
@@
 In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
-To be more specific, ``plausible'', means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
+To be more specific, "plausible", means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
 Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
@@
 
-```{r pension, cache=TRUE}
-###find the optimal scheme of pension.age based on mean forecast
+```{r pension, dependson="OADRat65"}
+### find the optimal scheme of pension.age based on mean forecast
 target <- oadp.f$mean[4]
@@
 pension.age <- proposed
-for(i in 6:50)
+for (i in 6:50)
 {
-  current <- oadr(pop2010,aus.sim,
-                  pension.age=pension.age)$mean[i]
+  current <- oadr(auspop, aus.sim,
+    pension.age = pension.age
+  )$mean[i]
   while ((current > target) &
-         (max(diff(pension.age[(i-1):50]))<=(1-1/12)))
-  {
-    pension.age[i:50] <- pension.age[i:50] + 1/12
-    current <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age)$mean[i]
+    (max(diff(pension.age[(i - 1):50])) <= (1 - 1 / 12))) {
+    pension.age[i:50] <- pension.age[i:50] + 1 / 12
+    current <- oadr(auspop, aus.sim,
+      pension.age = pension.age
+    )$mean[i]
   }
 }
-oadp.f.optimal <- oadr(pop2010,
-                    aus.sim,pension.age=pension.age)
-```
-
-```{r pensionupper, cache=TRUE}
-###find the upper boundary of pension ages whose prediction interval contains target    
+oadp.f.optimal <- oadr(auspop,
+  aus.sim,
+  pension.age = pension.age
+)
+```
+
+```{r pensionupper, dependson="simulationresults"}
+### find the upper boundary of pension ages whose prediction interval contains target
 pension.age.upper <- proposed
-for(i in 6:50)
+for (i in 6:50)
 {
-  current.upper <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.upper)$upper[i]
+  current.upper <- oadr(auspop, aus.sim,
+    pension.age = pension.age.upper
+  )$upper[i]
   while ((current.upper > target) &
-         (max(diff(pension.age.upper[(i-1):50]))<=(1-1/12)))   {
-    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1/12
-    current.upper <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.upper)$upper[i]
+    (max(diff(pension.age.upper[(i - 1):50])) <= (1 - 1 / 12))) {
+    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1 / 12
+    current.upper <- oadr(auspop, aus.sim,
+      pension.age = pension.age.upper
+    )$upper[i]
   }
 }
-oadp.f.upper<- oadr(pop2010,
-                    aus.sim,pension.age=pension.age.upper)
-```
-
-```{r pensionlower, cache=TRUE}
-#####find the lower boundary of pension ages whose prediction interval contains target
+oadp.f.upper <- oadr(auspop,
+  aus.sim,
+  pension.age = pension.age.upper
+)
+```
+
+```{r pensionlower, dependson="simulationresults"}
+##### find the lower boundary of pension ages whose prediction interval contains target
 pension.age.lower <- proposed
-for(i in 6:20)
+for (i in 6:20)
 {
-  current.lower <- oadr(pop2010,aus.sim,
-                    pension.age=pension.age.lower)$lower[i]
+  current.lower <- oadr(auspop, aus.sim,
+    pension.age = pension.age.lower
+  )$lower[i]
   while ((current.lower > target) &
-         (max(diff(pension.age.lower[(i-1):20]))<=(1-1/12)))   {
-    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1/12
-    current.lower <- oadr(pop2010,aus.sim,
-                  pension.age=pension.age.lower)$lower[i]
+    (max(diff(pension.age.lower[(i - 1):20])) <= (1 - 1 / 12))) {
+    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1 / 12
+    current.lower <- oadr(auspop, aus.sim,
+      pension.age = pension.age.lower
+    )$lower[i]
   }
 }
-oadp.f.lower<- oadr(pop2010, aus.sim,pension.age=pension.age.lower)
-```
-
-```{r pension forecast, cache=TRUE}
+oadp.f.lower <- oadr(auspop, aus.sim, pension.age = pension.age.lower)
+```
+
+```{r pension forecast, dependson="simulationresults"}
 pension.fc <- structure(list(
-  mean=ts(pension.age, start=2011),
-  upper=pension.age.upper,
-  lower=pension.age.lower,
-  level=80,
-  x=ts(rep(65,50),end=2010)),class='forecast')
+  mean = ts(pension.age, start = 2011),
+  upper = pension.age.upper,
+  lower = pension.age.lower,
+  level = 80,
+  x = ts(rep(65, 50), end = 2010)
+), class = "forecast")
 ```
@@
 
-```{r pensionagetables, cache=TRUE}
+```{r pensionagetables, dependson="OADRat65"}
 year <- time(oadp.f$mean)
@@
 mth <- trunc((pension.age - trunc(pension.age)) * 12)
-agechar <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
-
-tab <- matrix("",nrow=5,ncol=8)
-for(i in 1:4)
+agechar <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
+
+tab <- matrix("", nrow = 5, ncol = 8)
+for (i in 1:4)
 {
-  tab[,(i-1)*2+1] <- as.character(year[(5*(i-1))+(1:5)])
-  tab[,(i-1)*2+2] <- agechar[(5*(i-1))+(1:5)]
+  tab[, (i - 1) * 2 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
+  tab[, (i - 1) * 2 + 2] <- agechar[(5 * (i - 1)) + (1:5)]
 }
-colnames(tab) <- rep(c("Year","Age"),4)
-knitr::kable(format(tab), booktabs=TRUE, 
-             caption="Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.")
-```
-
-```{r pensionagetables2, cache=TRUE}
+colnames(tab) <- rep(c("Year", "Age"), 4)
+knitr::kable(format(tab),
+  booktabs = TRUE,
+  caption = "Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months."
+)
+```
+
+```{r pensionagetables2, dependson="OADRat65"}
 year <- time(oadp.f$mean)
@@
 mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
-age.lo <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
+age.lo <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
 yr <- trunc(pension.age.upper)
 mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
-age.up <- paste(yr,"Y",ifelse(mth>0,paste("+",mth,"M",sep=""),""),sep="")
-
-tab <- matrix("",nrow=5,ncol=12)
-for(i in 1:4)
+age.up <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
+
+tab <- matrix("", nrow = 5, ncol = 12)
+for (i in 1:4)
 {
-  tab[,(i-1)*3+1] <- as.character(year[(5*(i-1))+(1:5)])
-  tab[,(i-1)*3+2] <- age.lo[(5*(i-1))+(1:5)]
-  tab[,(i-1)*3+3] <- age.up[(5*(i-1))+(1:5)]
+  tab[, (i - 1) * 3 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
+  tab[, (i - 1) * 3 + 2] <- age.lo[(5 * (i - 1)) + (1:5)]
+  tab[, (i - 1) * 3 + 3] <- age.up[(5 * (i - 1)) + (1:5)]
 }
-colnames(tab) <- rep(c("Year","Lo","Hi"),4)
-knitr::kable(format(tab), booktabs=TRUE, 
-             caption="Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months.")
+colnames(tab) <- rep(c("Year", "Lo", "Hi"), 4)
+knitr::kable(format(tab),
+  booktabs = TRUE,
+  caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
+)
 ```
@@
 ```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as blue shading.", cache=TRUE}
-##plots of OADR with plausible pension age schemes 
+The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
+## plots of OADR with plausible pension age schemes
 autoplot(oadp.f.optimal$x) +
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
+  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
   autolayer(oadp.f.optimal) +
@@
 
-```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", cache=TRUE}
+```{r OADRboundaries, fig.cap="The  80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
 p1 <- autoplot(oadp.f.upper$x) +
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
-  #autolayer(oadp.f.upper) +
+  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
+  # autolayer(oadp.f.upper) +
   ggtitle("OADR for upper boundary pension ages") +
   xlab("Year") + ylab("ratio") +
-  ylim(0.07,0.27)
+  ylim(0.07, 0.27)
 p2 <- autoplot(oadp.f.lower$x) +
-  geom_hline(yintercept=oadp.f$mean[4], col='red') +
-  #autolayer(oadp.f.lower) +
+  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
+  # autolayer(oadp.f.lower) +
   ggtitle("OADR for lower boundary pension ages") +
   xlab("Year") + ylab("ratio") +
-  ylim(0.07,0.27)
-gridExtra::grid.arrange(p1,p2, ncol=2)
+  ylim(0.07, 0.27)
+gridExtra::grid.arrange(p1, p2, ncol = 2)
 ```
@@
 ```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
-The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", cache=TRUE}
+The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
 ggplot() +
-  autolayer(pension.fc, series="Pension age to give OADR=0.21") +
+  autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
   #  geom_hline(yintercept=65, color='black') +
-  autolayer(ts(c(rep(65,7),c(65.5,65.5,66.5,66.5,67,67),rep(67,37))[1:50],
-  start=2013), series="Approved change") +
-  autolayer(ts(c(rep(65,50)),start=1990), series="Pension age at 65") +
+  autolayer(ts(c(rep(65, 7), c(65.5, 65.5, 66.5, 66.5, 67, 67), rep(67, 37))[1:50],
+    start = 2013
+  ), series = "Approved change") +
+  autolayer(ts(c(rep(65, 50)), start = 1990), series = "Pension age at 65") +
   xlab("Year") + ylab("Age of retirement")
@@
 
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", cache=TRUE}
+```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}
 ```
@@
 ```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading.", cache=TRUE}
+The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRat65"}
 ```
@@
 Therefore, it is worth performing a sensitivity test on the desired level here.
+
 Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
@@
 Further research should allow the effect of other economic factors to be taken into account.
-For instance,
-the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.
+For instance, the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.

### 2019-01-04 make.R

@@ -1,1 +1,0 @@
-bookdown::render_book("PensionAge.Rmd","bookdown::pdf_document2",quiet=FALSE)

### 2019-01-05 PensionAge.Rmd
MBSportrait.pdf

@@
 - familyname: Shang
-  othernames: Hanlin
+  othernames: Han Lin
   address: Australian National University
@@
 This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "blah, blah"
+keywords: "functional time series model, coherent forecasts, demographic components, pension and insurance"
 wpnumber: no/yr
@@
 They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
-This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR03].
+This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR02].
 
@@
 \begin{equation}
-  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \E[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
+  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \text{E}[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
 \end{equation}
@@
 \begin{align*}
-  log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
+  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
 \end{align*}
@@
 \begin{equation}
-  \bm{p}^{work}_{n+1} = [\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]
+  \bm{p}^{work}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]
 \end{equation}
@@
 \begin{equation}
-  \bm{p}^{aged}_{n+1}=[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]
+  \bm{p}^{aged}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]
 \end{equation}
@@
 # HMD credentials
-username <- "rob.hyndman@buseco.monash.edu.au"
-password <- "Q234.,mnb"
+username <- "shl8858@telstra.com"
+password <- "hshang85"
+
+hmd.pop <- function (country, username, password, label = country) 
+{
+    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
+        "Population.txt", sep = "")
+    userpwd <- paste(username, ":", password, sep = "")
+    txt <- RCurl::getURL(path, userpwd = userpwd)
+    con <- textConnection(txt)
+    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
+        na.strings = "."), TRUE)
+    close(con)
+    if (class(pop) == "try-error") 
+        stop("Population file not found at www.mortality.org")
+    obj <- list(type = "population", label = label, lambda = 0)
+    obj$year = sort(unique(pop[, 1]))
+    n <- length(obj$year)
+    m <- length(unique(pop[, 2]))
+    obj$age <- pop[1:m, 2]
+    mnames <- names(pop)[-c(1, 2)]
+    n.pop <- length(mnames)
+    obj$pop <- list()
+    for (i in 1:n.pop) {
+        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
+        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
+        dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
+    }
+    names(obj$pop) <- tolower(mnames)
+    obj$age <- as.numeric(as.character(obj$age))
+    if (is.na(obj$age[m])) 
+        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
+    return(structure(obj, class = "demogdata"))
+}
+
+hmd.mx <- function (country, username, password, label = country) 
+{
+    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
+        "Mx_1x1.txt", sep = "")
+    userpwd <- paste(username, ":", password, sep = "")
+    txt <- RCurl::getURL(path, userpwd = userpwd)
+    con <- textConnection(txt)
+    mx <- try(utils::read.table(con, skip = 2, header = TRUE, 
+        na.strings = "."), TRUE)
+    close(con)
+    if (class(mx) == "try-error") 
+        stop("Connection error at www.mortality.org. Please check username, password and country label.")
+    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
+        "Exposures_1x1.txt", sep = "")
+    userpwd <- paste(username, ":", password, sep = "")
+    txt <- RCurl::getURL(path, userpwd = userpwd)
+    con <- textConnection(txt)
+    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
+        na.strings = "."), TRUE)
+    close(con)
+    if (class(pop) == "try-error") 
+        stop("Exposures file not found at www.mortality.org")
+    obj <- list(type = "mortality", label = label, lambda = 0)
+    obj$year <- sort(unique(mx[, 1]))
+    n <- length(obj$year)
+    m <- length(unique(mx[, 2]))
+    obj$age <- mx[1:m, 2]
+    mnames <- names(mx)[-c(1, 2)]
+    n.mort <- length(mnames)
+    obj$rate <- obj$pop <- list()
+    for (i in 1:n.mort) {
+        obj$rate[[i]] <- matrix(mx[, i + 2], nrow = m, ncol = n)
+        obj$rate[[i]][obj$rate[[i]] < 0] <- NA
+        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
+        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
+        dimnames(obj$rate[[i]]) <- dimnames(obj$pop[[i]]) <- list(obj$age, 
+            obj$year)
+    }
+    names(obj$pop) = names(obj$rate) <- tolower(mnames)
+    obj$age <- as.numeric(as.character(obj$age))
+    if (is.na(obj$age[m])) 
+        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
+    return(structure(obj, class = "demogdata"))
+}
 
 # Get population data for 1 Jan 2015
-auspop <- hmd.pop("AUS", username, password, "Australia")
+auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
 auspop <- extract.ages(auspop, age = 0:100)
@@
 
+aus.fert_v0 = extract.years(aus.fert, 1921:2014)
+
 ##### MIGRATION
-aus.mig <- netmigration(aus.mort, aus.fert, startyearpop = auspop, mfratio = 1.05)
+aus.mig <- netmigration(mort = aus.mort, fert = aus.fert_v0, mfratio = 1.05)
 ```
@@
 ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
-ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
+ausfert.sm <- smooth.demogdata(aus.fert_v0, obs.var = "theoretical")
 ausmig.sm <- smooth.demogdata(aus.mig)
@@
 nsim <- 20 # Change to 2000 or higher to get better estimates
-aus.sim <- pop.sim(mortf, fertf, migf, firstyearpop = auspop, N = nsim)
+aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
 ```
@@
   migfs <- forecast(mig.fit.s, H)
-  aus.sim.s <- pop.sim(mortfs, fertfs, migfs, firstyearpop = pop.short, N = 3)
+  aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs, firstyearpop = pop.short, 
+                       N = 3)
   oadp.fs <- oadr(pop.short, aus.sim.s)

### 2019-01-06 PensionAge.Rmd
PensionAge.pdf

@@
 ---
-title: "Forecasting the old age dependency ratio to determine the best pension age"
+title: "Forecasting the old-age dependency ratio to determine the best pension age"
 author:
@@
   address: Australian National University
-abstract: "We forecast the old-aged dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old aged dependency ratio at a specified level.
+abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old aged dependency ratio at the current level, which is 21%.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the current level, which is 21%.
 This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
@@
 # devtools::install_github("rstudio/bookdown")
-# And the latest versions of my packages
+# And the latest versions of Our packages
 # devtools::install_github("robjhyndman/forecast")
@@
 Similar demographic challenges face many other countries.
-One way of measuring this problem is via the old-age dependency ratio (OADP): the number of people post-retirement to the number of people of working age [@Walker1982].
-The OADP has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
+One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age [@Walker1982].
+The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
 
@@
 This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014.
-In this paper, we investigate the effect of these changes in the pension age on the forecast OADP.
+In this paper, we investigate the effect of these changes in the pension age on the forecast OADR.
 
@@
 
-In this paper, we use the old aged dependency ratio as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
+In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
 The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07].
@@
 One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
-Forecasts of population structure have been built on forecasts of age and gender-specific mortality rates, fertility rates and net migration using this method.
+Forecasts of population structure have been built on forecasts of age- and gender-specific mortality rates, fertility rates and net migration using this method.
 These forecasts presuppose that the historical trends of past years will continue.
-Historical data of those rates have thus been used as input to simulate future paths of age and gender-specific population structure.
-
-Using these predicted population paths, we can calculate the average OADR and predict the levels of old age dependency that correspond to different pension age schemes.
+Historical data of those rates have thus been used as input to simulate future paths of age- and gender-specific population structure.
+
+Using these predicted population paths, we can calculate the average OADR and predict the levels of old-age dependency that correspond to different pension age schemes.
 By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
@@
 However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
-The National Commission of Audit (NCOA)(2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
+The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
 The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government.
@@
 However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-My study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
-My approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
+Our study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
+Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
 
@@
 In population forecasting, two very different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
-For instance, the Australian Bureau of Statistics is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
+For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
 In the deterministic approach, experts project future demographic changes using judgement-based scenarios.
 It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour [@PC13].
-In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method.
+In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method [see, e.g., @SBH11].
 Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates [@PC13].
@@
 \begin{equation}
-  \log(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
+  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
 \end{equation}
-where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section.3} for age $x$ in year $t$.
+where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$.
 This model involves fitting a matrix of log central rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
@@
 Also, we normally seek the least squares solution when estimating parameters.
-However, in this case, the model cannot be estimated using ordinary regression methods because there is no regressor on the right side of the equation.
-@LC92 choose a singular value decomposition (SVD) method to undertake PCA, and hence find the least squares solution.
-It has been shown that applying SVD methods to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
-Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\log(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\log(m_{x,t})-a_x$).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the log transformation.
+However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation.
+@LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
+It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
+Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\ln(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\ln(m_{x,t})-a_x$).
+However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\ln$ transformation.
 To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
@@
 @HU07 proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
-First, the rates are smoothed using penalized regression splines [@BHT14] before modeling.
-Second, it uses functional principal components analysis, which is a continuous version of PCA.
-Further, it uses more than one principal component, which address the main weakness of the LC method.
-Finally, the forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
+\begin{enumerate}
+\item The rates are smoothed using penalized regression splines [@BHT14] before modeling.
+\item It uses functional principal components analysis, which is a continuous version of PCA.
+\item It uses more than one principal component, which address the main weakness of the LC method.
+\item The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
+\end{enumerate}
 
@@
 \begin{align}
-  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\\
-  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)
+  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
+  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
 \end{align}
-The first equation describes the smoothing process.
-$y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [BHT14].
+Equation \eqref{eq:HU_1} describes the smoothing process.
+$y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14].
 $\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms.
-The second equation has a similar structure to the LC method, except that it incorporates more than one principal component and score.
+Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
 It describes the dynamics of $s_t(x)$ over time.
@@
 The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively.
-In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then equation (7) now becomes
-\begin{equation}
+In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
+\begin{equation*}
   s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
-\end{equation}
+\end{equation*}
 We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
@@
 \begin{equation}
-  \hat{y}_{n+h\mid n}(x)=\hat{s}_{n+h\mid n}(x) = \text{E}[\hat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \hat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\hat{\beta}_{n+h\mid n,j}
+  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
 \end{equation}
-where $\hat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$.
+where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$.
 Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process.
 For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
-The fitted process as follows:
-\begin{equation}
-  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t ~\forall j=1,2,\dots,J,
-\end{equation}
+The fitted process is given as follows:
+\begin{equation*}
+  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
+\end{equation*}
 where the parameters are estimated using maximum likelihood estimation.
@@
 
-We use the same notation and similar procedures to construct data as [@HB08], because the fundamental model for forecasting population for this study is the Hyndman and Ullah method.
-The data used to construct population age structure included: age and gender-specific birth and death numbers of each calendar year, age and gender-specific population members on 1\ January of each year, and age and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year.
+We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method.
+The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year.
 The notations are as follows:
@@
   m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = B_t(x)/E^F_t(x)=\text{age-specific fertility rates in calendar year t}
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
 \end{align*}
 
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
-The equation is:
+In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
+The equation is expressed as: \todo{Please define $p$ and $^+$}
 \begin{align*}
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2009.
-The start-year population for 2010 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2009 was obtained from the @ABS12.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.
+The start-year population for 2015 is also used to estimate net migration.
+Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12.
 Even though annual mortality rates are available from 1921 to 2009, only data collected after 1950 is used for two reasons.
@@
 Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
+\todo{Han has updated the data period.}
 
@@
 A stochastic functional model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
-Age and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
+age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
 The Monte Carlo simulation method was used consistently in this research.
@@
 The corresponding R code is attached in Appendix B.
+\todo{There is no appendix, Han recommends to put the R code as a supplement}
 
@@
 The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
-Therefore, to fit the model to historical fertility rates, the $y_t(x)$ in equation (16) denotes the observed historical fertility data.
+Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
 However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13].
 In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
-\begin{align*}
-  p_t(x)=\sqrt{s_{t,M}(x)s_{t,F}(x)},
-  r_t(x)=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}
-\end{align*}
+\begin{align}
+  p_t(x)&=\sqrt{s_{t,M}(x)s_{t,F}(x)}, \label{eq:coherent_1}\\
+  r_t(x)&=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}. \label{eq:coherent_2}
+\end{align}
 Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
@@
 It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
-Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to equation (18) and (19).
+Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
 From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
@@
 
-After simulating paths for age-specific fertility rate, age and gender-specific mortality rate and age and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
+After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
 The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
-Hence, we can simulate $h$-step-ahead age and gender-specific births and deaths based on simulated mortality and fertility rates.
+Hence, we can simulate $h$-step-ahead age- and gender-specific births and deaths based on simulated mortality and fertility rates.
 According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age.
@@
 The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research).
-It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in equation (17)), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
-It should be noted that the simulated population will be an array with 3 dimensions: age, year and simulation.
+It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
+It should be noted that the simulated population will be an array with three dimensions: age, year and simulation.
 
@@
 Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
-I will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age.
+We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age.
 The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
 Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers.
-I will also show how this issue was handled in the example below.
+We will also show how this issue was handled in the example below.
 
@@
 Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
-\begin{equation}
-  \bm{p}_{n+1}=[p_{mi}] =
+\begin{equation*}
+  \bm{p}_{n+1}=[p_{m,i}] =
     \begin{bmatrix}
@@
       \end{bmatrix}.
-\end{equation}
+\end{equation*}
 When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
@@
     p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
-  \end{bmatrix}.
+  \end{bmatrix}. \label{eq:population_mat}
 \end{equation}
-To calculate the total number of working age, we take a column sum of the trimmed matrix (22). The simulations of total number of work age become a vector:
+To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
 \begin{equation}
-  \bm{p}^{work}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]
+  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
 \end{equation}
@@
 \begin{equation}
-  \bm{p}^{aged}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]
+  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
 \end{equation}
 
-When $r\neq0$, the vector of total number of work age (23) is added, and the vecor of total number of aged population is subtracted with an adjustment:
+When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
 \begin{equation}
@@
 Then, $r\times100\%$ of population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age.
-In other words,$(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population.
-The simulation vectors of total work age population and total aged population should then be:
+In other words, $(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population.
+The simulation vectors of total work age population and total aged population should then be: \todo{Han feel the second equation does not have \%?}
 \begin{align*}
-  \bm{p}^{work}_{n+1}
-    & = [p^{work}_{n+1,1},p^{work}_{n+1,2},\dots,p^{work}_{n+1,1000}]\\
-    & = [\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}]+0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]   \\
-  \bm{p}^{aged}_{n+1}
-    & = [p^{aged}_{n+1,1},p^{aged}_{n+1,2},\dots,p^{aged}_{n+1,1000}]\\
-    & = [\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}]-0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
+  \bm{p}^{\text{work}}_{n+1}
+    & = \left[p^{\text{work}}_{n+1,1},p^{\text{work}}_{n+1,2},\dots,p^{\text{work}}_{n+1,1000}\right]\\
+    & = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]+0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]   \\
+  \bm{p}^{\text{aged}}_{n+1}
+    & = \left[p^{\text{aged}}_{n+1,1},p^{\text{aged}}_{n+1,2},\dots,p^{\text{aged}}_{n+1,1000}\right]\\
+    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
 \end{align*}
 
-After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{work}_{n+1}$ by the corresponding element of $\bm{p}^{aged}_{n+1}$, i.e.:
+After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{\text{work}}_{n+1}$ by the corresponding element of $\bm{p}^{\text{aged}}_{n+1}$, i.e.:
 \begin{align*}
-  \bm{OADR}_{n+1} & = [OADR_{n+1,1},OADR_{n+1,2},\dots,OADR_{n+1,1000}]\\
-                  & = \left[\frac{p^{work}_{n+1,1}}{p^{aged}_{n+1,1}},\dots,\frac{p^{work}_{n+1,1000}}{p^{aged}_{n+1,1000}}\right]
+  \bm{\text{OADR}}_{n+1} & = \left[\text{OADR}_{n+1,1},\text{OADR}_{n+1,2},\dots,\text{OADR}_{n+1,1000}\right]\\
+                  & = \left[\frac{p^{\text{work}}_{n+1,1}}{p^{\text{aged}}_{n+1,1}},\dots,\frac{p^{\text{work}}_{n+1,1000}}{p^{\text{aged}}_{n+1,1000}}\right]
 \end{align*}
-The average value of elements of $\bm{OADR}_{n+1}$ is the mean prediction of one-step-ahead OADR (i.e mean forecast of OADR in 2011).
-
-The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2011 to 2060).
+The average value of elements of $\bm{\text{OADR}}_{n+1}$ is the mean prediction of one-step-ahead OADR.
+
+The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2015 to 2064).
 Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
 \begin{equation}
-  \bm{OADR}^{forecast}=[OADR_{h,i}] =
+  \bm{\text{OADR}}^{forecast}=\left[\text{OADR}_{h,i}\right] =
   \begin{bmatrix}
-    OADR_{n+1,1} & \cdots\cdots & OADR_{n+50,1000} \\
+    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+50,1000} \\
     \vdots & \ddots & \vdots \\
-    OADR_{n+50,1} & \cdots\cdots &OADR_{n+50,1000}
+    \text{OADR}_{n+50,1} & \cdots\cdots & \text{OADR}_{n+50,1000}
   \end{bmatrix}.
@@
 
-I use the fitted model of fertility rates as an example to interpret the results of fitted models.
+We use the fitted model of fertility rates as an example to interpret the results of fitted models.
 It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
@@
 It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom\footnote{between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
+This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
 The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
@@
   ylab = "Population (millions)",
-  main = "Total females"
+  main = "Total female population"
 )
@@
   ylab = "Population (millions)",
-  main = "Total males"
+  main = "Total male population"
 )
@@
 plot(c(0, 100), c(0, 100),
-  type = "n", main = "Forecast population: 2028", yaxt = "n",
+  type = "n", main = "Forecast population: 2035", yaxt = "n",
   xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
@@
 lines(auspop$pop$female[, ncol(auspop$pop$female)] / 1000, 0:100, col = 1, lty = 2)
-text(100, 60, "2010")
-text(-100, 60, "2010")
+text(100, 60,  "2015")
+text(-100, 60, "2015")
 lines(-popm.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
@@
 
-Both \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2028} show the forecast results of population.
-\ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2028.
+Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2028} show the forecast results of population.
+Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2028.
 \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to 18 million by 2060.
@@
 
-```{r OADRat65, fig.cap="Fifty-year forecasts of the old aged dependency ratio with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", dependson='simulationresults'}
-oadp.f <- oadr(auspop, aus.sim, pension.age = current)
-autoplot(oadp.f) + xlab("year") + ylab("ratio") +
-  ggtitle("Old age dependency ratio forecasts with pension age=65")
-```
-
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the old aged dependency ratio associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
+```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", dependson='simulationresults'}
+OADR.f <- oadr(auspop, aus.sim, pension.age = current)
+autoplot(OADR.f) + xlab("year") + ylab("ratio") +
+  ggtitle("OADR forecasts with pension age=65")
+```
+
+```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
 The actual OADRs for 1950-2010 are shown in black.", dependson='OADRat65'}
-oadp.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
-oadp.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
-autoplot(oadp.f$x) +
+OADR.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
+OADR.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
+autoplot(OADR.f$x) +
   geom_hline(yintercept = 0.21, col = "gray") +
-  autolayer(oadp.f, series = "current", alpha = 0.5) +
-  autolayer(oadp.f.67, series = "approved", alpha = 0.5) +
-  autolayer(oadp.f.prop, series = "proposed", alpha = 0.5) +
+  autolayer(OADR.f, series = "current", alpha = 0.5) +
+  autolayer(OADR.f.67, series = "approved", alpha = 0.5) +
+  autolayer(OADR.f.prop, series = "proposed", alpha = 0.5) +
   ylab("ratio") + xlab("Year") +
-  ggtitle("Old-age dependency ratio forecasts") +
+  ggtitle("OADR forecasts") +
   scale_color_manual(
@@
 Analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
-Even though the government might further increase the pension age in future, I kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \ref{fig:OADRat65} shows the mean forecast and prediction interval of the old aged dependency ratio with a pension age of 65, along with the historical OADR for 1920-2010.
+Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
+Figure \ref{fig:OADRat65} shows the mean forecast and prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1920-2010.
 A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
@@
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Therefore, \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
+Therefore, Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
 However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
@@
 The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $F$ prediction horizon.
-Then we are allowed to repeat the test $n-F-k+1$ times, where $n$ is the number of total years of observation.
+Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $F$ \todo{Han thinks $H$?} prediction horizon.
+Then we are allowed to repeat the test $n-F-k+1$ \todo{Han thinks $n-H-k+1$} times, where $n$ is the number of total years of observation.
 The procedure is as follows:
 
-Let $i=1$, we first select historical data for a time interval of $[i,i+1,\dots,i+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{the OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Let $i=1$, we first select historical data for a time interval of $[i,i+1,\dots,i+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
 Then, we can calculate the difference of forecasted OADR over the period $[i+k,i+k+1,\dots,i+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
@@
 \end{equation}
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,i}=|OADR^{mean}_{h,i}-OADR^{real}_{h,i}|$.
+where $h$ denotes for the forecast horizon and $\text{AE}_{h,i}=\left|\text{OADR}^{mean}_{h,i}-\text{OADR}^{real}_{h,i}\right|$.
 This process is also known as "rolling forecasting origin", because the "origin" ($k+i-1$) at which the forecast is based rolls forward in time.
@@
 ######## Run a rolling forecast origin
+# replace 2010 by 2014 (Han?)
 t <- 2010 - 1950 + 1
@@
                          N = 3)
-  oadp.fs <- oadr(pop.short, aus.sim.s)
-  oadrtest[, i] <- oadp.fs$mean
-}
-oadrtest
+    OADR.fs <- oadr(pop.short, aus.sim.s)
+    oadrtest[, i] <- OADR.fs$mean
+}
 oadr.real <- oadr(auspop, aus.sim)$x
@@
 oadrave <- apply(oadr.error, 1, mean)
-oadrave
 
@@
 In our sample, $n=2010-1950+1=61$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in \ref{fig:rollingtest}.
+The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \ref{fig:rollingtest}.
 From this figure, we observe that the absolute mean error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
@@
 
-It would normally be ideal to compare the mean absolute error of the forecast from my model to other available models to measure the accuracy.
+It would normally be ideal to compare the mean absolute error of the forecast from our model to other available models to measure the accuracy.
 For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
@@
 According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
-Suppose we denote pension age schemes over the prediction horizon by $\bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}]$.
-The OADR function of pension age over the prediction horizon is denoted as $OADR_h(PA_{n+h})$ for $h=1,2,3,\dots,H$.
+Suppose we denote pension age schemes over the prediction horizon by $\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]$.
+The OADR function of pension age over the prediction horizon is denoted as $OADR_h(\text{PA}_{n+h})$ for $h=1,2,\dots,H$.
 There is a negative relationship between pension age and OADR.
@@
 Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
-Therefore, the target pension age scheme $\bm{PA}^{target}$ can be defined in the following way:
+Therefore, the target pension age scheme $\bm{\text{PA}}^{target}$ can be defined in the following way:
 for $h=1,2,\dots,H$
 \begin{equation}
-  \text{minimise~} PA_{n+h}  \text{~such that~} OADR_h(PA_{n+h})\leq OADR^{desired}
+  \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
 \end{equation}
 \begin{align*}
-  \text{subject to the constraint~} 0\leq PA_{n+h}-PA_{n+h-1}\leq 1
+  \text{subject to the constraint~} 0\leq \text{PA}_{n+h}-\text{PA}_{n+h-1}\leq 1
 \end{align*}
@@
 The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in 2017 onward.}, which is:
+This simplification is reasonable because the pension age will be same in 2017 onward}, which is:
 \begin{align*}
-  \bm{PA}=[PA_{n+1},PA_{n+2},\dots,PA_{n+H}] = [65,65,\dots,65]
+  \bm{\text{PA}}=\left[\text{PA}_{n+1},\text{PA}_{n+2},\dots,\text{PA}_{n+H}\right] = \left[65,65,\dots,65\right]
 \end{align*}
 We take the following algorithm:
-For $h=1,2,\dots,H$, we keep increasing pension age vector $[PA_{n+h},PA_{n+h+1},\dots,PA_{n+H}]$ by a month at a time, unless we find that
+For $h=1,2,\dots,H$, we keep increasing pension age vector $[\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]$ by a month at a time, unless we find that
 \begin{align}
-  OADR^{mean}_h(PA_{n+h})> OADR^{desired} \text{~or~} PA_{n+h}-PA_{n+h-1}\geq 1
+  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \text{~or~} \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
 \end{align}
-where $OADR^{mean}_h(PA_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $PA_{n+h}$.
+where $\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $\text{PA}_{n+h}$.
 
@@
 ### find the optimal scheme of pension.age based on mean forecast
-target <- oadp.f$mean[4]
+target <- OADR.f$mean[4]
 
@@
 }
-oadp.f.optimal <- oadr(auspop,
+OADR.f.optimal <- oadr(auspop,
   aus.sim,
@@
 }
-oadp.f.upper <- oadr(auspop,
+OADR.f.upper <- oadr(auspop,
   aus.sim,
@@
 }
-oadp.f.lower <- oadr(auspop, aus.sim, pension.age = pension.age.lower)
+OADR.f.lower <- oadr(auspop, aus.sim, pension.age = pension.age.lower)
 ```
@@
 It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years.
-\ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
+Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
 Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
@@
 ```{r pensionagetables, dependson="OADRat65"}
-year <- time(oadp.f$mean)
+year <- time(OADR.f$mean)
 yr <- trunc(pension.age)
@@
 ```{r pensionagetables2, dependson="OADRat65"}
-year <- time(oadp.f$mean)
+year <- time(OADR.f$mean)
 yr <- trunc(pension.age.lower)
@@
 
-```{r OADRwithoptimal, fig.cap="The mean forecast of old aged dependency ratio associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
+```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
 The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
 ## plots of OADR with plausible pension age schemes
-autoplot(oadp.f.optimal$x) +
-  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
-  autolayer(oadp.f.optimal) +
+autoplot(OADR.f.optimal$x) +
+  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
+  autolayer(OADR.f.optimal) +
   ggtitle("OADR forecast estimates for optimal pension ages") +
@@
 ```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
-p1 <- autoplot(oadp.f.upper$x) +
-  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
-  # autolayer(oadp.f.upper) +
+p1 <- autoplot(OADR.f.upper$x) +
+  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
+  # autolayer(OADR.f.upper) +
   ggtitle("OADR for upper boundary pension ages") +
@@
   ylim(0.07, 0.27)
-p2 <- autoplot(oadp.f.lower$x) +
-  geom_hline(yintercept = oadp.f$mean[4], col = "red") +
-  # autolayer(oadp.f.lower) +
+p2 <- autoplot(OADR.f.lower$x) +
+  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
+  # autolayer(OADR.f.lower) +
   ggtitle("OADR for lower boundary pension ages") +
@@
 
-```{r OADR_realpensionage, fig.cap="The mean forecast of old aged dependency ratio associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
+```{r OADR_realpensionage, fig.cap="The mean forecast of OADR associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
 The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRat65"}
@@
 
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRatboundaries}.
+The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRboundaries}.
 It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
@@
 On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
-
-\ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
+\todo{Han feels Tables 3 and 4 should be removed?}
+
+Figure \ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
 It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
@@
 Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it and its 80% confidence level with real pension age scheme in Figure \ref{ComparisonwithOADR22}.
+We have shown the comparison of it \todo{Han confused} and its 80% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
 When we allow 1% more in desired OADR, the real pension age becomes plausible.
-Figure \ref{OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+Figure \ref{fig:OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
 It confirms that OADR is stable around a level higher than current level of OADR before 2035.
@@
 
-In this paper, I have suggested a statistical and demographic approach to address the issue.
-I attempt to quantify the effects of changes in the pension age on financial burdens using an old aged dependency ratio as a measure of financial burden on Australian society.
-The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable old age dependency ratio around the desired level.
+In this paper, we have suggested a statistical and demographic approach to address the issue.
+We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of financial burden on Australian society.
+The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable OADR around the desired level.
 To forecast population age structure, three demographic components of population were modelled separately using @HU07 functional time series method, with an extension of the product-ratio method [@HBY13].
-Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the old age dependency ratio no greater than desired level.
+Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than desired level.
 This approach is proposed to find target pension age scheme based on a given desired level of OADR.
 
-I undertake the approach based on assuming the desired level of OADR is at current level of 21%.
+We undertake the approach based on assuming the desired level of OADR is at current level of 21%.
 Using the historical data from 1950 to 2010, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
-It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable old aged dependency ratio at a level which can be affordable to Australians of working age.
+It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
 Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
@@
 However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
-T
-
-herefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
+Therefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
 This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval.
@@
 
-Although my results are promising, there are still grounds for further research.
-First, my research results are based on forecasts from one particular model.
+Although our results are promising, there are still grounds for further research.
+First, our research results are based on forecasts from one particular model.
 Further studies can apply the same approach but with different models of population forecasting, which allows for enhanced credibility of results.
-Moreover, my research addresses the issue from a purely demographic perspective.
+Moreover, our research addresses the issue from a purely demographic perspective.
 It is possible to include an economic perspective.
 For example, the economic implications of retaining older workers in workforce can be considered.
-Second, my research uses an old age dependency ratio as a single measurement of financial burden.
+Second, Our research uses an OADR as a single measurement of financial burden.
 Further research should allow the effect of other economic factors to be taken into account.

### 2019-01-06 PensionAge.tex
PensionAge.pdf

--- 2019-01-06 PensionAge.Rmd
@@
----
-title: "Forecasting the old-age dependency ratio to determine the best pension age"
-author:
-- familyname: Hyndman
-  othernames: Rob J
-  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
-  email: Rob.Hyndman@monash.edu
-  correspondingauthor: true
-- familyname: Zeng
-  othernames: Yijun
-  address: Monash University
-- familyname: Shang
-  othernames: Han Lin
-  address: Australian National University
-abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the current level, which is 21%.
-This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "functional time series model, coherent forecasts, demographic components, pension and insurance"
-wpnumber: no/yr
-jelcodes: C10,C14,C22
-blind: false
-cover: true
-toc: false
-bibliography: pensionage.bib
-biblio-style: authoryear-comp
-output:
-  MonashEBSTemplates::workingpaper:
-    fig_caption: yes
-    fig_height: 5
-    fig_width: 8
-    keep_tex: yes
-    number_sections: yes
-    citation_package: biblatex
-    includes:
-      in_header: preamble.tex
----
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
-# Make sure you have the latest version of rmarkdown and bookdown
-# devtools::install_github("rstudio/rmarkdown")
-# devtools::install_github("rstudio/bookdown")
-# And the latest versions of Our packages
-# devtools::install_github("robjhyndman/forecast")
-# devtools::install_github("robjhyndman/demography")
-# devtools::install_github("robjhyndman/addb")
-library(demography)
-library(addb)
-library(ggplot2)
-source("functions-v4.R")
-```
-
-# Introduction
-
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].
-Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
-Similar demographic challenges face many other countries.
-One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age [@Walker1982].
-The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
-
-This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations.
-To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
-In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010].
-In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035.
-This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014.
-In this paper, we investigate the effect of these changes in the pension age on the forecast OADR.
-
-The research presented in this paper contributes to the discussion by forecasting the age structure of the population, quantifying the effects of changing the pension age on financial burdens, and hence finding an appropriate pension age scheme which is economically viable for Australia.
-The analysis of economic impact of increasing pension age can be complicated.
-In this paper, we will focus on only one aspect: the impact on the burden of future working age generations.
-
-In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
-The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07].
-This can be expressed using the formula below:
+\documentclass[11pt,a4paper,]{article}
+\usepackage{lmodern}
+
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage[]{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
+\hypersetup{
+            pdftitle={Forecasting the old-age dependency ratio to determine the best pension age},
+            pdfkeywords={functional time series model, coherent forecasts, demographic
+components, pension and insurance},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{geometry}
+\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
+\usepackage[style=authoryear-comp,]{biblatex}
+\addbibresource{pensionage.bib}
+\usepackage{longtable,booktabs}
+% Fix footnotes in tables (requires footnote package)
+\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\title{Forecasting the old-age dependency ratio to determine the best pension
+age}
+
+%% MONASH STUFF
+
+%% CAPTIONS
+\RequirePackage{caption}
+\DeclareCaptionStyle{italic}[justification=centering]
+ {labelfont={bf},textfont={it},labelsep=colon}
+\captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
+\captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
+
+%% FONT
+\RequirePackage{bera}
+\RequirePackage{mathpazo}
+
+%% HEADERS AND FOOTERS
+\RequirePackage{fancyhdr}
+\pagestyle{fancy}
+\rfoot{\Large\sffamily\raisebox{-0.1cm}{\textbf{\thepage}}}
+\makeatletter
+\lhead{\textsf{\expandafter{\@title}}}
+\makeatother
+\rhead{}
+\cfoot{}
+\setlength{\headheight}{15pt}
+\renewcommand{\headrulewidth}{0.4pt}
+\renewcommand{\footrulewidth}{0.4pt}
+\fancypagestyle{plain}{%
+\fancyhf{} % clear all header and footer fields
+\fancyfoot[C]{\sffamily\thepage} % except the center
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrulewidth}{0pt}}
+
+%% MATHS
+\RequirePackage{bm,amsmath}
+\allowdisplaybreaks
+
+%% GRAPHICS
+\RequirePackage{graphicx}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.8}
+
+%\RequirePackage[section]{placeins}
+
+%% SECTION TITLES
+\RequirePackage[compact,sf,bf]{titlesec}
+\titleformat{\section}[block]
+  {\fontsize{15}{17}\bfseries\sffamily}
+  {\thesection}
+  {0.4em}{}
+\titleformat{\subsection}[block]
+  {\fontsize{12}{14}\bfseries\sffamily}
+  {\thesubsection}
+  {0.4em}{}
+\titlespacing{\section}{0pt}{*5}{*1}
+\titlespacing{\subsection}{0pt}{*2}{*0.2}
+
+%% TITLE PAGE
+\def\Date{\number\day}
+\def\Month{\ifcase\month\or
+ January\or February\or March\or April\or May\or June\or
+ July\or August\or September\or October\or November\or December\fi}
+\def\Year{\number\year}
+
+\makeatletter
+\def\wp#1{\gdef\@wp{#1}}\def\@wp{??/??}
+\def\jel#1{\gdef\@jel{#1}}\def\@jel{??}
+\def\showjel{{\large\textsf{\textbf{JEL classification:}}~\@jel}}
+\def\nojel{\def\showjel{}}
+\def\addresses#1{\gdef\@addresses{#1}}\def\@addresses{??}
+\def\cover{{\sffamily\setcounter{page}{0}
+        \thispagestyle{empty}%
+        \vspace*{-2cm}
+        \centerline{\raisebox{-1.8cm}{\includegraphics[width=5cm]{MBSportrait}}\hspace*{9cm} ISSN 1440-771X}\vspace{0.99cm}
+        \begin{center}\Large
+        Department of Econometrics and Business Statistics\\[.5cm]
+        \scriptsize http://business.monash.edu/econometrics-and-business-statistics/research/publications
+        \end{center}\vspace{2cm}
+        \begin{center}
+        \fbox{\parbox{14cm}{\begin{onehalfspace}\centering\Huge\vspace*{0.3cm}
+                \textsf{\textbf{\expandafter{\@title}}}\vspace{1cm}\par
+                \LARGE\@author\end{onehalfspace}
+        }}
+        \end{center}
+        \vfill
+                \begin{center}\Large
+                \Month~\Year\\[1cm]
+                Working Paper \@wp
+        \end{center}}}
+\def\pageone{{\sffamily\setstretch{1}%
+        \thispagestyle{empty}%
+        \vbox to \textheight{%
+        \raggedright\baselineskip=1.2cm
+     {\fontsize{24.88}{30}\sffamily\textbf{\expandafter{\@title}}}
+        \vspace{2cm}\par
+        \hspace{1cm}\parbox{14cm}{\sffamily\large\@addresses}\vspace{1cm}\vfill
+        \hspace{1cm}{\large\Date~\Month~\Year}\\[1cm]
+        \hspace{1cm}\showjel\vss}}}
+\def\blindtitle{{\sffamily
+     \thispagestyle{plain}\raggedright\baselineskip=1.2cm
+     {\fontsize{24.88}{30}\sffamily\textbf{\expandafter{\@title}}}\vspace{1cm}\par
+        }}
+\def\titlepage{{\cover\newpage\pageone\newpage\blindtitle}}
+
+\def\blind{\def\titlepage{{\blindtitle}}\let\maketitle\blindtitle}
+\def\titlepageonly{\def\titlepage{{\pageone\end{document}}}}
+\def\nocover{\def\titlepage{{\pageone\newpage\blindtitle}}\let\maketitle\titlepage}
+\let\maketitle\titlepage
+\makeatother
+
+%% SPACING
+\RequirePackage{setspace}
+\spacing{1.5}
+
+%% LINE AND PAGE BREAKING
+\sloppy
+\clubpenalty = 10000
+\widowpenalty = 10000
+\brokenpenalty = 10000
+\RequirePackage{microtype}
+
+%% PARAGRAPH BREAKS
+\setlength{\parskip}{1.4ex}
+\setlength{\parindent}{0em}
+
+%% HYPERLINKS
+\RequirePackage{xcolor} % Needed for links
+\definecolor{darkblue}{rgb}{0,0,.6}
+\RequirePackage{url}
+
+\makeatletter
+\@ifpackageloaded{hyperref}{}{\RequirePackage{hyperref}}
+\makeatother
+\hypersetup{
+     citecolor=0 0 0,
+     breaklinks=true,
+     bookmarksopen=true,
+     bookmarksnumbered=true,
+     linkcolor=darkblue,
+     urlcolor=blue,
+     citecolor=darkblue,
+     colorlinks=true}
+
+%% KEYWORDS
+\newenvironment{keywords}{\par\vspace{0.5cm}\noindent{\sffamily\textbf{Keywords:}}}{\vspace{0.25cm}\par\hrule\vspace{0.5cm}\par}
+
+%% ABSTRACT
+\renewenvironment{abstract}{\begin{minipage}{\textwidth}\parskip=1.4ex\noindent
+\hrule\vspace{0.1cm}\par{\sffamily\textbf{\abstractname}}\newline}
+  {\end{minipage}}
+
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+
+\usepackage[showonlyrefs]{mathtools}
+\usepackage[no-weekday]{eukdate}
+
+%% BIBLIOGRAPHY
+
+\makeatletter
+\@ifpackageloaded{biblatex}{}{\usepackage[style=authoryear-comp, backend=biber, natbib=true]{biblatex}}
+\makeatother
+\ExecuteBibliographyOptions{bibencoding=utf8,minnames=1,maxnames=3, maxbibnames=99,dashed=false,terseinits=true,giveninits=true,uniquename=false,uniquelist=false,doi=false, isbn=false,url=true,sortcites=false}
+
+\DeclareFieldFormat{url}{\texttt{\url{#1}}}
+\DeclareFieldFormat[article]{pages}{#1}
+\DeclareFieldFormat[inproceedings]{pages}{\lowercase{pp.}#1}
+\DeclareFieldFormat[incollection]{pages}{\lowercase{pp.}#1}
+\DeclareFieldFormat[article]{volume}{\mkbibbold{#1}}
+\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
+\DeclareFieldFormat[article]{title}{\MakeCapital{#1}}
+\DeclareFieldFormat[inproceedings]{title}{#1}
+\DeclareFieldFormat{shorthandwidth}{#1}
+% No dot before number of articles
+\usepackage{xpatch}
+\xpatchbibmacro{volume+number+eid}{\setunit*{\adddot}}{}{}{}
+% Remove In: for an article.
+\renewbibmacro{in:}{%
+  \ifentrytype{article}{}{%
+  \printtext{\bibstring{in}\intitlepunct}}}
+
+\makeatletter
+\DeclareDelimFormat[cbx@textcite]{nameyeardelim}{\addspace}
+\makeatother
+\renewcommand*{\finalnamedelim}{%
+  %\ifnumgreater{\value{liststop}}{2}{\finalandcomma}{}% there really should be no funny Oxford comma business here
+  \addspace\&\space}
+
+\wp{no/yr}
+\jel{C10,C14,C22}
+
+\author{Rob J~Hyndman, Yijun~Zeng, Han Lin~Shang}
+\addresses{\textbf{Rob J Hyndman}\newline
+Department of Econometrics \& Business Statistics\newline Monash
+University, Clayton VIC 3800, Australia
+\newline{Email: \href{mailto:Rob.Hyndman@monash.edu}{\nolinkurl{Rob.Hyndman@monash.edu}}}\newline Corresponding author\\[1cm]
+\textbf{Yijun Zeng}\newline
+Monash University
+\\[1cm]
+\textbf{Han Lin Shang}\newline
+Australian National University
+\\[1cm]
+}
+
+\date{\sf\Date~\Month~\Year}
+\makeatletter
+ \lfoot{\sf Hyndman, Zeng, Shang: \@date}
+\makeatother
+
+\usepackage{todonotes}
+
+\begin{document}
+\maketitle
+\begin{abstract}
+We forecast the old-age dependency ratio for Australia under various
+pension age proposals, and estimate a pension age scheme that will
+provide a stable old-age dependency ratio at a specified level. Our
+approach involves a stochastic population forecasting method based on
+coherent functional data models for mortality, fertility and net
+migration, which we use to simulate future age-structures of the
+population. We apply these ideas to Australian historical demographic
+data and the results suggest that the pension age should be increased to
+67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age
+dependency ratio at the current level, which is 21\%. This approach can
+easily be extended to other target levels of the old-aged dependency
+ratio and to other countries.
+\end{abstract}
+\begin{keywords}
+functional time series model, coherent forecasts, demographic
+components, pension and insurance
+\end{keywords}
+
+\section{Introduction}\label{introduction}
+
+Australia's ageing population is a result of three factors: (1)
+significant technological advances in medical care leading to longer
+life spans; (2) high fertility rates after World War II resulting in the
+``baby-boomer'' generation; and (3) a large decline in fertility rates
+over the past twenty or so years \autocite{Fehr2008}. Consequently,
+there are many older people leaving the workforce, and fewer workers
+replacing them. Similar demographic challenges face many other
+countries. One way of measuring this problem is via the old-age
+dependency ratio (OADR): the number of people post-retirement to the
+number of people of working age \autocite{Walker1982}. The OADR has been
+increasing for many decades, but recently the rate of increase has
+jumped markedly, and we show that it will continue to increase at a
+rapid rate if there are no age-related policy changes.
+
+This is consistent with the Australian Intergenerational Reports
+\autocites{IGR02}{IGR07}{Swan2010} that explored the extent to which
+existing age-related policies would affect the burden of future working
+generations. To date, the Australian government has addressed the
+problem through a variety of approaches including modifications to
+compulsory superannuation policies, instigating work incentives for
+older people, and increasing the pension age (defined as the age at
+which eligible residents can access the age pension for the first time).
+In 2009, the federal government announced an increase in pension age
+from 65 to 67 by 2023 \autocite{Nielson2010}. In May 2014, the Federal
+Treasurer proposed a further increase in the pension age to 70 by 2035.
+This new proposal is in line with the recommendations from the
+\textcite{PC13} and the \textcite{NCOA2014}. In this paper, we
+investigate the effect of these changes in the pension age on the
+forecast OADR.
+
+The research presented in this paper contributes to the discussion by
+forecasting the age structure of the population, quantifying the effects
+of changing the pension age on financial burdens, and hence finding an
+appropriate pension age scheme which is economically viable for
+Australia. The analysis of economic impact of increasing pension age can
+be complicated. In this paper, we will focus on only one aspect: the
+impact on the burden of future working age generations.
+
+In this paper, we use the OADR as a measure of the financial burden on
+the Australian workforce because a rise in the OADR will reduce the
+ability of working age population to finance pensions and health costs
+\autocites{ARW07}{IGR02}{IGR07}. The OADR is defined as the ratio of the
+number of people aged over the pension age to the number of people of
+working age \autocite{ARW07}. This can be expressed using the formula
+below:
+
 \begin{equation}
@@
 \end{equation}
-We provide forecasts of future population age structures over the next 50 years.
-We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments.
-One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
-Forecasts of population structure have been built on forecasts of age- and gender-specific mortality rates, fertility rates and net migration using this method.
-These forecasts presuppose that the historical trends of past years will continue.
-Historical data of those rates have thus been used as input to simulate future paths of age- and gender-specific population structure.
-
-Using these predicted population paths, we can calculate the average OADR and predict the levels of old-age dependency that correspond to different pension age schemes.
-By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
-Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
-It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2014.
-Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
-This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.
-
-Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14].
-Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.
-Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
-We do not consider these here.
-Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables.
-
-The remainder of this paper proceeds as follows.
-Section \@ref(sec:litreview) reviews key literature on population forecasting and the pension age in Australia.
-Section \@ref(sec:data) describes the data and modelling framework we use in this study.
-We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \@ref(sec:target).
-Finally, Section \@ref(sec:conclusions) gives concluding remarks as well as identifies the scope for future research.
-
-# Background and Literature Review {#sec:litreview}
-
-## The age pension in Australia
-
-Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing.
-For example, it provides single home-owners with a real income of \$13653 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
-The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases.
-The age pension in Australia is very generous, even with the means test.
-For instance, a couple holding assets of more than one million dollars is still eligible for a partial age pension.
-
-Currently, the age pension is the primary source of income for 70% -80% of Australian residents over 64 years [@ABS06].
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the current average less than \$100,000 at retirement [@ASFA07].
-It has been estimated by @PT08 that a retiree will need to have \$450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
-The required wealth to comply with personal-funded retirement savings requirements is too high for most Australians, suggesting that retirees will continue to rely on the age pension in the coming decades.
-
-The ageing trend in Australia, along with retirees' dependence on the age pension, has dramatically increased the fiscal cost of the age pension.
-For instance, the fiscal cost of the age pension is currently around at 2.5% of Gross Domestic Profit (GDP), but is expected to increase to 4.4% by the 2050s (Australian Government, 2007).
-The @PC13 also indicates the government will need to raise taxes by 21% to pay for extra aged care and health costs, which is caused by longer life expectancies in newer generations.
-
-The issue is not only a problem for the government, but also for future retirees.
-Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65).
-They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
-This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR02].
-
-```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
-year <- 2065 - 2007
-proposed <- ts(pmin(
-  70,
-  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
-)[1:50],
-start = 2008
-)
-approved <- pmin(proposed, 67)
-current <- pmin(proposed, 65)
-cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
-ggplot() +
-  forecast::autolayer(proposed, series = "proposed") +
-  forecast::autolayer(approved, series = "approved") +
-  forecast::autolayer(current, series = "current") +
-  xlab("Year") + ylab("Age of retirement") +
-  scale_color_manual(
-    values = cols, name = " ",
-    breaks = c("current", "approved", "proposed"),
-    labels = c("Pension age at 65", "Approved change", "Proposed further change")
-  )
-```
-
-The Australian government is trying to take early intervention in relation to the pension age to balance between providing social support and fiscal cost.
-The pension age for males has been set at 65 for over a century.
-While the pension age for females was 60 years until 1994, it has steadily increased to 65 years, in line with that of males.
-The previous Labor government announced in 2009 that the pension age will increase six months every two years until 2017, capping at 67 in July 2023.
-This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because pension age is regarded as a normal age for retirement in Australia.
-However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
-The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
-The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government.
-Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.
-This announcement received overwhelmingly negative responses in the media.
-@Guest14 argues from an economic prospective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is  less than half of the OECD average.
-He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time.
-Further, @Power14 contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more a complex social problem.
-
-In fact, all supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age.
-No justification on the pace or degree of the change has been provided.
-Also, the government has not disclosed the method it used to determine the new pension age.
-It is therefore not surprising that the adjustment of the pension age has been questioned by the public.
-A consistent method to determine the appropriate pension age would be more persuasive in general.
-For example, it is preferred by OECD countries that pension age should be linked to life expectancy [@OECD12].
-There is a practical issue as to how to link life expectancy with pension ages given that there is no information on future mortality rates [@PC13].
-@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that "pension age should increase by approximately 50% of any increase in life expectancy".
-However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-Our study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
-Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
-
-## Population forecasting
-
-In population forecasting, two very different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
-For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
-In the deterministic approach, experts project future demographic changes using judgement-based scenarios.
-It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour [@PC13].
-In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method [see, e.g., @SBH11].
-Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates [@PC13].
-
-Therefore, some official agencies decide to mix the two approaches in their forecasts in order to provide a supplement to both approaches.
-For instance, the most recent forecast of population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The approach of forecasting used in this study is very similar to the @PC13.
-The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of Lee-Carter method.
-In addition, an adapted product-ratio method is used to eliminate the potential long-term divergence between female and male mortality rates.
-A more detailed review of forecasting methods is given below.
-
-### Deterministic Methods Used by the ABS
-
-The deterministic method is judgment-based.
-The Australian Bureau of Statistics formulates assumptions on the basis of demographic trends, in conjunction with advice from individual experts or government departments.
-The projections are not predictions or forecasts, "but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period" [@ABS12, p.2].
-In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
-Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for variety of population projections.
-
-### Lee-Carter Method
-
-The Lee-Carter method [@LC92] is a significant milestone in demographic forecasting. It has been widely used to forecast mortality rates across various countries, including Australia.
-
-The model proposed by @LC92 is as follows:
+
+We provide forecasts of future population age structures over the next
+50 years. We then use those forecasts to compute the OADR associated
+with pension age both before and after the adjustments. One contribution
+of the current study is the combined use of the Hyndman-Ullah
+forecasting method \autocite{HU07} and the product-ratio method
+\autocite{HBY13} to forecast a population age structure. Forecasts of
+population structure have been built on forecasts of age- and
+gender-specific mortality rates, fertility rates and net migration using
+this method. These forecasts presuppose that the historical trends of
+past years will continue. Historical data of those rates have thus been
+used as input to simulate future paths of age- and gender-specific
+population structure.
+
+Using these predicted population paths, we can calculate the average
+OADR and predict the levels of old-age dependency that correspond to
+different pension age schemes. By testing different pension age schemes,
+we aim to find the pension age with the desired OADR outcome. Therefore,
+other contributions of this research are (1) to examine the effect of
+adjusting pension ages by comparing OADR before and after adjustment;
+and (2) to suggest a suitable pension age scheme to ensure that the
+economic burden will remain relatively constant at a desired level in
+the future. It should be noted that the desired level has been set at
+21\%, the estimated level of OADR in 2014. Whether this OADR level is
+the most appropriate level for Australia remains to be examined and is
+not the focus of this paper. This paper concentrates on providing a
+framework for policy makers to find a target pension age for a given
+desired level of OADR.
+
+Some may argue that using OADR as a measure of financial burden for the
+next generation could be biased, with a large number of retirees able to
+rely on self-financed retirement income, such as superannuation.
+However, 80\% of Australians over pension age rely fully or partly on
+the age pension \autocite{Power14}. Therefore, the proportion of people
+over working age is still a good representation of financial burden on
+future working generations. Nevertheless, using OADR as a single
+measurement of financial burden may overlook some important economic
+factors, and \textcite{HY12} have suggested the use of an adjusted OADR
+that takes account of some of these factors in analyzing pension
+finance. We do not consider these here. Our approach is intended to
+illustrate how population forecasting can be used to explore the pension
+age issue in a simple context, and it could be extended to take into
+account other variables.
+
+The remainder of this paper proceeds as follows. Section
+\ref{sec:litreview} reviews key literature on population forecasting and
+the pension age in Australia. Section \ref{sec:data} describes the data
+and modelling framework we use in this study. We show how our framework
+can be used to estimate a pension age scheme that leads to a target OADR
+in Section \ref{sec:target}. Finally, Section \ref{sec:conclusions}
+gives concluding remarks as well as identifies the scope for future
+research.
+
+\section{Background and Literature Review}\label{sec:litreview}
+
+\subsection{The age pension in
+Australia}\label{the-age-pension-in-australia}
+
+Age pension in Australia is an income support and provides access to a
+range of concessions for older Australians who have passed means
+testing. For example, it provides single home-owners with a real income
+of \$13653 p.a and additional allowances to cover expenses such as rent
+or
+pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
+The means test ensures that retirees with enough personal savings will
+become ineligible for public provision by reducing the pension at fixed
+levels of pay as personal wealth increases. The age pension in Australia
+is very generous, even with the means test. For instance, a couple
+holding assets of more than one million dollars is still eligible for a
+partial age pension.
+
+Currently, the age pension is the primary source of income for 70\%
+-80\% of Australian residents over 64 years \autocite{ABS06}. Even
+though the government has promoted self-financed retirement by
+introducing the Superannuation Guarantee in 1992, the Superannuation
+Guarantee accumulations are still modest, with the current average less
+than \$100,000 at retirement \autocite{ASFA07}. It has been estimated by
+\textcite{PT08} that a retiree will need to have \$450,000 at 65 in
+order to support a pension-equivalent income and this is more than eight
+times of the average retirement accumulation of Australians. The
+required wealth to comply with personal-funded retirement savings
+requirements is too high for most Australians, suggesting that retirees
+will continue to rely on the age pension in the coming decades.
+
+The ageing trend in Australia, along with retirees' dependence on the
+age pension, has dramatically increased the fiscal cost of the age
+pension. For instance, the fiscal cost of the age pension is currently
+around at 2.5\% of Gross Domestic Profit (GDP), but is expected to
+increase to 4.4\% by the 2050s (Australian Government, 2007). The
+\textcite{PC13} also indicates the government will need to raise taxes
+by 21\% to pay for extra aged care and health costs, which is caused by
+longer life expectancies in newer generations.
+
+The issue is not only a problem for the government, but also for future
+retirees. Given children born today are expected to live up to their 90s
+on average, the \textcite{PC13} suggests that Australians won't be able
+to afford to spend 35 years in retirement (i.e., retire around 65). They
+have predicted that a third of baby boomers are expected to spend all
+their money and assets before they
+die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
+This problem might eventually deteriorate the sustainability of the age
+pension, although the welfare system works well at the moment, because
+demographic changes often have delayed effects \autocite{IGR02}.
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/changespension-1.pdf}
+\caption{\label{fig:changespension}Government's adjustments on pension age
+scheme.}
+\end{figure}
+
+The Australian government is trying to take early intervention in
+relation to the pension age to balance between providing social support
+and fiscal cost. The pension age for males has been set at 65 for over a
+century. While the pension age for females was 60 years until 1994, it
+has steadily increased to 65 years, in line with that of males. The
+previous Labor government announced in 2009 that the pension age will
+increase six months every two years until 2017, capping at 67 in July
+2023. This change is expected to have a significant impact on labor
+force participation and to decrease the retirement duration of residents
+because pension age is regarded as a normal age for retirement in
+Australia. However, the \textcite{PC13} proposed further lifting of the
+pension age to 70 on the grounds that increasing the pension age to 70
+would save taxpayers \$150 billion in welfare costs and health spending,
+and elderly people are capable of continuing work. The National
+Commission of Audit (NCOA) (2014) holds the same opinion, and
+recommended lifting the pension age to 70 from 2053. The current
+Treasurer Joe Hockey announced that the government would increase the
+pension age to 70 from 2035, which is proposed in the Federal Budget
+Statement for 2014-2015 to be confirmed by Australian Federal
+Government. Figure \ref{fig:changespension} illustrates the process of
+the adjustments on pension age scheme. This announcement received
+overwhelmingly negative responses in the media. \textcite{Guest14}
+argues from an economic prospective that Australia currently has much
+better circumstances than other OECD countries in terms of age pension
+pressure, because spending on the age pension in Australia is less than
+half of the OECD average. He also claims that Australia has a higher
+consumption of all other goods and services, and so why are they not
+allowed to have more leisure time. Further, \textcite{Power14} contends
+that many Australians are not physically able to work full-time to 70,
+so that recommendations made by the PC and NCOA are simplistic solutions
+to a more a complex social problem.
+
+In fact, all supportive arguments for increasing the pension age in
+Australia have only justified the need to increase the pension age. No
+justification on the pace or degree of the change has been provided.
+Also, the government has not disclosed the method it used to determine
+the new pension age. It is therefore not surprising that the adjustment
+of the pension age has been questioned by the public. A consistent
+method to determine the appropriate pension age would be more persuasive
+in general. For example, it is preferred by OECD countries that pension
+age should be linked to life expectancy \autocite{OECD12}. There is a
+practical issue as to how to link life expectancy with pension ages
+given that there is no information on future mortality rates
+\autocite{PC13}. \textcite[p7]{CEDA07} proposed directly linking pension
+age with life expectancy in the way that ``pension age should increase
+by approximately 50\% of any increase in life expectancy''. However,
+using a ``rule of thumb'' approach might not be ideal, as 50\% of the
+change in life expectancy may not be a good adjustment to pension age in
+the long term. Our study suggests an approach, linking the pension age
+with the the aged dependency ratio, based on forecasts of future
+mortality and fertility rates. Our approach has the advantage that it
+can be used to justify the change in pension age and directly links the
+pension age with our ultimate goal of a stable financial burden for the
+public.
+
+\subsection{Population forecasting}\label{population-forecasting}
+
+In population forecasting, two very different approaches: a
+deterministic approach (sometimes called a quasi-statistical approach)
+and a stochastic approach (a purely statistical approach) are frequently
+used. For instance, the Australian Bureau of Statistics (ABS) is using a
+deterministic approach for its demographic projection, while some other
+countries or institutes forecast demographic trends based on purely
+statistical approaches such as Statistics New Zealand and the United
+States Census Bureau. In the deterministic approach, experts project
+future demographic changes using judgement-based scenarios. It ignores
+the non-demographic factors such as major pandemics or wars, although
+historically they are important factors that affect demographic
+behaviour \autocite{PC13}. In stochastic approaches, the Lee-Carter (LC)
+method \autocite{LC92} is the most prominent demographic forecasting
+method, which now has several variants and extensions that relax some of
+the assumptions of the basic Lee-Carter method \autocite[see,
+e.g.,][]{SBH11}. Although statistical forecasting models are rigorous,
+they still leave a basis for judgment-based adaptation, as they
+sometimes produce unrealistic projections of demographic factors such as
+long-run projections of mortality rates \autocite{PC13}.
+
+Therefore, some official agencies decide to mix the two approaches in
+their forecasts in order to provide a supplement to both approaches. For
+instance, the most recent forecast of population in Australia by the
+\textcite{PC13} was based on basic Lee-Carter methods plus some
+judgement-based adaptations to address the characteristics of
+demographic trends that the Lee-Carter method failed to capture. The
+approach of forecasting used in this study is very similar to the
+\textcite{PC13}. The Hyndman-Ullah method (2007) is used as a basic
+forecasting approach, which is a comprehensive extension of Lee-Carter
+method. In addition, an adapted product-ratio method is used to
+eliminate the potential long-term divergence between female and male
+mortality rates. A more detailed review of forecasting methods is given
+below.
+
+\subsubsection{Deterministic Methods Used by the
+ABS}\label{deterministic-methods-used-by-the-abs}
+
+The deterministic method is judgment-based. The Australian Bureau of
+Statistics formulates assumptions on the basis of demographic trends, in
+conjunction with advice from individual experts or government
+departments. The projections are not predictions or forecasts, ``but are
+simply illustrations of the growth and change in population which would
+occur if certain assumptions about future levels of fertility,
+mortality, internal migration and overseas migration were to prevail
+over the projection period'' \autocite[p.2]{ABS12}. In addition, they do
+not attempt to take into account of non-demographic factors, such as
+major government policy changes and catastrophes. Therefore, they
+normally report multiple (usually three) series based on different
+levels of assumptions of demographic factors to allow for variety of
+population projections.
+
+\subsubsection{Lee-Carter Method}\label{lee-carter-method}
+
+The Lee-Carter method \autocite{LC92} is a significant milestone in
+demographic forecasting. It has been widely used to forecast mortality
+rates across various countries, including Australia.
+
+The model proposed by \textcite{LC92} is as follows:
+
 \begin{equation}
@@
 \end{equation}
-where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$.
-This model involves fitting a matrix of log central rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
-$b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$.
-$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
-
-The model is under-determined in terms of estimation of parameters.
-For example, if the vector $a,b,k$ is one solution, then for any scalar $c, a-bc, b, k+bc$ also must be one solution.
-Therefore, Lee and Carter (1992) impose the following constraints:
+
+where \(m_{x,t}\) is the central death
+rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}}
+for age \(x\) in year \(t\). This model involves fitting a matrix of log
+central rates with sets of age-specific constants, \{\(a_x\)\} and
+\{\(b_x\)\}, and a time-varying index \(k_t\). \(b_x\) is a set of
+parameters that tell us the rate at which each age responds to changes
+in \(k_t\). \(k_t\) measures the general level of the log death rates;
+\(a_x\) is the general pattern across age of the log mortality rate and
+\(\epsilon_{x,t}\) is an error term with zero mean and constant
+variance, reflecting the randomness that can't be captured by the model.
+
+The model is under-determined in terms of estimation of parameters. For
+example, if the vector \(a,b,k\) is one solution, then for any scalar
+\(c, a-bc, b, k+bc\) also must be one solution. Therefore, Lee and
+Carter (1992) impose the following constraints:
+
 \begin{equation}
@@
 \end{equation}
-Also, we normally seek the least squares solution when estimating parameters.
-However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation.
-@LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
-It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
-Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\ln(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\ln(m_{x,t})-a_x$).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\ln$ transformation.
-To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to ARIMA ($0,1,0$) model with $c\neq0$.
-
-### Hyndman-Ullah Method
-
-@HU07 proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
+
+Also, we normally seek the least squares solution when estimating
+parameters. However, in this case, the model cannot be estimated using
+simple regression methods because there is no regressor on the right
+side of the equation. \textcite{LC92} choose a singular value
+decomposition (SVD) method to undertake principal component analysis
+(PCA), and hence find the least squares solution. It has been shown that
+applying SVD method to a matrix of the logarithms of the rates after
+subtracting the average over time of the log age-specific rates can find
+the least square solution (Good, 1969). Therefore, the estimations of
+\(b_x\) and \(k_t\) are the first principal component and scores of
+\(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when
+\(\bm{X}=\ln(m_{x,t})-a_x\)). However, the empirical results suggest
+that the resulting fitted number of deaths are biased estimates of
+actual number of deaths because of the \(\ln\) transformation. To
+overcome this problem, the LC method adjusts \(k_t\) such that for each
+year, the implied number of deaths will be equal to the actual number of
+deaths. The adjusted \(k_t\) is then extrapolated using random walk with
+drift models, which is equivalent to ARIMA (\(0,1,0\)) model with
+\(c\neq0\).
+
+\subsubsection{Hyndman-Ullah Method}\label{hyndman-ullah-method}
+
+\textcite{HU07} proposed a nonparametric method for demographic
+modelling and forecasting. It extended the LC model in four ways:
+
 \begin{enumerate}
@@
 
-The model proposed by @HU07 is as follows:
+The model proposed by \textcite{HU07} is as follows:
+
 \begin{align}
@@
 \end{align}
-Equation \eqref{eq:HU_1} describes the smoothing process.
-$y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14].
-$\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms.
-Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
-It describes the dynamics of $s_t(x)$ over time.
-The $\beta_{t,j}$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\phi_j(x)$ for every $j$ is a time-varying index.
-The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation.
-The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$.
-The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively.
-In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
+
+Equation \eqref{eq:HU_1} describes the smoothing process. \(y_t(x)\) is
+the observed data in year \(t\) and age \(x\), and \(s_t(x)\) is the
+smoothed function of \(y_t(x)\), estimated by constrained weighted
+penalized regression splines \autocite{BHT14}. \(\sigma_t(x)\) allows
+the variance to be a function of time and age; and \(\epsilon_{t,x}\)
+are independent identical distributed standard normal error terms.
+Equation \eqref{eq:HU_2} has a similar structure to the LC method,
+except that it incorporates more than one principal component and score.
+It describes the dynamics of \(s_t(x)\) over time. The \(\beta_{t,j}\)
+for every \(j\) and \(\mu(x)\) are sets of age-specific constants, and
+\(\phi_j(x)\) for every \(j\) is a time-varying index. The \(e_t(x)\) is
+the model error, which is the residual function with mean zero and no
+serial correlation. The \(\mu(x)\) is estimated by the average of
+\(s_t(x)\) across years, which measures the general shape of the
+observed data \(y_t(x)\). The estimates of \(\phi_j(x)\) and
+\(\beta_{t,j}\) are the \(j\)th principal component and scores of
+\(s_t(x)-\mu(x)\) respectively. In other words, we take singular value
+decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
+
 \begin{equation*}
@@
 \end{equation*}
-We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
-
-In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
+
+We chose \(J\) in a way that we believe the majority of information for
+\(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.
+
+In terms of forecasting, by conditioning on the observed data
+\(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of
+functional principal components
+\(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the
+\(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
+
 \begin{equation}
@@
 \end{equation}
-where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$.
-Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process.
-For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
-The fitted process is given as follows:
+
+where \(\widehat{\beta}_{n+h\mid n,j}\) denotes the \(h\)-step-ahead
+forecast of \(\beta_{n+h\mid n,j}\). Because of the time-varying
+property of \(\left\{\beta_{t,j}\right\}\), it controls the dynamics of
+the process. For every component series \(\left\{\beta_{t,j}\right\}\),
+we fit them with an ARIMA\((p_j,d_j,q_j)\) process, where
+\(p_j,d_j,q_j\) are determined by minimizing the Akaike Information
+Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given
+as follows:
+
 \begin{equation*}
@@
 \end{equation*}
+
 where the parameters are estimated using maximum likelihood estimation.
 
-# Data {#sec:data}
-
-We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method.
-The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year.
-The notations are as follows:
+\section{Data}\label{sec:data}
+
+We use the same notation and similar procedures to construct data as in
+\textcite{HB08}, because the fundamental model for forecasting
+population for this study is the \textcite{HU07} method. The data used
+to construct population age structure included: age- and gender-specific
+birth and death numbers of each calendar year, age- and gender-specific
+population members on 1~January of each year, and age- and
+gender-specific exposures to risk (i.e., population of age \(x\) at 30
+June) for each year. The notations are as follows:
+
 \begin{align*}
@@
 \end{align*}
-where $x$ denotes age and $x=0,1,2,\dots,m^+$.
-$m^+$ is the open-ended upper age group, which is 100 in this study.
-$t$ denotes year and $t=1,2,\dots,n$, where $n$ is the horizon of historical data used.
-Therefore, all of those data points can be recorded in an $m\times n$ matrix.
-The super-scripts $M$ and $F$ denote male and female respectively.
-
-We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
+
+where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\) is the
+open-ended upper age group, which is 100 in this study. \(t\) denotes
+year and \(t=1,2,\dots,n\), where \(n\) is the horizon of historical
+data used. Therefore, all of those data points can be recorded in an
+\(m\times n\) matrix. The super-scripts \(M\) and \(F\) denote male and
+female respectively.
+
+We can obtain historical mortality rates \(m_t(x)\) (also called central
+death rates) and fertility rates \(f_t(x)\) as follows:
+
 \begin{align*}
@@
 
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
+In addition, the net
+migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame}
+(denoted \(G\)) is estimated using a demographic growth-balance
+equation, which is an equation to summarize the relationship between
+population change and three factors: net migration, births and deaths.
 The equation is expressed as: \todo{Please define $p$ and $^+$}
+
 \begin{align*}
@@
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$.
-The deaths are estimated using the standard life table approach of population projection.
-It should be noted that the estimated net migration includes errors in data recording.
-
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.
-The start-year population for 2015 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12.
-Even though annual mortality rates are available from 1921 to 2009, only data collected after 1950 is used for two reasons.
-First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
-Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
+
+where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of
+persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\) refers
+to migration in calendar year \(t\) of persons aged \(p-1\) and older at
+beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar
+year \(t\) of births during year \(t\); and similarly for deaths,
+\(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\). The deaths are estimated using
+the standard life table approach of population projection. It should be
+noted that the estimated net migration includes errors in data
+recording.
+
+Historical central death rates and start-year and mid-year populations
+of residents in Australia by sex and age in single years for age group
+0-99 and 100+ have been sourced from the \textcite{HMD} for 1921--2014.
+The start-year population for 2015 is also used to estimate net
+migration. Data for age-specific annual fertility rates by single years
+of age for 15-49 over the period 1950-2014 was obtained from the
+\textcite{ABS12}. Even though annual mortality rates are available from
+1921 to 2009, only data collected after 1950 is used for two reasons.
+First, the period between 1921-1950 has very different mortality
+patterns from later years because of wars and epidemics \autocite{HB08}.
+Since the model for this study is valid under the assumption that
+extrapolative methods can be used, it seemed best to delete the less
+relevant data, which might influence estimations of parameters if we
+include them. Secondly, fertility rates are only available from 1950, so
+the mortality rate was cut to fit the same period.
 \todo{Han has updated the data period.}
 
-## Forecasting Population Age Structure and OADR {#sec:forecasting}
-
-In this study, three steps were taken to simulate OADR associated with a specific pension age scheme.
-A stochastic functional model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
-age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
-The Monte Carlo simulation method was used consistently in this research.
-Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula.
-Even though the process seems complicated, it is relatively resy to implement using \textit{R}.
-The detailed explanation of each step is as follows.
-The corresponding R code is attached in Appendix B.
+\subsection{Forecasting Population Age Structure and
+OADR}\label{sec:forecasting}
+
+In this study, three steps were taken to simulate OADR associated with a
+specific pension age scheme. A stochastic functional model was applied
+to five components of population change: female mortality rates, male
+mortality rates, female net migration, male net migration and fertility
+rates to simulate these five components over the prediction horizon
+(which is 50 years in this study). age- and gender-specific population
+paths over the prediction horizon were simulated using the demographic
+growth-balance equation. The Monte Carlo simulation method was used
+consistently in this research. Finally, calculation of OADR associated
+with a specific pension age scheme was performed by applying the OADR
+formula. Even though the process seems complicated, it is relatively
+resy to implement using \textit{R}. The detailed explanation of each
+step is as follows. The corresponding R code is attached in Appendix B.
 \todo{There is no appendix, Han recommends to put the R code as a supplement}
 
-### Step 1 {-}
-
-The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
-The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
-Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
-However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13].
-In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
+\subsubsection*{Step 1}\label{step-1}
+\addcontentsline{toc}{subsubsection}{Step 1}
+
+The main procedure for forecasting the population age structure follows
+\textcite{HB08}, except that the data is updated, and we incorporate the
+product-ratio method \autocite{HBY13} to improve the accuracy of the
+forecast. The \textcite{HU07} model, introduced in section 2.3.2, is
+applied to the mortality rate, fertility rate and net migration
+separately, based on the assumption that they behave independently.
+Therefore, to fit the model to historical fertility rates, let
+\(y_t(x)\) in equation \eqref{eq:HU_1} denote the observed historical
+fertility data. However, for mortality rate by sex, the product-ratio
+method is used to ensure the forecast of females and males are
+non-divergent or coherent \autocite{HBY13}. In the product-ratio method,
+after smoothing the female and male mortality rates, two other series
+were created: product series (denoted by \(p_t(x)\)) and ratio series
+(denoted by \(r_t(x)\)), which are defined as follows:
+
 \begin{align}
@@
 \end{align}
-Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
+
+Then, \textcite{HU07} was applied to these two new variables instead of
+male and female mortality rate as follows:
+
 \begin{align*}
@@
 \end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$).
-It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
-Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
-From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
+
+where time series \(\left\{\beta_{t,j}\right\}\) are fitted with an
+ARIMA model while \(\left\{\gamma_{t,l}\right\}\) are fitted by
+stationary ARFIMA model (i.e., \(d\) in ARIMA(\(p,d,q\)) constrained to
+\(0<d<\frac{1}{2}\)). It is the stationary constraint on
+\(\gamma_{t,l}\) that ensures the forecast of male and female do not
+diverge. Then, simulation h-step-ahead forecast values of product
+variable and ratio variable was performed (denoted by
+\(p_{n+h\mid n}(x)\) and \(r_{n+h\mid n}(x)\) respectively) according to
+\eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining
+h-step-ahead forecast of sex-specific coherent mortality rates (denoted
+\(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was performed using a
+back-transformation:
+
 \begin{align*}
@@
 \end{align*}
-The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration.
-A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.
-
-### Step 2 {-}
-
-After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
-The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
-Hence, we can simulate $h$-step-ahead age- and gender-specific births and deaths based on simulated mortality and fertility rates.
-According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age.
-This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population.
-The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research).
-It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
-It should be noted that the simulated population will be an array with three dimensions: age, year and simulation.
-
-### Step 3 {-}
-
-Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time.
-To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations.
-Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
-We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age.
-The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
-Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers.
-We will also show how this issue was handled in the example below.
-
-Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age.
-Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
+
+The method for simulating \(h\)-step-ahead values of net migration by
+sex is similar to the above method used on mortality rates except no log
+scale is applied to net migration. A stationary constraint was imposed
+on the ARIMA model for net migration to make sure the difference between
+sexes did not diverge.
+
+\subsubsection*{Step 2}\label{step-2}
+\addcontentsline{toc}{subsubsection}{Step 2}
+
+After simulating paths for age-specific fertility rate, age- and
+gender-specific mortality rate and age- and gender-specific net
+migration, future population value were simulated using the demographic
+growth-balance equations over the prediction horizon. The future deaths
+and births in this equation are assumed to follow Poisson distribution,
+with parameters as a function of future mortality and fertility rates
+(see Hyndman and Booth, 2008 for the details of the functions). Hence,
+we can simulate \(h\)-step-ahead age- and gender-specific births and
+deaths based on simulated mortality and fertility rates. According to
+the demographic growth-balance equation, one-step-ahead net migrations,
+deaths, births and population in the last year were simulated, allowing
+for the generation of one-step-ahead population predictions by sex and
+age. This simulation was repeated for years \(t=n+1,\dots,n+h\) to
+obtain a path of population. The process was repeated and simulated
+\(i\) paths of population based on Monte Carlo simulation method were
+created (we set \(i=1000\) in these research). It should be noted that
+there are three types of randomness in the simulation: randomness from
+the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\)
+in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal
+component scores and randomness from the Poisson distribution. It should
+be noted that the simulated population will be an array with three
+dimensions: age, year and simulation.
+
+\subsubsection*{Step 3}\label{step-3}
+\addcontentsline{toc}{subsubsection}{Step 3}
+
+Even though the OADR is a simple function of the population age
+structure and pension age, the formula can't be directly applied to the
+simulated population array because the pension age changes over time. To
+overcome this problem, we assume that the pension age can only be
+adjusted at the beginning of a year for these calculations. Therefore,
+one pension age is applicable for a whole year and hence OADR is
+generated at the beginning of each year to show the trend. We will show
+the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR
+in year 2011), given a specific pension age. The same method can be
+applied to all years over the prediction horizon, given their
+corresponding pension age. Further, the fractional pension age causes
+practical issues in calculating OADR, since ages are recorded as
+integers. We will also show how this issue was handled in the example
+below.
+
+Suppose the pension age for \(n+1\) is \(a.r\) where \(a\) is the
+integer and and \(r\) is the reminder of pension age. Recall that for
+\(h=1\), we can express the simulated population paths as a matrix with
+age in the row and simulation in the column as follows:
+
 \begin{equation*}
@@
 \end{equation*}
-When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
+
+When \(r=0\), then the simulation of a population aged 15 to pension age
+is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\)
+row, which is:
+
 \begin{equation}
@@
 \end{equation}
-To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
+
+To calculate the total number of working age, we take a column sum of
+the trimmed matrix \eqref{eq:population_mat}. The simulations of total
+number of work age become a vector:
+
 \begin{equation}
@@
 \end{equation}
-Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
+
+Using the same method, the simulations of total number of aged
+pensioners in the population can be shown as:
+
 \begin{equation}
@@
 
-When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
+When \(r\neq0\), the vector of total number of working age population in
+\eqref{eq:work} is added, and the vector of total number of aged
+population in \eqref{eq:aged} is subtracted with an adjustment:
+
 \begin{equation}
@@
 \end{equation}
-This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year.
-Then, $r\times100\%$ of population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age.
-In other words, $(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population.
-The simulation vectors of total work age population and total aged population should then be: \todo{Han feel the second equation does not have \%?}
+
+This adjustment is based on the assumption that the birthday of
+population is uniformly distributed over the year. Then,
+\(r\times100\%\) of population with a recorded integer age of \(a\) at
+beginning of the year is actually younger than \(a.r\), so they are
+still under the pension age. In other words, \((1-r\times100\%)\) of
+population with recorded integer age \(a\) at beginning of the year is
+actually older than \(a.r\), so they should be counted as the aged
+population. The simulation vectors of total work age population and
+total aged population should then be:
+\todo{Han feel the second equation does not have \%?}
+
 \begin{align*}
@@
 
-After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{\text{work}}_{n+1}$ by the corresponding element of $\bm{p}^{\text{aged}}_{n+1}$, i.e.:
+After the adjustment, we can generate simulation vectors of the
+one-step-ahead OADR by dividing every element of
+\(\bm{p}^{\text{work}}_{n+1}\) by the corresponding element of
+\(\bm{p}^{\text{aged}}_{n+1}\), i.e.:
+
 \begin{align*}
@@
 \end{align*}
-The average value of elements of $\bm{\text{OADR}}_{n+1}$ is the mean prediction of one-step-ahead OADR.
-
-The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2015 to 2064).
-Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
+
+The average value of elements of \(\bm{\text{OADR}}_{n+1}\) is the mean
+prediction of one-step-ahead OADR.
+
+The same algorithm is applied to the simulation matrix of the population
+age structure to obtain \(h\)-step-ahead simulation vectors of OADR for
+\(h=1,2,\dots,H\), where \(H=50\) for this study (i.e., a prediction
+horizon of 2015 to 2064). Simulations of OADR over a 50 year prediction
+horizon by the matrix is summarised below, with the forecast year in
+rows and simulation in the columns:
+
 \begin{equation}
@@
 
-## Results
-
-```{r getdata, include=FALSE}
-############################
-## GET ALL THE DATA
-############################
-
-# HMD credentials
-username <- "shl8858@telstra.com"
-password <- "hshang85"
-
-hmd.pop <- function (country, username, password, label = country) 
-{
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Population.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(pop) == "try-error") 
-        stop("Population file not found at www.mortality.org")
-    obj <- list(type = "population", label = label, lambda = 0)
-    obj$year = sort(unique(pop[, 1]))
-    n <- length(obj$year)
-    m <- length(unique(pop[, 2]))
-    obj$age <- pop[1:m, 2]
-    mnames <- names(pop)[-c(1, 2)]
-    n.pop <- length(mnames)
-    obj$pop <- list()
-    for (i in 1:n.pop) {
-        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
-        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
-        dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
-    }
-    names(obj$pop) <- tolower(mnames)
-    obj$age <- as.numeric(as.character(obj$age))
-    if (is.na(obj$age[m])) 
-        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
-    return(structure(obj, class = "demogdata"))
-}
-
-hmd.mx <- function (country, username, password, label = country) 
-{
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Mx_1x1.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    mx <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(mx) == "try-error") 
-        stop("Connection error at www.mortality.org. Please check username, password and country label.")
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Exposures_1x1.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(pop) == "try-error") 
-        stop("Exposures file not found at www.mortality.org")
-    obj <- list(type = "mortality", label = label, lambda = 0)
-    obj$year <- sort(unique(mx[, 1]))
-    n <- length(obj$year)
-    m <- length(unique(mx[, 2]))
-    obj$age <- mx[1:m, 2]
-    mnames <- names(mx)[-c(1, 2)]
-    n.mort <- length(mnames)
-    obj$rate <- obj$pop <- list()
-    for (i in 1:n.mort) {
-        obj$rate[[i]] <- matrix(mx[, i + 2], nrow = m, ncol = n)
-        obj$rate[[i]][obj$rate[[i]] < 0] <- NA
-        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
-        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
-        dimnames(obj$rate[[i]]) <- dimnames(obj$pop[[i]]) <- list(obj$age, 
-            obj$year)
-    }
-    names(obj$pop) = names(obj$rate) <- tolower(mnames)
-    obj$age <- as.numeric(as.character(obj$age))
-    if (is.na(obj$age[m])) 
-        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
-    return(structure(obj, class = "demogdata"))
-}
-
-# Get population data for 1 Jan 2015
-auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
-auspop <- extract.ages(auspop, age = 0:100)
-
-# Get mortality data
-aus.mort <- hmd.mx("AUS", username, password, "Australia")
-aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
-  combine.upper = FALSE
-),
-year = 1950:max(aus.mort$year)
-)
-
-# Get fertility data:
-# Need to install addb package from http://robjhyndman.com/software/addb/
-library(addb) # Contains fertility data for 1921-2006
-aus.fert <- aus.fertility
-births <- aus.fert$rate$female * aus.fert$pop$female
-# Update fertility data to 2015
-ausf <- read.csv("FERTILITY_AGE_STATE_16062017173020984.csv",
-  header = TRUE,
-  stringsAsFactors = FALSE
-)
-# National births only
-ausf <- ausf[ausf$Region == "Australia", ]
-# Remove age aggregations
-ausf <- ausf[ausf$Age %in% paste(15:49), ]
-ausf[, "Age"] <- as.numeric(ausf[, "Age"])
-# Extract births and population values
-newbirths <- matrix(ausf[ausf$Measure == "Births", "Value"],
-  nrow = nrow(births), byrow = TRUE
-) * 1000
-newpop <- matrix(ausf[ausf$Measure == "Female population", "Value"],
-  nrow = nrow(births), byrow = TRUE
-) * 1000
-rownames(newbirths) <- rownames(newpop) <- 15:49
-colnames(newbirths) <- colnames(newpop) <- 2004:2015
-births <- cbind(births[, 1:83], newbirths)
-fpop <- cbind(aus.fert$pop$female[, 1:83], newpop / 1000)
-# Use populations in ausf rather than auspop to get the same rates
-aus.fert$rate$female <- births / fpop
-aus.fert$pop$female <- fpop
-aus.fert$year <- 1921:2015
-
-aus.fert_v0 = extract.years(aus.fert, 1921:2014)
-
-##### MIGRATION
-aus.mig <- netmigration(mort = aus.mort, fert = aus.fert_v0, mfratio = 1.05)
-```
-
-```{r smoothing, dependson='getdata'}
-################################################
-################ SMOOTHING STEP ################
-################################################
-
-ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
-ausfert.sm <- smooth.demogdata(aus.fert_v0, obs.var = "theoretical")
-ausmig.sm <- smooth.demogdata(aus.mig)
-```
-
-```{r models, dependson='smoothing'}
-################################################
-################ MODELLING STEP ################
-################################################
-
-# MORTALITY
-mort.fit <- coherentfdm(ausmort.sm)
-mortf <- forecast(mort.fit, h = 50)
-
-# FERTILITY
-fert.fit <- fdm(ausfert.sm)
-fertf <- forecast(fert.fit, h = 50)
-
-# MIGRATION
-mig.fit <- coherentfdm(ausmig.sm)
-migf <- forecast(mig.fit, h = 50)
-```
-
-We use the fitted model of fertility rates as an example to interpret the results of fitted models.
-It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
-Figure \ref{fig:componentsfertility} above shows the mean age pattern ($\mu(x)$), the first two basis functions ($\phi_1(x)$ and $\phi_2(x)$) and first two coefficients (i.e., principal component scores $\beta_{t,1}$ and $\beta_{t,2}$) for fertility rates.
-The first term ($\phi_1(x)*\beta_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of coefficient 1,
-estimated historical first principal component scores $\beta_{t,1}$ are shown in black for 1950-2009.
-It captures the general trend of fertility change over time.
-It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
-The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
-A  noticeable further reduction of fertility rates in late 1960s may be due to a change in the law allowing abortion in some states in Australia.
-
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates.", dependson='models'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
-plot(fertf, "c", comp = 2)
-```
-
-The first basis function $\phi_1(x)$ measures the different effects of the trend over time across ages.
-It indicates the general pattern of fertility has very little effect on females of age 15.
-This makes intuitive sense because most early pregnancies are accidental, therefore, any of previously discussed events has no effect on early pregnancies.
-In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-Furthermore, the blue line is the fitted value of future coefficients (i.e., $\beta_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% prediction interval according to the fitted ARIMA model of first coefficients $\left\{\beta_{t,1}\right\}$.
-Other terms further explain variation that has not been captured by first term, but less economic explanations can be given for them.
-
-```{r simulation, dependson='models'}
-############### SIMULATION STEP #################
-# This takes a while!
-set.seed(2019-01-04)
-nsim <- 20 # Change to 2000 or higher to get better estimates
-aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
-```
-
-```{r simulationresults}
-## Means and intervals
-popm.mean <- apply(aus.sim$male, c(1, 2), mean, na.rm = TRUE)
-popm.lo <- apply(aus.sim$male, c(1, 2), quantile, p = .1, na.rm = TRUE)
-popm.hi <- apply(aus.sim$male, c(1, 2), quantile, p = .9, na.rm = TRUE)
-popf.mean <- apply(aus.sim$female, c(1, 2), mean, na.rm = TRUE)
-popf.lo <- apply(aus.sim$female, c(1, 2), quantile, p = .1, na.rm = TRUE)
-popf.hi <- apply(aus.sim$female, c(1, 2), quantile, p = .9, na.rm = TRUE)
-
-## TOTAL POPULATION COMPARISONS
-totfpop <- apply(aus.sim$female, c(2, 3), sum, na.rm = TRUE)
-totmpop <- apply(aus.sim$male, c(2, 3), sum, na.rm = TRUE)
-totfpop.q <- apply(totfpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
-totmpop.q <- apply(totmpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
-```
-
-```{r totalpopulationbyyears, fig.cap="Fifth-year forecasts of total population for each sex, along with 80% prediction intervals.
-The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
-par(mfrow = c(1, 2))
-fy <- fertf$year
-plot(auspop$year, colSums(auspop$pop$female) / 1e6,
-  xlim = c(1975, 2030),
-  ylim = range(c(7, 17), na.rm = TRUE),
-  xlab = "Year",
-  ylab = "Population (millions)",
-  main = "Total female population"
-)
-polygon(c(fy, rev(fy)),
-  c(totfpop.q[2, ], rev(totfpop.q[4, ])),
-  col = "yellow", border = FALSE
-)
-lines(fy, totfpop.q[3, ], lwd = 2, col = "blue")
-
-plot(auspop$year, colSums(auspop$pop$male) / 1e6,
-  xlim = c(1975, 2030),
-  ylim = range(c(7, 17), na.rm = TRUE),
-  xlab = "Year",
-  ylab = "Population (millions)",
-  main = "Total male population"
-)
-polygon(c(fy, rev(fy)),
-  c(totmpop.q[2, ], rev(totmpop.q[4, ])),
-  col = "yellow", border = FALSE
-)
-lines(fy, totmpop.q[3, ], lwd = 2, col = "blue")
-```
-
-```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals.
-The actual pyramid for 2010 is shown using dashed lines.", , dependson='simulationresults'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(4.3, 3.6, 3.0, 3.3))
-plot(c(0, 100), c(0, 100),
-  type = "n", main = "Forecast population: 2035", yaxt = "n",
-  xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
-)
-mtext("Male                       Female")
-abline(v = 0)
-axis(1, at = seq(-300, 0, by = 50), labels = rev(seq(0, 300, by = 50)))
-axis(1, at = seq(50, 300, by = 50))
-axis(2, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
-axis(4, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
-axis(2, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
-axis(4, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
-axis(4, at = 50, line = 1.5, labels = "Age", col = 2, tick = FALSE)
-polygon(c(-popm.lo[, 20], rev(-popm.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
-polygon(c(popf.lo[, 20], rev(popf.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
-lines(-auspop$pop$male[, ncol(auspop$pop$male)] / 1000, 0:100, col = 1, lty = 2)
-lines(auspop$pop$female[, ncol(auspop$pop$female)] / 1000, 0:100, col = 1, lty = 2)
-text(100, 60,  "2015")
-text(-100, 60, "2015")
-lines(-popm.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
-lines(popf.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
-```
-
-Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2028} show the forecast results of population.
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2028.
-\ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to 18 million by 2060.
-Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
-We can also observe that the further the projected year is, the bigger the forecast variation of population.
-This increase in variation shows that we have less relevant information for further apart prediction horizons.
-
-Figure \ref{fig:totalpopulationin2028} shows the mean and the 80% prediction interval of simulated population paths for year 2028, along with the 2010 base population.
-It can be observed that overall population size is expected to increase substantially.
-The uncertainty of population of infant is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates.
-The uncertainty of the young age population is mainly due to migration [@HB08].
-
-```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", dependson='simulationresults'}
-OADR.f <- oadr(auspop, aus.sim, pension.age = current)
-autoplot(OADR.f) + xlab("year") + ylab("ratio") +
-  ggtitle("OADR forecasts with pension age=65")
-```
-
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The actual OADRs for 1950-2010 are shown in black.", dependson='OADRat65'}
-OADR.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
-OADR.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
-autoplot(OADR.f$x) +
-  geom_hline(yintercept = 0.21, col = "gray") +
-  autolayer(OADR.f, series = "current", alpha = 0.5) +
-  autolayer(OADR.f.67, series = "approved", alpha = 0.5) +
-  autolayer(OADR.f.prop, series = "proposed", alpha = 0.5) +
-  ylab("ratio") + xlab("Year") +
-  ggtitle("OADR forecasts") +
-  scale_color_manual(
-    values = cols, name = " ",
-    breaks = c("current", "approved", "proposed"),
-    labels = c("Pension age at 65", "Approved change", "Proposed further change")
-  )
-```
-
-Analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
-Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \ref{fig:OADRat65} shows the mean forecast and prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1920-2010.
-A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
-This is consistent with the prediction by inter-generation reports in 2002 [@IGR02] and in 2007 [@IGR07].
-According to former Australian Treasurer @Costello04, this could be a result of better health care and low fertility rates.
-These two reasons could be regarded as permanent change and therefore a persistent trend.
-In addition, there is a big jump from actual data to predicted data.
-This jump is possibly a result of the Baby Boomers’ retirement.
-Those born in 1946, the start of the baby boom, would begin retiring in 2011 when the pension age was 65.
-
-Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21%.
-It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment.
-However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at nearly same rate as the OADR of a pension age equal of 65.
-This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Therefore, Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
-However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
-This answer will allow us to respond to the recent proposal of further increasing pension age to 70 by 2035.
-
-## Evaluating Forecast Accuracy {#sec:accuracy}
-
-Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
-It is not valid to assess the model's fit in terms of historical data.
-We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
-Therefore, we will use a Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to evaluate the accuracy of the models used in this paper.
-
-The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $F$ \todo{Han thinks $H$?} prediction horizon.
-Then we are allowed to repeat the test $n-F-k+1$ \todo{Han thinks $n-H-k+1$} times, where $n$ is the number of total years of observation.
-The procedure is as follows:
-
-Let $i=1$, we first select historical data for a time interval of $[i,i+1,\dots,i+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
-Then, we can calculate the difference of forecasted OADR over the period $[i+k,i+k+1,\dots,i+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
-We repeat the following steps for $i=1,2,\dots,n-k-H+1$.
-Then, we can summary the information into a matrix as follows:
+\subsection{Results}\label{results}
+
+We use the fitted model of fertility rates as an example to interpret
+the results of fitted models. It should be noted that models fitted to
+product and ratio series are less likely to be interpreted in an
+economic sense. Figure \ref{fig:componentsfertility} above shows the
+mean age pattern (\(\mu(x)\)), the first two basis functions
+(\(\phi_1(x)\) and \(\phi_2(x)\)) and first two coefficients (i.e.,
+principal component scores \(\beta_{t,1}\) and \(\beta_{t,2}\)) for
+fertility rates. The first term (\(\phi_1(x)*\beta_{t,1}\)) accounts for
+the most variation in fertility, so a relatively sensible interpretation
+can be given to the first term. In the plot of coefficient 1, estimated
+historical first principal component scores \(\beta_{t,1}\) are shown in
+black for 1950-2009. It captures the general trend of fertility change
+over time. It indicates a sharp increase between 1950-1960, followed by
+a rapid decline of fertility rates from 1961. This increase of fertility
+is linked to the Post-World War II baby
+boom\footnote{Between the years 1946 and 1964} in Australia, resulting
+from the recovery from war and the Great
+Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
+The dramatic decrease from 1960 was due to the availability of
+contraception pills in Australia. A noticeable further reduction of
+fertility rates in late 1960s may be due to a change in the law allowing
+abortion in some states in Australia.
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/componentsfertility-1.pdf}
+\caption{\label{fig:componentsfertility}Fitted basis functions and
+coefficients for Australian fertility rates.}
+\end{figure}
+
+The first basis function \(\phi_1(x)\) measures the different effects of
+the trend over time across ages. It indicates the general pattern of
+fertility has very little effect on females of age 15. This makes
+intuitive sense because most early pregnancies are accidental,
+therefore, any of previously discussed events has no effect on early
+pregnancies. In addition, there are two spikes in the first basic
+function, which suggests that the historical trend has a distinct impact
+on females aged around their 20s and 40s. Furthermore, the blue line is
+the fitted value of future coefficients (i.e., \(\beta_{n+h,1}\), for
+\(h=1,2,\dots,50\)) and the yellow shading shows their 80\% prediction
+interval according to the fitted ARIMA model of first coefficients
+\(\left\{\beta_{t,1}\right\}\). Other terms further explain variation
+that has not been captured by first term, but less economic explanations
+can be given for them.
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/totalpopulationbyyears-1.pdf}
+\caption{\label{fig:totalpopulationbyyears}Fifth-year forecasts of total
+population for each sex, along with 80\% prediction intervals. The
+actually population from 1950 to 2015 is shown using circles.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/totalpopulationin2028-1.pdf}
+\caption{\label{fig:totalpopulationin2028}Forecast population pyramid for
+2028, along with 80\% prediction intervals. The actual pyramid for 2010
+is shown using dashed lines.}
+\end{figure}
+
+Both Figures \ref{fig:totalpopulationbyyears} and
+\ref{fig:totalpopulationin2028} show the forecast results of population.
+Figure \ref{fig:totalpopulationbyyears} shows the forecast of total
+population by gender over the prediction horizon, while Figure
+\ref{fig:totalpopulationin2028} shows the forecast of population age
+structure in a specific year, 2028. \ref{fig:totalpopulationbyyears}
+indicates that both the female and male population are expected to
+increase to 18 million by 2060. Since the fertility rate is expected to
+remain low, the possible reason of the significant increase in
+population size is net migration. We can also observe that the further
+the projected year is, the bigger the forecast variation of population.
+This increase in variation shows that we have less relevant information
+for further apart prediction horizons.
+
+Figure \ref{fig:totalpopulationin2028} shows the mean and the 80\%
+prediction interval of simulated population paths for year 2028, along
+with the 2010 base population. It can be observed that overall
+population size is expected to increase substantially. The uncertainty
+of population of infant is much higher than other ages, which reflects
+the higher forecast variation of fertility rates than mortality rates.
+The uncertainty of the young age population is mainly due to migration
+\autocite{HB08}.
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/OADRat65-1.pdf}
+\caption{\label{fig:OADRat65}Fifty-year forecasts of the OADR with
+assumption of pension age equal to 65 for both sexes, along with 80\%
+prediction interval.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/OADRcurrent-1.pdf}
+\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated
+with a pension age equal to 65 (black line) and equal to the pension age
+scheme with approved change (red line) respectively, along with the
+desired OADR level in grey (i.e., mean forecast of OADR in 2014). The
+actual OADRs for 1950-2010 are shown in black.}
+\end{figure}
+
+Analysis was performed by first generating an OADR associated with a
+fixed pension age of 65 and an OADR associated with pension age scheme
+with approved change, gradually increasing the pension age from 65 to 67
+by mid-2023. Even though the government might further increase the
+pension age in future, we kept the pension age at 67 from 2024 to see
+what would happen if no further action was taken. Figure
+\ref{fig:OADRat65} shows the mean forecast and prediction interval of
+the OADR with a pension age of 65, along with the historical OADR for
+1920-2010. A strong positive trend was observed, which indicates an
+increasing burden on the next working-age generation if the pension age
+is fixed at 65. This is consistent with the prediction by
+inter-generation reports in 2002 \autocite{IGR02} and in 2007
+\autocite{IGR07}. According to former Australian Treasurer
+\textcite{Costello04}, this could be a result of better health care and
+low fertility rates. These two reasons could be regarded as permanent
+change and therefore a persistent trend. In addition, there is a big
+jump from actual data to predicted data. This jump is possibly a result
+of the Baby Boomers' retirement. Those born in 1946, the start of the
+baby boom, would begin retiring in 2011 when the pension age was 65.
+
+Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast
+of OADR with the pension age equal to 65 and a pension age equal to the
+pension age scheme with approved change, along with comparison of both
+forecasts with desired level of OADR, which has been set at 21\%. It
+should be noted that OADR corresponding to pension age scheme with
+approved change is approaching the desired level, which suggests that
+the approved change does achieve the aim of providing an affordable
+financial burden, at least for a moment. However, once the pension age
+reaches 67, the OADR of the pension scheme with approved adjustment
+grows at nearly same rate as the OADR of a pension age equal of 65. This
+is consistent with the idea that there is a persistent positive trend in
+OADR associated with a constant pension age, due to low fertility rates
+and better health care. Therefore, Figure \ref{fig:OADRcurrent}
+demonstrates that the pension age scheme requires constant review to
+ensure a stable OADR over the long term. However, the questions of when
+the action needs to be taken and how much of an adjustment needs to be
+made remain to be answered. This answer will allow us to respond to the
+recent proposal of further increasing pension age to 70 by 2035.
+
+\subsection{Evaluating Forecast Accuracy}\label{sec:accuracy}
+
+Since all the results and implications are dependent on the forecast
+accuracy, it is important to evaluate the accuracy of our forecast. It
+is not valid to assess the model's fit in terms of historical data. We
+are concerned with how well a model performs on out-of-sample data,
+which is known but not used to fit the model. Therefore, we will use a
+Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to
+evaluate the accuracy of the models used in this paper.
+
+The logic of a Cross-Validation test is to use a portion of available
+data for fitting, and use the remaining data to test. Suppose we need
+\(k\) years' observations to produce a reliable
+forecast\footnote{$k$ can't be too small}, we are interested in the
+\(F\) \todo{Han thinks $H$?} prediction horizon. Then we are allowed to
+repeat the test \(n-F-k+1\) \todo{Han thinks $n-H-k+1$} times, where
+\(n\) is the number of total years of observation. The procedure is as
+follows:
+
+Let \(i=1\), we first select historical data for a time interval of
+\([i,i+1,\dots,i+k-1]\) as ``in sample data'' to fit the model, and then
+forecast \(H\) years'
+OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Then, we can calculate the difference of forecasted OADR over the period
+\([i+k,i+k+1,\dots,i+k+H-1]\) from the real OADR for the same period,
+which is known as absolute error. We repeat the following steps for
+\(i=1,2,\dots,n-k-H+1\). Then, we can summary the information into a
+matrix as follows:
+
 \begin{equation}
@@
 \end{equation}
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,i}=\left|\text{OADR}^{mean}_{h,i}-\text{OADR}^{real}_{h,i}\right|$.
-This process is also known as "rolling forecasting origin", because the "origin" ($k+i-1$) at which the forecast is based rolls forward in time.
-We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR  where $h=1,2,\dots,H$.
-
-```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
-######## Run a rolling forecast origin
-# replace 2010 by 2014 (Han?)
-t <- 2010 - 1950 + 1
-H <- 25 ## forecast horizon for test
-k <- 25 ## years of data required to make a forecast
-oadrtest <- matrix(0, 25, t - k - H)
-for (i in 1:(t - k - H))
-{
-    ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
-    ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
-    ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
-    pop.short <- extract.years(auspop, years = 1949 + i + (0:k))
-    mort.fit.s <- coherentfdm(ausmort.short)
-    mortfs <- forecast(mort.fit.s, H)
-    fert.fit.s <- fdm(ausfert.short)
-    # Fix problem
-    #  miss <- is.na(fert.fit.s$residuals$y)
-    #  fert.fit.s$residuals$y[miss] <- 0
-    # End fix
-    fertfs <- forecast(fert.fit.s, H)
-    mig.fit.s <- coherentfdm(ausmig.short)
-    migfs <- forecast(mig.fit.s, H)
-    aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs, firstyearpop = pop.short, 
-                         N = 3)
-    OADR.fs <- oadr(pop.short, aus.sim.s)
-    oadrtest[, i] <- OADR.fs$mean
-}
-oadr.real <- oadr(auspop, aus.sim)$x
-oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
-for (i in 1:25)
-  oadr.real.mat[i, ] <- oadr.real[(i + 59):(59 + 11 + i)]
-
-oadr.error <- abs(oadrtest - oadr.real.mat[, 1:11])
-oadrave <- apply(oadr.error, 1, mean)
-
-plot(oadrave, xlab = "forecast horizon", ylab = "mean ")
-```
-
-In our sample, $n=2010-1950+1=61$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \ref{fig:rollingtest}.
-From this figure, we observe that the absolute mean error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is very small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.5%, which is very small if compared to the desired level of OADR, which is at 21%.
-
-It would normally be ideal to compare the mean absolute error of the forecast from our model to other available models to measure the accuracy.
-For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
-However, we are not able to actually perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
-
-# Finding the Target Pension Age Scheme {#sec:target}
-
-The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level.
-According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
-Suppose we denote pension age schemes over the prediction horizon by $\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]$.
-The OADR function of pension age over the prediction horizon is denoted as $OADR_h(\text{PA}_{n+h})$ for $h=1,2,\dots,H$.
-There is a negative relationship between pension age and OADR.
-The negative relationship implies that the higher the pension age, the lower the OADR.
-Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level.
-Several practical issues need to be considered to achieve this goal.
-First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR.
-Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
-Therefore, the target pension age scheme $\bm{\text{PA}}^{target}$ can be defined in the following way:
-for $h=1,2,\dots,H$
+
+where \(h\) denotes for the forecast horizon and
+\(\text{AE}_{h,i}=\left|\text{OADR}^{mean}_{h,i}-\text{OADR}^{real}_{h,i}\right|\).
+This process is also known as ``rolling forecasting origin'', because
+the ``origin'' (\(k+i-1\)) at which the forecast is based rolls forward
+in time. We take the average of each row to obtain an absolute mean
+error of \(h\)-step-ahead forecast of OADR where \(h=1,2,\dots,H\).
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/rollingtest-1.pdf}
+\caption{\label{fig:rollingtest}The mean absolute error of \(h\)-step-ahead
+forecast for \(h=1,2,\dots,25\).}
+\end{figure}
+
+In our sample, \(n=2010-1950+1=61\) and we set \(k=25\) and \(H=25\) to
+perform the test. The mean absolute error of \(h\)-step-ahead forecast
+of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
+From this figure, we observe that the absolute mean error is increasing
+as \(h\) increases, which is reasonable as we have less relevant
+information to make a forecast for further apart OADR. Overall, the mean
+absolute error is very small. For example, the mean absolute error for
+25-step-ahead forecast is 1.5\%, which is very small if compared to the
+desired level of OADR, which is at 21\%.
+
+It would normally be ideal to compare the mean absolute error of the
+forecast from our model to other available models to measure the
+accuracy. For example, suppose we can take the population projections
+from ABS reports over the last few decades, their projection of
+population age structure reported in different years can be used to
+mimic the rolling origin test of OADR, because we now have the real OADR
+for those projected years. However, we are not able to actually perform
+it because full projection data is no longer available online and ABS
+projections have not used a consistent and replicate methodology.
+
+\section{Finding the Target Pension Age Scheme}\label{sec:target}
+
+The goal of this research is to keep the pension age low, as long as
+OADR is lower than or equal to the desired OADR level. According to the
+formula of OADR, OADR at a given time can be written as a function of
+pension age, when the population age structure is given. Suppose we
+denote pension age schemes over the prediction horizon by
+\(\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]\).
+The OADR function of pension age over the prediction horizon is denoted
+as \(OADR_h(\text{PA}_{n+h})\) for \(h=1,2,\dots,H\). There is a
+negative relationship between pension age and OADR. The negative
+relationship implies that the higher the pension age, the lower the
+OADR. Therefore, our goal becomes finding the minimum pension age which
+has an OADR lower than desired OADR level. Several practical issues need
+to be considered to achieve this goal. First, only simulated forecasting
+values of future OADR are available, so it is assumed that the mean
+value of the simulated OADR is a good estimate of true underlying OADR.
+Second, pension age cannot be increased by more than one within a year
+or decreased because either one of the two actions will force some
+retirees back to the workforce, which is unreasonable in practical
+applications. Therefore, the target pension age scheme
+\(\bm{\text{PA}}^{target}\) can be defined in the following way: for
+\(h=1,2,\dots,H\)
+
 \begin{equation}
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation}
-\begin{align*}
+\end{equation}\begin{align*}
   \text{subject to the constraint~} 0\leq \text{PA}_{n+h}-\text{PA}_{n+h-1}\leq 1
 \end{align*}
-In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
-It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
+
+In order to achieve this maximization subject to constraint, these
+calculations assume that the adjustment unit of pension age is one month
+for practical convenience. It is also supposed that the set starting
+value of pension age is at 65 for all
+years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
 The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in 2017 onward}, which is:
+This simplification is reasonable because the pension age will be same in 2017 onward},
+which is:
+
 \begin{align*}
@@
 \end{align*}
-We take the following algorithm:
-For $h=1,2,\dots,H$, we keep increasing pension age vector $[\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]$ by a month at a time, unless we find that
+
+We take the following algorithm: For \(h=1,2,\dots,H\), we keep
+increasing pension age vector
+\([\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]\) by a month
+at a time, unless we find that
+
 \begin{align}
@@
 \end{align}
-where $\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $\text{PA}_{n+h}$.
-
-In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
-To be more specific, "plausible", means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
-Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
-Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as 80% confidence interval of pension age scheme where we are 80% sure that there will be a desired outcome.
-In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.
-
-The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR in equation (28) is replaced by the boundary of the 80% prediction interval.
-Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.
-
-## Plausible Pension Age Schemes
-
-```{r pension, dependson="OADRat65"}
-### find the optimal scheme of pension.age based on mean forecast
-target <- OADR.f$mean[4]
-
-pension.age <- proposed
-for (i in 6:50)
-{
-  current <- oadr(auspop, aus.sim,
-    pension.age = pension.age
-  )$mean[i]
-  while ((current > target) &
-    (max(diff(pension.age[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension.age[i:50] <- pension.age[i:50] + 1 / 12
-    current <- oadr(auspop, aus.sim,
-      pension.age = pension.age
-    )$mean[i]
-  }
-}
-OADR.f.optimal <- oadr(auspop,
-  aus.sim,
-  pension.age = pension.age
-)
-```
-
-```{r pensionupper, dependson="simulationresults"}
-### find the upper boundary of pension ages whose prediction interval contains target
-pension.age.upper <- proposed
-for (i in 6:50)
-{
-  current.upper <- oadr(auspop, aus.sim,
-    pension.age = pension.age.upper
-  )$upper[i]
-  while ((current.upper > target) &
-    (max(diff(pension.age.upper[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1 / 12
-    current.upper <- oadr(auspop, aus.sim,
-      pension.age = pension.age.upper
-    )$upper[i]
-  }
-}
-OADR.f.upper <- oadr(auspop,
-  aus.sim,
-  pension.age = pension.age.upper
-)
-```
-
-```{r pensionlower, dependson="simulationresults"}
-##### find the lower boundary of pension ages whose prediction interval contains target
-pension.age.lower <- proposed
-for (i in 6:20)
-{
-  current.lower <- oadr(auspop, aus.sim,
-    pension.age = pension.age.lower
-  )$lower[i]
-  while ((current.lower > target) &
-    (max(diff(pension.age.lower[(i - 1):20])) <= (1 - 1 / 12))) {
-    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1 / 12
-    current.lower <- oadr(auspop, aus.sim,
-      pension.age = pension.age.lower
-    )$lower[i]
-  }
-}
-OADR.f.lower <- oadr(auspop, aus.sim, pension.age = pension.age.lower)
-```
-
-```{r pension forecast, dependson="simulationresults"}
-pension.fc <- structure(list(
-  mean = ts(pension.age, start = 2011),
-  upper = pension.age.upper,
-  lower = pension.age.lower,
-  level = 80,
-  x = ts(rep(65, 50), end = 2010)
-), class = "forecast")
-```
-
-Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
-It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years.
-Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
-
-```{r pensionagetables, dependson="OADRat65"}
-year <- time(OADR.f$mean)
-yr <- trunc(pension.age)
-mth <- trunc((pension.age - trunc(pension.age)) * 12)
-agechar <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-
-tab <- matrix("", nrow = 5, ncol = 8)
-for (i in 1:4)
-{
-  tab[, (i - 1) * 2 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
-  tab[, (i - 1) * 2 + 2] <- agechar[(5 * (i - 1)) + (1:5)]
-}
-colnames(tab) <- rep(c("Year", "Age"), 4)
-knitr::kable(format(tab),
-  booktabs = TRUE,
-  caption = "Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months."
-)
-```
-
-```{r pensionagetables2, dependson="OADRat65"}
-year <- time(OADR.f$mean)
-yr <- trunc(pension.age.lower)
-mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
-age.lo <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-yr <- trunc(pension.age.upper)
-mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
-age.up <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-
-tab <- matrix("", nrow = 5, ncol = 12)
-for (i in 1:4)
-{
-  tab[, (i - 1) * 3 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
-  tab[, (i - 1) * 3 + 2] <- age.lo[(5 * (i - 1)) + (1:5)]
-  tab[, (i - 1) * 3 + 3] <- age.up[(5 * (i - 1)) + (1:5)]
-}
-colnames(tab) <- rep(c("Year", "Lo", "Hi"), 4)
-knitr::kable(format(tab),
-  booktabs = TRUE,
-  caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
-)
-```
+
+where \(\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})\) is the mean value
+of \(h\)-step-ahead forecast of OADR with a pension age at the time
+\(n+h\) equal to \(\text{PA}_{n+h}\).
+
+In addition to finding the target pension age based on the mean value of
+OADR, the aim is to find plausible pension age schemes that could give
+the desired OADR level. To be more specific, ``plausible'', means
+finding a range of pension age schemes that could possibly lead to the
+desired OADR, contained by 80\% prediction intervals of simulated OADR.
+Because of the monotonic relationship between pension age and OADR, we
+only need to find the upper (lower) boundary of plausible pension age
+schemes, at which the upper (lower) limit of 80\% prediction intervals
+of OADR is equal to the desired OADR level. Hence, any pension age
+scheme within those two boundaries is plausible. The range of plausible
+pension age schemes can be thought of as 80\% confidence interval of
+pension age scheme where we are 80\% sure that there will be a desired
+outcome. In other words, any pension age scheme outside the range is
+undesirable to use, because we are 80\% certain that the corresponding
+OADR will deviate from the desired level of OADR.
+
+The algorithm to find the upper and lower boundary of plausible pension
+age schemes is similar to the algorithm to find the target pension age
+scheme, except that the mean value of OADR in equation (28) is replaced
+by the boundary of the 80\% prediction interval. Mean is replaced by the
+upper (lower) limit of the 80\% prediction interval to find upper
+(lower) boundary for pension age schemes.
+
+\subsection{Plausible Pension Age
+Schemes}\label{plausible-pension-age-schemes}
+
+Table 1 shows the target pension age scheme, which is properly defined
+in section 3.2.2. It is assumed that it is impractical to change the
+pension age during 2011--2015, so the pension age has to be set at 65
+for those years. Figure \ref{fig:OADRwithoptimal} provides a visible
+comparison of the desired OADR level of 21\% and the mean forecast of
+the OADR corresponding to the target pension age. Note that the OADR
+associated with target pension age scheme has nearly overlapped the
+desired OADR level, which indicates that we have successfully found the
+pension age with stable OADR at the desired levels.
+
+\begin{table}[t]
+
+\caption{\label{tab:pensionagetables}Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}
+\centering
+\begin{tabular}{llllllll}
+\toprule
+Year & Age & Year & Age & Year & Age & Year & Age\\
+\midrule
+2016 & 65Y & 2021 & 65Y+6M & 2026 & 66Y+9M & 2031 & 68Y+3M\\
+2017 & 65Y & 2022 & 65Y+8M & 2027 & 67Y+3M & 2032 & 68Y+3M\\
+2018 & 65Y & 2023 & 65Y+11M & 2028 & 67Y+3M & 2033 & 68Y+9M\\
+2019 & 65Y & 2024 & 66Y+3M & 2029 & 67Y+9M & 2034 & 68Y+9M\\
+2020 & 65Y & 2025 & 66Y+9M & 2030 & 67Y+9M & 2035 & 69Y+3M\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[t]
+
+\caption{\label{tab:pensionagetables2}Fifty-year lower and higher boundary of pension age scheme with 80\% confidence. Y denotes years and M denotes months.}
+\centering
+\begin{tabular}{llllllllllll}
+\toprule
+Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi\\
+\midrule
+2016 & 65Y & 65Y & 2021 & 65Y+4M & 65Y+7M & 2026 & 66Y+6M & 66Y+11M & 2031 & 68Y & 68Y+7M\\
+2017 & 65Y & 65Y & 2022 & 65Y+7M & 65Y+11M & 2027 & 67Y & 67Y+5M & 2032 & 68Y & 68Y+8M\\
+2018 & 65Y & 65Y & 2023 & 65Y+9M & 66Y+2M & 2028 & 67Y & 67Y+6M & 2033 & 68Y+6M & 69Y+2M\\
+2019 & 65Y & 65Y & 2024 & 66Y & 66Y+5M & 2029 & 67Y+6M & 68Y & 2034 & 68Y+6M & 69Y+2M\\
+2020 & 65Y & 65Y & 2025 & 66Y+6M & 66Y+11M & 2030 & 67Y+6M & 68Y+1M & 2035 & 69Y & 69Y+8M\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
-## plots of OADR with plausible pension age schemes
-autoplot(OADR.f.optimal$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  autolayer(OADR.f.optimal) +
-  ggtitle("OADR forecast estimates for optimal pension ages") +
-  xlab("year") + ylab("ratio")
-```
-
-```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
-p1 <- autoplot(OADR.f.upper$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  # autolayer(OADR.f.upper) +
-  ggtitle("OADR for upper boundary pension ages") +
-  xlab("Year") + ylab("ratio") +
-  ylim(0.07, 0.27)
-p2 <- autoplot(OADR.f.lower$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  # autolayer(OADR.f.lower) +
-  ggtitle("OADR for lower boundary pension ages") +
-  xlab("Year") + ylab("ratio") +
-  ylim(0.07, 0.27)
-gridExtra::grid.arrange(p1, p2, ncol = 2)
-```
-
-```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
-The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
-ggplot() +
-  autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
-  #  geom_hline(yintercept=65, color='black') +
-  autolayer(ts(c(rep(65, 7), c(65.5, 65.5, 66.5, 66.5, 67, 67), rep(67, 37))[1:50],
-    start = 2013
-  ), series = "Approved change") +
-  autolayer(ts(c(rep(65, 50)), start = 1990), series = "Pension age at 65") +
-  xlab("Year") + ylab("Age of retirement")
-```
-
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}
-```
-
-```{r OADR_realpensionage, fig.cap="The mean forecast of OADR associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRat65"}
-```
-
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRboundaries}.
-It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
-Note the negative relationship between OADR and pension age.
-It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
-On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/OADRwithoptimal-1.pdf}
+\caption{\label{fig:OADRwithoptimal}The mean forecast of OADR associated
+with target pension age scheme (listed in Table 1) shown in blue, along
+with the desired OADR level in red (i.e., mean forecast of OADR in
+2014). The 80\% prediction interval of the forecast of OADR is shown as
+blue shading.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/OADRboundaries-1.pdf}
+\caption{\label{fig:OADRboundaries}The 80\% prediction interval forecast of
+OADR (in blue) associated with upper and lower boundary of plausible
+pension age schemes (listed in Table.2), along with desired OADR level
+(in red).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{PensionAge_files/figure-latex/comparisonofpensionages-1.pdf}
+\caption{\label{fig:comparisonofpensionages}The comparison between the
+target pension age scheme (in green) and real pension age scheme that
+has been set or proposed by government, along with the 80\% confidence
+interval of the target pension age shown in green shade. The red solid
+line indicates the changes to the pension age from 65 to 67, announced
+in 2009.}
+\end{figure}
+
+The upper and lower boundaries of the plausible pension age schemes
+(also called the 80 \% confidence interval of the target pension age
+scheme in this paper) are reported in Table 2, and their corresponding
+OADR simulation results are shown in \ref{fig:OADRboundaries}. It can be
+seen that the lower (upper) limit of the 80\% prediction interval of
+OADR associated with lower (upper) boundary of the 80\% confidence
+interval pension age scheme is entirely stable around the desired level.
+Note the negative relationship between OADR and pension age. It
+suggests, on one hand, that any pension age higher than the upper
+boundary in table 2 is deemed to be undesirable because the age is too
+high to allow the age pension to provide enough welfare support or
+insurance to the aged. On the other hand, any pension age scheme lower
+than the lower boundary of the pension age reported in Table 2 will also
+be regarded as unreasonable, because it sacrifices the interests of the
+next generation to provide a very generous age pension immediately.
 \todo{Han feels Tables 3 and 4 should be removed?}
 
-Figure \ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
-It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
-Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
-Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than desired level.
-From this result, it is concluded that government will need to adjust  pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21%.
-
-However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
-Therefore, it is worth performing a sensitivity test on the desired level here.
-
-Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it \todo{Han confused} and its 80% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
-When we allow 1% more in desired OADR, the real pension age becomes plausible.
-Figure \ref{fig:OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
-It confirms that OADR is stable around a level higher than current level of OADR before 2035.
-This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
-
-# Conclusions {#sec:conclusions}
-
-The ageing of population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers.
-The fiscal cost of the age pension is projected to sharply increase as a result.
-For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden on society.
-
-In this paper, we have suggested a statistical and demographic approach to address the issue.
-We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of financial burden on Australian society.
-The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable OADR around the desired level.
-To forecast population age structure, three demographic components of population were modelled separately using @HU07 functional time series method, with an extension of the product-ratio method [@HBY13].
-Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than desired level.
-This approach is proposed to find target pension age scheme based on a given desired level of OADR.
-
-We undertake the approach based on assuming the desired level of OADR is at current level of 21%.
-Using the historical data from 1950 to 2010, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
-It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
-Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
-It was concluded that the pension age set by government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.
-
-The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at 21%.
-However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
-Therefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
-This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
-This generates a stable OADR of around 21%.
-The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
-
-Although our results are promising, there are still grounds for further research.
-First, our research results are based on forecasts from one particular model.
-Further studies can apply the same approach but with different models of population forecasting, which allows for enhanced credibility of results.
-Moreover, our research addresses the issue from a purely demographic perspective.
-It is possible to include an economic perspective.
-For example, the economic implications of retaining older workers in workforce can be considered.
-Second, Our research uses an OADR as a single measurement of financial burden.
-Further research should allow the effect of other economic factors to be taken into account.
-For instance, the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.
+Figure \ref{fig:comparisonofpensionages} compares the target pension age
+scheme and its 80\% confidence interval with the pension age scheme with
+proposed further change. It was found that the target pension age
+increases at higher rate than the proposed new pension age scheme.
+Reported in Table 1, the target pension age is supposed to reach 67 by
+2021 and 70 by 2032, while pension age has been proposed to change to 67
+by 2023 and 70 by 2035. Moreover, the proposed pension age scheme is
+below the lower boundary of plausible pension age schemes, which means
+we are 80\% sure that it will cause an OADR higher than desired level.
+From this result, it is concluded that government will need to adjust
+pension age slightly quicker than proposed pace to ensure we have a
+stable OADR around desired level at 21\%.
+
+However, it is interesting to note that the proposed pension age scheme
+does not diverge too far from the plausible pension age schemes,
+suggesting proposed new pension age scheme may be appropriate if we can
+afford slightly higher OADR. Therefore, it is worth performing a
+sensitivity test on the desired level here.
+
+Using the approach suggested in this paper, the target pension age
+associated with desired OADR equal to current level plus 1\% has been
+found. We have shown the comparison of it \todo{Han confused} and its
+80\% confidence level with real pension age scheme in Figure
+\ref{fig:ComparisonwithOADR22}. When we allow 1\% more in desired OADR,
+the real pension age becomes plausible. Figure
+\ref{fig:OADR_realpensionage} shows simulated OADR associated with
+proposed pension age
+scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+It confirms that OADR is stable around a level higher than current level
+of OADR before 2035. This results suggest that pension age scheme with
+proposed change could be suitable if the government are targeting a
+slightly higher financial pressure than current level.
+
+\section{Conclusions}\label{sec:conclusions}
+
+The ageing of population is expected to become a critical issue in
+Australia due to the increase in life expectancy and the retirement of
+baby boomers. The fiscal cost of the age pension is projected to sharply
+increase as a result. For the purpose of sustainability of the welfare
+system in Australia, the government has announced an increase in the
+pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden
+on society.
+
+In this paper, we have suggested a statistical and demographic approach
+to address the issue. We attempt to quantify the effects of changes in
+the pension age on financial burdens using an OADR as a measure of
+financial burden on Australian society. The quantification process
+involves applying stochastic models to forecast future population age
+structure and then using those future age structure projections to find
+the most appropriate pension age scheme that will ensure stable OADR
+around the desired level. To forecast population age structure, three
+demographic components of population were modelled separately using
+\textcite{HU07} functional time series method, with an extension of the
+product-ratio method \autocite{HBY13}. Next, future age structures were
+used to simulate OADR associated with different pension age schemes
+until the minimum pension age scheme was found, which ensures the OADR
+no greater than desired level. This approach is proposed to find target
+pension age scheme based on a given desired level of OADR.
+
+We undertake the approach based on assuming the desired level of OADR is
+at current level of 21\%. Using the historical data from 1950 to 2010,
+the forecast of future populations suggests a substantial increase in
+total population, and confirms the inherent ageing trend. It was found
+that pension age should not be fixed, but instead should grow at a rate
+that will ensure a stable OADR at a level which can be affordable to
+Australians of working age. Findings indicate that the pension age
+scheme with proposed change was not too high, as it is still lower than
+the target pension age scheme and outside its confidence interval. It
+was concluded that the pension age set by government should be adjusted
+slight quicker to be in line with our target pension age, which ensures
+a stable OADR of around 21\%.
+
+The empirical analysis presented in this paper shows the adjustment of
+the pension age announced in 2009 was effective in reducing the
+financial burden to the desired level, which was set at 21\%. However, a
+one-time adjustment is not sufficient to ensure a stable OADR in the
+long term, due to ongoing changes in the population age structure.
+Therefore, we recommend consistently reviewing the pension age according
+to the presented statistical approach. This approach has been used to
+calculate the target pension age from now until 2060 and its 80\%
+confidence interval. The target pension age found in this research
+increases to 67 by 2023, 70 by 2032 and 75 by 2058. This generates a
+stable OADR of around 21\%. The rate of growth in the pension age as
+proposed by the government in 2014 is slightly lower than the target
+pension age found in this study, which suggests that the government may
+need to slightly accelerate the growth of the pension age to maintain an
+OADR at the current level.
+
+Although our results are promising, there are still grounds for further
+research. First, our research results are based on forecasts from one
+particular model. Further studies can apply the same approach but with
+different models of population forecasting, which allows for enhanced
+credibility of results. Moreover, our research addresses the issue from
+a purely demographic perspective. It is possible to include an economic
+perspective. For example, the economic implications of retaining older
+workers in workforce can be considered. Second, Our research uses an
+OADR as a single measurement of financial burden. Further research
+should allow the effect of other economic factors to be taken into
+account. For instance, the effect of growth in superannuation can be
+considered in a way that the effects of high OADR can be offset by the
+growth in superannuation.
+
+\printbibliography
+
+\end{document}

### 2019-01-13 PensionAge.Rmd
Draft_13/Jan/2019

@@
 library(ggplot2)
+library(kableExtra)
 source("functions-v4.R")
@@
 ```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
-year <- 2065 - 2007
+year <- 2057 - 2007
 proposed <- ts(pmin(
@@
 where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$.
-This model involves fitting a matrix of log central rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
+This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
 $b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$.
@@
 The model is under-determined in terms of estimation of parameters.
-For example, if the vector $a,b,k$ is one solution, then for any scalar $c, a-bc, b, k+bc$ also must be one solution.
+For example, if the vector $a,b,k$ is one solution, then for any scalar $c$, $a, b/c, kc$ or $a - bc, b, k+c$ also must be two possible solutions.
 Therefore, Lee and Carter (1992) impose the following constraints:
 \begin{equation}
-  \sum_{t=1}^{n}k_t=0, \sum_{x=x_1}^{x_m}b_x=1
+  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
 \end{equation}
@@
 
-### Hyndman-Ullah Method
+### Hyndman-Ullah Method \label{sec:HU}
 
@@
 The model proposed by @HU07 is as follows:
+\vspace{-.3in}
 \begin{align}
@@
 In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
+\vspace{-.2in}
 \begin{equation*}
-  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
+  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
 \end{equation*}
@@
 In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
+\vspace{-.2in}
 \begin{equation}
@@
 The fitted process is given as follows:
+\vspace{-.3in}
 \begin{equation*}
@@
 The notations are as follows:
+\vspace{-.4in}
 \begin{align*}
@@
 \end{align*}
-where $x$ denotes age and $x=0,1,2,\dots,m^+$.
+\vspace{-.4in}where $x$ denotes age and $x=0,1,2,\dots,m^+$.
 $m^+$ is the open-ended upper age group, which is 100 in this study.
@@
 Therefore, all of those data points can be recorded in an $m\times n$ matrix.
-The super-scripts $M$ and $F$ denote male and female respectively.
+The superscripts M and F denote male and female respectively.
 
 We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
+\vspace{-.3in}
 \begin{align*}
@@
 The equation is expressed as: \todo{Please define $p$ and $^+$}
+\vspace{-.3in}
 \begin{align*}
@@
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$.
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ \todo{should it be $p^+$} refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$.
 The deaths are estimated using the standard life table approach of population projection.
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.
-The start-year population for 2015 is also used to estimate net migration.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.\todo{Han has updated the data period.} The start-year population for 2015 is also used to estimate net migration.
 Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12.
-Even though annual mortality rates are available from 1921 to 2009, only data collected after 1950 is used for two reasons.
+Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons.
 First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
@@
 Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
-\todo{Han has updated the data period.}
 
@@
 In this study, three steps were taken to simulate OADR associated with a specific pension age scheme.
-A stochastic functional model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
-age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
+A stochastic functional data model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
+Age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
 The Monte Carlo simulation method was used consistently in this research.
 Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula.
-Even though the process seems complicated, it is relatively resy to implement using \textit{R}.
+Even though the process seems complicated, it is relatively resy to implement using \textit{R} [@Team18].
 The detailed explanation of each step is as follows.
-The corresponding R code is attached in Appendix B.
-\todo{There is no appendix, Han recommends to put the R code as a supplement}
+The corresponding R code is attached as a supplement.
 
@@
 The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
-The @HU07 model, introduced in section 2.3.2, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
+The @HU07 model, introduced in section \ref{sec:HU}, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
 Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
@@
 In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
+\vspace{-.4in}
 \begin{align}
-  p_t(x)&=\sqrt{s_{t,M}(x)s_{t,F}(x)}, \label{eq:coherent_1}\\
-  r_t(x)&=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}. \label{eq:coherent_2}
+  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
+  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
 \end{align}
 Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
+\vspace{-.3in}
 \begin{align*}
@@
 It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
-Then, simulation h-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
-From here, obtaining h-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
+Then, simulating $h$-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
+From here, obtaining $h$-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
+\vspace{-.3in}
 \begin{align*}
-  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
-  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
+  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
+  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
 \end{align*}
@@
 Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
-We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2011), given a specific pension age.
+We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2015), given a specific pension age.
 The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
@@
 \begin{equation*}
-  \bm{p}_{n+1}=[p_{m,i}] =
+  \bm{p}_{n+1}=[p_{n+1,m,i}] =
     \begin{bmatrix}
@@
 When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
+\vspace{-.2in}
 \begin{equation}
-  \text{adjustment}=0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
+  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
 \end{equation}
@@
 In other words, $(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population.
-The simulation vectors of total work age population and total aged population should then be: \todo{Han feel the second equation does not have \%?}
+The simulation vectors of total work age population and total aged population should then be:
 \begin{align*}
@@
     & = \left[p^{\text{aged}}_{n+1,1},p^{\text{aged}}_{n+1,2},\dots,p^{\text{aged}}_{n+1,1000}\right]\\
-    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
+    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
 \end{align*}
@@
 After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{\text{work}}_{n+1}$ by the corresponding element of $\bm{p}^{\text{aged}}_{n+1}$, i.e.:
+\vspace{-.3in}
 \begin{align*}
@@
 Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
-\begin{equation}
-  \bm{\text{OADR}}^{forecast}=\left[\text{OADR}_{h,i}\right] =
+\begin{equation*}
+  \bm{\text{OADR}}^{\text{forecast}}=\left[\text{OADR}_{h,i}\right] =
   \begin{bmatrix}
-    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+50,1000} \\
+    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+1,1000} \\
     \vdots & \ddots & \vdots \\
@@
   \end{bmatrix}.
-\end{equation}
+\end{equation*}
 
@@
 It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
-Figure \ref{fig:componentsfertility} above shows the mean age pattern ($\mu(x)$), the first two basis functions ($\phi_1(x)$ and $\phi_2(x)$) and first two coefficients (i.e., principal component scores $\beta_{t,1}$ and $\beta_{t,2}$) for fertility rates.
-The first term ($\phi_1(x)*\beta_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of coefficient 1,
-estimated historical first principal component scores $\beta_{t,1}$ are shown in black for 1950-2009.
+Figure \ref{fig:componentsfertility} above shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
+The first term ($\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
+In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950-2014.
 It captures the general trend of fertility change over time.
@@
 
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian fertility rates.", dependson='models'}
+```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
 par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
@@
 
-The first basis function $\phi_1(x)$ measures the different effects of the trend over time across ages.
+The first estimated basis function $\widehat{\phi}_1(x)$ measures the different effects of the trend over time across ages.
 It indicates the general pattern of fertility has very little effect on females of age 15.
@@
 In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-Furthermore, the blue line is the fitted value of future coefficients (i.e., $\beta_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% prediction interval according to the fitted ARIMA model of first coefficients $\left\{\beta_{t,1}\right\}$.
+Furthermore, the blue line is the fitted value of future coefficients (i.e., $\widehat{\beta}_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% pointwise prediction interval according to the fitted ARIMA model of first coefficients $\left\{\widehat{\beta}_{t,1}\right\}$.
 Other terms further explain variation that has not been captured by first term, but less economic explanations can be given for them.
+
+Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2034} show the forecast results of population.
+Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2034.
+Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 23 million by 2064.
+Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
+We can also observe that the further the projected year is, the bigger the forecast variation of population.
+This increase in variation shows that we have less relevant information for further apart prediction horizons.
 
@@
 # This takes a while!
-set.seed(2019-01-04)
+set.seed(2019-01-13)
 nsim <- 20 # Change to 2000 or higher to get better estimates
@@
 
-```{r totalpopulationbyyears, fig.cap="Fifth-year forecasts of total population for each sex, along with 80% prediction intervals.
+```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals.
 The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
@@
 plot(auspop$year, colSums(auspop$pop$female) / 1e6,
-  xlim = c(1975, 2030),
-  ylim = range(c(7, 17), na.rm = TRUE),
+  xlim = c(1950, 2064),
+  ylim = range(c(0, 30), na.rm = TRUE),
   xlab = "Year",
@@
 plot(auspop$year, colSums(auspop$pop$male) / 1e6,
-  xlim = c(1975, 2030),
-  ylim = range(c(7, 17), na.rm = TRUE),
+  xlim = c(1950, 2064),
+  ylim = range(c(0, 30), na.rm = TRUE),
   xlab = "Year",
@@
 
-```{r totalpopulationin2028, fig.cap="Forecast population pyramid for 2028, along with 80% prediction intervals.
-The actual pyramid for 2010 is shown using dashed lines.", , dependson='simulationresults'}
+```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals.
+The actual pyramid for 2015 is shown using dashed lines.", , dependson='simulationresults'}
 par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(4.3, 3.6, 3.0, 3.3))
 plot(c(0, 100), c(0, 100),
-  type = "n", main = "Forecast population: 2035", yaxt = "n",
+  type = "n", main = "Forecast population: 2034", yaxt = "n",
   xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
@@
 
-Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2028} show the forecast results of population.
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2028.
-\ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to 18 million by 2060.
-Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
-We can also observe that the further the projected year is, the bigger the forecast variation of population.
-This increase in variation shows that we have less relevant information for further apart prediction horizons.
-
-Figure \ref{fig:totalpopulationin2028} shows the mean and the 80% prediction interval of simulated population paths for year 2028, along with the 2010 base population.
+Figure \ref{fig:totalpopulationin2034} shows the mean and the 80% pointwise prediction interval of simulated population paths for year 2034, along with the 2015 base population.
 It can be observed that overall population size is expected to increase substantially.
@@
 
-```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% prediction interval.", dependson='simulationresults'}
+```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
 OADR.f <- oadr(auspop, aus.sim, pension.age = current)
@@
 
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (black line) and equal to the pension age scheme with approved change (red line) respectively, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The actual OADRs for 1950-2010 are shown in black.", dependson='OADRat65'}
+```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
+The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
 OADR.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
@@
 Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \ref{fig:OADRat65} shows the mean forecast and prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1920-2010.
+Figure \ref{fig:OADRat65} shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921-2014.
 A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
@@
 The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $F$ \todo{Han thinks $H$?} prediction horizon.
-Then we are allowed to repeat the test $n-F-k+1$ \todo{Han thinks $n-H-k+1$} times, where $n$ is the number of total years of observation.
+Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $H$ prediction horizon.
+Then we are allowed to repeat the test $n-H-k+1$ times, where $n$ is the number of total years of observation.
 The procedure is as follows:
 
-Let $i=1$, we first select historical data for a time interval of $[i,i+1,\dots,i+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
-Then, we can calculate the difference of forecasted OADR over the period $[i+k,i+k+1,\dots,i+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
-We repeat the following steps for $i=1,2,\dots,n-k-H+1$.
+Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
+We repeat the following steps for $\omega=1,2,\dots,n-k-H+1$.
 Then, we can summary the information into a matrix as follows:
-\begin{equation}
-  \text{\textbf{Absolute Error}} = [\text{AE}_{h,i}] =
+\begin{equation*}
+  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
     \begin{bmatrix}
@@
     \end{bmatrix}
-\end{equation}
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,i}=\left|\text{OADR}^{mean}_{h,i}-\text{OADR}^{real}_{h,i}\right|$.
-This process is also known as "rolling forecasting origin", because the "origin" ($k+i-1$) at which the forecast is based rolls forward in time.
+\end{equation*}
+where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
+This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
 We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR  where $h=1,2,\dots,H$.
+
+In our sample, $n=2014-1950+1=65$ and we set $k=25$ and $H=25$ to perform the test.
+The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \ref{fig:rollingtest}.
+From this figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
+Overall, the mean absolute error is very small.
+For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is very small if compared to the desired level of OADR, which is at 21%.
 
@@
 ######## Run a rolling forecast origin
-# replace 2010 by 2014 (Han?)
-t <- 2010 - 1950 + 1
+t <- 2014 - 1950 + 1
 H <- 25 ## forecast horizon for test
@@
 oadr.real <- oadr(auspop, aus.sim)$x
-oadr.real.mat <- oadr.error <- matrix(NA, 25, 12)
+oadr.real.mat <- oadr.error <- matrix(NA, 25, 15)
 for (i in 1:25)
-  oadr.real.mat[i, ] <- oadr.real[(i + 59):(59 + 11 + i)]
-
-oadr.error <- abs(oadrtest - oadr.real.mat[, 1:11])
+  oadr.real.mat[i, ] <- oadr.real[(i + 56):(56 + 14 + i)]
+
+oadr.error <- abs(oadrtest - oadr.real.mat)
 oadrave <- apply(oadr.error, 1, mean)
 
-plot(oadrave, xlab = "forecast horizon", ylab = "mean ")
-```
-
-In our sample, $n=2010-1950+1=61$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \ref{fig:rollingtest}.
-From this figure, we observe that the absolute mean error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is very small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.5%, which is very small if compared to the desired level of OADR, which is at 21%.
+plot(oadrave, xlab = "forecast horizon", ylab = "mean", ylim = c(0, 0.02))
+```
 
@@
 According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
-Suppose we denote pension age schemes over the prediction horizon by $\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]$.
-The OADR function of pension age over the prediction horizon is denoted as $OADR_h(\text{PA}_{n+h})$ for $h=1,2,\dots,H$.
+Suppose we denote pension age (PA) schemes over the prediction horizon by $\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]$.
+The OADR function of pension age over the prediction horizon is denoted as $\text{OADR}_h(\text{PA}_{n+h})$ for $h=1,2,\dots,H$.
 There is a negative relationship between pension age and OADR.
@@
 Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
-Therefore, the target pension age scheme $\bm{\text{PA}}^{target}$ can be defined in the following way:
+Therefore, the target pension age scheme $\bm{\text{PA}}^{\text{target}}$ can be defined in the following way:
 for $h=1,2,\dots,H$
-\begin{equation}
+\begin{equation*}
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation}
+\end{equation*}
 \begin{align*}
@@
 In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
-It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
+It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65.5 in mid-2017.
 The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in 2017 onward}, which is:
+This simplification is reasonable because the pension age will be same in mid-2017 onward}, which is:
+\vspace{-.3in}
 \begin{align*}
@@
 For $h=1,2,\dots,H$, we keep increasing pension age vector $[\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]$ by a month at a time, unless we find that
-\begin{align}
-  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \text{~or~} \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
-\end{align}
+\vspace{-.2in}
+\begin{align*}
+  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \quad \text{~or~}\quad  \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
+\end{align*}
 where $\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $\text{PA}_{n+h}$.
@@
 
-The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR in equation (28) is replaced by the boundary of the 80% prediction interval.
+The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR is replaced by the boundary of the 80% prediction interval.
 Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.
@@
 }
-OADR.f.lower <- oadr(auspop, aus.sim, pension.age = pension.age.lower)
+OADR.f.lower <- oadr(auspop, 
+    aus.sim, 
+    pension.age = pension.age.lower
+)
 ```
@@
 pension.fc <- structure(list(
-  mean = ts(pension.age, start = 2011),
+  mean = ts(pension.age, start = 2015),
   upper = pension.age.upper,
@@
   level = 80,
-  x = ts(rep(65, 50), end = 2010)
+  x = ts(rep(65, 50), end = 2014)
 ), class = "forecast")
@@
 Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
-It is assumed that it is impractical to change the pension age during 2011--2015, so the pension age has to be set at 65 for those years.
+It is assumed that it is impractical to change the pension age during 2011--2014, so the pension age has to be set at 65 for those years.
 Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
+Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
 
 ```{r pensionagetables, dependson="OADRat65"}
-year <- time(OADR.f$mean)
+year <- time(OADR.f$mean) - 1
 yr <- trunc(pension.age)
@@
 
-tab <- matrix("", nrow = 5, ncol = 8)
-for (i in 1:4)
+tab <- matrix(NA, nrow = 10, ncol = 10)
+for (i in 1:5)
 {
-  tab[, (i - 1) * 2 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
-  tab[, (i - 1) * 2 + 2] <- agechar[(5 * (i - 1)) + (1:5)]
-}
-colnames(tab) <- rep(c("Year", "Age"), 4)
+  tab[, (i - 1) * 2 + 1] <- as.character(year[(10 * (i - 1)) + (1:10)])
+  tab[, (i - 1) * 2 + 2] <- agechar[(10 * (i - 1)) + (1:10)]
+}
+colnames(tab) <- rep(c("Year", "Age"), 5)
 knitr::kable(format(tab),
@@
 ```{r pensionagetables2, dependson="OADRat65"}
-year <- time(OADR.f$mean)
+year <- time(OADR.f$mean) - 1
 yr <- trunc(pension.age.lower)
@@
 
-tab <- matrix("", nrow = 5, ncol = 12)
-for (i in 1:4)
+tab <- matrix("", nrow = 10, ncol = 15)
+for (i in 1:5)
 {
-  tab[, (i - 1) * 3 + 1] <- as.character(year[(5 * (i - 1)) + (1:5)])
-  tab[, (i - 1) * 3 + 2] <- age.lo[(5 * (i - 1)) + (1:5)]
-  tab[, (i - 1) * 3 + 3] <- age.up[(5 * (i - 1)) + (1:5)]
-}
-colnames(tab) <- rep(c("Year", "Lo", "Hi"), 4)
-knitr::kable(format(tab),
+  tab[, (i - 1) * 3 + 1] <- as.character(year[(10 * (i - 1)) + (1:10)])
+  tab[, (i - 1) * 3 + 2] <- age.lo[(10 * (i - 1)) + (1:10)]
+  tab[, (i - 1) * 3 + 3] <- age.up[(10 * (i - 1)) + (1:10)]
+}
+colnames(tab) <- rep(c("Year", "Lo", "Hi"), 5)
+kable_output = knitr::kable(format(tab),
   booktabs = TRUE,
@@
 )
-```
-
-\begin{table}
-\centering
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year & 2011   & 2012     & 2013   & 2014  & 2015   & 2016   & 2017   & 2018  \\
-Age  & 65Y    & 65Y      & 65Y    & 65Y   & 65Y    & 65Y7M  & 65Y10M & 66Y2M \\
-\hline
-Year & 2019   & 2020     & 2021   & 2022  & 2023   & 2024   & 2025   & 2026  \\
-Age  & 66Y5M  & 66Y8M    & 67Y    & 67Y3M & 67Y7M  & 67Y10M & 68Y2M  & 68Y5M \\
-\hline
-Year & 2027   & 2028     & 2029   & 2030  & 2031   & 2032   & 2033   & 2034  \\
-Age  & 68Y8M  & 69Y      & 69Y3M  & 69Y7M & 69Y10M & 70Y2M  & 70Y5M  & 70Y8M \\
-\hline
-Year & 2035   & 2036     & 2037   & 2038  & 2039   & 2040   & 2041   & 2042  \\
-Age  & 70Y11M & 71Y2M    & 71Y3M  & 71Y6M & 71Y8M  & 71Y10M & 72Y    & 72Y2M \\
-\hline
-Year & 2043   & 2044     & 2045   & 2046  & 2047   & 2048   & 2049   & 2050  \\
-Age  & 72Y5M  & 72Y8M    & 72Y11M & 73Y1M & 73Y3M  & 73Y5M  & 73Y7M  & 73Y8M \\
-\hline
-Year & 2051   & 2052     & 2053   & 2054  & 2055   & 2056   & 2057   & 2058  \\
-Age  & 73Y10M & 73Y11M   & 74Y1M  & 74Y3M & 74Y5M  & 74Y7M  & 74Y9M  & 75Y   \\
-\hline
-Year & 2059   & 2060  \\
-Age  & 75Y3M  & 75Y4M \\
-\hline
-\end{tabular}
-
-\caption{Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}
-
-\vspace{0.6cm}
-
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year  & 2011  & 2012      & 2013   & 2014   & 2015   & 2016   & 2017   & 2018   \\
-Lower & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y5M  & 65Y8M  & 66Y11M \\
-Upper & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y9M  & 66Y    & 66Y4M  \\
-\hline
-Year  & 2019  & 2020      & 2021   & 2022   & 2023   & 2024   & 2025   & 2026   \\
-Lower & 66Y2M & 66Y5M     & 66Y8M  & 66Y11M & 67Y2M  & 67Y5M  & 67Y8M  & 67Y11M \\
-Upper & 66Y8M & 67Y       & 67Y4M  & 67Y8M  & 67Y11M & 68Y4M  & 68Y7M  & 68Y11M \\
-\hline
-Year  & 2027  & 2028      & 2029   & 2030   & 2031   & 2032   & 2033   & 2034   \\
-Lower & 68Y2M & 68Y5M     & 68Y8M  & 68Y11M & 69Y4M  & 69Y5M  & 69Y8M  & 69Y11M \\
-Upper & 69Y4M & 69Y6M     & 69Y10M & 70Y2M  & 70Y6M  & 70Y9M  & 71Y1M  & 71Y4M  \\
-\hline
-Year  & 2035  & 2036      & 2037   & 2038   & 2039   & 2040   & 2041   & 2042   \\
-Lower & 70Y1M & 70Y4M     & 70Y5M  & 70Y6M  & 70Y8M  & 70Y10M & 71Y    & 71Y4M  \\
-Upper & 71Y8M & 71Y11M    & 72Y2M  & 72Y4M  & 72Y7M  & 72Y9M  & 73Y    & 73Y4M  \\
-\hline
-Year  & 2043  & 2044      & 2045   & 2046   & 2047   & 2048   & 2049   & 2050   \\
-Lower & 71Y5M & 71Y8M     & 71Y10M & 71Y11M & 72Y    & 72Y2M  & 72Y3M  & 72Y4M  \\
-Upper & 73Y5M & 73Y8M     & 74Y    & 74Y3M  & 74Y5M  & 74M8M  & 74Y10M & 75Y    \\
-\hline
-Year  & 2051  & 2052      & 2053   & 2054   & 2055   & 2056   & 2057   & 2058   \\
-Lower & 72Y5M & 72Y7M     & 72Y8M  & 72Y10M & 73Y    & 73Y2M  & 73Y4M  & 73Y7M  \\
-Upper & 75Y2M & 75Y4M     & 75Y6M  & 75Y8M  & 75Y10M & 76Y    & 76Y3M  & 76Y5M  \\
-\hline
-Year  & 2059  & 2060 \\
-Lower & 73Y9M & 73Y11M \\
-Upper & 76Y8M & 76Y10M \\
-\hline
-\end{tabular}
-
-\caption{Fifth-years lower and higher boundary of pension age scheme with one boundary of 80\% OADR around desired OADR. Y denotes years and M denotes months.}
-\end{table}
+kable_styling(kable_output, font_size = 7)
+```
 
@@
   geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  # autolayer(OADR.f.upper) +
+  autolayer(OADR.f.upper) +
   ggtitle("OADR for upper boundary pension ages") +
@@
   geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  # autolayer(OADR.f.lower) +
+  autolayer(OADR.f.lower) +
   ggtitle("OADR for lower boundary pension ages") +
@@
   autolayer(ts(c(rep(65, 7), c(65.5, 65.5, 66.5, 66.5, 67, 67), rep(67, 37))[1:50],
-    start = 2013
+    start = 2015
   ), series = "Approved change") +
@@
 
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in \ref{fig:OADRboundaries}.
+The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \ref{fig:OADRboundaries}.
 It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
@@
 On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
-\todo{Han feels Tables 3 and 4 should be removed?}
 
@@
 Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it \todo{Han confused} and its 80% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
+We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
 When we allow 1% more in desired OADR, the real pension age becomes plausible.

### 2019-01-13 PensionAge.tex
Draft_13/Jan/2019

@@
 
-\usepackage{todonotes}
+\usepackage{todonotes, xcolor}
 
@@
 for age \(x\) in year \(t\). This model involves fitting a matrix of log
-central rates with sets of age-specific constants, \{\(a_x\)\} and
+central death rates with sets of age-specific constants, \{\(a_x\)\} and
 \{\(b_x\)\}, and a time-varying index \(k_t\). \(b_x\) is a set of
@@
 example, if the vector \(a,b,k\) is one solution, then for any scalar
-\(c, a-bc, b, k+bc\) also must be one solution. Therefore, Lee and
-Carter (1992) impose the following constraints:
+\(c\), \(a, b/c, kc\) or \(a - bc, b, k+c\) also must be two possible
+solutions. Therefore, Lee and Carter (1992) impose the following
+constraints:
 
 \begin{equation}
-  \sum_{t=1}^{n}k_t=0, \sum_{x=x_1}^{x_m}b_x=1
+  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
 \end{equation}
@@
 
-\subsubsection{Hyndman-Ullah Method}\label{hyndman-ullah-method}
+\subsubsection{\texorpdfstring{Hyndman-Ullah Method
+\label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}
 
@@
 
-The model proposed by \textcite{HU07} is as follows:
+The model proposed by \textcite{HU07} is as follows: \vspace{-.3in}
 
@@
 decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
+\vspace{-.2in}
 
 \begin{equation*}
-  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_k(x)\beta_{t,k}
+  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
 \end{equation*}
@@
 \(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
+\vspace{-.2in}
 
@@
 Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given
-as follows:
+as follows: \vspace{-.3in}
 
@@
 gender-specific exposures to risk (i.e., population of age \(x\) at 30
-June) for each year. The notations are as follows:
+June) for each year. The notations are as follows: \vspace{-.4in}
 
@@
 
-where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\) is the
-open-ended upper age group, which is 100 in this study. \(t\) denotes
-year and \(t=1,2,\dots,n\), where \(n\) is the horizon of historical
-data used. Therefore, all of those data points can be recorded in an
-\(m\times n\) matrix. The super-scripts \(M\) and \(F\) denote male and
-female respectively.
+\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\)
+is the open-ended upper age group, which is 100 in this study. \(t\)
+denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of
+historical data used. Therefore, all of those data points can be
+recorded in an \(m\times n\) matrix. The superscripts M and F denote
+male and female respectively.
 
 We can obtain historical mortality rates \(m_t(x)\) (also called central
-death rates) and fertility rates \(f_t(x)\) as follows:
+death rates) and fertility rates \(f_t(x)\) as follows: \vspace{-.3in}
 
@@
 The equation is expressed as: \todo{Please define $p$ and $^+$}
+\vspace{-.3in}
 
@@
 where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of
-persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\) refers
-to migration in calendar year \(t\) of persons aged \(p-1\) and older at
-beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar
-year \(t\) of births during year \(t\); and similarly for deaths,
+persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\)
+\todo{should it be $p^+$} refers to migration in calendar year \(t\) of
+persons aged \(p-1\) and older at beginning of year \(t\), and
+\(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during
+year \(t\); and similarly for deaths,
 \(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\). The deaths are estimated using
@@
 of residents in Australia by sex and age in single years for age group
-0-99 and 100+ have been sourced from the \textcite{HMD} for 1921--2014.
-The start-year population for 2015 is also used to estimate net
-migration. Data for age-specific annual fertility rates by single years
-of age for 15-49 over the period 1950-2014 was obtained from the
-\textcite{ABS12}. Even though annual mortality rates are available from
-1921 to 2009, only data collected after 1950 is used for two reasons.
-First, the period between 1921-1950 has very different mortality
-patterns from later years because of wars and epidemics \autocite{HB08}.
-Since the model for this study is valid under the assumption that
-extrapolative methods can be used, it seemed best to delete the less
-relevant data, which might influence estimations of parameters if we
-include them. Secondly, fertility rates are only available from 1950, so
-the mortality rate was cut to fit the same period.
-\todo{Han has updated the data period.}
+0-99 and 100+ have been sourced from the \textcite{HMD} for
+1921--2014.\todo{Han has updated the data period.} The start-year
+population for 2015 is also used to estimate net migration. Data for
+age-specific annual fertility rates by single years of age for 15-49
+over the period 1950-2014 was obtained from the \textcite{ABS12}. Even
+though annual mortality rates are available from 1921 to 2014, only data
+collected after 1950 is used for two reasons. First, the period between
+1921-1950 has very different mortality patterns from later years because
+of wars and epidemics \autocite{HB08}. Since the model for this study is
+valid under the assumption that extrapolative methods can be used, it
+seemed best to delete the less relevant data, which might influence
+estimations of parameters if we include them. Secondly, fertility rates
+are only available from 1950, so the mortality rate was cut to fit the
+same period.
 
@@
 In this study, three steps were taken to simulate OADR associated with a
-specific pension age scheme. A stochastic functional model was applied
-to five components of population change: female mortality rates, male
-mortality rates, female net migration, male net migration and fertility
-rates to simulate these five components over the prediction horizon
-(which is 50 years in this study). age- and gender-specific population
-paths over the prediction horizon were simulated using the demographic
-growth-balance equation. The Monte Carlo simulation method was used
-consistently in this research. Finally, calculation of OADR associated
-with a specific pension age scheme was performed by applying the OADR
-formula. Even though the process seems complicated, it is relatively
-resy to implement using \textit{R}. The detailed explanation of each
-step is as follows. The corresponding R code is attached in Appendix B.
-\todo{There is no appendix, Han recommends to put the R code as a supplement}
+specific pension age scheme. A stochastic functional data model was
+applied to five components of population change: female mortality rates,
+male mortality rates, female net migration, male net migration and
+fertility rates to simulate these five components over the prediction
+horizon (which is 50 years in this study). Age- and gender-specific
+population paths over the prediction horizon were simulated using the
+demographic growth-balance equation. The Monte Carlo simulation method
+was used consistently in this research. Finally, calculation of OADR
+associated with a specific pension age scheme was performed by applying
+the OADR formula. Even though the process seems complicated, it is
+relatively resy to implement using \textit{R} \autocite{Team18}. The
+detailed explanation of each step is as follows. The corresponding R
+code is attached as a supplement.
 
@@
 product-ratio method \autocite{HBY13} to improve the accuracy of the
-forecast. The \textcite{HU07} model, introduced in section 2.3.2, is
-applied to the mortality rate, fertility rate and net migration
+forecast. The \textcite{HU07} model, introduced in section \ref{sec:HU},
+is applied to the mortality rate, fertility rate and net migration
 separately, based on the assumption that they behave independently.
@@
 were created: product series (denoted by \(p_t(x)\)) and ratio series
-(denoted by \(r_t(x)\)), which are defined as follows:
+(denoted by \(r_t(x)\)), which are defined as follows: \vspace{-.4in}
 
 \begin{align}
-  p_t(x)&=\sqrt{s_{t,M}(x)s_{t,F}(x)}, \label{eq:coherent_1}\\
-  r_t(x)&=\sqrt{\frac{s_{t,M}(x)}{s_{t,F}(x)}}. \label{eq:coherent_2}
+  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
+  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
 \end{align}
@@
 Then, \textcite{HU07} was applied to these two new variables instead of
-male and female mortality rate as follows:
+male and female mortality rate as follows: \vspace{-.3in}
 
@@
 \(\gamma_{t,l}\) that ensures the forecast of male and female do not
-diverge. Then, simulation h-step-ahead forecast values of product
+diverge. Then, simulating \(h\)-step-ahead forecast values of product
 variable and ratio variable was performed (denoted by
@@
 \eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining
-h-step-ahead forecast of sex-specific coherent mortality rates (denoted
-\(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was performed using a
-back-transformation:
+\(h\)-step-ahead forecast of sex-specific coherent mortality rates
+(denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was
+performed using a back-transformation: \vspace{-.3in}
 
 \begin{align*}
-  m_{n+h\mid n,M}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
-  m_{n+h\mid n,F}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
+  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
+  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
 \end{align*}
@@
 the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR
-in year 2011), given a specific pension age. The same method can be
+in year 2015), given a specific pension age. The same method can be
 applied to all years over the prediction horizon, given their
@@
 population in \eqref{eq:aged} is subtracted with an adjustment:
+\vspace{-.2in}
 
 \begin{equation}
-  \text{adjustment}=0.r\times100%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
+  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
 \end{equation}
@@
 total aged population should then be:
-\todo{Han feel the second equation does not have \%?}
 
@@
 \(\bm{p}^{\text{work}}_{n+1}\) by the corresponding element of
-\(\bm{p}^{\text{aged}}_{n+1}\), i.e.:
+\(\bm{p}^{\text{aged}}_{n+1}\), i.e.: \vspace{-.3in}
 
@@
 
-\begin{equation}
-  \bm{\text{OADR}}^{forecast}=\left[\text{OADR}_{h,i}\right] =
+\begin{equation*}
+  \bm{\text{OADR}}^{\text{forecast}}=\left[\text{OADR}_{h,i}\right] =
   \begin{bmatrix}
-    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+50,1000} \\
+    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+1,1000} \\
     \vdots & \ddots & \vdots \\
@@
 economic sense. Figure \ref{fig:componentsfertility} above shows the
-mean age pattern (\(\mu(x)\)), the first two basis functions
-(\(\phi_1(x)\) and \(\phi_2(x)\)) and first two coefficients (i.e.,
-principal component scores \(\beta_{t,1}\) and \(\beta_{t,2}\)) for
-fertility rates. The first term (\(\phi_1(x)*\beta_{t,1}\)) accounts for
-the most variation in fertility, so a relatively sensible interpretation
-can be given to the first term. In the plot of coefficient 1, estimated
-historical first principal component scores \(\beta_{t,1}\) are shown in
-black for 1950-2009. It captures the general trend of fertility change
-over time. It indicates a sharp increase between 1950-1960, followed by
-a rapid decline of fertility rates from 1961. This increase of fertility
-is linked to the Post-World War II baby
-boom\footnote{Between the years 1946 and 1964} in Australia, resulting
-from the recovery from war and the Great
+estimated mean age pattern \(\widehat{\mu}(x)\), the first two estimated
+basis functions, \(\widehat{\phi}_1(x)\) and \(\widehat{\phi}_2(x)\),
+and first two estimated coefficients (i.e., estimated principal
+component scores \(\widehat{\beta}_{t,1}\) and
+\(\widehat{\beta}_{t,2}\)) for fertility rates. The first term
+(\(\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}\)) accounts for the
+most variation in fertility, so a relatively sensible interpretation can
+be given to the first term. In the plot of the first coefficient,
+estimated historical first principal component scores
+\(\widehat{\beta}_{t,1}\) are shown in black for 1950-2014. It captures
+the general trend of fertility change over time. It indicates a sharp
+increase between 1950-1960, followed by a rapid decline of fertility
+rates from 1961. This increase of fertility is linked to the Post-World
+War II baby boom\footnote{Between the years 1946 and 1964} in Australia,
+resulting from the recovery from war and the Great
 Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
@@
 \caption{\label{fig:componentsfertility}Fitted basis functions and
-coefficients for Australian fertility rates.}
+coefficients for Australian age-specific fertility rates.}
 \end{figure}
 
-The first basis function \(\phi_1(x)\) measures the different effects of
-the trend over time across ages. It indicates the general pattern of
-fertility has very little effect on females of age 15. This makes
-intuitive sense because most early pregnancies are accidental,
-therefore, any of previously discussed events has no effect on early
-pregnancies. In addition, there are two spikes in the first basic
-function, which suggests that the historical trend has a distinct impact
-on females aged around their 20s and 40s. Furthermore, the blue line is
-the fitted value of future coefficients (i.e., \(\beta_{n+h,1}\), for
-\(h=1,2,\dots,50\)) and the yellow shading shows their 80\% prediction
-interval according to the fitted ARIMA model of first coefficients
-\(\left\{\beta_{t,1}\right\}\). Other terms further explain variation
-that has not been captured by first term, but less economic explanations
-can be given for them.
+The first estimated basis function \(\widehat{\phi}_1(x)\) measures the
+different effects of the trend over time across ages. It indicates the
+general pattern of fertility has very little effect on females of age
+15. This makes intuitive sense because most early pregnancies are
+accidental, therefore, any of previously discussed events has no effect
+on early pregnancies. In addition, there are two spikes in the first
+basic function, which suggests that the historical trend has a distinct
+impact on females aged around their 20s and 40s. Furthermore, the blue
+line is the fitted value of future coefficients (i.e.,
+\(\widehat{\beta}_{n+h,1}\), for \(h=1,2,\dots,50\)) and the yellow
+shading shows their 80\% pointwise prediction interval according to the
+fitted ARIMA model of first coefficients
+\(\left\{\widehat{\beta}_{t,1}\right\}\). Other terms further explain
+variation that has not been captured by first term, but less economic
+explanations can be given for them.
+
+Both Figures \ref{fig:totalpopulationbyyears} and
+\ref{fig:totalpopulationin2034} show the forecast results of population.
+Figure \ref{fig:totalpopulationbyyears} shows the forecast of total
+population by gender over the prediction horizon, while Figure
+\ref{fig:totalpopulationin2028} shows the forecast of population age
+structure in a specific year, 2034. Figure
+\ref{fig:totalpopulationbyyears} indicates that both the female and male
+population are expected to increase to around 23 million by 2064. Since
+the fertility rate is expected to remain low, the possible reason of the
+significant increase in population size is net migration. We can also
+observe that the further the projected year is, the bigger the forecast
+variation of population. This increase in variation shows that we have
+less relevant information for further apart prediction horizons.
 
@@
 \includegraphics{PensionAge_files/figure-latex/totalpopulationbyyears-1.pdf}
-\caption{\label{fig:totalpopulationbyyears}Fifth-year forecasts of total
+\caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of total
 population for each sex, along with 80\% prediction intervals. The
@@
 \centering
-\includegraphics{PensionAge_files/figure-latex/totalpopulationin2028-1.pdf}
-\caption{\label{fig:totalpopulationin2028}Forecast population pyramid for
-2028, along with 80\% prediction intervals. The actual pyramid for 2010
-is shown using dashed lines.}
+\includegraphics{PensionAge_files/figure-latex/totalpopulationin2034-1.pdf}
+\caption{\label{fig:totalpopulationin2034}Forecast population pyramid for
+2034, along with 80\% pointwise prediction intervals. The actual pyramid
+for 2015 is shown using dashed lines.}
 \end{figure}
 
-Both Figures \ref{fig:totalpopulationbyyears} and
-\ref{fig:totalpopulationin2028} show the forecast results of population.
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of total
-population by gender over the prediction horizon, while Figure
-\ref{fig:totalpopulationin2028} shows the forecast of population age
-structure in a specific year, 2028. \ref{fig:totalpopulationbyyears}
-indicates that both the female and male population are expected to
-increase to 18 million by 2060. Since the fertility rate is expected to
-remain low, the possible reason of the significant increase in
-population size is net migration. We can also observe that the further
-the projected year is, the bigger the forecast variation of population.
-This increase in variation shows that we have less relevant information
-for further apart prediction horizons.
-
-Figure \ref{fig:totalpopulationin2028} shows the mean and the 80\%
-prediction interval of simulated population paths for year 2028, along
-with the 2010 base population. It can be observed that overall
-population size is expected to increase substantially. The uncertainty
-of population of infant is much higher than other ages, which reflects
-the higher forecast variation of fertility rates than mortality rates.
-The uncertainty of the young age population is mainly due to migration
-\autocite{HB08}.
+Figure \ref{fig:totalpopulationin2034} shows the mean and the 80\%
+pointwise prediction interval of simulated population paths for year
+2034, along with the 2015 base population. It can be observed that
+overall population size is expected to increase substantially. The
+uncertainty of population of infant is much higher than other ages,
+which reflects the higher forecast variation of fertility rates than
+mortality rates. The uncertainty of the young age population is mainly
+due to migration \autocite{HB08}.
 
@@
 assumption of pension age equal to 65 for both sexes, along with 80\%
-prediction interval.}
+pointwise prediction interval.}
 \end{figure}
@@
 \caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated
-with a pension age equal to 65 (black line) and equal to the pension age
-scheme with approved change (red line) respectively, along with the
-desired OADR level in grey (i.e., mean forecast of OADR in 2014). The
-actual OADRs for 1950-2010 are shown in black.}
+with a pension age equal to 65 (green line) and equal to the pension age
+scheme with approved change (orange line) respectively, along with the
+desired OADR level in purple. The actual OADRs for 1950-2014 are shown
+in black.}
 \end{figure}
@@
 what would happen if no further action was taken. Figure
-\ref{fig:OADRat65} shows the mean forecast and prediction interval of
-the OADR with a pension age of 65, along with the historical OADR for
-1920-2010. A strong positive trend was observed, which indicates an
-increasing burden on the next working-age generation if the pension age
-is fixed at 65. This is consistent with the prediction by
+\ref{fig:OADRat65} shows the mean forecast and pointwise prediction
+interval of the OADR with a pension age of 65, along with the historical
+OADR for 1921-2014. A strong positive trend was observed, which
+indicates an increasing burden on the next working-age generation if the
+pension age is fixed at 65. This is consistent with the prediction by
 inter-generation reports in 2002 \autocite{IGR02} and in 2007
@@
 forecast\footnote{$k$ can't be too small}, we are interested in the
-\(F\) \todo{Han thinks $H$?} prediction horizon. Then we are allowed to
-repeat the test \(n-F-k+1\) \todo{Han thinks $n-H-k+1$} times, where
-\(n\) is the number of total years of observation. The procedure is as
-follows:
-
-Let \(i=1\), we first select historical data for a time interval of
-\([i,i+1,\dots,i+k-1]\) as ``in sample data'' to fit the model, and then
-forecast \(H\) years'
+\(H\) prediction horizon. Then we are allowed to repeat the test
+\(n-H-k+1\) times, where \(n\) is the number of total years of
+observation. The procedure is as follows:
+
+Let \(\omega=1\), we first select historical data for a time interval of
+\([\omega,\omega+1,\dots,\omega+k-1]\) as ``in sample data'' to fit the
+model, and then forecast \(H\) years'
 OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
 Then, we can calculate the difference of forecasted OADR over the period
-\([i+k,i+k+1,\dots,i+k+H-1]\) from the real OADR for the same period,
-which is known as absolute error. We repeat the following steps for
-\(i=1,2,\dots,n-k-H+1\). Then, we can summary the information into a
-matrix as follows:
-
-\begin{equation}
-  \text{\textbf{Absolute Error}} = [\text{AE}_{h,i}] =
+\([\omega+k,\omega+k+1,\dots,\omega+k+H-1]\) from the real OADR for the
+same period, which is known as absolute error. We repeat the following
+steps for \(\omega=1,2,\dots,n-k-H+1\). Then, we can summary the
+information into a matrix as follows:
+
+\begin{equation*}
+  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
     \begin{bmatrix}
@@
     \end{bmatrix}
-\end{equation}
+\end{equation*}
 
 where \(h\) denotes for the forecast horizon and
-\(\text{AE}_{h,i}=\left|\text{OADR}^{mean}_{h,i}-\text{OADR}^{real}_{h,i}\right|\).
+\(\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|\).
 This process is also known as ``rolling forecasting origin'', because
-the ``origin'' (\(k+i-1\)) at which the forecast is based rolls forward
-in time. We take the average of each row to obtain an absolute mean
-error of \(h\)-step-ahead forecast of OADR where \(h=1,2,\dots,H\).
+the ``origin'' (\(k+\omega-1\)) at which the forecast is based rolls
+forward in time. We take the average of each row to obtain an absolute
+mean error of \(h\)-step-ahead forecast of OADR where \(h=1,2,\dots,H\).
+
+In our sample, \(n=2014-1950+1=65\) and we set \(k=25\) and \(H=25\) to
+perform the test. The mean absolute error of \(h\)-step-ahead forecast
+of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
+From this figure, we observe that the mean absolute error is increasing
+as \(h\) increases, which is reasonable as we have less relevant
+information to make a forecast for further apart OADR. Overall, the mean
+absolute error is very small. For example, the mean absolute error for
+25-step-ahead forecast is 1.6\%, which is very small if compared to the
+desired level of OADR, which is at 21\%.
 
@@
 \end{figure}
-
-In our sample, \(n=2010-1950+1=61\) and we set \(k=25\) and \(H=25\) to
-perform the test. The mean absolute error of \(h\)-step-ahead forecast
-of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
-From this figure, we observe that the absolute mean error is increasing
-as \(h\) increases, which is reasonable as we have less relevant
-information to make a forecast for further apart OADR. Overall, the mean
-absolute error is very small. For example, the mean absolute error for
-25-step-ahead forecast is 1.5\%, which is very small if compared to the
-desired level of OADR, which is at 21\%.
 
@@
 pension age, when the population age structure is given. Suppose we
-denote pension age schemes over the prediction horizon by
+denote pension age (PA) schemes over the prediction horizon by
 \(\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]\).
 The OADR function of pension age over the prediction horizon is denoted
-as \(OADR_h(\text{PA}_{n+h})\) for \(h=1,2,\dots,H\). There is a
+as \(\text{OADR}_h(\text{PA}_{n+h})\) for \(h=1,2,\dots,H\). There is a
 negative relationship between pension age and OADR. The negative
@@
 applications. Therefore, the target pension age scheme
-\(\bm{\text{PA}}^{target}\) can be defined in the following way: for
-\(h=1,2,\dots,H\)
-
-\begin{equation}
+\(\bm{\text{PA}}^{\text{target}}\) can be defined in the following way:
+for \(h=1,2,\dots,H\)
+
+\begin{equation*}
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation}\begin{align*}
+\end{equation*}\begin{align*}
   \text{subject to the constraint~} 0\leq \text{PA}_{n+h}-\text{PA}_{n+h-1}\leq 1
@@
 value of pension age is at 65 for all
-years\footnote{Even though pension age for males and females is 65 and 64.5 respectively.
+years\footnote{Even though pension age for males and females is 65.5 in mid-2017.
 The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in 2017 onward},
-which is:
+This simplification is reasonable because the pension age will be same in mid-2017 onward},
+which is: \vspace{-.3in}
 
@@
 \([\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]\) by a month
-at a time, unless we find that
-
-\begin{align}
-  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \text{~or~} \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
-\end{align}
+at a time, unless we find that \vspace{-.2in}
+
+\begin{align*}
+  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \quad \text{~or~}\quad  \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
+\end{align*}
 
@@
 age schemes is similar to the algorithm to find the target pension age
-scheme, except that the mean value of OADR in equation (28) is replaced
-by the boundary of the 80\% prediction interval. Mean is replaced by the
-upper (lower) limit of the 80\% prediction interval to find upper
-(lower) boundary for pension age schemes.
+scheme, except that the mean value of OADR is replaced by the boundary
+of the 80\% prediction interval. Mean is replaced by the upper (lower)
+limit of the 80\% prediction interval to find upper (lower) boundary for
+pension age schemes.
 
@@
 in section 3.2.2. It is assumed that it is impractical to change the
-pension age during 2011--2015, so the pension age has to be set at 65
+pension age during 2011--2014, so the pension age has to be set at 65
 for those years. Figure \ref{fig:OADRwithoptimal} provides a visible
@@
 desired OADR level, which indicates that we have successfully found the
-pension age with stable OADR at the desired levels.
+pension age with stable OADR at the desired
+levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
 
@@
 \centering
-\begin{tabular}{llllllll}
+\begin{tabular}{llllllllll}
 \toprule
-Year & Age & Year & Age & Year & Age & Year & Age\\
+Year & Age & Year & Age & Year & Age & Year & Age & Year & Age\\
 \midrule
-2016 & 65Y & 2021 & 65Y+6M & 2026 & 66Y+9M & 2031 & 68Y+3M\\
-2017 & 65Y & 2022 & 65Y+8M & 2027 & 67Y+3M & 2032 & 68Y+3M\\
-2018 & 65Y & 2023 & 65Y+11M & 2028 & 67Y+3M & 2033 & 68Y+9M\\
-2019 & 65Y & 2024 & 66Y+3M & 2029 & 67Y+9M & 2034 & 68Y+9M\\
-2020 & 65Y & 2025 & 66Y+9M & 2030 & 67Y+9M & 2035 & 69Y+3M\\
+2015 & 65Y & 2025 & 66Y+9M & 2035 & 69Y+3M & 2045 & 71Y+3M & 2055 & 71Y+3M\\
+2016 & 65Y & 2026 & 67Y+3M & 2036 & 69Y+9M & 2046 & 71Y+3M & 2056 & 71Y+3M\\
+2017 & 65Y & 2027 & 67Y+3M & 2037 & 69Y+9M & 2047 & 71Y+3M & 2057 & 71Y+3M\\
+2018 & 65Y & 2028 & 67Y+9M & 2038 & 70Y+3M & 2048 & 71Y+3M & 2058 & 71Y+3M\\
+2019 & 65Y & 2029 & 67Y+9M & 2039 & 70Y+3M & 2049 & 71Y+3M & 2059 & 71Y+4M\\
+\addlinespace
+2020 & 65Y+5M & 2030 & 68Y+3M & 2040 & 70Y+9M & 2050 & 71Y+3M & 2060 & 71Y+5M\\
+2021 & 65Y+9M & 2031 & 68Y+3M & 2041 & 70Y+9M & 2051 & 71Y+3M & 2061 & 71Y+7M\\
+2022 & 65Y+11M & 2032 & 68Y+9M & 2042 & 71Y+3M & 2052 & 71Y+3M & 2062 & 71Y+9M\\
+2023 & 66Y+3M & 2033 & 68Y+9M & 2043 & 71Y+3M & 2053 & 71Y+3M & 2063 & 71Y+10M\\
+2024 & 66Y+9M & 2034 & 69Y+3M & 2044 & 71Y+3M & 2054 & 71Y+3M & 2064 & 71Y+10M\\
 \bottomrule
@@
 \centering
-\begin{tabular}{llllllllllll}
+\fontsize{7}{9}\selectfont
+\begin{tabular}{lllllllllllllll}
 \toprule
-Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi\\
+Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi & Year & Lo & Hi\\
 \midrule
-2016 & 65Y & 65Y & 2021 & 65Y+4M & 65Y+7M & 2026 & 66Y+6M & 66Y+11M & 2031 & 68Y & 68Y+7M\\
-2017 & 65Y & 65Y & 2022 & 65Y+7M & 65Y+11M & 2027 & 67Y & 67Y+5M & 2032 & 68Y & 68Y+8M\\
-2018 & 65Y & 65Y & 2023 & 65Y+9M & 66Y+2M & 2028 & 67Y & 67Y+6M & 2033 & 68Y+6M & 69Y+2M\\
-2019 & 65Y & 65Y & 2024 & 66Y & 66Y+5M & 2029 & 67Y+6M & 68Y & 2034 & 68Y+6M & 69Y+2M\\
-2020 & 65Y & 65Y & 2025 & 66Y+6M & 66Y+11M & 2030 & 67Y+6M & 68Y+1M & 2035 & 69Y & 69Y+8M\\
+2015 & 65Y & 65Y & 2025 & 66Y+6M & 66Y+11M & 2035 & 68Y & 69Y+8M & 2045 & 70Y & 71Y+8M & 2055 & 70Y & 72Y+1M\\
+2016 & 65Y & 65Y & 2026 & 67Y & 67Y+5M & 2036 & 68Y+6M & 70Y+2M & 2046 & 70Y & 71Y+8M & 2056 & 70Y & 72Y+3M\\
+2017 & 65Y & 65Y & 2027 & 67Y & 67Y+6M & 2037 & 68Y+6M & 70Y+2M & 2047 & 70Y & 71Y+8M & 2057 & 70Y & 72Y+6M\\
+2018 & 65Y & 65Y & 2028 & 67Y+6M & 68Y & 2038 & 69Y & 70Y+8M & 2048 & 70Y & 71Y+8M & 2058 & 70Y & 72Y+8M\\
+2019 & 65Y & 65Y & 2029 & 67Y+6M & 68Y+1M & 2039 & 69Y & 70Y+8M & 2049 & 70Y & 71Y+8M & 2059 & 70Y & 72Y+10M\\
+\addlinespace
+2020 & 65Y+4M & 65Y+7M & 2030 & 68Y & 68Y+7M & 2040 & 69Y+6M & 71Y+2M & 2050 & 70Y & 71Y+8M & 2060 & 70Y & 73Y+1M\\
+2021 & 65Y+6M & 65Y+11M & 2031 & 68Y & 68Y+8M & 2041 & 69Y+6M & 71Y+2M & 2051 & 70Y & 71Y+8M & 2061 & 70Y & 73Y+3M\\
+2022 & 65Y+9M & 66Y+2M & 2032 & 68Y+6M & 69Y+2M & 2042 & 70Y & 71Y+8M & 2052 & 70Y & 71Y+8M & 2062 & 70Y & 73Y+5M\\
+2023 & 66Y & 66Y+5M & 2033 & 68Y+6M & 69Y+2M & 2043 & 70Y & 71Y+8M & 2053 & 70Y & 71Y+9M & 2063 & 70Y & 73Y+8M\\
+2024 & 66Y+6M & 66Y+11M & 2034 & 69Y & 69Y+8M & 2044 & 70Y & 71Y+8M & 2054 & 70Y & 71Y+11M & 2064 & 70Y & 73Y+10M\\
 \bottomrule
 \end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year & 2011   & 2012     & 2013   & 2014  & 2015   & 2016   & 2017   & 2018  \\
-Age  & 65Y    & 65Y      & 65Y    & 65Y   & 65Y    & 65Y7M  & 65Y10M & 66Y2M \\
-\hline
-Year & 2019   & 2020     & 2021   & 2022  & 2023   & 2024   & 2025   & 2026  \\
-Age  & 66Y5M  & 66Y8M    & 67Y    & 67Y3M & 67Y7M  & 67Y10M & 68Y2M  & 68Y5M \\
-\hline
-Year & 2027   & 2028     & 2029   & 2030  & 2031   & 2032   & 2033   & 2034  \\
-Age  & 68Y8M  & 69Y      & 69Y3M  & 69Y7M & 69Y10M & 70Y2M  & 70Y5M  & 70Y8M \\
-\hline
-Year & 2035   & 2036     & 2037   & 2038  & 2039   & 2040   & 2041   & 2042  \\
-Age  & 70Y11M & 71Y2M    & 71Y3M  & 71Y6M & 71Y8M  & 71Y10M & 72Y    & 72Y2M \\
-\hline
-Year & 2043   & 2044     & 2045   & 2046  & 2047   & 2048   & 2049   & 2050  \\
-Age  & 72Y5M  & 72Y8M    & 72Y11M & 73Y1M & 73Y3M  & 73Y5M  & 73Y7M  & 73Y8M \\
-\hline
-Year & 2051   & 2052     & 2053   & 2054  & 2055   & 2056   & 2057   & 2058  \\
-Age  & 73Y10M & 73Y11M   & 74Y1M  & 74Y3M & 74Y5M  & 74Y7M  & 74Y9M  & 75Y   \\
-\hline
-Year & 2059   & 2060  \\
-Age  & 75Y3M  & 75Y4M \\
-\hline
-\end{tabular}
-
-\caption{Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months.}
-
-\vspace{0.6cm}
-
-\begin{tabular}{rrrrrrrrr}
-\hline
-Year  & 2011  & 2012      & 2013   & 2014   & 2015   & 2016   & 2017   & 2018   \\
-Lower & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y5M  & 65Y8M  & 66Y11M \\
-Upper & 65Y   & 65Y       & 65Y    & 65Y    & 65Y    & 65Y9M  & 66Y    & 66Y4M  \\
-\hline
-Year  & 2019  & 2020      & 2021   & 2022   & 2023   & 2024   & 2025   & 2026   \\
-Lower & 66Y2M & 66Y5M     & 66Y8M  & 66Y11M & 67Y2M  & 67Y5M  & 67Y8M  & 67Y11M \\
-Upper & 66Y8M & 67Y       & 67Y4M  & 67Y8M  & 67Y11M & 68Y4M  & 68Y7M  & 68Y11M \\
-\hline
-Year  & 2027  & 2028      & 2029   & 2030   & 2031   & 2032   & 2033   & 2034   \\
-Lower & 68Y2M & 68Y5M     & 68Y8M  & 68Y11M & 69Y4M  & 69Y5M  & 69Y8M  & 69Y11M \\
-Upper & 69Y4M & 69Y6M     & 69Y10M & 70Y2M  & 70Y6M  & 70Y9M  & 71Y1M  & 71Y4M  \\
-\hline
-Year  & 2035  & 2036      & 2037   & 2038   & 2039   & 2040   & 2041   & 2042   \\
-Lower & 70Y1M & 70Y4M     & 70Y5M  & 70Y6M  & 70Y8M  & 70Y10M & 71Y    & 71Y4M  \\
-Upper & 71Y8M & 71Y11M    & 72Y2M  & 72Y4M  & 72Y7M  & 72Y9M  & 73Y    & 73Y4M  \\
-\hline
-Year  & 2043  & 2044      & 2045   & 2046   & 2047   & 2048   & 2049   & 2050   \\
-Lower & 71Y5M & 71Y8M     & 71Y10M & 71Y11M & 72Y    & 72Y2M  & 72Y3M  & 72Y4M  \\
-Upper & 73Y5M & 73Y8M     & 74Y    & 74Y3M  & 74Y5M  & 74M8M  & 74Y10M & 75Y    \\
-\hline
-Year  & 2051  & 2052      & 2053   & 2054   & 2055   & 2056   & 2057   & 2058   \\
-Lower & 72Y5M & 72Y7M     & 72Y8M  & 72Y10M & 73Y    & 73Y2M  & 73Y4M  & 73Y7M  \\
-Upper & 75Y2M & 75Y4M     & 75Y6M  & 75Y8M  & 75Y10M & 76Y    & 76Y3M  & 76Y5M  \\
-\hline
-Year  & 2059  & 2060 \\
-Lower & 73Y9M & 73Y11M \\
-Upper & 76Y8M & 76Y10M \\
-\hline
-\end{tabular}
-
-\caption{Fifth-years lower and higher boundary of pension age scheme with one boundary of 80\% OADR around desired OADR. Y denotes years and M denotes months.}
 \end{table}
@@
 scheme in this paper) are reported in Table 2, and their corresponding
-OADR simulation results are shown in \ref{fig:OADRboundaries}. It can be
-seen that the lower (upper) limit of the 80\% prediction interval of
-OADR associated with lower (upper) boundary of the 80\% confidence
+OADR simulation results are shown in Figure \ref{fig:OADRboundaries}. It
+can be seen that the lower (upper) limit of the 80\% prediction interval
+of OADR associated with lower (upper) boundary of the 80\% confidence
 interval pension age scheme is entirely stable around the desired level.
@@
 next generation to provide a very generous age pension immediately.
-\todo{Han feels Tables 3 and 4 should be removed?}
 
@@
 associated with desired OADR equal to current level plus 1\% has been
-found. We have shown the comparison of it \todo{Han confused} and its
-80\% confidence level with real pension age scheme in Figure
-\ref{fig:ComparisonwithOADR22}. When we allow 1\% more in desired OADR,
-the real pension age becomes plausible. Figure
-\ref{fig:OADR_realpensionage} shows simulated OADR associated with
-proposed pension age
+found. We have shown the comparison of it
+\todo{code are missing for two figures} and its 80\% confidence level
+with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
+When we allow 1\% more in desired OADR, the real pension age becomes
+plausible. Figure \ref{fig:OADR_realpensionage} shows simulated OADR
+associated with proposed pension age
 scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.

### 2020-05-03 PensionAge.Rmd
New Australian data

@@
 knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
-# Make sure you have the latest version of rmarkdown and bookdown
-# devtools::install_github("rstudio/rmarkdown")
-# devtools::install_github("rstudio/bookdown")
-# And the latest versions of Our packages
-# devtools::install_github("robjhyndman/forecast")
-# devtools::install_github("robjhyndman/demography")
-# devtools::install_github("robjhyndman/addb")
+library(tidyverse)
 library(demography)
+#remotes::install_github("robjhyndman/addb")
 library(addb)
-library(ggplot2)
 library(kableExtra)
+library(patchwork)
 source("functions-v4.R")
+source("hmd.R")
 ```
@@
 ```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
-year <- 2057 - 2007
-proposed <- ts(pmin(
-  70,
-  c(rep(65, 2017 - 2008), 65 + cumsum(rep(c(0.5, 0), 55)))
-)[1:50],
-start = 2008
-)
-approved <- pmin(proposed, 67)
-current <- pmin(proposed, 65)
-cols <- c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3")
-ggplot() +
-  forecast::autolayer(proposed, series = "proposed") +
-  forecast::autolayer(approved, series = "approved") +
-  forecast::autolayer(current, series = "current") +
+# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
+pension_age <- tibble(
+    year = 2008:2068,
+    current = 65
+  ) %>%
+  mutate(
+    proposed = pmin(70, current + 0.5*pmax(0, trunc((year - 2015)/2))),
+    approved = pmin(proposed, 67),
+  ) %>%
+  pivot_longer(-year, values_to="age", names_to="policy")
+
+pension_age %>%
+  filter(year <= 2050) %>%
+  ggplot(aes(x=year, y=age, group=policy)) +
+    geom_line(aes(col=policy)) +
     xlab("Year") + ylab("Age of retirement") +
     scale_color_manual(
-    values = cols, name = " ",
+      values = c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3"),
+      name = " ",
       breaks = c("current", "approved", "proposed"),
@@
 
-```{r getdata, include=FALSE}
-############################
-## GET ALL THE DATA
-############################
-
-# HMD credentials
-username <- "shl8858@telstra.com"
-password <- "hshang85"
-
-hmd.pop <- function (country, username, password, label = country) 
-{
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Population.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(pop) == "try-error") 
-        stop("Population file not found at www.mortality.org")
-    obj <- list(type = "population", label = label, lambda = 0)
-    obj$year = sort(unique(pop[, 1]))
-    n <- length(obj$year)
-    m <- length(unique(pop[, 2]))
-    obj$age <- pop[1:m, 2]
-    mnames <- names(pop)[-c(1, 2)]
-    n.pop <- length(mnames)
-    obj$pop <- list()
-    for (i in 1:n.pop) {
-        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
-        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
-        dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
-    }
-    names(obj$pop) <- tolower(mnames)
-    obj$age <- as.numeric(as.character(obj$age))
-    if (is.na(obj$age[m])) 
-        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
-    return(structure(obj, class = "demogdata"))
-}
-
-hmd.mx <- function (country, username, password, label = country) 
-{
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Mx_1x1.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    mx <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(mx) == "try-error") 
-        stop("Connection error at www.mortality.org. Please check username, password and country label.")
-    path <- paste("https://www.mortality.org/hmd/", country, "/STATS/", 
-        "Exposures_1x1.txt", sep = "")
-    userpwd <- paste(username, ":", password, sep = "")
-    txt <- RCurl::getURL(path, userpwd = userpwd)
-    con <- textConnection(txt)
-    pop <- try(utils::read.table(con, skip = 2, header = TRUE, 
-        na.strings = "."), TRUE)
-    close(con)
-    if (class(pop) == "try-error") 
-        stop("Exposures file not found at www.mortality.org")
-    obj <- list(type = "mortality", label = label, lambda = 0)
-    obj$year <- sort(unique(mx[, 1]))
-    n <- length(obj$year)
-    m <- length(unique(mx[, 2]))
-    obj$age <- mx[1:m, 2]
-    mnames <- names(mx)[-c(1, 2)]
-    n.mort <- length(mnames)
-    obj$rate <- obj$pop <- list()
-    for (i in 1:n.mort) {
-        obj$rate[[i]] <- matrix(mx[, i + 2], nrow = m, ncol = n)
-        obj$rate[[i]][obj$rate[[i]] < 0] <- NA
-        obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
-        obj$pop[[i]][obj$pop[[i]] < 0] <- NA
-        dimnames(obj$rate[[i]]) <- dimnames(obj$pop[[i]]) <- list(obj$age, 
-            obj$year)
-    }
-    names(obj$pop) = names(obj$rate) <- tolower(mnames)
-    obj$age <- as.numeric(as.character(obj$age))
-    if (is.na(obj$age[m])) 
-        obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
-    return(structure(obj, class = "demogdata"))
-}
-
-# Get population data for 1 Jan 2015
+```{r getdata, eval=FALSE}
+################################################
+################### DATA STEP ##################
+################################################
+
+# Get population data to 1 Jan 2019
 auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
-auspop <- extract.ages(auspop, age = 0:100)
-
-# Get mortality data
+auspop <- extract.ages(auspop, ages = 0:100)
+
+# Get mortality data to 2018
 aus.mort <- hmd.mx("AUS", username, password, "Australia")
-aus.mort <- extract.years(extract.ages(aus.mort, 0:100,
-  combine.upper = FALSE
-),
-year = 1950:max(aus.mort$year)
-)
-
-# Get fertility data:
-# Need to install addb package from http://robjhyndman.com/software/addb/
-library(addb) # Contains fertility data for 1921-2006
+aus.mort <- aus.mort %>%
+  extract.ages(ages = 0:100, combine.upper = FALSE) %>%
+  extract.years(years = 1950:max(aus.mort$year))
+
+# Get fertility data for 1921-2006
 aus.fert <- aus.fertility
 births <- aus.fert$rate$female * aus.fert$pop$female
-# Update fertility data to 2015
-ausf <- read.csv("FERTILITY_AGE_STATE_16062017173020984.csv",
-  header = TRUE,
-  stringsAsFactors = FALSE
-)
-# National births only
-ausf <- ausf[ausf$Region == "Australia", ]
-# Remove age aggregations
-ausf <- ausf[ausf$Age %in% paste(15:49), ]
-ausf[, "Age"] <- as.numeric(ausf[, "Age"])
+# Get latest fertility data from ABS (downloaded 30 April 2020)
+ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
+  filter(
+    Region == "Australia",
+    Age %in% paste(15:49),
+  ) %>%
+  mutate(
+    Year = Time,
+    Age = as.numeric(Age)
+  ) %>%
+  select(Year, Age, Measure, Value) 
 # Extract births and population values
-newbirths <- matrix(ausf[ausf$Measure == "Births", "Value"],
-  nrow = nrow(births), byrow = TRUE
-) * 1000
-newpop <- matrix(ausf[ausf$Measure == "Female population", "Value"],
-  nrow = nrow(births), byrow = TRUE
-) * 1000
+newbirths <- ausf %>%
+  filter(Measure == "Births") %>%
+  mutate(Value = Value * 1000) %>%
+  select(-Measure) %>%
+  pivot_wider(names_from=Year, values_from=Value) %>%
+  select(-Age) %>%
+  as.matrix()
+newpop <- ausf %>%
+  filter(Measure == "Female population") %>%
+  mutate(Value = Value) %>%
+  select(-Measure) %>%
+  pivot_wider(names_from=Year, values_from=Value) %>%
+  select(-Age) %>%
+  as.matrix()
 rownames(newbirths) <- rownames(newpop) <- 15:49
-colnames(newbirths) <- colnames(newpop) <- 2004:2015
-births <- cbind(births[, 1:83], newbirths)
-fpop <- cbind(aus.fert$pop$female[, 1:83], newpop / 1000)
+
+# Use ABS data where available
+births <- cbind(births[, 1:54], newbirths)
+fpop <- cbind(aus.fert$pop$female[, 1:54], newpop)
 # Use populations in ausf rather than auspop to get the same rates
@@
 aus.fert$pop$female <- fpop
-aus.fert$year <- 1921:2015
-
-aus.fert_v0 = extract.years(aus.fert, 1921:2014)
-
-##### MIGRATION
-aus.mig <- netmigration(mort = aus.mort, fert = aus.fert_v0, mfratio = 1.05)
-```
-
-```{r smoothing, dependson='getdata'}
+aus.fert$year <- 1920 + seq(NCOL(births))
+
+# Compute migration data
+aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = auspop, mfratio = 1.05)
+save(aus.fert, aus.mort, aus.mig, file="ausdata.Rdata")
+```
+
+```{r maketibble}
+load("ausdata.Rdata")
+
+auspop_df <- bind_rows(
+  as_tibble(auspop$pop$male / 1000) %>%
+    mutate(
+      Age = auspop$age,
+      Sex = "Male"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+  as_tibble(auspop$pop$female / 1000) %>%
+    mutate(
+      Age = auspop$age,
+      Sex = "Female"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+)
+```
+
+```{r smoothing}
 ################################################
@@
 ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
-ausfert.sm <- smooth.demogdata(aus.fert_v0, obs.var = "theoretical")
+ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
 ausmig.sm <- smooth.demogdata(aus.mig)
@@
 ```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
-plot(fertf, "c", comp = 2)
+autoplot(fertf)
 ```
@@
 # This takes a while!
-set.seed(2019-01-13)
+set.seed(2020-05-02)
 nsim <- 20 # Change to 2000 or higher to get better estimates
@@
 
-```{r simulationresults}
-## Means and intervals
-popm.mean <- apply(aus.sim$male, c(1, 2), mean, na.rm = TRUE)
-popm.lo <- apply(aus.sim$male, c(1, 2), quantile, p = .1, na.rm = TRUE)
-popm.hi <- apply(aus.sim$male, c(1, 2), quantile, p = .9, na.rm = TRUE)
-popf.mean <- apply(aus.sim$female, c(1, 2), mean, na.rm = TRUE)
-popf.lo <- apply(aus.sim$female, c(1, 2), quantile, p = .1, na.rm = TRUE)
-popf.hi <- apply(aus.sim$female, c(1, 2), quantile, p = .9, na.rm = TRUE)
-
-## TOTAL POPULATION COMPARISONS
-totfpop <- apply(aus.sim$female, c(2, 3), sum, na.rm = TRUE)
-totmpop <- apply(aus.sim$male, c(2, 3), sum, na.rm = TRUE)
-totfpop.q <- apply(totfpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
-totmpop.q <- apply(totmpop, 1, quantile, p = c(0.025, .1, .5, .9, .975), na.rm = TRUE) / 1e6
+```{r simtibble, dependson = 'simulation}
+# Combine simulation results into one tibble
+dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
+  Age = dimnames(aus.sim[[1]])[[1]],
+  Year = dimnames(aus.sim[[1]])[[2]],
+  Rep = dimnames(aus.sim[[1]])[[3]]
+)
+aussim_df <- bind_rows(
+  as.tbl_cube(aus.sim[["male"]]/1e3, met_name = "Population") %>% 
+    as_tibble() %>% mutate(Sex = "Male"),
+  as.tbl_cube(aus.sim[["female"]]/1e3, met_name = "Population") %>% 
+    as_tibble() %>% mutate(Sex = "Female")
+)
+#rm(aus.sim)
+# Combine simulations to create means and quantiles of future years
+future_pop <- aussim_df %>%
+  group_by(Sex, Age, Year) %>%
+  summarise(
+    Mean = mean(Population),
+    Lower = quantile(Population, prob=0.1),
+    Upper = quantile(Population, prob=0.9)
+  ) %>%
+  ungroup()
+future_tot_pop <- aussim_df %>%
+  group_by(Rep, Sex, Year) %>%
+  summarise(Population = sum(Population)/1e3) %>%
+  group_by(Sex, Year) %>%
+  summarise(
+    Mean = mean(Population),
+    Median = median(Population),
+    Lo95 = quantile(Population, prob=0.025),
+    Up95 = quantile(Population, prob=0.975),
+    Lo80 = quantile(Population, prob=0.1),
+    Up80 = quantile(Population, prob=0.9)
+  ) %>%
+  ungroup()
+# Historical data as a tibble
+history_pop <- bind_rows(
+  as_tibble(auspop$pop$male / 1000) %>%
+    mutate(
+      Age = auspop$age,
+      Sex = "Male"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+  as_tibble(auspop$pop$female / 1000) %>%
+    mutate(
+      Age = auspop$age,
+      Sex = "Female"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+  ) %>%
+  mutate(Year = as.numeric(Year))
+history_tot_pop <- history_pop %>%
+  group_by(Sex, Year) %>%
+  summarise(Population = sum(Population)/1e3)
 ```
@@
 The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(3.3, 3.6, 1.1, 1.1))
-par(mfrow = c(1, 2))
-fy <- fertf$year
-plot(auspop$year, colSums(auspop$pop$female) / 1e6,
-  xlim = c(1950, 2064),
-  ylim = range(c(0, 30), na.rm = TRUE),
-  xlab = "Year",
-  ylab = "Population (millions)",
-  main = "Total female population"
-)
-polygon(c(fy, rev(fy)),
-  c(totfpop.q[2, ], rev(totfpop.q[4, ])),
-  col = "yellow", border = FALSE
-)
-lines(fy, totfpop.q[3, ], lwd = 2, col = "blue")
-
-plot(auspop$year, colSums(auspop$pop$male) / 1e6,
-  xlim = c(1950, 2064),
-  ylim = range(c(0, 30), na.rm = TRUE),
-  xlab = "Year",
-  ylab = "Population (millions)",
-  main = "Total male population"
-)
-polygon(c(fy, rev(fy)),
-  c(totmpop.q[2, ], rev(totmpop.q[4, ])),
-  col = "yellow", border = FALSE
-)
-lines(fy, totmpop.q[3, ], lwd = 2, col = "blue")
+history_tot_pop %>% 
+  ggplot(aes(x=Year, y=Population, group=Sex)) +
+    geom_line(size=1) +
+    ylab("Population (millions)") + 
+    ggtitle("Total population") +
+    facet_grid(. ~ Sex) +
+    geom_ribbon(aes(y=Mean, ymin=Lo80, ymax=Up80), fill='#7d7def', data=future_tot_pop) +
+    geom_line(data=future_tot_pop, col='blue', mapping=aes(y=Mean), size=1) 
 ```
@@
 The actual pyramid for 2015 is shown using dashed lines.", , dependson='simulationresults'}
-par(mgp = c(2.2, 0.45, 0), tcl = -0.4, mar = c(4.3, 3.6, 3.0, 3.3))
-plot(c(0, 100), c(0, 100),
-  type = "n", main = "Forecast population: 2034", yaxt = "n",
-  xlab = "Population ('000)", ylab = "Age", xaxt = "n", xlim = c(-1, 1) * max(abs(popm.hi[, 20]), abs(popf.hi[, 20])) / 1e3
+pyramid <- function(history, future) {
+  data <- bind_rows(history, future)
+  p_male <- data %>%
+    filter(Sex == "Male") %>%
+    ggplot(aes(x = Age, y = Population, group=Year)) +
+      labs(y = "Population ('000)") +
+      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
+      geom_line(linetype=2) + geom_line(aes(y=Mean), col='blue') + 
+      coord_flip() +
+      scale_y_reverse(expand=c(0.012, 0.012)) +
+      scale_x_continuous(expand=c(0.012,0.012)) +
+      facet_grid(. ~ Sex)
+  p_female <- data %>%
+    filter(Sex == "Female") %>%
+    ggplot(aes(x = Age, y = Population, group=Year)) +
+      labs(y = "Population ('000)") +
+      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
+      geom_line(linetype=2) + geom_line(aes(y=Mean), col='blue') + 
+      coord_flip() +
+      scale_y_continuous(expand=c(0.012,0.012)) +
+      theme(axis.title.y.left=element_blank(),
+        axis.text.y.left=element_blank(),
+        axis.ticks.y.left=element_blank()) +
+      scale_x_continuous(position="top", sec.axis = sec_axis(~ .), expand=c(0.012,0.012)) +
+      facet_grid(. ~ Sex)
+
+  (p_male | p_female) 
+}
+pyramid(
+  history_pop %>% filter(Year == max(Year)),
+  future_pop %>% filter(Year == max(history_pop$Year) + 20) 
 )
-mtext("Male                       Female")
-abline(v = 0)
-axis(1, at = seq(-300, 0, by = 50), labels = rev(seq(0, 300, by = 50)))
-axis(1, at = seq(50, 300, by = 50))
-axis(2, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
-axis(4, at = seq(0, 100, by = 10), labels = seq(0, 100, by = 10))
-axis(2, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
-axis(4, at = seq(0, 100, by = 20), labels = seq(0, 100, by = 20))
-axis(4, at = 50, line = 1.5, labels = "Age", col = 2, tick = FALSE)
-polygon(c(-popm.lo[, 20], rev(-popm.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
-polygon(c(popf.lo[, 20], rev(popf.hi[, 20])) / 1000, c(0:100, 100:0), col = "yellow", border = FALSE)
-lines(-auspop$pop$male[, ncol(auspop$pop$male)] / 1000, 0:100, col = 1, lty = 2)
-lines(auspop$pop$female[, ncol(auspop$pop$female)] / 1000, 0:100, col = 1, lty = 2)
-text(100, 60,  "2015")
-text(-100, 60, "2015")
-lines(-popm.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
-lines(popf.mean[, 20] / 1000, 0:100, col = "blue", lwd = 2)
 ```
@@
 ```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
-OADR.f <- oadr(auspop, aus.sim, pension.age = current)
-autoplot(OADR.f) + xlab("year") + ylab("ratio") +
+current <- pension_age %>% 
+  filter(policy=="current", year %in% unique(tot_pop$Year) ) %>% 
+  arrange(year) %>% pull(age)
+proposed <- pension_age %>% 
+  filter(policy=="proposed", year %in% unique(tot_pop$Year) ) %>% 
+  arrange(year) %>% pull(age)
+approved <- pension_age %>% 
+  filter(policy=="approved", year %in% unique(tot_pop$Year) ) %>% 
+  arrange(year) %>% pull(age)
+OADR.65 <- oadr(history, aussim_df, pension.age = current) %>% mutate(policy="Pension age 65")
+OADR.65 %>%
+  ggplot(aes(x=Year, y=OADP, group=Sex)) +
+    geom_ribbon(aes(ymin=Lo, ymax=Hi), fill='#7d7def') +
+    geom_line(col='blue', size=1) +
+    facet_grid(. ~ Sex) +
+    xlab("year") + ylab("ratio") +
     ggtitle("OADR forecasts with pension age=65")
@@
 The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
-OADR.f.67 <- oadr(auspop, aus.sim, pension.age = approved)
-OADR.f.prop <- oadr(auspop, aus.sim, pension.age = proposed)
-autoplot(OADR.f$x) +
+OADR.67 <- oadr(history, aussim_df, pension.age = approved) %>% 
+  mutate(policy="Current policy")
+OADR.prop <- oadr(history, aussim_df, pension.age = proposed) %>% 
+  mutate(policy="Proposed policy")
+bind_rows(OADR.65,OADR.67,OADR.prop) %>%
+  mutate(policy = factor(policy, 
+    levels = c("Pension age 65","Current policy","Proposed policy"))) %>%
+  ggplot(aes(x=Year, y=OADP, group=policy)) +
+    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=policy), alpha=0.5) +
+    geom_line(aes(col=policy), size=1) +
     geom_hline(yintercept = 0.21, col = "gray") +
-  autolayer(OADR.f, series = "current", alpha = 0.5) +
-  autolayer(OADR.f.67, series = "approved", alpha = 0.5) +
-  autolayer(OADR.f.prop, series = "proposed", alpha = 0.5) +
-  ylab("ratio") + xlab("Year") +
-  ggtitle("OADR forecasts") +
-  scale_color_manual(
-    values = cols, name = " ",
-    breaks = c("current", "approved", "proposed"),
-    labels = c("Pension age at 65", "Approved change", "Proposed further change")
-  )
+    facet_grid(. ~ Sex) +
+    xlab("year") + ylab("ratio") +
+    ggtitle("OADR forecasts with pension age=65") +
+    scale_color_brewer(palette="Dark2") + scale_fill_brewer(palette="Dark2")
 ```

### 2020-05-03 PensionAge.tex
New Australian data

@@
             pdftitle={Forecasting the old-age dependency ratio to determine the best pension age},
-            pdfkeywords={functional time series model, coherent forecasts, demographic
-components, pension and insurance},
+            pdfkeywords={functional time series model, coherent forecasts, demographic components, pension and insurance},
             pdfborder={0 0 0},
@@
 
-\title{Forecasting the old-age dependency ratio to determine the best pension
-age}
+\title{Forecasting the old-age dependency ratio to determine the best pension age}
 
@@
 \addresses{\textbf{Rob J Hyndman}\newline
-Department of Econometrics \& Business Statistics\newline Monash
-University, Clayton VIC 3800, Australia
+Department of Econometrics \& Business Statistics\newline Monash University, Clayton VIC 3800, Australia
 \newline{Email: \href{mailto:Rob.Hyndman@monash.edu}{\nolinkurl{Rob.Hyndman@monash.edu}}}\newline Corresponding author\\[1cm]
@@
 \usepackage{todonotes, xcolor}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 \begin{abstract}
-We forecast the old-age dependency ratio for Australia under various
-pension age proposals, and estimate a pension age scheme that will
-provide a stable old-age dependency ratio at a specified level. Our
-approach involves a stochastic population forecasting method based on
-coherent functional data models for mortality, fertility and net
-migration, which we use to simulate future age-structures of the
-population. We apply these ideas to Australian historical demographic
-data and the results suggest that the pension age should be increased to
-67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age
-dependency ratio at the current level, which is 21\%. This approach can
-easily be extended to other target levels of the old-aged dependency
-ratio and to other countries.
+We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
+Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the current level, which is 21\%.
+This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
 \end{abstract}
 \begin{keywords}
-functional time series model, coherent forecasts, demographic
-components, pension and insurance
+functional time series model, coherent forecasts, demographic components, pension and insurance
 \end{keywords}
 
-\section{Introduction}\label{introduction}
-
-Australia's ageing population is a result of three factors: (1)
-significant technological advances in medical care leading to longer
-life spans; (2) high fertility rates after World War II resulting in the
-``baby-boomer'' generation; and (3) a large decline in fertility rates
-over the past twenty or so years \autocite{Fehr2008}. Consequently,
-there are many older people leaving the workforce, and fewer workers
-replacing them. Similar demographic challenges face many other
-countries. One way of measuring this problem is via the old-age
-dependency ratio (OADR): the number of people post-retirement to the
-number of people of working age \autocite{Walker1982}. The OADR has been
-increasing for many decades, but recently the rate of increase has
-jumped markedly, and we show that it will continue to increase at a
-rapid rate if there are no age-related policy changes.
-
-This is consistent with the Australian Intergenerational Reports
-\autocites{IGR02}{IGR07}{Swan2010} that explored the extent to which
-existing age-related policies would affect the burden of future working
-generations. To date, the Australian government has addressed the
-problem through a variety of approaches including modifications to
-compulsory superannuation policies, instigating work incentives for
-older people, and increasing the pension age (defined as the age at
-which eligible residents can access the age pension for the first time).
-In 2009, the federal government announced an increase in pension age
-from 65 to 67 by 2023 \autocite{Nielson2010}. In May 2014, the Federal
-Treasurer proposed a further increase in the pension age to 70 by 2035.
-This new proposal is in line with the recommendations from the
-\textcite{PC13} and the \textcite{NCOA2014}. In this paper, we
-investigate the effect of these changes in the pension age on the
-forecast OADR.
-
-The research presented in this paper contributes to the discussion by
-forecasting the age structure of the population, quantifying the effects
-of changing the pension age on financial burdens, and hence finding an
-appropriate pension age scheme which is economically viable for
-Australia. The analysis of economic impact of increasing pension age can
-be complicated. In this paper, we will focus on only one aspect: the
-impact on the burden of future working age generations.
-
-In this paper, we use the OADR as a measure of the financial burden on
-the Australian workforce because a rise in the OADR will reduce the
-ability of working age population to finance pensions and health costs
-\autocites{ARW07}{IGR02}{IGR07}. The OADR is defined as the ratio of the
-number of people aged over the pension age to the number of people of
-working age \autocite{ARW07}. This can be expressed using the formula
-below:
-
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past twenty or so years \autocite{Fehr2008}.
+Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
+Similar demographic challenges face many other countries.
+One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \autocite{Walker1982}.
+The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
+
+This is consistent with the Australian Intergenerational Reports \autocites{IGR02}{IGR07}{Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
+To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
+In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 \autocite{Nielson2010}.
+In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035.
+This new proposal is in line with the recommendations from the \textcite{PC13} and the \textcite{NCOA2014}.
+In this paper, we investigate the effect of these changes in the pension age on the forecast OADR.
+
+The research presented in this paper contributes to the discussion by forecasting the age structure of the population, quantifying the effects of changing the pension age on financial burdens, and hence finding an appropriate pension age scheme which is economically viable for Australia.
+The analysis of economic impact of increasing pension age can be complicated.
+In this paper, we will focus on only one aspect: the impact on the burden of future working age generations.
+
+In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs \autocites{ARW07}{IGR02}{IGR07}.
+The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age \autocite{ARW07}.
+This can be expressed using the formula below:
 \begin{equation}
@@
 \end{equation}
-
-We provide forecasts of future population age structures over the next
-50 years. We then use those forecasts to compute the OADR associated
-with pension age both before and after the adjustments. One contribution
-of the current study is the combined use of the Hyndman-Ullah
-forecasting method \autocite{HU07} and the product-ratio method
-\autocite{HBY13} to forecast a population age structure. Forecasts of
-population structure have been built on forecasts of age- and
-gender-specific mortality rates, fertility rates and net migration using
-this method. These forecasts presuppose that the historical trends of
-past years will continue. Historical data of those rates have thus been
-used as input to simulate future paths of age- and gender-specific
-population structure.
-
-Using these predicted population paths, we can calculate the average
-OADR and predict the levels of old-age dependency that correspond to
-different pension age schemes. By testing different pension age schemes,
-we aim to find the pension age with the desired OADR outcome. Therefore,
-other contributions of this research are (1) to examine the effect of
-adjusting pension ages by comparing OADR before and after adjustment;
-and (2) to suggest a suitable pension age scheme to ensure that the
-economic burden will remain relatively constant at a desired level in
-the future. It should be noted that the desired level has been set at
-21\%, the estimated level of OADR in 2014. Whether this OADR level is
-the most appropriate level for Australia remains to be examined and is
-not the focus of this paper. This paper concentrates on providing a
-framework for policy makers to find a target pension age for a given
-desired level of OADR.
-
-Some may argue that using OADR as a measure of financial burden for the
-next generation could be biased, with a large number of retirees able to
-rely on self-financed retirement income, such as superannuation.
-However, 80\% of Australians over pension age rely fully or partly on
-the age pension \autocite{Power14}. Therefore, the proportion of people
-over working age is still a good representation of financial burden on
-future working generations. Nevertheless, using OADR as a single
-measurement of financial burden may overlook some important economic
-factors, and \textcite{HY12} have suggested the use of an adjusted OADR
-that takes account of some of these factors in analyzing pension
-finance. We do not consider these here. Our approach is intended to
-illustrate how population forecasting can be used to explore the pension
-age issue in a simple context, and it could be extended to take into
-account other variables.
-
-The remainder of this paper proceeds as follows. Section
-\ref{sec:litreview} reviews key literature on population forecasting and
-the pension age in Australia. Section \ref{sec:data} describes the data
-and modelling framework we use in this study. We show how our framework
-can be used to estimate a pension age scheme that leads to a target OADR
-in Section \ref{sec:target}. Finally, Section \ref{sec:conclusions}
-gives concluding remarks as well as identifies the scope for future
-research.
-
-\section{Background and Literature Review}\label{sec:litreview}
-
-\subsection{The age pension in
-Australia}\label{the-age-pension-in-australia}
-
-Age pension in Australia is an income support and provides access to a
-range of concessions for older Australians who have passed means
-testing. For example, it provides single home-owners with a real income
-of \$13653 p.a and additional allowances to cover expenses such as rent
-or
-pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
-The means test ensures that retirees with enough personal savings will
-become ineligible for public provision by reducing the pension at fixed
-levels of pay as personal wealth increases. The age pension in Australia
-is very generous, even with the means test. For instance, a couple
-holding assets of more than one million dollars is still eligible for a
-partial age pension.
-
-Currently, the age pension is the primary source of income for 70\%
--80\% of Australian residents over 64 years \autocite{ABS06}. Even
-though the government has promoted self-financed retirement by
-introducing the Superannuation Guarantee in 1992, the Superannuation
-Guarantee accumulations are still modest, with the current average less
-than \$100,000 at retirement \autocite{ASFA07}. It has been estimated by
-\textcite{PT08} that a retiree will need to have \$450,000 at 65 in
-order to support a pension-equivalent income and this is more than eight
-times of the average retirement accumulation of Australians. The
-required wealth to comply with personal-funded retirement savings
-requirements is too high for most Australians, suggesting that retirees
-will continue to rely on the age pension in the coming decades.
-
-The ageing trend in Australia, along with retirees' dependence on the
-age pension, has dramatically increased the fiscal cost of the age
-pension. For instance, the fiscal cost of the age pension is currently
-around at 2.5\% of Gross Domestic Profit (GDP), but is expected to
-increase to 4.4\% by the 2050s (Australian Government, 2007). The
-\textcite{PC13} also indicates the government will need to raise taxes
-by 21\% to pay for extra aged care and health costs, which is caused by
-longer life expectancies in newer generations.
-
-The issue is not only a problem for the government, but also for future
-retirees. Given children born today are expected to live up to their 90s
-on average, the \textcite{PC13} suggests that Australians won't be able
-to afford to spend 35 years in retirement (i.e., retire around 65). They
-have predicted that a third of baby boomers are expected to spend all
-their money and assets before they
-die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
-This problem might eventually deteriorate the sustainability of the age
-pension, although the welfare system works well at the moment, because
-demographic changes often have delayed effects \autocite{IGR02}.
+We provide forecasts of future population age structures over the next 50 years.
+We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments.
+One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method \autocite{HU07} and the product-ratio method \autocite{HBY13} to forecast a population age structure.
+Forecasts of population structure have been built on forecasts of age- and gender-specific mortality rates, fertility rates and net migration using this method.
+These forecasts presuppose that the historical trends of past years will continue.
+Historical data of those rates have thus been used as input to simulate future paths of age- and gender-specific population structure.
+
+Using these predicted population paths, we can calculate the average OADR and predict the levels of old-age dependency that correspond to different pension age schemes.
+By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
+Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
+It should be noted that the desired level has been set at 21\%, the estimated level of OADR in 2014.
+Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
+This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.
+
+Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
+However, 80\% of Australians over pension age rely fully or partly on the age pension \autocite{Power14}.
+Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.
+Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and \textcite{HY12} have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
+We do not consider these here.
+Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables.
+
+The remainder of this paper proceeds as follows.
+Section \ref{sec:litreview} reviews key literature on population forecasting and the pension age in Australia.
+Section \ref{sec:data} describes the data and modelling framework we use in this study.
+We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \ref{sec:target}.
+Finally, Section \ref{sec:conclusions} gives concluding remarks as well as identifies the scope for future research.
+
+\hypertarget{sec:litreview}{%
+\section{Background and Literature Review}\label{sec:litreview}}
+
+\hypertarget{the-age-pension-in-australia}{%
+\subsection{The age pension in Australia}\label{the-age-pension-in-australia}}
+
+Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing.
+For example, it provides single home-owners with a real income of \$13653 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
+The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases.
+The age pension in Australia is very generous, even with the means test.
+For instance, a couple holding assets of more than one million dollars is still eligible for a partial age pension.
+
+Currently, the age pension is the primary source of income for 70\% -80\% of Australian residents over 64 years \autocite{ABS06}.
+Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the current average less than \$100,000 at retirement \autocite{ASFA07}.
+It has been estimated by \textcite{PT08} that a retiree will need to have \$450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
+The required wealth to comply with personal-funded retirement savings requirements is too high for most Australians, suggesting that retirees will continue to rely on the age pension in the coming decades.
+
+The ageing trend in Australia, along with retirees' dependence on the age pension, has dramatically increased the fiscal cost of the age pension.
+For instance, the fiscal cost of the age pension is currently around at 2.5\% of Gross Domestic Profit (GDP), but is expected to increase to 4.4\% by the 2050s (Australian Government, 2007).
+The \textcite{PC13} also indicates the government will need to raise taxes by 21\% to pay for extra aged care and health costs, which is caused by longer life expectancies in newer generations.
+
+The issue is not only a problem for the government, but also for future retirees.
+Given children born today are expected to live up to their 90s on average, the \textcite{PC13} suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65).
+They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
+This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects \autocite{IGR02}.
 
@@
 \includegraphics{PensionAge_files/figure-latex/changespension-1.pdf}
-\caption{\label{fig:changespension}Government's adjustments on pension age
-scheme.}
+\caption{\label{fig:changespension}Government's adjustments on pension age scheme.}
 \end{figure}
 
-The Australian government is trying to take early intervention in
-relation to the pension age to balance between providing social support
-and fiscal cost. The pension age for males has been set at 65 for over a
-century. While the pension age for females was 60 years until 1994, it
-has steadily increased to 65 years, in line with that of males. The
-previous Labor government announced in 2009 that the pension age will
-increase six months every two years until 2017, capping at 67 in July
-2023. This change is expected to have a significant impact on labor
-force participation and to decrease the retirement duration of residents
-because pension age is regarded as a normal age for retirement in
-Australia. However, the \textcite{PC13} proposed further lifting of the
-pension age to 70 on the grounds that increasing the pension age to 70
-would save taxpayers \$150 billion in welfare costs and health spending,
-and elderly people are capable of continuing work. The National
-Commission of Audit (NCOA) (2014) holds the same opinion, and
-recommended lifting the pension age to 70 from 2053. The current
-Treasurer Joe Hockey announced that the government would increase the
-pension age to 70 from 2035, which is proposed in the Federal Budget
-Statement for 2014-2015 to be confirmed by Australian Federal
-Government. Figure \ref{fig:changespension} illustrates the process of
-the adjustments on pension age scheme. This announcement received
-overwhelmingly negative responses in the media. \textcite{Guest14}
-argues from an economic prospective that Australia currently has much
-better circumstances than other OECD countries in terms of age pension
-pressure, because spending on the age pension in Australia is less than
-half of the OECD average. He also claims that Australia has a higher
-consumption of all other goods and services, and so why are they not
-allowed to have more leisure time. Further, \textcite{Power14} contends
-that many Australians are not physically able to work full-time to 70,
-so that recommendations made by the PC and NCOA are simplistic solutions
-to a more a complex social problem.
-
-In fact, all supportive arguments for increasing the pension age in
-Australia have only justified the need to increase the pension age. No
-justification on the pace or degree of the change has been provided.
-Also, the government has not disclosed the method it used to determine
-the new pension age. It is therefore not surprising that the adjustment
-of the pension age has been questioned by the public. A consistent
-method to determine the appropriate pension age would be more persuasive
-in general. For example, it is preferred by OECD countries that pension
-age should be linked to life expectancy \autocite{OECD12}. There is a
-practical issue as to how to link life expectancy with pension ages
-given that there is no information on future mortality rates
-\autocite{PC13}. \textcite[p7]{CEDA07} proposed directly linking pension
-age with life expectancy in the way that ``pension age should increase
-by approximately 50\% of any increase in life expectancy''. However,
-using a ``rule of thumb'' approach might not be ideal, as 50\% of the
-change in life expectancy may not be a good adjustment to pension age in
-the long term. Our study suggests an approach, linking the pension age
-with the the aged dependency ratio, based on forecasts of future
-mortality and fertility rates. Our approach has the advantage that it
-can be used to justify the change in pension age and directly links the
-pension age with our ultimate goal of a stable financial burden for the
-public.
-
-\subsection{Population forecasting}\label{population-forecasting}
-
-In population forecasting, two very different approaches: a
-deterministic approach (sometimes called a quasi-statistical approach)
-and a stochastic approach (a purely statistical approach) are frequently
-used. For instance, the Australian Bureau of Statistics (ABS) is using a
-deterministic approach for its demographic projection, while some other
-countries or institutes forecast demographic trends based on purely
-statistical approaches such as Statistics New Zealand and the United
-States Census Bureau. In the deterministic approach, experts project
-future demographic changes using judgement-based scenarios. It ignores
-the non-demographic factors such as major pandemics or wars, although
-historically they are important factors that affect demographic
-behaviour \autocite{PC13}. In stochastic approaches, the Lee-Carter (LC)
-method \autocite{LC92} is the most prominent demographic forecasting
-method, which now has several variants and extensions that relax some of
-the assumptions of the basic Lee-Carter method \autocite[see,
-e.g.,][]{SBH11}. Although statistical forecasting models are rigorous,
-they still leave a basis for judgment-based adaptation, as they
-sometimes produce unrealistic projections of demographic factors such as
-long-run projections of mortality rates \autocite{PC13}.
-
-Therefore, some official agencies decide to mix the two approaches in
-their forecasts in order to provide a supplement to both approaches. For
-instance, the most recent forecast of population in Australia by the
-\textcite{PC13} was based on basic Lee-Carter methods plus some
-judgement-based adaptations to address the characteristics of
-demographic trends that the Lee-Carter method failed to capture. The
-approach of forecasting used in this study is very similar to the
-\textcite{PC13}. The Hyndman-Ullah method (2007) is used as a basic
-forecasting approach, which is a comprehensive extension of Lee-Carter
-method. In addition, an adapted product-ratio method is used to
-eliminate the potential long-term divergence between female and male
-mortality rates. A more detailed review of forecasting methods is given
-below.
-
-\subsubsection{Deterministic Methods Used by the
-ABS}\label{deterministic-methods-used-by-the-abs}
-
-The deterministic method is judgment-based. The Australian Bureau of
-Statistics formulates assumptions on the basis of demographic trends, in
-conjunction with advice from individual experts or government
-departments. The projections are not predictions or forecasts, ``but are
-simply illustrations of the growth and change in population which would
-occur if certain assumptions about future levels of fertility,
-mortality, internal migration and overseas migration were to prevail
-over the projection period'' \autocite[p.2]{ABS12}. In addition, they do
-not attempt to take into account of non-demographic factors, such as
-major government policy changes and catastrophes. Therefore, they
-normally report multiple (usually three) series based on different
-levels of assumptions of demographic factors to allow for variety of
-population projections.
-
-\subsubsection{Lee-Carter Method}\label{lee-carter-method}
-
-The Lee-Carter method \autocite{LC92} is a significant milestone in
-demographic forecasting. It has been widely used to forecast mortality
-rates across various countries, including Australia.
+The Australian government is trying to take early intervention in relation to the pension age to balance between providing social support and fiscal cost.
+The pension age for males has been set at 65 for over a century.
+While the pension age for females was 60 years until 1994, it has steadily increased to 65 years, in line with that of males.
+The previous Labor government announced in 2009 that the pension age will increase six months every two years until 2017, capping at 67 in July 2023.
+This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because pension age is regarded as a normal age for retirement in Australia.
+However, the \textcite{PC13} proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
+The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
+The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government.
+Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.
+This announcement received overwhelmingly negative responses in the media.
+\textcite{Guest14} argues from an economic prospective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is less than half of the OECD average.
+He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time.
+Further, \textcite{Power14} contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more a complex social problem.
+
+In fact, all supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age.
+No justification on the pace or degree of the change has been provided.
+Also, the government has not disclosed the method it used to determine the new pension age.
+It is therefore not surprising that the adjustment of the pension age has been questioned by the public.
+A consistent method to determine the appropriate pension age would be more persuasive in general.
+For example, it is preferred by OECD countries that pension age should be linked to life expectancy \autocite{OECD12}.
+There is a practical issue as to how to link life expectancy with pension ages given that there is no information on future mortality rates \autocite{PC13}.
+\textcite[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''.
+However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term.
+Our study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
+Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
+
+\hypertarget{population-forecasting}{%
+\subsection{Population forecasting}\label{population-forecasting}}
+
+In population forecasting, two very different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
+For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
+In the deterministic approach, experts project future demographic changes using judgement-based scenarios.
+It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour \autocite{PC13}.
+In stochastic approaches, the Lee-Carter (LC) method \autocite{LC92} is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method \autocite[see, e.g.,][]{SBH11}.
+Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates \autocite{PC13}.
+
+Therefore, some official agencies decide to mix the two approaches in their forecasts in order to provide a supplement to both approaches.
+For instance, the most recent forecast of population in Australia by the \textcite{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
+The approach of forecasting used in this study is very similar to the \textcite{PC13}.
+The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of Lee-Carter method.
+In addition, an adapted product-ratio method is used to eliminate the potential long-term divergence between female and male mortality rates.
+A more detailed review of forecasting methods is given below.
+
+\hypertarget{deterministic-methods-used-by-the-abs}{%
+\subsubsection{Deterministic Methods Used by the ABS}\label{deterministic-methods-used-by-the-abs}}
+
+The deterministic method is judgment-based.
+The Australian Bureau of Statistics formulates assumptions on the basis of demographic trends, in conjunction with advice from individual experts or government departments.
+The projections are not predictions or forecasts, ``but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period'' \autocite[p.2]{ABS12}.
+In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
+Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for variety of population projections.
+
+\hypertarget{lee-carter-method}{%
+\subsubsection{Lee-Carter Method}\label{lee-carter-method}}
+
+The Lee-Carter method \autocite{LC92} is a significant milestone in demographic forecasting. It has been widely used to forecast mortality rates across various countries, including Australia.
 
 The model proposed by \textcite{LC92} is as follows:
-
 \begin{equation}
@@
 \end{equation}
-
-where \(m_{x,t}\) is the central death
-rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}}
-for age \(x\) in year \(t\). This model involves fitting a matrix of log
-central death rates with sets of age-specific constants, \{\(a_x\)\} and
-\{\(b_x\)\}, and a time-varying index \(k_t\). \(b_x\) is a set of
-parameters that tell us the rate at which each age responds to changes
-in \(k_t\). \(k_t\) measures the general level of the log death rates;
-\(a_x\) is the general pattern across age of the log mortality rate and
-\(\epsilon_{x,t}\) is an error term with zero mean and constant
-variance, reflecting the randomness that can't be captured by the model.
-
-The model is under-determined in terms of estimation of parameters. For
-example, if the vector \(a,b,k\) is one solution, then for any scalar
-\(c\), \(a, b/c, kc\) or \(a - bc, b, k+c\) also must be two possible
-solutions. Therefore, Lee and Carter (1992) impose the following
-constraints:
-
+where \(m_{x,t}\) is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age \(x\) in year \(t\).
+This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(a_x\)\} and \{\(b_x\)\}, and a time-varying index \(k_t\).
+\(b_x\) is a set of parameters that tell us the rate at which each age responds to changes in \(k_t\).
+\(k_t\) measures the general level of the log death rates; \(a_x\) is the general pattern across age of the log mortality rate and \(\epsilon_{x,t}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
+
+The model is under-determined in terms of estimation of parameters.
+For example, if the vector \(a,b,k\) is one solution, then for any scalar \(c\), \(a, b/c, kc\) or \(a - bc, b, k+c\) also must be two possible solutions.
+Therefore, Lee and Carter (1992) impose the following constraints:
 \begin{equation}
@@
 \end{equation}
-
-Also, we normally seek the least squares solution when estimating
-parameters. However, in this case, the model cannot be estimated using
-simple regression methods because there is no regressor on the right
-side of the equation. \textcite{LC92} choose a singular value
-decomposition (SVD) method to undertake principal component analysis
-(PCA), and hence find the least squares solution. It has been shown that
-applying SVD method to a matrix of the logarithms of the rates after
-subtracting the average over time of the log age-specific rates can find
-the least square solution (Good, 1969). Therefore, the estimations of
-\(b_x\) and \(k_t\) are the first principal component and scores of
-\(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when
-\(\bm{X}=\ln(m_{x,t})-a_x\)). However, the empirical results suggest
-that the resulting fitted number of deaths are biased estimates of
-actual number of deaths because of the \(\ln\) transformation. To
-overcome this problem, the LC method adjusts \(k_t\) such that for each
-year, the implied number of deaths will be equal to the actual number of
-deaths. The adjusted \(k_t\) is then extrapolated using random walk with
-drift models, which is equivalent to ARIMA (\(0,1,0\)) model with
-\(c\neq0\).
-
-\subsubsection{\texorpdfstring{Hyndman-Ullah Method
-\label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}
-
-\textcite{HU07} proposed a nonparametric method for demographic
-modelling and forecasting. It extended the LC model in four ways:
+Also, we normally seek the least squares solution when estimating parameters.
+However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation.
+\textcite{LC92} choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
+It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
+Therefore, the estimations of \(b_x\) and \(k_t\) are the first principal component and scores of \(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when \(\bm{X}=\ln(m_{x,t})-a_x\)).
+However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the \(\ln\) transformation.
+To overcome this problem, the LC method adjusts \(k_t\) such that for each year, the implied number of deaths will be equal to the actual number of deaths.
+The adjusted \(k_t\) is then extrapolated using random walk with drift models, which is equivalent to ARIMA (\(0,1,0\)) model with \(c\neq0\).
+
+\hypertarget{hyndman-ullah-method}{%
+\subsubsection{\texorpdfstring{Hyndman-Ullah Method \label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}}
+
+\textcite{HU07} proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
 
@@
 
-The model proposed by \textcite{HU07} is as follows: \vspace{-.3in}
-
+The model proposed by \textcite{HU07} is as follows:
+\vspace{-.3in}
 \begin{align}
@@
 \end{align}
-
-Equation \eqref{eq:HU_1} describes the smoothing process. \(y_t(x)\) is
-the observed data in year \(t\) and age \(x\), and \(s_t(x)\) is the
-smoothed function of \(y_t(x)\), estimated by constrained weighted
-penalized regression splines \autocite{BHT14}. \(\sigma_t(x)\) allows
-the variance to be a function of time and age; and \(\epsilon_{t,x}\)
-are independent identical distributed standard normal error terms.
-Equation \eqref{eq:HU_2} has a similar structure to the LC method,
-except that it incorporates more than one principal component and score.
-It describes the dynamics of \(s_t(x)\) over time. The \(\beta_{t,j}\)
-for every \(j\) and \(\mu(x)\) are sets of age-specific constants, and
-\(\phi_j(x)\) for every \(j\) is a time-varying index. The \(e_t(x)\) is
-the model error, which is the residual function with mean zero and no
-serial correlation. The \(\mu(x)\) is estimated by the average of
-\(s_t(x)\) across years, which measures the general shape of the
-observed data \(y_t(x)\). The estimates of \(\phi_j(x)\) and
-\(\beta_{t,j}\) are the \(j\)th principal component and scores of
-\(s_t(x)-\mu(x)\) respectively. In other words, we take singular value
-decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
+Equation \eqref{eq:HU_1} describes the smoothing process.
+\(y_t(x)\) is the observed data in year \(t\) and age \(x\), and \(s_t(x)\) is the smoothed function of \(y_t(x)\), estimated by constrained weighted penalized regression splines \autocite{BHT14}.
+\(\sigma_t(x)\) allows the variance to be a function of time and age; and \(\epsilon_{t,x}\) are independent identical distributed standard normal error terms.
+Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
+It describes the dynamics of \(s_t(x)\) over time.
+The \(\beta_{t,j}\) for every \(j\) and \(\mu(x)\) are sets of age-specific constants, and \(\phi_j(x)\) for every \(j\) is a time-varying index.
+The \(e_t(x)\) is the model error, which is the residual function with mean zero and no serial correlation.
+The \(\mu(x)\) is estimated by the average of \(s_t(x)\) across years, which measures the general shape of the observed data \(y_t(x)\).
+The estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j\)th principal component and scores of \(s_t(x)-\mu(x)\) respectively.
+In other words, we take singular value decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
 \vspace{-.2in}
-
 \begin{equation*}
@@
 \end{equation*}
-
-We chose \(J\) in a way that we believe the majority of information for
-\(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.
-
-In terms of forecasting, by conditioning on the observed data
-\(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of
-functional principal components
-\(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the
-\(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
+We chose \(J\) in a way that we believe the majority of information for \(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.
+
+In terms of forecasting, by conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
 \vspace{-.2in}
-
 \begin{equation}
@@
 \end{equation}
-
-where \(\widehat{\beta}_{n+h\mid n,j}\) denotes the \(h\)-step-ahead
-forecast of \(\beta_{n+h\mid n,j}\). Because of the time-varying
-property of \(\left\{\beta_{t,j}\right\}\), it controls the dynamics of
-the process. For every component series \(\left\{\beta_{t,j}\right\}\),
-we fit them with an ARIMA\((p_j,d_j,q_j)\) process, where
-\(p_j,d_j,q_j\) are determined by minimizing the Akaike Information
-Criterion (Booth, Hyndman \& Tickle, 2014). The fitted process is given
-as follows: \vspace{-.3in}
-
+where \(\widehat{\beta}_{n+h\mid n,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{n+h\mid n,j}\).
+Because of the time-varying property of \(\left\{\beta_{t,j}\right\}\), it controls the dynamics of the process.
+For every component series \(\left\{\beta_{t,j}\right\}\), we fit them with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
+The fitted process is given as follows:
+\vspace{-.3in}
 \begin{equation*}
@@
 \end{equation*}
-
 where the parameters are estimated using maximum likelihood estimation.
 
-\section{Data}\label{sec:data}
-
-We use the same notation and similar procedures to construct data as in
-\textcite{HB08}, because the fundamental model for forecasting
-population for this study is the \textcite{HU07} method. The data used
-to construct population age structure included: age- and gender-specific
-birth and death numbers of each calendar year, age- and gender-specific
-population members on 1~January of each year, and age- and
-gender-specific exposures to risk (i.e., population of age \(x\) at 30
-June) for each year. The notations are as follows: \vspace{-.4in}
-
+\hypertarget{sec:data}{%
+\section{Data}\label{sec:data}}
+
+We use the same notation and similar procedures to construct data as in \textcite{HB08}, because the fundamental model for forecasting population for this study is the \textcite{HU07} method.
+The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1~January of each year, and age- and gender-specific exposures to risk (i.e., population of age \(x\) at 30 June) for each year.
+The notations are as follows:
+\vspace{-.4in}
 \begin{align*}
@@
 \end{align*}
-
-\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\). \(m^+\)
-is the open-ended upper age group, which is 100 in this study. \(t\)
-denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of
-historical data used. Therefore, all of those data points can be
-recorded in an \(m\times n\) matrix. The superscripts M and F denote
-male and female respectively.
-
-We can obtain historical mortality rates \(m_t(x)\) (also called central
-death rates) and fertility rates \(f_t(x)\) as follows: \vspace{-.3in}
-
+\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\).
+\(m^+\) is the open-ended upper age group, which is 100 in this study.
+\(t\) denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of historical data used.
+Therefore, all of those data points can be recorded in an \(m\times n\) matrix.
+The superscripts M and F denote male and female respectively.
+
+We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
+\vspace{-.3in}
 \begin{align*}
@@
 
-In addition, the net
-migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame}
-(denoted \(G\)) is estimated using a demographic growth-balance
-equation, which is an equation to summarize the relationship between
-population change and three factors: net migration, births and deaths.
+In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted \(G\)) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
 The equation is expressed as: \todo{Please define $p$ and $^+$}
 \vspace{-.3in}
-
 \begin{align*}
@@
 \end{align*}
-
-where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of
-persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\)
-\todo{should it be $p^+$} refers to migration in calendar year \(t\) of
-persons aged \(p-1\) and older at beginning of year \(t\), and
-\(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during
-year \(t\); and similarly for deaths,
-\(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\). The deaths are estimated using
-the standard life table approach of population projection. It should be
-noted that the estimated net migration includes errors in data
-recording.
-
-Historical central death rates and start-year and mid-year populations
-of residents in Australia by sex and age in single years for age group
-0-99 and 100+ have been sourced from the \textcite{HMD} for
-1921--2014.\todo{Han has updated the data period.} The start-year
-population for 2015 is also used to estimate net migration. Data for
-age-specific annual fertility rates by single years of age for 15-49
-over the period 1950-2014 was obtained from the \textcite{ABS12}. Even
-though annual mortality rates are available from 1921 to 2014, only data
-collected after 1950 is used for two reasons. First, the period between
-1921-1950 has very different mortality patterns from later years because
-of wars and epidemics \autocite{HB08}. Since the model for this study is
-valid under the assumption that extrapolative methods can be used, it
-seemed best to delete the less relevant data, which might influence
-estimations of parameters if we include them. Secondly, fertility rates
-are only available from 1950, so the mortality rate was cut to fit the
-same period.
-
-\subsection{Forecasting Population Age Structure and
-OADR}\label{sec:forecasting}
-
-In this study, three steps were taken to simulate OADR associated with a
-specific pension age scheme. A stochastic functional data model was
-applied to five components of population change: female mortality rates,
-male mortality rates, female net migration, male net migration and
-fertility rates to simulate these five components over the prediction
-horizon (which is 50 years in this study). Age- and gender-specific
-population paths over the prediction horizon were simulated using the
-demographic growth-balance equation. The Monte Carlo simulation method
-was used consistently in this research. Finally, calculation of OADR
-associated with a specific pension age scheme was performed by applying
-the OADR formula. Even though the process seems complicated, it is
-relatively resy to implement using \textit{R} \autocite{Team18}. The
-detailed explanation of each step is as follows. The corresponding R
-code is attached as a supplement.
-
-\subsubsection*{Step 1}\label{step-1}
+where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\) \todo{should it be $p^+$} refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\).
+The deaths are estimated using the standard life table approach of population projection.
+It should be noted that the estimated net migration includes errors in data recording.
+
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the \textcite{HMD} for 1921--2014.\todo{Han has updated the data period.} The start-year population for 2015 is also used to estimate net migration.
+Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the \textcite{ABS12}.
+Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons.
+First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics \autocite{HB08}.
+Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
+Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
+
+\hypertarget{sec:forecasting}{%
+\subsection{Forecasting Population Age Structure and OADR}\label{sec:forecasting}}
+
+In this study, three steps were taken to simulate OADR associated with a specific pension age scheme.
+A stochastic functional data model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
+Age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
+The Monte Carlo simulation method was used consistently in this research.
+Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula.
+Even though the process seems complicated, it is relatively resy to implement using \textit{R} \autocite{Team18}.
+The detailed explanation of each step is as follows.
+The corresponding R code is attached as a supplement.
+
+\hypertarget{step-1}{%
+\subsubsection*{Step 1}\label{step-1}}
 \addcontentsline{toc}{subsubsection}{Step 1}
 
-The main procedure for forecasting the population age structure follows
-\textcite{HB08}, except that the data is updated, and we incorporate the
-product-ratio method \autocite{HBY13} to improve the accuracy of the
-forecast. The \textcite{HU07} model, introduced in section \ref{sec:HU},
-is applied to the mortality rate, fertility rate and net migration
-separately, based on the assumption that they behave independently.
-Therefore, to fit the model to historical fertility rates, let
-\(y_t(x)\) in equation \eqref{eq:HU_1} denote the observed historical
-fertility data. However, for mortality rate by sex, the product-ratio
-method is used to ensure the forecast of females and males are
-non-divergent or coherent \autocite{HBY13}. In the product-ratio method,
-after smoothing the female and male mortality rates, two other series
-were created: product series (denoted by \(p_t(x)\)) and ratio series
-(denoted by \(r_t(x)\)), which are defined as follows: \vspace{-.4in}
-
+The main procedure for forecasting the population age structure follows \textcite{HB08}, except that the data is updated, and we incorporate the product-ratio method \autocite{HBY13} to improve the accuracy of the forecast.
+The \textcite{HU07} model, introduced in section \ref{sec:HU}, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
+Therefore, to fit the model to historical fertility rates, let \(y_t(x)\) in equation \eqref{eq:HU_1} denote the observed historical fertility data.
+However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent \autocite{HBY13}.
+In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by \(p_t(x)\)) and ratio series (denoted by \(r_t(x)\)), which are defined as follows:
+\vspace{-.4in}
 \begin{align}
@@
 \end{align}
-
-Then, \textcite{HU07} was applied to these two new variables instead of
-male and female mortality rate as follows: \vspace{-.3in}
-
+Then, \textcite{HU07} was applied to these two new variables instead of male and female mortality rate as follows:
+\vspace{-.3in}
 \begin{align*}
@@
 \end{align*}
-
-where time series \(\left\{\beta_{t,j}\right\}\) are fitted with an
-ARIMA model while \(\left\{\gamma_{t,l}\right\}\) are fitted by
-stationary ARFIMA model (i.e., \(d\) in ARIMA(\(p,d,q\)) constrained to
-\(0<d<\frac{1}{2}\)). It is the stationary constraint on
-\(\gamma_{t,l}\) that ensures the forecast of male and female do not
-diverge. Then, simulating \(h\)-step-ahead forecast values of product
-variable and ratio variable was performed (denoted by
-\(p_{n+h\mid n}(x)\) and \(r_{n+h\mid n}(x)\) respectively) according to
-\eqref{eq:coherent_1} and \eqref{eq:coherent_2}. From here, obtaining
-\(h\)-step-ahead forecast of sex-specific coherent mortality rates
-(denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was
-performed using a back-transformation: \vspace{-.3in}
-
+where time series \(\left\{\beta_{t,j}\right\}\) are fitted with an ARIMA model while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA model (i.e., \(d\) in ARIMA(\(p,d,q\)) constrained to \(0<d<\frac{1}{2}\)).
+It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecast of male and female do not diverge.
+Then, simulating \(h\)-step-ahead forecast values of product variable and ratio variable was performed (denoted by \(p_{n+h\mid n}(x)\) and \(r_{n+h\mid n}(x)\) respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
+From here, obtaining \(h\)-step-ahead forecast of sex-specific coherent mortality rates (denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was performed using a back-transformation:
+\vspace{-.3in}
 \begin{align*}
@@
 \end{align*}
-
-The method for simulating \(h\)-step-ahead values of net migration by
-sex is similar to the above method used on mortality rates except no log
-scale is applied to net migration. A stationary constraint was imposed
-on the ARIMA model for net migration to make sure the difference between
-sexes did not diverge.
-
-\subsubsection*{Step 2}\label{step-2}
+The method for simulating \(h\)-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration.
+A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.
+
+\hypertarget{step-2}{%
+\subsubsection*{Step 2}\label{step-2}}
 \addcontentsline{toc}{subsubsection}{Step 2}
 
-After simulating paths for age-specific fertility rate, age- and
-gender-specific mortality rate and age- and gender-specific net
-migration, future population value were simulated using the demographic
-growth-balance equations over the prediction horizon. The future deaths
-and births in this equation are assumed to follow Poisson distribution,
-with parameters as a function of future mortality and fertility rates
-(see Hyndman and Booth, 2008 for the details of the functions). Hence,
-we can simulate \(h\)-step-ahead age- and gender-specific births and
-deaths based on simulated mortality and fertility rates. According to
-the demographic growth-balance equation, one-step-ahead net migrations,
-deaths, births and population in the last year were simulated, allowing
-for the generation of one-step-ahead population predictions by sex and
-age. This simulation was repeated for years \(t=n+1,\dots,n+h\) to
-obtain a path of population. The process was repeated and simulated
-\(i\) paths of population based on Monte Carlo simulation method were
-created (we set \(i=1000\) in these research). It should be noted that
-there are three types of randomness in the simulation: randomness from
-the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\)
-in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal
-component scores and randomness from the Poisson distribution. It should
-be noted that the simulated population will be an array with three
-dimensions: age, year and simulation.
-
-\subsubsection*{Step 3}\label{step-3}
+After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
+The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
+Hence, we can simulate \(h\)-step-ahead age- and gender-specific births and deaths based on simulated mortality and fertility rates.
+According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age.
+This simulation was repeated for years \(t=n+1,\dots,n+h\) to obtain a path of population.
+The process was repeated and simulated \(i\) paths of population based on Monte Carlo simulation method were created (we set \(i=1000\) in these research).
+It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
+It should be noted that the simulated population will be an array with three dimensions: age, year and simulation.
+
+\hypertarget{step-3}{%
+\subsubsection*{Step 3}\label{step-3}}
 \addcontentsline{toc}{subsubsection}{Step 3}
 
-Even though the OADR is a simple function of the population age
-structure and pension age, the formula can't be directly applied to the
-simulated population array because the pension age changes over time. To
-overcome this problem, we assume that the pension age can only be
-adjusted at the beginning of a year for these calculations. Therefore,
-one pension age is applicable for a whole year and hence OADR is
-generated at the beginning of each year to show the trend. We will show
-the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR
-in year 2015), given a specific pension age. The same method can be
-applied to all years over the prediction horizon, given their
-corresponding pension age. Further, the fractional pension age causes
-practical issues in calculating OADR, since ages are recorded as
-integers. We will also show how this issue was handled in the example
-below.
-
-Suppose the pension age for \(n+1\) is \(a.r\) where \(a\) is the
-integer and and \(r\) is the reminder of pension age. Recall that for
-\(h=1\), we can express the simulated population paths as a matrix with
-age in the row and simulation in the column as follows:
-
+Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time.
+To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations.
+Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
+We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2015), given a specific pension age.
+The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
+Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers.
+We will also show how this issue was handled in the example below.
+
+Suppose the pension age for \(n+1\) is \(a.r\) where \(a\) is the integer and and \(r\) is the reminder of pension age.
+Recall that for \(h=1\), we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
 \begin{equation*}
@@
 \end{equation*}
-
-When \(r=0\), then the simulation of a population aged 15 to pension age
-is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\)
-row, which is:
-
+When \(r=0\), then the simulation of a population aged 15 to pension age is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\) row, which is:
 \begin{equation}
@@
 \end{equation}
-
-To calculate the total number of working age, we take a column sum of
-the trimmed matrix \eqref{eq:population_mat}. The simulations of total
-number of work age become a vector:
-
+To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
 \begin{equation}
@@
 \end{equation}
-
-Using the same method, the simulations of total number of aged
-pensioners in the population can be shown as:
-
+Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
 \begin{equation}
@@
 
-When \(r\neq0\), the vector of total number of working age population in
-\eqref{eq:work} is added, and the vector of total number of aged
-population in \eqref{eq:aged} is subtracted with an adjustment:
+When \(r\neq0\), the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
 \vspace{-.2in}
-
 \begin{equation}
@@
 \end{equation}
-
-This adjustment is based on the assumption that the birthday of
-population is uniformly distributed over the year. Then,
-\(r\times100\%\) of population with a recorded integer age of \(a\) at
-beginning of the year is actually younger than \(a.r\), so they are
-still under the pension age. In other words, \((1-r\times100\%)\) of
-population with recorded integer age \(a\) at beginning of the year is
-actually older than \(a.r\), so they should be counted as the aged
-population. The simulation vectors of total work age population and
-total aged population should then be:
-
+This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year.
+Then, \(r\times100\%\) of population with a recorded integer age of \(a\) at beginning of the year is actually younger than \(a.r\), so they are still under the pension age.
+In other words, \((1-r\times100\%)\) of population with recorded integer age \(a\) at beginning of the year is actually older than \(a.r\), so they should be counted as the aged population.
+The simulation vectors of total work age population and total aged population should then be:
 \begin{align*}
@@
 
-After the adjustment, we can generate simulation vectors of the
-one-step-ahead OADR by dividing every element of
-\(\bm{p}^{\text{work}}_{n+1}\) by the corresponding element of
-\(\bm{p}^{\text{aged}}_{n+1}\), i.e.: \vspace{-.3in}
-
+After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of \(\bm{p}^{\text{work}}_{n+1}\) by the corresponding element of \(\bm{p}^{\text{aged}}_{n+1}\), i.e.:
+\vspace{-.3in}
 \begin{align*}
@@
 \end{align*}
-
-The average value of elements of \(\bm{\text{OADR}}_{n+1}\) is the mean
-prediction of one-step-ahead OADR.
-
-The same algorithm is applied to the simulation matrix of the population
-age structure to obtain \(h\)-step-ahead simulation vectors of OADR for
-\(h=1,2,\dots,H\), where \(H=50\) for this study (i.e., a prediction
-horizon of 2015 to 2064). Simulations of OADR over a 50 year prediction
-horizon by the matrix is summarised below, with the forecast year in
-rows and simulation in the columns:
-
+The average value of elements of \(\bm{\text{OADR}}_{n+1}\) is the mean prediction of one-step-ahead OADR.
+
+The same algorithm is applied to the simulation matrix of the population age structure to obtain \(h\)-step-ahead simulation vectors of OADR for \(h=1,2,\dots,H\), where \(H=50\) for this study (i.e., a prediction horizon of 2015 to 2064).
+Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
 \begin{equation*}
@@
 
-\subsection{Results}\label{results}
-
-We use the fitted model of fertility rates as an example to interpret
-the results of fitted models. It should be noted that models fitted to
-product and ratio series are less likely to be interpreted in an
-economic sense. Figure \ref{fig:componentsfertility} above shows the
-estimated mean age pattern \(\widehat{\mu}(x)\), the first two estimated
-basis functions, \(\widehat{\phi}_1(x)\) and \(\widehat{\phi}_2(x)\),
-and first two estimated coefficients (i.e., estimated principal
-component scores \(\widehat{\beta}_{t,1}\) and
-\(\widehat{\beta}_{t,2}\)) for fertility rates. The first term
-(\(\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}\)) accounts for the
-most variation in fertility, so a relatively sensible interpretation can
-be given to the first term. In the plot of the first coefficient,
-estimated historical first principal component scores
-\(\widehat{\beta}_{t,1}\) are shown in black for 1950-2014. It captures
-the general trend of fertility change over time. It indicates a sharp
-increase between 1950-1960, followed by a rapid decline of fertility
-rates from 1961. This increase of fertility is linked to the Post-World
-War II baby boom\footnote{Between the years 1946 and 1964} in Australia,
-resulting from the recovery from war and the Great
-Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
-The dramatic decrease from 1960 was due to the availability of
-contraception pills in Australia. A noticeable further reduction of
-fertility rates in late 1960s may be due to a change in the law allowing
-abortion in some states in Australia.
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+We use the fitted model of fertility rates as an example to interpret the results of fitted models.
+It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
+Figure \ref{fig:componentsfertility} above shows the estimated mean age pattern \(\widehat{\mu}(x)\), the first two estimated basis functions, \(\widehat{\phi}_1(x)\) and \(\widehat{\phi}_2(x)\), and first two estimated coefficients (i.e., estimated principal component scores \(\widehat{\beta}_{t,1}\) and \(\widehat{\beta}_{t,2}\)) for fertility rates.
+The first term (\(\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}\)) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
+In the plot of the first coefficient, estimated historical first principal component scores \(\widehat{\beta}_{t,1}\) are shown in black for 1950-2014.
+It captures the general trend of fertility change over time.
+It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961.
+This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
+The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
+A noticeable further reduction of fertility rates in late 1960s may be due to a change in the law allowing abortion in some states in Australia.
 
@@
 \includegraphics{PensionAge_files/figure-latex/componentsfertility-1.pdf}
-\caption{\label{fig:componentsfertility}Fitted basis functions and
-coefficients for Australian age-specific fertility rates.}
+\caption{\label{fig:componentsfertility}Fitted basis functions and coefficients for Australian age-specific fertility rates.}
 \end{figure}
 
-The first estimated basis function \(\widehat{\phi}_1(x)\) measures the
-different effects of the trend over time across ages. It indicates the
-general pattern of fertility has very little effect on females of age
-15. This makes intuitive sense because most early pregnancies are
-accidental, therefore, any of previously discussed events has no effect
-on early pregnancies. In addition, there are two spikes in the first
-basic function, which suggests that the historical trend has a distinct
-impact on females aged around their 20s and 40s. Furthermore, the blue
-line is the fitted value of future coefficients (i.e.,
-\(\widehat{\beta}_{n+h,1}\), for \(h=1,2,\dots,50\)) and the yellow
-shading shows their 80\% pointwise prediction interval according to the
-fitted ARIMA model of first coefficients
-\(\left\{\widehat{\beta}_{t,1}\right\}\). Other terms further explain
-variation that has not been captured by first term, but less economic
-explanations can be given for them.
-
-Both Figures \ref{fig:totalpopulationbyyears} and
-\ref{fig:totalpopulationin2034} show the forecast results of population.
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of total
-population by gender over the prediction horizon, while Figure
-\ref{fig:totalpopulationin2028} shows the forecast of population age
-structure in a specific year, 2034. Figure
-\ref{fig:totalpopulationbyyears} indicates that both the female and male
-population are expected to increase to around 23 million by 2064. Since
-the fertility rate is expected to remain low, the possible reason of the
-significant increase in population size is net migration. We can also
-observe that the further the projected year is, the bigger the forecast
-variation of population. This increase in variation shows that we have
-less relevant information for further apart prediction horizons.
+The first estimated basis function \(\widehat{\phi}_1(x)\) measures the different effects of the trend over time across ages.
+It indicates the general pattern of fertility has very little effect on females of age 15.
+This makes intuitive sense because most early pregnancies are accidental, therefore, any of previously discussed events has no effect on early pregnancies.
+In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
+Furthermore, the blue line is the fitted value of future coefficients (i.e., \(\widehat{\beta}_{n+h,1}\), for \(h=1,2,\dots,50\)) and the yellow shading shows their 80\% pointwise prediction interval according to the fitted ARIMA model of first coefficients \(\left\{\widehat{\beta}_{t,1}\right\}\).
+Other terms further explain variation that has not been captured by first term, but less economic explanations can be given for them.
+
+Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2034} show the forecast results of population.
+Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2034.
+Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 23 million by 2064.
+Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
+We can also observe that the further the projected year is, the bigger the forecast variation of population.
+This increase in variation shows that we have less relevant information for further apart prediction horizons.
 
@@
 \includegraphics{PensionAge_files/figure-latex/totalpopulationbyyears-1.pdf}
-\caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of total
-population for each sex, along with 80\% prediction intervals. The
-actually population from 1950 to 2015 is shown using circles.}
+\caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of total population for each sex, along with 80\% prediction intervals.
+The actually population from 1950 to 2015 is shown using circles.}
 \end{figure}
@@
 \includegraphics{PensionAge_files/figure-latex/totalpopulationin2034-1.pdf}
-\caption{\label{fig:totalpopulationin2034}Forecast population pyramid for
-2034, along with 80\% pointwise prediction intervals. The actual pyramid
-for 2015 is shown using dashed lines.}
+\caption{\label{fig:totalpopulationin2034}Forecast population pyramid for 2034, along with 80\% pointwise prediction intervals. The actual pyramid for 2015 is shown using dashed lines.}
 \end{figure}
 
-Figure \ref{fig:totalpopulationin2034} shows the mean and the 80\%
-pointwise prediction interval of simulated population paths for year
-2034, along with the 2015 base population. It can be observed that
-overall population size is expected to increase substantially. The
-uncertainty of population of infant is much higher than other ages,
-which reflects the higher forecast variation of fertility rates than
-mortality rates. The uncertainty of the young age population is mainly
-due to migration \autocite{HB08}.
+Figure \ref{fig:totalpopulationin2034} shows the mean and the 80\% pointwise prediction interval of simulated population paths for year 2034, along with the 2015 base population.
+It can be observed that overall population size is expected to increase substantially.
+The uncertainty of population of infant is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates.
+The uncertainty of the young age population is mainly due to migration \autocite{HB08}.
 
@@
 \includegraphics{PensionAge_files/figure-latex/OADRat65-1.pdf}
-\caption{\label{fig:OADRat65}Fifty-year forecasts of the OADR with
-assumption of pension age equal to 65 for both sexes, along with 80\%
-pointwise prediction interval.}
+\caption{\label{fig:OADRat65}Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80\% pointwise prediction interval.}
 \end{figure}
@@
 \includegraphics{PensionAge_files/figure-latex/OADRcurrent-1.pdf}
-\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated
-with a pension age equal to 65 (green line) and equal to the pension age
-scheme with approved change (orange line) respectively, along with the
-desired OADR level in purple. The actual OADRs for 1950-2014 are shown
-in black.}
+\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
+The actual OADRs for 1950-2014 are shown in black.}
 \end{figure}
 
-Analysis was performed by first generating an OADR associated with a
-fixed pension age of 65 and an OADR associated with pension age scheme
-with approved change, gradually increasing the pension age from 65 to 67
-by mid-2023. Even though the government might further increase the
-pension age in future, we kept the pension age at 67 from 2024 to see
-what would happen if no further action was taken. Figure
-\ref{fig:OADRat65} shows the mean forecast and pointwise prediction
-interval of the OADR with a pension age of 65, along with the historical
-OADR for 1921-2014. A strong positive trend was observed, which
-indicates an increasing burden on the next working-age generation if the
-pension age is fixed at 65. This is consistent with the prediction by
-inter-generation reports in 2002 \autocite{IGR02} and in 2007
-\autocite{IGR07}. According to former Australian Treasurer
-\textcite{Costello04}, this could be a result of better health care and
-low fertility rates. These two reasons could be regarded as permanent
-change and therefore a persistent trend. In addition, there is a big
-jump from actual data to predicted data. This jump is possibly a result
-of the Baby Boomers' retirement. Those born in 1946, the start of the
-baby boom, would begin retiring in 2011 when the pension age was 65.
-
-Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast
-of OADR with the pension age equal to 65 and a pension age equal to the
-pension age scheme with approved change, along with comparison of both
-forecasts with desired level of OADR, which has been set at 21\%. It
-should be noted that OADR corresponding to pension age scheme with
-approved change is approaching the desired level, which suggests that
-the approved change does achieve the aim of providing an affordable
-financial burden, at least for a moment. However, once the pension age
-reaches 67, the OADR of the pension scheme with approved adjustment
-grows at nearly same rate as the OADR of a pension age equal of 65. This
-is consistent with the idea that there is a persistent positive trend in
-OADR associated with a constant pension age, due to low fertility rates
-and better health care. Therefore, Figure \ref{fig:OADRcurrent}
-demonstrates that the pension age scheme requires constant review to
-ensure a stable OADR over the long term. However, the questions of when
-the action needs to be taken and how much of an adjustment needs to be
-made remain to be answered. This answer will allow us to respond to the
-recent proposal of further increasing pension age to 70 by 2035.
-
-\subsection{Evaluating Forecast Accuracy}\label{sec:accuracy}
-
-Since all the results and implications are dependent on the forecast
-accuracy, it is important to evaluate the accuracy of our forecast. It
-is not valid to assess the model's fit in terms of historical data. We
-are concerned with how well a model performs on out-of-sample data,
-which is known but not used to fit the model. Therefore, we will use a
-Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to
-evaluate the accuracy of the models used in this paper.
-
-The logic of a Cross-Validation test is to use a portion of available
-data for fitting, and use the remaining data to test. Suppose we need
-\(k\) years' observations to produce a reliable
-forecast\footnote{$k$ can't be too small}, we are interested in the
-\(H\) prediction horizon. Then we are allowed to repeat the test
-\(n-H-k+1\) times, where \(n\) is the number of total years of
-observation. The procedure is as follows:
-
-Let \(\omega=1\), we first select historical data for a time interval of
-\([\omega,\omega+1,\dots,\omega+k-1]\) as ``in sample data'' to fit the
-model, and then forecast \(H\) years'
-OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
-Then, we can calculate the difference of forecasted OADR over the period
-\([\omega+k,\omega+k+1,\dots,\omega+k+H-1]\) from the real OADR for the
-same period, which is known as absolute error. We repeat the following
-steps for \(\omega=1,2,\dots,n-k-H+1\). Then, we can summary the
-information into a matrix as follows:
-
+Analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
+Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
+Figure \ref{fig:OADRat65} shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921-2014.
+A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
+This is consistent with the prediction by inter-generation reports in 2002 \autocite{IGR02} and in 2007 \autocite{IGR07}.
+According to former Australian Treasurer \textcite{Costello04}, this could be a result of better health care and low fertility rates.
+These two reasons could be regarded as permanent change and therefore a persistent trend.
+In addition, there is a big jump from actual data to predicted data.
+This jump is possibly a result of the Baby Boomers' retirement.
+Those born in 1946, the start of the baby boom, would begin retiring in 2011 when the pension age was 65.
+
+Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21\%.
+It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment.
+However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at nearly same rate as the OADR of a pension age equal of 65.
+This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
+Therefore, Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
+However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
+This answer will allow us to respond to the recent proposal of further increasing pension age to 70 by 2035.
+
+\hypertarget{sec:accuracy}{%
+\subsection{Evaluating Forecast Accuracy}\label{sec:accuracy}}
+
+Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
+It is not valid to assess the model's fit in terms of historical data.
+We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
+Therefore, we will use a Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to evaluate the accuracy of the models used in this paper.
+
+The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Suppose we need \(k\) years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the \(H\) prediction horizon.
+Then we are allowed to repeat the test \(n-H-k+1\) times, where \(n\) is the number of total years of observation.
+The procedure is as follows:
+
+Let \(\omega=1\), we first select historical data for a time interval of \([\omega,\omega+1,\dots,\omega+k-1]\) as ``in sample data'' to fit the model, and then forecast \(H\) years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Then, we can calculate the difference of forecasted OADR over the period \([\omega+k,\omega+k+1,\dots,\omega+k+H-1]\) from the real OADR for the same period, which is known as absolute error.
+We repeat the following steps for \(\omega=1,2,\dots,n-k-H+1\).
+Then, we can summary the information into a matrix as follows:
 \begin{equation*}
@@
 \end{equation*}
-
-where \(h\) denotes for the forecast horizon and
-\(\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|\).
-This process is also known as ``rolling forecasting origin'', because
-the ``origin'' (\(k+\omega-1\)) at which the forecast is based rolls
-forward in time. We take the average of each row to obtain an absolute
-mean error of \(h\)-step-ahead forecast of OADR where \(h=1,2,\dots,H\).
-
-In our sample, \(n=2014-1950+1=65\) and we set \(k=25\) and \(H=25\) to
-perform the test. The mean absolute error of \(h\)-step-ahead forecast
-of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
-From this figure, we observe that the mean absolute error is increasing
-as \(h\) increases, which is reasonable as we have less relevant
-information to make a forecast for further apart OADR. Overall, the mean
-absolute error is very small. For example, the mean absolute error for
-25-step-ahead forecast is 1.6\%, which is very small if compared to the
-desired level of OADR, which is at 21\%.
+where \(h\) denotes for the forecast horizon and \(\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|\).
+This process is also known as ``rolling forecasting origin'', because the ``origin'' (\(k+\omega-1\)) at which the forecast is based rolls forward in time.
+We take the average of each row to obtain an absolute mean error of \(h\)-step-ahead forecast of OADR where \(h=1,2,\dots,H\).
+
+In our sample, \(n=2014-1950+1=65\) and we set \(k=25\) and \(H=25\) to perform the test.
+The mean absolute error of \(h\)-step-ahead forecast of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
+From this figure, we observe that the mean absolute error is increasing as \(h\) increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
+Overall, the mean absolute error is very small.
+For example, the mean absolute error for 25-step-ahead forecast is 1.6\%, which is very small if compared to the desired level of OADR, which is at 21\%.
+
+\begin{verbatim}
+## Error in stats::arima(x = x, order = order, seasonal = seasonal, include.mean = include.mean,  : 
+##   non-stationary AR part from CSS
+## Error in stats::arima(x = x, order = order, seasonal = seasonal, include.mean = include.mean,  : 
+##   non-stationary AR part from CSS
+\end{verbatim}
 
@@
 \includegraphics{PensionAge_files/figure-latex/rollingtest-1.pdf}
-\caption{\label{fig:rollingtest}The mean absolute error of \(h\)-step-ahead
-forecast for \(h=1,2,\dots,25\).}
+\caption{\label{fig:rollingtest}The mean absolute error of \(h\)-step-ahead forecast for \(h=1,2,\dots,25\).}
 \end{figure}
 
-It would normally be ideal to compare the mean absolute error of the
-forecast from our model to other available models to measure the
-accuracy. For example, suppose we can take the population projections
-from ABS reports over the last few decades, their projection of
-population age structure reported in different years can be used to
-mimic the rolling origin test of OADR, because we now have the real OADR
-for those projected years. However, we are not able to actually perform
-it because full projection data is no longer available online and ABS
-projections have not used a consistent and replicate methodology.
-
-\section{Finding the Target Pension Age Scheme}\label{sec:target}
-
-The goal of this research is to keep the pension age low, as long as
-OADR is lower than or equal to the desired OADR level. According to the
-formula of OADR, OADR at a given time can be written as a function of
-pension age, when the population age structure is given. Suppose we
-denote pension age (PA) schemes over the prediction horizon by
-\(\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]\).
-The OADR function of pension age over the prediction horizon is denoted
-as \(\text{OADR}_h(\text{PA}_{n+h})\) for \(h=1,2,\dots,H\). There is a
-negative relationship between pension age and OADR. The negative
-relationship implies that the higher the pension age, the lower the
-OADR. Therefore, our goal becomes finding the minimum pension age which
-has an OADR lower than desired OADR level. Several practical issues need
-to be considered to achieve this goal. First, only simulated forecasting
-values of future OADR are available, so it is assumed that the mean
-value of the simulated OADR is a good estimate of true underlying OADR.
-Second, pension age cannot be increased by more than one within a year
-or decreased because either one of the two actions will force some
-retirees back to the workforce, which is unreasonable in practical
-applications. Therefore, the target pension age scheme
-\(\bm{\text{PA}}^{\text{target}}\) can be defined in the following way:
+It would normally be ideal to compare the mean absolute error of the forecast from our model to other available models to measure the accuracy.
+For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
+However, we are not able to actually perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
+
+\hypertarget{sec:target}{%
+\section{Finding the Target Pension Age Scheme}\label{sec:target}}
+
+The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level.
+According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
+Suppose we denote pension age (PA) schemes over the prediction horizon by \(\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]\).
+The OADR function of pension age over the prediction horizon is denoted as \(\text{OADR}_h(\text{PA}_{n+h})\) for \(h=1,2,\dots,H\).
+There is a negative relationship between pension age and OADR.
+The negative relationship implies that the higher the pension age, the lower the OADR.
+Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level.
+Several practical issues need to be considered to achieve this goal.
+First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR.
+Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
+Therefore, the target pension age scheme \(\bm{\text{PA}}^{\text{target}}\) can be defined in the following way:
 for \(h=1,2,\dots,H\)
-
 \begin{equation*}
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation*}\begin{align*}
+\end{equation*}
+\begin{align*}
   \text{subject to the constraint~} 0\leq \text{PA}_{n+h}-\text{PA}_{n+h-1}\leq 1
 \end{align*}
-
-In order to achieve this maximization subject to constraint, these
-calculations assume that the adjustment unit of pension age is one month
-for practical convenience. It is also supposed that the set starting
-value of pension age is at 65 for all
-years\footnote{Even though pension age for males and females is 65.5 in mid-2017.
+In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
+It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65.5 in mid-2017.
 The same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in mid-2017 onward},
-which is: \vspace{-.3in}
-
+This simplification is reasonable because the pension age will be same in mid-2017 onward}, which is:
+\vspace{-.3in}
 \begin{align*}
@@
 \end{align*}
-
-We take the following algorithm: For \(h=1,2,\dots,H\), we keep
-increasing pension age vector
-\([\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]\) by a month
-at a time, unless we find that \vspace{-.2in}
-
+We take the following algorithm:
+For \(h=1,2,\dots,H\), we keep increasing pension age vector \([\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]\) by a month at a time, unless we find that
+\vspace{-.2in}
 \begin{align*}
@@
 \end{align*}
-
-where \(\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})\) is the mean value
-of \(h\)-step-ahead forecast of OADR with a pension age at the time
-\(n+h\) equal to \(\text{PA}_{n+h}\).
-
-In addition to finding the target pension age based on the mean value of
-OADR, the aim is to find plausible pension age schemes that could give
-the desired OADR level. To be more specific, ``plausible'', means
-finding a range of pension age schemes that could possibly lead to the
-desired OADR, contained by 80\% prediction intervals of simulated OADR.
-Because of the monotonic relationship between pension age and OADR, we
-only need to find the upper (lower) boundary of plausible pension age
-schemes, at which the upper (lower) limit of 80\% prediction intervals
-of OADR is equal to the desired OADR level. Hence, any pension age
-scheme within those two boundaries is plausible. The range of plausible
-pension age schemes can be thought of as 80\% confidence interval of
-pension age scheme where we are 80\% sure that there will be a desired
-outcome. In other words, any pension age scheme outside the range is
-undesirable to use, because we are 80\% certain that the corresponding
-OADR will deviate from the desired level of OADR.
-
-The algorithm to find the upper and lower boundary of plausible pension
-age schemes is similar to the algorithm to find the target pension age
-scheme, except that the mean value of OADR is replaced by the boundary
-of the 80\% prediction interval. Mean is replaced by the upper (lower)
-limit of the 80\% prediction interval to find upper (lower) boundary for
-pension age schemes.
-
-\subsection{Plausible Pension Age
-Schemes}\label{plausible-pension-age-schemes}
-
-Table 1 shows the target pension age scheme, which is properly defined
-in section 3.2.2. It is assumed that it is impractical to change the
-pension age during 2011--2014, so the pension age has to be set at 65
-for those years. Figure \ref{fig:OADRwithoptimal} provides a visible
-comparison of the desired OADR level of 21\% and the mean forecast of
-the OADR corresponding to the target pension age. Note that the OADR
-associated with target pension age scheme has nearly overlapped the
-desired OADR level, which indicates that we have successfully found the
-pension age with stable OADR at the desired
-levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
-
-\begin{table}[t]
+where \(\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})\) is the mean value of \(h\)-step-ahead forecast of OADR with a pension age at the time \(n+h\) equal to \(\text{PA}_{n+h}\).
+
+In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
+To be more specific, ``plausible'', means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80\% prediction intervals of simulated OADR.
+Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80\% prediction intervals of OADR is equal to the desired OADR level.
+Hence, any pension age scheme within those two boundaries is plausible.
+The range of plausible pension age schemes can be thought of as 80\% confidence interval of pension age scheme where we are 80\% sure that there will be a desired outcome.
+In other words, any pension age scheme outside the range is undesirable to use, because we are 80\% certain that the corresponding OADR will deviate from the desired level of OADR.
+
+The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR is replaced by the boundary of the 80\% prediction interval.
+Mean is replaced by the upper (lower) limit of the 80\% prediction interval to find upper (lower) boundary for pension age schemes.
+
+\hypertarget{plausible-pension-age-schemes}{%
+\subsection{Plausible Pension Age Schemes}\label{plausible-pension-age-schemes}}
+
+Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
+It is assumed that it is impractical to change the pension age during 2011--2014, so the pension age has to be set at 65 for those years.
+Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21\% and the mean forecast of the OADR corresponding to the target pension age.
+Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
+
+\begin{table}
 
@@
 \centering
-\begin{tabular}{llllllllll}
+\begin{tabular}[t]{llllllllll}
 \toprule
@@
 \midrule
-2015 & 65Y & 2025 & 66Y+9M & 2035 & 69Y+3M & 2045 & 71Y+3M & 2055 & 71Y+3M\\
-2016 & 65Y & 2026 & 67Y+3M & 2036 & 69Y+9M & 2046 & 71Y+3M & 2056 & 71Y+3M\\
-2017 & 65Y & 2027 & 67Y+3M & 2037 & 69Y+9M & 2047 & 71Y+3M & 2057 & 71Y+3M\\
-2018 & 65Y & 2028 & 67Y+9M & 2038 & 70Y+3M & 2048 & 71Y+3M & 2058 & 71Y+3M\\
-2019 & 65Y & 2029 & 67Y+9M & 2039 & 70Y+3M & 2049 & 71Y+3M & 2059 & 71Y+4M\\
+2017 & 65Y & 2027 & 66Y+8M & 2037 & 69Y+2M & 2047 & 71Y+2M & 2057 & 71Y+2M\\
+2018 & 65Y & 2028 & 67Y+2M & 2038 & 69Y+8M & 2048 & 71Y+2M & 2058 & 71Y+2M\\
+2019 & 65Y & 2029 & 67Y+2M & 2039 & 69Y+8M & 2049 & 71Y+2M & 2059 & 71Y+2M\\
+2020 & 65Y & 2030 & 67Y+8M & 2040 & 70Y+2M & 2050 & 71Y+2M & 2060 & 71Y+2M\\
+2021 & 65Y & 2031 & 67Y+8M & 2041 & 70Y+2M & 2051 & 71Y+2M & 2061 & 71Y+2M\\
 \addlinespace
-2020 & 65Y+5M & 2030 & 68Y+3M & 2040 & 70Y+9M & 2050 & 71Y+3M & 2060 & 71Y+5M\\
-2021 & 65Y+9M & 2031 & 68Y+3M & 2041 & 70Y+9M & 2051 & 71Y+3M & 2061 & 71Y+7M\\
-2022 & 65Y+11M & 2032 & 68Y+9M & 2042 & 71Y+3M & 2052 & 71Y+3M & 2062 & 71Y+9M\\
-2023 & 66Y+3M & 2033 & 68Y+9M & 2043 & 71Y+3M & 2053 & 71Y+3M & 2063 & 71Y+10M\\
-2024 & 66Y+9M & 2034 & 69Y+3M & 2044 & 71Y+3M & 2054 & 71Y+3M & 2064 & 71Y+10M\\
+2022 & 65Y+5M & 2032 & 68Y+2M & 2042 & 70Y+8M & 2052 & 71Y+2M & 2062 & 71Y+2M\\
+2023 & 65Y+8M & 2033 & 68Y+2M & 2043 & 70Y+8M & 2053 & 71Y+2M & 2063 & 71Y+2M\\
+2024 & 65Y+11M & 2034 & 68Y+8M & 2044 & 71Y+2M & 2054 & 71Y+2M & 2064 & 71Y+2M\\
+2025 & 66Y+2M & 2035 & 68Y+8M & 2045 & 71Y+2M & 2055 & 71Y+2M & 2065 & 71Y+2M\\
+2026 & 66Y+8M & 2036 & 69Y+2M & 2046 & 71Y+2M & 2056 & 71Y+2M & 2066 & 71Y+3M\\
 \bottomrule
@@
 
-\begin{table}[t]
+\begin{table}
 
@@
 \fontsize{7}{9}\selectfont
-\begin{tabular}{lllllllllllllll}
+\begin{tabular}[t]{lllllllllllllll}
 \toprule
@@
 \midrule
-2015 & 65Y & 65Y & 2025 & 66Y+6M & 66Y+11M & 2035 & 68Y & 69Y+8M & 2045 & 70Y & 71Y+8M & 2055 & 70Y & 72Y+1M\\
-2016 & 65Y & 65Y & 2026 & 67Y & 67Y+5M & 2036 & 68Y+6M & 70Y+2M & 2046 & 70Y & 71Y+8M & 2056 & 70Y & 72Y+3M\\
-2017 & 65Y & 65Y & 2027 & 67Y & 67Y+6M & 2037 & 68Y+6M & 70Y+2M & 2047 & 70Y & 71Y+8M & 2057 & 70Y & 72Y+6M\\
-2018 & 65Y & 65Y & 2028 & 67Y+6M & 68Y & 2038 & 69Y & 70Y+8M & 2048 & 70Y & 71Y+8M & 2058 & 70Y & 72Y+8M\\
-2019 & 65Y & 65Y & 2029 & 67Y+6M & 68Y+1M & 2039 & 69Y & 70Y+8M & 2049 & 70Y & 71Y+8M & 2059 & 70Y & 72Y+10M\\
+2017 & 65Y & 65Y & 2027 & 66Y+4M & 67Y & 2037 & 68Y & 69Y+7M & 2047 & 70Y & 71Y+7M & 2057 & 70Y & 71Y+11M\\
+2018 & 65Y & 65Y & 2028 & 66Y+10M & 67Y+6M & 2038 & 68Y+6M & 70Y+1M & 2048 & 70Y & 71Y+7M & 2058 & 70Y & 72Y+2M\\
+2019 & 65Y & 65Y & 2029 & 66Y+10M & 67Y+7M & 2039 & 68Y+6M & 70Y+1M & 2049 & 70Y & 71Y+7M & 2059 & 70Y & 72Y+4M\\
+2020 & 65Y & 65Y & 2030 & 67Y+4M & 68Y+1M & 2040 & 69Y & 70Y+7M & 2050 & 70Y & 71Y+7M & 2060 & 70Y & 72Y+7M\\
+2021 & 65Y & 65Y & 2031 & 67Y+4M & 68Y+1M & 2041 & 69Y & 70Y+7M & 2051 & 70Y & 71Y+7M & 2061 & 70Y & 72Y+9M\\
 \addlinespace
-2020 & 65Y+4M & 65Y+7M & 2030 & 68Y & 68Y+7M & 2040 & 69Y+6M & 71Y+2M & 2050 & 70Y & 71Y+8M & 2060 & 70Y & 73Y+1M\\
-2021 & 65Y+6M & 65Y+11M & 2031 & 68Y & 68Y+8M & 2041 & 69Y+6M & 71Y+2M & 2051 & 70Y & 71Y+8M & 2061 & 70Y & 73Y+3M\\
-2022 & 65Y+9M & 66Y+2M & 2032 & 68Y+6M & 69Y+2M & 2042 & 70Y & 71Y+8M & 2052 & 70Y & 71Y+8M & 2062 & 70Y & 73Y+5M\\
-2023 & 66Y & 66Y+5M & 2033 & 68Y+6M & 69Y+2M & 2043 & 70Y & 71Y+8M & 2053 & 70Y & 71Y+9M & 2063 & 70Y & 73Y+8M\\
-2024 & 66Y+6M & 66Y+11M & 2034 & 69Y & 69Y+8M & 2044 & 70Y & 71Y+8M & 2054 & 70Y & 71Y+11M & 2064 & 70Y & 73Y+10M\\
+2022 & 65Y+4M & 65Y+7M & 2032 & 67Y+10M & 68Y+7M & 2042 & 69Y+6M & 71Y+1M & 2052 & 70Y & 71Y+7M & 2062 & 70Y & 73Y\\
+2023 & 65Y+6M & 65Y+10M & 2033 & 67Y+10M & 68Y+7M & 2043 & 69Y+6M & 71Y+1M & 2053 & 70Y & 71Y+7M & 2063 & 70Y & 73Y+2M\\
+2024 & 65Y+7M & 66Y+2M & 2034 & 68Y+4M & 69Y+1M & 2044 & 70Y & 71Y+7M & 2054 & 70Y & 71Y+7M & 2064 & 70Y & 73Y+4M\\
+2025 & 65Y+10M & 66Y+5M & 2035 & 68Y+4M & 69Y+1M & 2045 & 70Y & 71Y+7M & 2055 & 70Y & 71Y+7M & 2065 & 70Y & 73Y+6M\\
+2026 & 66Y+4M & 66Y+11M & 2036 & 68Y+10M & 69Y+7M & 2046 & 70Y & 71Y+7M & 2056 & 70Y & 71Y+8M & 2066 & 70Y & 73Y+9M\\
 \bottomrule
@@
 \includegraphics{PensionAge_files/figure-latex/OADRwithoptimal-1.pdf}
-\caption{\label{fig:OADRwithoptimal}The mean forecast of OADR associated
-with target pension age scheme (listed in Table 1) shown in blue, along
-with the desired OADR level in red (i.e., mean forecast of OADR in
-2014). The 80\% prediction interval of the forecast of OADR is shown as
-blue shading.}
+\caption{\label{fig:OADRwithoptimal}The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
+The 80\% prediction interval of the forecast of OADR is shown as blue shading.}
 \end{figure}
@@
 \includegraphics{PensionAge_files/figure-latex/OADRboundaries-1.pdf}
-\caption{\label{fig:OADRboundaries}The 80\% prediction interval forecast of
-OADR (in blue) associated with upper and lower boundary of plausible
-pension age schemes (listed in Table.2), along with desired OADR level
-(in red).}
+\caption{\label{fig:OADRboundaries}The 80\% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).}
 \end{figure}
@@
 \includegraphics{PensionAge_files/figure-latex/comparisonofpensionages-1.pdf}
-\caption{\label{fig:comparisonofpensionages}The comparison between the
-target pension age scheme (in green) and real pension age scheme that
-has been set or proposed by government, along with the 80\% confidence
-interval of the target pension age shown in green shade. The red solid
-line indicates the changes to the pension age from 65 to 67, announced
-in 2009.}
+\caption{\label{fig:comparisonofpensionages}The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80\% confidence interval of the target pension age shown in green shade.
+The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.}
 \end{figure}
 
-The upper and lower boundaries of the plausible pension age schemes
-(also called the 80 \% confidence interval of the target pension age
-scheme in this paper) are reported in Table 2, and their corresponding
-OADR simulation results are shown in Figure \ref{fig:OADRboundaries}. It
-can be seen that the lower (upper) limit of the 80\% prediction interval
-of OADR associated with lower (upper) boundary of the 80\% confidence
-interval pension age scheme is entirely stable around the desired level.
-Note the negative relationship between OADR and pension age. It
-suggests, on one hand, that any pension age higher than the upper
-boundary in table 2 is deemed to be undesirable because the age is too
-high to allow the age pension to provide enough welfare support or
-insurance to the aged. On the other hand, any pension age scheme lower
-than the lower boundary of the pension age reported in Table 2 will also
-be regarded as unreasonable, because it sacrifices the interests of the
-next generation to provide a very generous age pension immediately.
-
-Figure \ref{fig:comparisonofpensionages} compares the target pension age
-scheme and its 80\% confidence interval with the pension age scheme with
-proposed further change. It was found that the target pension age
-increases at higher rate than the proposed new pension age scheme.
-Reported in Table 1, the target pension age is supposed to reach 67 by
-2021 and 70 by 2032, while pension age has been proposed to change to 67
-by 2023 and 70 by 2035. Moreover, the proposed pension age scheme is
-below the lower boundary of plausible pension age schemes, which means
-we are 80\% sure that it will cause an OADR higher than desired level.
-From this result, it is concluded that government will need to adjust
-pension age slightly quicker than proposed pace to ensure we have a
-stable OADR around desired level at 21\%.
-
-However, it is interesting to note that the proposed pension age scheme
-does not diverge too far from the plausible pension age schemes,
-suggesting proposed new pension age scheme may be appropriate if we can
-afford slightly higher OADR. Therefore, it is worth performing a
-sensitivity test on the desired level here.
-
-Using the approach suggested in this paper, the target pension age
-associated with desired OADR equal to current level plus 1\% has been
-found. We have shown the comparison of it
-\todo{code are missing for two figures} and its 80\% confidence level
-with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
-When we allow 1\% more in desired OADR, the real pension age becomes
-plausible. Figure \ref{fig:OADR_realpensionage} shows simulated OADR
-associated with proposed pension age
-scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
-It confirms that OADR is stable around a level higher than current level
-of OADR before 2035. This results suggest that pension age scheme with
-proposed change could be suitable if the government are targeting a
-slightly higher financial pressure than current level.
-
-\section{Conclusions}\label{sec:conclusions}
-
-The ageing of population is expected to become a critical issue in
-Australia due to the increase in life expectancy and the retirement of
-baby boomers. The fiscal cost of the age pension is projected to sharply
-increase as a result. For the purpose of sustainability of the welfare
-system in Australia, the government has announced an increase in the
-pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden
-on society.
-
-In this paper, we have suggested a statistical and demographic approach
-to address the issue. We attempt to quantify the effects of changes in
-the pension age on financial burdens using an OADR as a measure of
-financial burden on Australian society. The quantification process
-involves applying stochastic models to forecast future population age
-structure and then using those future age structure projections to find
-the most appropriate pension age scheme that will ensure stable OADR
-around the desired level. To forecast population age structure, three
-demographic components of population were modelled separately using
-\textcite{HU07} functional time series method, with an extension of the
-product-ratio method \autocite{HBY13}. Next, future age structures were
-used to simulate OADR associated with different pension age schemes
-until the minimum pension age scheme was found, which ensures the OADR
-no greater than desired level. This approach is proposed to find target
-pension age scheme based on a given desired level of OADR.
-
-We undertake the approach based on assuming the desired level of OADR is
-at current level of 21\%. Using the historical data from 1950 to 2010,
-the forecast of future populations suggests a substantial increase in
-total population, and confirms the inherent ageing trend. It was found
-that pension age should not be fixed, but instead should grow at a rate
-that will ensure a stable OADR at a level which can be affordable to
-Australians of working age. Findings indicate that the pension age
-scheme with proposed change was not too high, as it is still lower than
-the target pension age scheme and outside its confidence interval. It
-was concluded that the pension age set by government should be adjusted
-slight quicker to be in line with our target pension age, which ensures
-a stable OADR of around 21\%.
-
-The empirical analysis presented in this paper shows the adjustment of
-the pension age announced in 2009 was effective in reducing the
-financial burden to the desired level, which was set at 21\%. However, a
-one-time adjustment is not sufficient to ensure a stable OADR in the
-long term, due to ongoing changes in the population age structure.
-Therefore, we recommend consistently reviewing the pension age according
-to the presented statistical approach. This approach has been used to
-calculate the target pension age from now until 2060 and its 80\%
-confidence interval. The target pension age found in this research
-increases to 67 by 2023, 70 by 2032 and 75 by 2058. This generates a
-stable OADR of around 21\%. The rate of growth in the pension age as
-proposed by the government in 2014 is slightly lower than the target
-pension age found in this study, which suggests that the government may
-need to slightly accelerate the growth of the pension age to maintain an
-OADR at the current level.
-
-Although our results are promising, there are still grounds for further
-research. First, our research results are based on forecasts from one
-particular model. Further studies can apply the same approach but with
-different models of population forecasting, which allows for enhanced
-credibility of results. Moreover, our research addresses the issue from
-a purely demographic perspective. It is possible to include an economic
-perspective. For example, the economic implications of retaining older
-workers in workforce can be considered. Second, Our research uses an
-OADR as a single measurement of financial burden. Further research
-should allow the effect of other economic factors to be taken into
-account. For instance, the effect of growth in superannuation can be
-considered in a way that the effects of high OADR can be offset by the
-growth in superannuation.
+The upper and lower boundaries of the plausible pension age schemes (also called the 80 \% confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \ref{fig:OADRboundaries}.
+It can be seen that the lower (upper) limit of the 80\% prediction interval of OADR associated with lower (upper) boundary of the 80\% confidence interval pension age scheme is entirely stable around the desired level.
+Note the negative relationship between OADR and pension age.
+It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
+On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
+
+Figure \ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80\% confidence interval with the pension age scheme with proposed further change.
+It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
+Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
+Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80\% sure that it will cause an OADR higher than desired level.
+From this result, it is concluded that government will need to adjust pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21\%.
+
+However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
+Therefore, it is worth performing a sensitivity test on the desired level here.
+
+Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1\% has been found.
+We have shown the comparison of it \todo{code are missing for two figures} and its 80\% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
+When we allow 1\% more in desired OADR, the real pension age becomes plausible.
+Figure \ref{fig:OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+It confirms that OADR is stable around a level higher than current level of OADR before 2035.
+This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
+
+\hypertarget{sec:conclusions}{%
+\section{Conclusions}\label{sec:conclusions}}
+
+The ageing of population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers.
+The fiscal cost of the age pension is projected to sharply increase as a result.
+For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden on society.
+
+In this paper, we have suggested a statistical and demographic approach to address the issue.
+We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of financial burden on Australian society.
+The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable OADR around the desired level.
+To forecast population age structure, three demographic components of population were modelled separately using \textcite{HU07} functional time series method, with an extension of the product-ratio method \autocite{HBY13}.
+Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than desired level.
+This approach is proposed to find target pension age scheme based on a given desired level of OADR.
+
+We undertake the approach based on assuming the desired level of OADR is at current level of 21\%.
+Using the historical data from 1950 to 2010, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
+It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
+Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
+It was concluded that the pension age set by government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21\%.
+
+The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at 21\%.
+However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
+Therefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
+This approach has been used to calculate the target pension age from now until 2060 and its 80\% confidence interval.
+The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
+This generates a stable OADR of around 21\%.
+The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
+
+Although our results are promising, there are still grounds for further research.
+First, our research results are based on forecasts from one particular model.
+Further studies can apply the same approach but with different models of population forecasting, which allows for enhanced credibility of results.
+Moreover, our research addresses the issue from a purely demographic perspective.
+It is possible to include an economic perspective.
+For example, the economic implications of retaining older workers in workforce can be considered.
+Second, Our research uses an OADR as a single measurement of financial burden.
+Further research should allow the effect of other economic factors to be taken into account.
+For instance, the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.
 

### 2020-05-03 functions-v4.R

@@ -1,15 +1,32 @@
+# Autoplot for fmforecast objects
+autoplot.fmforecast <- function(data) {
+  require(latex2exp)
+  p1 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,1])) +
+    geom_line() + xlab("Age (x)") + ylab(TeX("$\\mu(x)"))
+  p2 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,2])) +
+    geom_line() + xlab("Age (x)") + ylab(TeX("$\\phi_1(x)$"))
+  p3 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,3])) +
+    geom_line() + xlab("Age (x)") + ylab(TeX("$\\phi_2(x)$"))
+  p4 <- autoplot(data$coeff[[2]]) +
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{1,t}$"))
+  p5 <- autoplot(data$coeff[[3]]) +
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{2,t}$"))
+
+  print((p1 | p2 | p3) / ( plot_spacer() | p4 | p5))
+}
+
 
 # Function to produce old age dependency ratio
 oadr <- function(x, sim, pension.age=65, historical.pension.age=65, level=80)
-{  
+{
   adjustment<-(historical.pension.age%%1)*colSums(extract.ages(x,as.integer(historical.pension.age)+1,FALSE)$pop$total,na.rm=TRUE)
   workers <-colSums(extract.ages(x,15:as.integer(historical.pension.age),FALSE)$pop$total,na.rm=TRUE)+adjustment
   aged <- colSums(extract.ages(x,as.integer(historical.pension.age):max(x$age),TRUE)$pop$total,na.rm=TRUE)-adjustment
-  
-  xhistory <- ts(aged/workers,s=x$year[1],f=1) 
+
+  xhistory <- ts(aged/workers,s=x$year[1],f=1)
 
   ##ts is "time series" s is starting f is frequency
-  
+
   h <- dim(sim[[1]])[2]
   N <- dim(sim[[1]])[3]
   if(length(pension.age)==1)
@@ -22,11 +39,11 @@ oadr <- function(x, sim, pension.age=65, historical.pension.age=65, level=80)
   # Check that pension.age does not increase too quickly
   if(max(diff(pension.age)) > 1)
[…]

### 2020-05-03 hmd.R

@@ -1,0 +1,81 @@
+# HMD credentials
+username <- "hanlin.shang@gmail.com"
+password <- "hshang85"
+
+hmd.pop <- function (country, username, password, label = country)
+{
+  path <- paste("https://www.mortality.org/hmd/", country, "/STATS/",
+                "Population.txt", sep = "")
+  userpwd <- paste(username, ":", password, sep = "")
+  txt <- RCurl::getURL(path, userpwd = userpwd)
+  con <- textConnection(txt)
+  pop <- try(utils::read.table(con, skip = 2, header = TRUE,
+                               na.strings = "."), TRUE)
+  close(con)
+  if (class(pop) == "try-error")
+    stop("Population file not found at www.mortality.org")
+  obj <- list(type = "population", label = label, lambda = 0)
+  obj$year = sort(unique(pop[, 1]))
+  n <- length(obj$year)
+  m <- length(unique(pop[, 2]))
+  obj$age <- pop[1:m, 2]
+  mnames <- names(pop)[-c(1, 2)]
+  n.pop <- length(mnames)
+  obj$pop <- list()
+  for (i in 1:n.pop) {
+    obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
+    obj$pop[[i]][obj$pop[[i]] < 0] <- NA
+    dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
+  }
+  names(obj$pop) <- tolower(mnames)
+  obj$age <- as.numeric(as.character(obj$age))
+  if (is.na(obj$age[m]))
+    obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
+  return(structure(obj, class = "demogdata"))
+}
+
+hmd.mx <- function (country, username, password, label = country)
+{
+  path <- paste("https://www.mortality.org/hmd/", country, "/STATS/",
+                "Mx_1x1.txt", sep = "")
+  userpwd <- paste(username, ":", password, sep = "")
+  txt <- RCurl::getURL(path, userpwd = userpwd)
+  con <- textConnection(txt)
+  mx <- try(utils::read.table(con, skip = 2, header = TRUE,
+                              na.strings = "."), TRUE)
+  close(con)
+  if (class(mx) == "try-error")
+    stop("Connection error at www.mortality.org. Please check username, password and country label.")
[…]

### 2020-05-03 PensionAge.Rmd
Functions converted to tidyverse

@@
 library(addb)
+library(patchwork)
 library(kableExtra)
-library(patchwork)
 source("functions-v4.R")
@@
 # Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
+# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10 
+# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
 pension_age <- tibble(
-    year = 2008:2068,
-    current = 65
+    Year = 1920:2068,
+    Current = 65
   ) %>%
   mutate(
-    proposed = pmin(70, current + 0.5*pmax(0, trunc((year - 2015)/2))),
-    approved = pmin(proposed, 67),
-  ) %>%
-  pivot_longer(-year, values_to="age", names_to="policy")
+    Proposed = pmin(70, Current + 0.5*pmax(0, trunc((Year - 2015)/2))),
+    Approved = pmin(Proposed, 67),
+  ) %>%
+  pivot_longer(-Year, values_to="Age", names_to="Policy")
 
 pension_age %>%
-  filter(year <= 2050) %>%
-  ggplot(aes(x=year, y=age, group=policy)) +
-    geom_line(aes(col=policy)) +
-    xlab("Year") + ylab("Age of retirement") +
-    scale_color_manual(
-      values = c(current = "#1b9e77", approved = "#d95f02", proposed = "#7570b3"),
-      name = " ",
-      breaks = c("current", "approved", "proposed"),
-      labels = c("Pension age at 65", "Approved change", "Proposed further change")
+  filter(Year >= 2008, Year <= 2050) %>%
+  ggplot(aes(x=Year, y=Age, group=Policy, col=Policy)) +
+    geom_line() + 
+    ylab("Age of retirement") +
+    scale_color_brewer(palette="Dark2",
+      breaks = c("Proposed", "Approved", "Current"),
+      labels = c("Proposed further change",  "Approved change", "Pension age at 65")
     )
@@
 # Get population data to 1 Jan 2019
-auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
-auspop <- extract.ages(auspop, ages = 0:100)
+aus.pop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
+aus.pop <- extract.ages(aus.pop, ages = 0:100)
 
@@
 fpop <- cbind(aus.fert$pop$female[, 1:54], newpop)
-# Use populations in ausf rather than auspop to get the same rates
+# Use populations in ausf rather than aus.pop to get the same rates
 aus.fert$rate$female <- births / fpop
@@
 # Compute migration data
-aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = auspop, mfratio = 1.05)
-save(aus.fert, aus.mort, aus.mig, file="ausdata.Rdata")
+aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = aus.pop, mfratio = 1.05)
+save(aus.fert, aus.mort, aus.mig, aus.pop, file="ausdata.Rdata")
+rm(ausf,births,fpop,newbirths,newpop)
 ```
@@
 auspop_df <- bind_rows(
-  as_tibble(auspop$pop$male / 1000) %>%
+  as_tibble(aus.pop$pop$male / 1000) %>%
     mutate(
-      Age = auspop$age,
+      Age = aus.pop$age,
       Sex = "Male"
@@
     pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-  as_tibble(auspop$pop$female / 1000) %>%
+  as_tibble(aus.pop$pop$female / 1000) %>%
     mutate(
-      Age = auspop$age,
+      Age = aus.pop$age,
       Sex = "Female"
@@
 nsim <- 20 # Change to 2000 or higher to get better estimates
-aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = auspop, N = nsim)
-```
-
-```{r simtibble, dependson = 'simulation}
+aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)
+
 # Combine simulation results into one tibble
@@
   ungroup()
+# Historical data as a tibble
+history_pop <- bind_rows(
+  as_tibble(aus.pop$pop$male / 1000) %>%
+    mutate(
+      Age = aus.pop$age,
+      Sex = "Male"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+  as_tibble(aus.pop$pop$female / 1000) %>%
+    mutate(
+      Age = aus.pop$age,
+      Sex = "Female"
+    ) %>%
+    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
+  ) %>%
+  mutate(Year = as.numeric(Year))
+```
+
+```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals.
+The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
 future_tot_pop <- aussim_df %>%
@@
   ungroup()
-# Historical data as a tibble
-history_pop <- bind_rows(
-  as_tibble(auspop$pop$male / 1000) %>%
-    mutate(
-      Age = auspop$age,
-      Sex = "Male"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-  as_tibble(auspop$pop$female / 1000) %>%
-    mutate(
-      Age = auspop$age,
-      Sex = "Female"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-  ) %>%
-  mutate(Year = as.numeric(Year))
-history_tot_pop <- history_pop %>%
+history_pop %>%
   group_by(Sex, Year) %>%
-  summarise(Population = sum(Population)/1e3)
-```
-
-```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals.
-The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
-history_tot_pop %>% 
+  summarise(Population = sum(Population)/1e3) %>%
   ggplot(aes(x=Year, y=Population, group=Sex)) +
@@
     geom_ribbon(aes(y=Mean, ymin=Lo80, ymax=Up80), fill='#7d7def', data=future_tot_pop) +
-    geom_line(data=future_tot_pop, col='blue', mapping=aes(y=Mean), size=1) 
+    geom_line(data=future_tot_pop, col='#0000cc', mapping=aes(y=Mean), size=1)
 ```
@@
 ```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals.
-The actual pyramid for 2015 is shown using dashed lines.", , dependson='simulationresults'}
+The actual pyramid for 2015 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
 pyramid <- function(history, future) {
@@
       geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
-      geom_line(linetype=2) + geom_line(aes(y=Mean), col='blue') + 
+      geom_line(linetype=2) + geom_line(aes(y=Mean), col='#0000cc') +
       coord_flip() +
@@
 ```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
-current <- pension_age %>% 
-  filter(policy=="current", year %in% unique(tot_pop$Year) ) %>% 
-  arrange(year) %>% pull(age)
-proposed <- pension_age %>% 
-  filter(policy=="proposed", year %in% unique(tot_pop$Year) ) %>% 
-  arrange(year) %>% pull(age)
-approved <- pension_age %>% 
-  filter(policy=="approved", year %in% unique(tot_pop$Year) ) %>% 
-  arrange(year) %>% pull(age)
-OADR.65 <- oadr(history, aussim_df, pension.age = current) %>% mutate(policy="Pension age 65")
+OADR_history <- oadr(history_pop, filter(pension_age, Policy=='Current'))
+OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy=='Current')) %>%
+  mutate(Policy="Pension age 65")
 OADR.65 %>%
-  ggplot(aes(x=Year, y=OADP, group=Sex)) +
+  ggplot(aes(x=Year, y=OADR)) +
     geom_ribbon(aes(ymin=Lo, ymax=Hi), fill='#7d7def') +
-    geom_line(col='blue', size=1) +
-    facet_grid(. ~ Sex) +
+    geom_line(col='#0000aa', size=.75) +
+    geom_line(col='black', size=.75, data=OADR_history) +
     xlab("year") + ylab("ratio") +
@@
 The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
-OADR.67 <- oadr(history, aussim_df, pension.age = approved) %>% 
-  mutate(policy="Current policy")
-OADR.prop <- oadr(history, aussim_df, pension.age = proposed) %>% 
-  mutate(policy="Proposed policy")
-bind_rows(OADR.65,OADR.67,OADR.prop) %>%
-  mutate(policy = factor(policy, 
-    levels = c("Pension age 65","Current policy","Proposed policy"))) %>%
-  ggplot(aes(x=Year, y=OADP, group=policy)) +
-    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=policy), alpha=0.5) +
-    geom_line(aes(col=policy), size=1) +
+df <- bind_rows(
+  OADR.65,
+  oadr_sim(aussim_df, filter(pension_age, Policy=='Approved')) %>%
+    mutate(Policy="Current policy"),
+  oadr_sim(aussim_df, filter(pension_age, Policy=='Proposed')) %>%
+    mutate(Policy="Proposed policy")
+) %>%
+  mutate(Policy = factor(Policy,
+    levels = c("Pension age 65","Current policy","Proposed policy")))
+df %>%
+  ggplot(aes(x=Year, y=OADR)) +
     geom_hline(yintercept = 0.21, col = "gray") +
-    facet_grid(. ~ Sex) +
+    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=Policy, group=Policy), alpha=0.5) +
+    geom_line(aes(col=Policy, group=Policy), size=.75) +
+    geom_line(col='black', size=.75, data=OADR_history) +
     xlab("year") + ylab("ratio") +
     ggtitle("OADR forecasts with pension age=65") +
-    scale_color_brewer(palette="Dark2") + scale_fill_brewer(palette="Dark2")
+    scale_color_brewer(palette="Dark2") +
+    scale_fill_brewer(palette="Dark2")
 ```
@@
 k <- 25 ## years of data required to make a forecast
-oadrtest <- matrix(0, 25, t - k - H)
-for (i in 1:(t - k - H))
+rolling_sim <- NULL
+for (i in seq(t - k - H))
 {
@@
     ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
-    pop.short <- extract.years(auspop, years = 1949 + i + (0:k))
+    pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
     mort.fit.s <- coherentfdm(ausmort.short)
@@
     migfs <- forecast(mig.fit.s, H)
-    aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs, firstyearpop = pop.short, 
-                         N = 3)
-    OADR.fs <- oadr(pop.short, aus.sim.s)
-    oadrtest[, i] <- OADR.fs$mean
+    aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs,
+                         firstyearpop = pop.short, N = 3)
+    # Combine simulation results into one tibble
+    dimnames(aus.sim.s[["male"]]) <-
+      dimnames(aus.sim.s[["female"]]) <-
+      list(
+        Age = dimnames(aus.sim.s[[1]])[[1]],
+        Year = dimnames(aus.sim.s[[1]])[[2]],
+        Rep = dimnames(aus.sim.s[[1]])[[3]]
+    )
+    rolling_sim <- bind_rows(
+      rolling_sim,
+      as.tbl_cube(aus.sim.s[["male"]]/1e3, met_name = "Population") %>%
+        as_tibble() %>% mutate(Sex = "Male", id=i),
+      as.tbl_cube(aus.sim.s[["female"]]/1e3, met_name = "Population") %>%
+        as_tibble() %>% mutate(Sex = "Female", id=i)
+    )
 }
-oadr.real <- oadr(auspop, aus.sim)$x
-oadr.real.mat <- oadr.error <- matrix(NA, 25, 15)
-for (i in 1:25)
-  oadr.real.mat[i, ] <- oadr.real[(i + 56):(56 + 14 + i)]
-
-oadr.error <- abs(oadrtest - oadr.real.mat)
-oadrave <- apply(oadr.error, 1, mean)
-
-plot(oadrave, xlab = "forecast horizon", ylab = "mean", ylim = c(0, 0.02))
+```
+
+```{r rmseplot, dependson="rollingtest"}
+oadr_rolling_sim(rolling_sim, 
+    filter(pension_age, Policy=='Approved')) %>%
+  group_by(id) %>%
+  mutate(h = row_number()) %>%
+  ungroup() %>%
+  select(Year, h, OADR) %>% 
+  rename(Forecast = OADR) %>%
+  left_join(OADR_history, by="Year") %>%
+  mutate(e = OADR-Forecast) %>%
+  group_by(h) %>%
+  summarise(RMSE = sqrt(mean(e^2))) %>%
+  ggplot(aes(x=h, y=RMSE)) +
+    geom_point()
 ```
@@
 
-```{r pension, dependson="OADRat65"}
-### find the optimal scheme of pension.age based on mean forecast
-target <- OADR.f$mean[4]
-
-pension.age <- proposed
-for (i in 6:50)
-{
-  current <- oadr(auspop, aus.sim,
-    pension.age = pension.age
-  )$mean[i]
+```{r optimal_pension, dependson="OADRat65"}
+### find the pension.age scheme with OADR closest to target
+### find upper boundary of pension ages whose OADR PI contains target
+### find Lower boundary of pension ages whose OADR PI contains target
+### Constrained such that solution is in minimum jumps of 1 month
+### and the pension age can't change until 2023
+
+# Chosen target OADR
+target <- 0.22
+
+# Lower bound (starting at age 65)
+pension_age_lower <- pension_age %>%
+  filter(Policy == "Current", Year >= 2019) %>% select(-Policy) 
+for (i in seq(5,50)) {
+  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
   while ((current > target) & 
-    (max(diff(pension.age[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension.age[i:50] <- pension.age[i:50] + 1 / 12
-    current <- oadr(auspop, aus.sim,
-      pension.age = pension.age
-    )$mean[i]
+         (max(diff(pension_age_lower$Age[(i-1):50])) <= (1 - 1/12))) {
+    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1/12
+    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
   }
 }
-OADR.f.optimal <- oadr(auspop,
-  aus.sim,
-  pension.age = pension.age
-)
-```
-
-```{r pensionupper, dependson="simulationresults"}
-### find the upper boundary of pension ages whose prediction interval contains target
-pension.age.upper <- proposed
-for (i in 6:50)
-{
-  current.upper <- oadr(auspop, aus.sim,
-    pension.age = pension.age.upper
-  )$upper[i]
-  while ((current.upper > target) &
-    (max(diff(pension.age.upper[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension.age.upper[i:50] <- pension.age.upper[i:50] + 1 / 12
-    current.upper <- oadr(auspop, aus.sim,
-      pension.age = pension.age.upper
-    )$upper[i]
+# Mean (start at lower bound)
+pension_age_optimal <- pension_age_lower
+for (i in seq(5,50)) {
+  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
+  while ((current > target) & 
+         (max(diff(pension_age_optimal$Age[(i-1):50])) <= (1 - 1/12))) {
+    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1/12
+    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
   }
 }
-OADR.f.upper <- oadr(auspop,
-  aus.sim,
-  pension.age = pension.age.upper
-)
-```
-
-```{r pensionlower, dependson="simulationresults"}
-##### find the lower boundary of pension ages whose prediction interval contains target
-pension.age.lower <- proposed
-for (i in 6:20)
-{
-  current.lower <- oadr(auspop, aus.sim,
-    pension.age = pension.age.lower
-  )$lower[i]
-  while ((current.lower > target) &
-    (max(diff(pension.age.lower[(i - 1):20])) <= (1 - 1 / 12))) {
-    pension.age.lower[i:20] <- pension.age.lower[i:20] + 1 / 12
-    current.lower <- oadr(auspop, aus.sim,
-      pension.age = pension.age.lower
-    )$lower[i]
+# Upper bound (start at mean)
+pension_age_upper <- pension_age_optimal
+for (i in seq(5,50)) {
+  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
+  while ((current > target) & 
+         (max(diff(pension_age_upper$Age[(i-1):50])) <= (1 - 1/12))) {
+    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1/12
+    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
   }
 }
-OADR.f.lower <- oadr(auspop, 
-    aus.sim, 
-    pension.age = pension.age.lower
+# Final results
+OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal) 
+pension_age_optimal <- pension_age_optimal %>%
+  mutate(
+    Lo80 = pension_age_lower$Age,
+    Hi80 = pension_age_upper$Age
   )
-```
-
-```{r pension forecast, dependson="simulationresults"}
-pension.fc <- structure(list(
-  mean = ts(pension.age, start = 2015),
-  upper = pension.age.upper,
-  lower = pension.age.lower,
-  level = 80,
-  x = ts(rep(65, 50), end = 2014)
-), class = "forecast")
 ```
@@
 
-```{r pensionagetables, dependson="OADRat65"}
-year <- time(OADR.f$mean) - 1
-yr <- trunc(pension.age)
-mth <- trunc((pension.age - trunc(pension.age)) * 12)
-agechar <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-
-tab <- matrix(NA, nrow = 10, ncol = 10)
-for (i in 1:5)
-{
-  tab[, (i - 1) * 2 + 1] <- as.character(year[(10 * (i - 1)) + (1:10)])
-  tab[, (i - 1) * 2 + 2] <- agechar[(10 * (i - 1)) + (1:10)]
-}
-colnames(tab) <- rep(c("Year", "Age"), 5)
-knitr::kable(format(tab),
+```{r pensionagetables, dependson="optimal_pension", message=FALSE}
+pension_age_optimal %>%
+  mutate(
+    Month = round((Age - trunc(Age)) * 12),
+    Agestring = paste0(trunc(Age),"Y",
+      if_else(Month > 0, paste0("+", Month, "M"), "")),
+    Column = trunc((Year - 2019) / 10) + 1,
+  ) %>% 
+  select(Year, Agestring, Column) %>%
+  nest(data=c(Year=Year, Age=Agestring)) %>%
+  pivot_wider(names_from=Column, values_from=data) %>%
+  unnest(cols=paste(1:5), names_repair='unique') %>%
+  knitr::kable(
+    format="latex",
+    col.names = rep(c("Year","Age"),5),
     booktabs = TRUE,
@@
 ```{r pensionagetables2, dependson="OADRat65"}
-year <- time(OADR.f$mean) - 1
-yr <- trunc(pension.age.lower)
-mth <- trunc((pension.age.lower - trunc(pension.age.lower)) * 12)
-age.lo <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-yr <- trunc(pension.age.upper)
-mth <- trunc((pension.age.upper - trunc(pension.age.upper)) * 12)
-age.up <- paste(yr, "Y", ifelse(mth > 0, paste("+", mth, "M", sep = ""), ""), sep = "")
-
-tab <- matrix("", nrow = 10, ncol = 15)
-for (i in 1:5)
-{
-  tab[, (i - 1) * 3 + 1] <- as.character(year[(10 * (i - 1)) + (1:10)])
-  tab[, (i - 1) * 3 + 2] <- age.lo[(10 * (i - 1)) + (1:10)]
-  tab[, (i - 1) * 3 + 3] <- age.up[(10 * (i - 1)) + (1:10)]
-}
-colnames(tab) <- rep(c("Year", "Lo", "Hi"), 5)
-kable_output = knitr::kable(format(tab),
+pension_age_optimal %>%
+  mutate(
+    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
+    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
+    AgeLo = paste0(trunc(Lo80),"Y",
+      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")),
+    AgeHi = paste0(trunc(Hi80),"Y",
+      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")),
+    Column = trunc((Year - 2019) / 10) + 1,
+  ) %>% 
+  select(Year, AgeLo, AgeHi, Column) %>%
+  nest(data=c(Year=Year, Lo=AgeLo, Hi = AgeHi)) %>%
+  pivot_wider(names_from=Column, values_from=data) %>%
+  unnest(cols=paste(1:5), names_repair='unique') %>%
+  knitr::kable(
+    format="latex",
+    col.names = rep(c("Year","Lo","Hi"),5),
     booktabs = TRUE,
@@
 ## plots of OADR with plausible pension age schemes
+OADR_optimal %>%
+  ggplot(aes(x=Year)) +
+  geom_ribbon(aes(ymin=Lo, ymax=Hi), fill="#7d7def") +
+
 autoplot(OADR.f.optimal$x) +

### 2020-05-03 functions-v4.R

@@ -15,106 +15,59 @@ autoplot.fmforecast <- function(data) {
   print((p1 | p2 | p3) / ( plot_spacer() | p4 | p5))
 }
 
-
-# Function to produce old age dependency ratio
-oadr <- function(x, sim, pension.age=65, historical.pension.age=65, level=80)
-{
-  adjustment<-(historical.pension.age%%1)*colSums(extract.ages(x,as.integer(historical.pension.age)+1,FALSE)$pop$total,na.rm=TRUE)
-  workers <-colSums(extract.ages(x,15:as.integer(historical.pension.age),FALSE)$pop$total,na.rm=TRUE)+adjustment
-  aged <- colSums(extract.ages(x,as.integer(historical.pension.age):max(x$age),TRUE)$pop$total,na.rm=TRUE)-adjustment
-
-  xhistory <- ts(aged/workers,s=x$year[1],f=1)
-
-  ##ts is "time series" s is starting f is frequency
-
-  h <- dim(sim[[1]])[2]
-  N <- dim(sim[[1]])[3]
-  if(length(pension.age)==1)
-    pension.age <- rep(pension.age, h)
-  if(length(pension.age) != h)
-    stop("length of pension.age should be equal to forecast horizon")
-  # Check that pension.age does not decrease
-  if(max(diff(pension.age)) < 0)
-    stop("Pension ages should not decrease")
-  # Check that pension.age does not increase too quickly
-  if(max(diff(pension.age)) > 1)
-    stop("Pension age should not rise more than 1 year at a time")
-
-  simages <- as.numeric(dimnames(sim[[1]])[[1]]) # Ages vector from sim
-  # Set up matrices to store populations from each forecast horizon and each simulation
-  male.workers <- female.workers <- male.aged <- female.aged <- matrix(NA,nrow=h,ncol=N)
-
-  for (i in (1:h))
-  {
-    worker.rows <- (simages >= 15 & simages < as.integer(pension.age[i]))
-    pension.rows <- (simages >= as.integer(pension.age[i]))
-    adjustment.male<-(pension.age[i]%%1)*sim$male[as.integer(pension.age[i]),i,]
-    adjustment.female<-(pension.age[i]%%1)*sim$female[as.integer(pension.age[i]),i,]
-    male.workers[i,] <- colSums(sim$male[worker.rows,i,])+adjustment.male
[…]

### 2020-05-04 PensionAge.Rmd
Merge with changes from January

@@
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the current level, which is 21%.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2014 level, which is 21%.
 This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
@@
 
-# Background and Literature Review {#sec:litreview}
+# Background {#sec:litreview}
 
@@
 Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing.
-For example, it provides single home-owners with a real income of \$13653 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
+For example, it provides single home-owners with a real income of $23,889 p.a and additional allowances to cover expenses such as rent or pharmaceuticals^[The pension amount is adjusted every 6 months for inflation].
 The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases.
@@
 
-Currently, the age pension is the primary source of income for 70% -80% of Australian residents over 64 years [@ABS06].
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the current average less than \$100,000 at retirement [@ASFA07].
-It has been estimated by @PT08 that a retiree will need to have \$450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
+In 2006, the age pension was the primary source of income for 70--80% of Australian residents over 64 years [@ABS06].
+Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the average less than $100,000 at retirement [@ASFA07].
+It has been estimated by @PT08 that a retiree will need to have $450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
 The required wealth to comply with personal-funded retirement savings requirements is too high for most Australians, suggesting that retirees will continue to rely on the age pension in the coming decades.
@@
 Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65).
-They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
+They have predicted that a third of baby boomers are expected to spend all their money and assets before they die^[Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964.].
 This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR02].
@@
 This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because pension age is regarded as a normal age for retirement in Australia.
-However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
+However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
 The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
-The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government.
-Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.
+The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014--2015 to be confirmed by Australian Federal Government.
+Figure \@ref(fig:changespension) illustrates the process of the adjustments on pension age scheme.
 This announcement received overwhelmingly negative responses in the media.
@@
 
-### Deterministic Methods Used by the ABS
+### Deterministic methods used by the ABS
 
@@
 In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
-Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for variety of population projections.
-
-### Lee-Carter Method
+Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for a variety of population projections.
+
+### Lee-Carter method
 
@@
 \begin{equation}
-  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
+  \log(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
 \end{equation}
-where $m_{x,t}$ is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age $x$ in year $t$.
+where $m_{x,t}$ is the central death rate (properly defined in Section~\@ref(sec:data)) for age $x$ in year $t$.
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
@@
 @LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
-It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
-Therefore, the estimations of $b_x$ and $k_t$ are the first principal component and scores of $\ln(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\ln(m_{x,t})-a_x$).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\ln$ transformation.
+It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least squares solution (Good, 1969).
+Therefore, the estimates of $b_x$ and $k_t$ are the first principal component and scores of $\log(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\log(m_{x,t})-a_x$).
+However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\log$ transformation.
 To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to ARIMA ($0,1,0$) model with $c\neq0$.
-
-### Hyndman-Ullah Method \label{sec:HU}
+The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to an ARIMA ($0,1,0$) model with $c\neq0$.
+
+### Hyndman-Ullah method \label{sec:HU}
 
 @HU07 proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
-\begin{enumerate}
-\item The rates are smoothed using penalized regression splines [@BHT14] before modeling.
-\item It uses functional principal components analysis, which is a continuous version of PCA.
-\item It uses more than one principal component, which address the main weakness of the LC method.
-\item The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
-\end{enumerate}
+
+  1. The rates are smoothed using penalized regression splines [@BHT14] before modeling.
+  2. It uses functional principal components analysis, which is a continuous version of PCA.
+  3. It uses more than one principal component, which address the main weakness of the LC method.
+  4. The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
 
 The model proposed by @HU07 is as follows:
-\vspace{-.3in}
 \begin{align}
@@
 In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
-\vspace{-.2in}
-\begin{equation*}
+$$
   s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
-\end{equation*}
+$$
 We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
@@
 In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
-\vspace{-.2in}
 \begin{equation}
@@
 The fitted process is given as follows:
-\vspace{-.3in}
-\begin{equation*}
+$$
   (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
-\end{equation*}
+$$
 where the parameters are estimated using maximum likelihood estimation.
@@
 The notations are as follows:
-\vspace{-.4in}
 \begin{align*}
@@
   P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
+  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}
 \end{align*}
-\vspace{-.4in}where $x$ denotes age and $x=0,1,2,\dots,m^+$.
-$m^+$ is the open-ended upper age group, which is 100 in this study.
-$t$ denotes year and $t=1,2,\dots,n$, where $n$ is the horizon of historical data used.
-Therefore, all of those data points can be recorded in an $m\times n$ matrix.
-The superscripts M and F denote male and female respectively.
+where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
+The years is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
 
 We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
-\vspace{-.3in}
 \begin{align*}
   m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
 \end{align*}
 
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted $G$) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
-The equation is expressed as: \todo{Please define $p$ and $^+$}
-\vspace{-.3in}
+In addition, the net migration^[Net migration is the difference between immigration and emigration in a certain area during a specified time frame.] (denoted $G$) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
+The equations are expressed as:
 \begin{align*}
-  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
-  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
-  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
+  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
+  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
+  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p)$ \todo{should it be $p^+$} refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)$.
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
 The deaths are estimated using the standard life table approach of population projection.
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the @HMD for 1921--2014.\todo{Han has updated the data period.} The start-year population for 2015 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the @ABS12.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the @HMD for 1921--2014.
+The start-year population for 2015 is also used to estimate net migration.
+Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2014 was obtained from the @ABS12.
 Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons.
-First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
+First, the period between 1921--1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
-
-## Forecasting Population Age Structure and OADR {#sec:forecasting}
+Second, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
+
+## Forecasting population age structure and OADR {#sec:forecasting}
 
@@
 The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
-The @HU07 model, introduced in section \ref{sec:HU}, is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
+The @HU07 model, introduced in section \@ref(sec:HU), is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
 Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
@@
 In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
-\vspace{-.4in}
 \begin{align}
@@
 Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
-\vspace{-.3in}
 \begin{align*}
-  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
+  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
 \end{align*}
@@
 From here, obtaining $h$-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
-\vspace{-.3in}
 \begin{align*}
@@
 Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
-\begin{equation*}
+$$
   \bm{p}_{n+1}=[p_{n+1,m,i}] =
@@
       \end{bmatrix}.
-\end{equation*}
+$$
 When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
@@
 When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
-\vspace{-.2in}
 \begin{equation}
@@
 After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{\text{work}}_{n+1}$ by the corresponding element of $\bm{p}^{\text{aged}}_{n+1}$, i.e.:
-\vspace{-.3in}
 \begin{align*}
@@
 Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
-\begin{equation*}
+$$
   \bm{\text{OADR}}^{\text{forecast}}=\left[\text{OADR}_{h,i}\right] =
@@
   \end{bmatrix}.
-\end{equation*}
+$$
 
@@
 It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
-Figure \ref{fig:componentsfertility} above shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
+Figure \@ref(fig:componentsfertility) above shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
 The first term ($\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950-2014.
+In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950--2014.
 It captures the general trend of fertility change over time.
-It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
+It indicates a sharp increase between 1950--1960, followed by a rapid decline of fertility rates from 1961.
+This increase of fertility is linked to the Post-World War II baby boom^[Between the years 1946 and 1964.] in Australia, resulting from the recovery from war and the Great Depression^[The Great Depression was a severe economic depression in the decade before World War II.].
 The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
@@
 
-Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2034} show the forecast results of population.
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2034.
-Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 23 million by 2064.
+oth Figures \@ref(fig:totalpopulationbyyears) and \@ref(fig:totalpopulationin2034) show the forecast results of population.
+Figure \@ref(fig:totalpopulationbyyears) shows the forecast of total population by gender over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2034.
+Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 23 million by 2064.
 Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
@@
 
-Figure \ref{fig:totalpopulationin2034} shows the mean and the 80% pointwise prediction interval of simulated population paths for year 2034, along with the 2015 base population.
+Figure \@ref(fig:totalpopulationin2034) shows the mean and the 80% pointwise prediction interval of simulated population paths for year 2034, along with the 2015 base population.
 It can be observed that overall population size is expected to increase substantially.
@@
 ```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
-The actual OADRs for 1950-2014 are shown in black.", dependson='OADRat65'}
+The actual OADRs for 1950--2014 are shown in black.", dependson='OADRat65'}
 df <- bind_rows(
@@
 Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \ref{fig:OADRat65} shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921-2014.
+Figure \@ref(fig:OADRat65) shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921--2014.
 A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
@@
 
-Figure \ref{fig:OADRcurrent} presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21%.
+Figure \@ref(fig:OADRcurrent) presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21%.
 It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment.
@@
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Therefore, Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
+Therefore, Figure \@ref(fig:OADRcurrent) demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
 However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
@@
 
-## Evaluating Forecast Accuracy {#sec:accuracy}
+## Evaluating forecast accuracy {#sec:accuracy}
 
@@
 
-The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the $H$ prediction horizon.
+The logic of a cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
 Then we are allowed to repeat the test $n-H-k+1$ times, where $n$ is the number of total years of observation.
@@
 
-Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
 Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
@@
 Then, we can summary the information into a matrix as follows:
-\begin{equation*}
+$$
   \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
@@
     \end{bmatrix}
-\end{equation*}
+$$
 where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
@@
 
-In our sample, $n=2014-1950+1=65$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \ref{fig:rollingtest}.
+n our sample, $n=2014-1950+1=65$ and we set $k=25$ and $H=25$ to perform the test.
+The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
 From this figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
@@
 
-# Finding the Target Pension Age Scheme {#sec:target}
+# Finding the target pension age scheme {#sec:target}
 
@@
 for $h=1,2,\dots,H$
-\begin{equation*}
+$$
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation*}
+$$
 \begin{align*}
@@
 This simplification is reasonable because the pension age will be same in mid-2017 onward}, which is:
-\vspace{-.3in}
 \begin{align*}
@@
 For $h=1,2,\dots,H$, we keep increasing pension age vector $[\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]$ by a month at a time, unless we find that
-\vspace{-.2in}
 \begin{align*}
@@
 
-## Plausible Pension Age Schemes
+## Plausible pension age schemes
 
@@
 It is assumed that it is impractical to change the pension age during 2011--2014, so the pension age has to be set at 65 for those years.
-Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
+Figure \@ref(fig:OADRwithoptimal) provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
+Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
 
@@
 
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \ref{fig:OADRboundaries}.
+The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \@ref(fig:OADRboundaries).
 It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
@@
 
-Figure \ref{fig:comparisonofpensionages} compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
+Figure \@ref(fig:comparisonofpensionages) compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
 It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
@@
 Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with real pension age scheme in Figure \ref{fig:ComparisonwithOADR22}.
+We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with real pension age scheme in Figure \@ref(fig:ComparisonwithOADR22).
 When we allow 1% more in desired OADR, the real pension age becomes plausible.
-Figure \ref{fig:OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+Figure \@ref(fig:OADR_realpensionage) shows simulated OADR associated with proposed pension age scheme^[Since we don't know the change rate set by government for 2023--2035, we assume it follows increase rate for 2017--2023, which increase half year pension age in every two years.].
 It confirms that OADR is stable around a level higher than current level of OADR before 2035.

### 2020-05-04 hmd.R

@@ -2,80 +2,6 @@
 username <- "hanlin.shang@gmail.com"
 password <- "hshang85"
 
-hmd.pop <- function (country, username, password, label = country)
-{
-  path <- paste("https://www.mortality.org/hmd/", country, "/STATS/",
-                "Population.txt", sep = "")
-  userpwd <- paste(username, ":", password, sep = "")
-  txt <- RCurl::getURL(path, userpwd = userpwd)
-  con <- textConnection(txt)
-  pop <- try(utils::read.table(con, skip = 2, header = TRUE,
-                               na.strings = "."), TRUE)
-  close(con)
-  if (class(pop) == "try-error")
-    stop("Population file not found at www.mortality.org")
-  obj <- list(type = "population", label = label, lambda = 0)
-  obj$year = sort(unique(pop[, 1]))
-  n <- length(obj$year)
-  m <- length(unique(pop[, 2]))
-  obj$age <- pop[1:m, 2]
-  mnames <- names(pop)[-c(1, 2)]
-  n.pop <- length(mnames)
-  obj$pop <- list()
-  for (i in 1:n.pop) {
-    obj$pop[[i]] <- matrix(pop[, i + 2], nrow = m, ncol = n)
-    obj$pop[[i]][obj$pop[[i]] < 0] <- NA
-    dimnames(obj$pop[[i]]) <- list(obj$age, obj$year)
-  }
-  names(obj$pop) <- tolower(mnames)
-  obj$age <- as.numeric(as.character(obj$age))
-  if (is.na(obj$age[m]))
-    obj$age[m] <- 2 * obj$age[m - 1] - obj$age[m - 2]
-  return(structure(obj, class = "demogdata"))
-}
-
-hmd.mx <- function (country, username, password, label = country)
-{
-  path <- paste("https://www.mortality.org/hmd/", country, "/STATS/",
-                "Mx_1x1.txt", sep = "")
-  userpwd <- paste(username, ":", password, sep = "")
-  txt <- RCurl::getURL(path, userpwd = userpwd)
-  con <- textConnection(txt)
-  mx <- try(utils::read.table(con, skip = 2, header = TRUE,
-                              na.strings = "."), TRUE)
-  close(con)
-  if (class(mx) == "try-error")
-    stop("Connection error at www.mortality.org. Please check username, password and country label.")
[…]

### 2020-05-04 PensionAge.Rmd
Removed hmd.R from repo

@@
 source("functions-v4.R")
-source("hmd.R")
 ```
@@
 # Get population data to 1 Jan 2019
-aus.pop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
+source("hmd.R") # File only stores username and password
+aus.pop <- hmd.pop(country = "AUS", username = username, password = password, 
+                   label = "Australia")
 aus.pop <- extract.ages(aus.pop, ages = 0:100)
@@
 # Compute migration data
-aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = aus.pop, mfratio = 1.05)
+aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, 
+                        startyearpop = aus.pop, mfratio = 1.05)
 save(aus.fert, aus.mort, aus.mig, aus.pop, file="ausdata.Rdata")

### 2020-05-04 hmd.R

@@ -1,7 +1,0 @@
-# HMD credentials
-username <- "hanlin.shang@gmail.com"
-password <- "hshang85"
-
-# Get population data for 1 Jan 2015
-auspop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
-auspop <- extract.ages(auspop, age = 0:100)

### 2020-05-04 PensionAge.Rmd
Code styling

--- 2020-05-04 PensionAge.Rmd
@@
 library(demography)
-#remotes::install_github("robjhyndman/addb")
+# remotes::install_github("robjhyndman/addb")
 library(addb)
@@
   mutate(
-    Proposed = pmin(70, Current + 0.5*pmax(0, trunc((Year - 2015)/2))),
+    Proposed = pmin(70, Current + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
     Approved = pmin(Proposed, 67),
   ) %>%
-  pivot_longer(-Year, values_to="Age", names_to="Policy")
+  pivot_longer(-Year, values_to = "Age", names_to = "Policy")
 
@@
   filter(Year >= 2008, Year <= 2050) %>%
-  ggplot(aes(x=Year, y=Age, group=Policy, col=Policy)) +
+  ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
   geom_line() +
   ylab("Age of retirement") +
-    scale_color_brewer(palette="Dark2",
+  scale_color_brewer(
+    palette = "Dark2",
     breaks = c("Proposed", "Approved", "Current"),
@@
 # Get population data to 1 Jan 2019
-aus.pop <- hmd.pop(country = "AUS", username = username, password = password, label = "Australia")
+source("hmd.R") # File only stores username and password
+aus.pop <- hmd.pop(
+  country = "AUS", username = username, password = password,
+  label = "Australia"
+)
 aus.pop <- extract.ages(aus.pop, ages = 0:100)
@@
   select(-Measure) %>%
-  pivot_wider(names_from=Year, values_from=Value) %>%
+  pivot_wider(names_from = Year, values_from = Value) %>%
   select(-Age) %>%
@@
 # Compute migration data
-aus.mig <- netmigration(mort = aus.mort, fert = aus.fert, startyearpop = aus.pop, mfratio = 1.05)
-save(aus.fert, aus.mort, aus.mig, aus.pop, file="ausdata.Rdata")
-rm(ausf,births,fpop,newbirths,newpop)
+aus.mig <- netmigration(
+  mort = aus.mort, fert = aus.fert,
+  startyearpop = aus.pop, mfratio = 1.05
+)
+save(aus.fert, aus.mort, aus.mig, aus.pop, file = "ausdata.Rdata")
+rm(ausf, births, fpop, newbirths, newpop)
 ```
@@
 # This takes a while!
-set.seed(2020-05-02)
+set.seed(2020 - 05 - 02)
 nsim <- 20 # Change to 2000 or higher to get better estimates
@@
 aussim_df <- bind_rows(
-  as.tbl_cube(aus.sim[["male"]]/1e3, met_name = "Population") %>%
+  as.tbl_cube(aus.sim[["male"]] / 1e3, met_name = "Population") %>%
     as_tibble() %>% mutate(Sex = "Male"),
-  as.tbl_cube(aus.sim[["female"]]/1e3, met_name = "Population") %>%
+  as.tbl_cube(aus.sim[["female"]] / 1e3, met_name = "Population") %>%
     as_tibble() %>% mutate(Sex = "Female")
 )
-#rm(aus.sim)
+# rm(aus.sim)
 # Combine simulations to create means and quantiles of future years
@@
     Mean = mean(Population),
-    Lower = quantile(Population, prob=0.1),
-    Upper = quantile(Population, prob=0.9)
+    Lower = quantile(Population, prob = 0.1),
+    Upper = quantile(Population, prob = 0.9)
   ) %>%
@@
   group_by(Rep, Sex, Year) %>%
-  summarise(Population = sum(Population)/1e3) %>%
+  summarise(Population = sum(Population) / 1e3) %>%
   group_by(Sex, Year) %>%
@@
     Median = median(Population),
-    Lo95 = quantile(Population, prob=0.025),
-    Up95 = quantile(Population, prob=0.975),
-    Lo80 = quantile(Population, prob=0.1),
-    Up80 = quantile(Population, prob=0.9)
+    Lo95 = quantile(Population, prob = 0.025),
+    Up95 = quantile(Population, prob = 0.975),
+    Lo80 = quantile(Population, prob = 0.1),
+    Up80 = quantile(Population, prob = 0.9)
   ) %>%
@@
   group_by(Sex, Year) %>%
-  summarise(Population = sum(Population)/1e3) %>%
-  ggplot(aes(x=Year, y=Population, group=Sex)) +
-    geom_line(size=1) +
+  summarise(Population = sum(Population) / 1e3) %>%
+  ggplot(aes(x = Year, y = Population, group = Sex)) +
+  geom_line(size = 1) +
   ylab("Population (millions)") +
@@
   facet_grid(. ~ Sex) +
-    geom_ribbon(aes(y=Mean, ymin=Lo80, ymax=Up80), fill='#7d7def', data=future_tot_pop) +
-    geom_line(data=future_tot_pop, col='#0000cc', mapping=aes(y=Mean), size=1)
+  geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
+  geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1)
 ```
@@
     filter(Sex == "Male") %>%
-    ggplot(aes(x = Age, y = Population, group=Year)) +
+    ggplot(aes(x = Age, y = Population, group = Year)) +
     labs(y = "Population ('000)") +
-      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
-      geom_line(linetype=2) + geom_line(aes(y=Mean), col='#0000cc') +
+    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
+    geom_line(linetype = 2) +
+    geom_line(aes(y = Mean), col = "#0000cc") +
     coord_flip() +
-      scale_y_reverse(expand=c(0.012, 0.012)) +
-      scale_x_continuous(expand=c(0.012,0.012)) +
+    scale_y_reverse(expand = c(0.012, 0.012)) +
+    scale_x_continuous(expand = c(0.012, 0.012)) +
     facet_grid(. ~ Sex)
@@
     filter(Sex == "Female") %>%
-    ggplot(aes(x = Age, y = Population, group=Year)) +
+    ggplot(aes(x = Age, y = Population, group = Year)) +
     labs(y = "Population ('000)") +
-      geom_ribbon(aes(x=Age, ymin=Lower, ymax=Upper, y=Mean), fill='#7d7def') +
-      geom_line(linetype=2) + geom_line(aes(y=Mean), col='#0000cc') +
+    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
+    geom_line(linetype = 2) +
+    geom_line(aes(y = Mean), col = "#0000cc") +
     coord_flip() +
-      scale_y_continuous(expand=c(0.012,0.012)) +
-      theme(axis.title.y.left=element_blank(),
-        axis.text.y.left=element_blank(),
-        axis.ticks.y.left=element_blank()) +
-      scale_x_continuous(position="top", sec.axis = sec_axis(~ .), expand=c(0.012,0.012)) +
+    scale_y_continuous(expand = c(0.012, 0.012)) +
+    theme(
+      axis.title.y.left = element_blank(),
+      axis.text.y.left = element_blank(),
+      axis.ticks.y.left = element_blank()
+    ) +
+    scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
     facet_grid(. ~ Sex)
@@
 ```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
-OADR_history <- oadr(history_pop, filter(pension_age, Policy=='Current'))
-OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy=='Current')) %>%
-  mutate(Policy="Pension age 65")
+OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
+OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy == "Current")) %>%
+  mutate(Policy = "Pension age 65")
 OADR.65 %>%
-  ggplot(aes(x=Year, y=OADR)) +
-    geom_ribbon(aes(ymin=Lo, ymax=Hi), fill='#7d7def') +
-    geom_line(col='#0000aa', size=.75) +
-    geom_line(col='black', size=.75, data=OADR_history) +
-    xlab("year") + ylab("ratio") +
+  ggplot(aes(x = Year, y = OADR)) +
+  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
+  geom_line(col = "#0000aa", size = .75) +
+  geom_line(col = "black", size = .75, data = OADR_history) +
+  xlab("year") +
+  ylab("ratio") +
   ggtitle("OADR forecasts with pension age=65")
@@
   OADR.65,
-  oadr_sim(aussim_df, filter(pension_age, Policy=='Approved')) %>%
-    mutate(Policy="Current policy"),
-  oadr_sim(aussim_df, filter(pension_age, Policy=='Proposed')) %>%
-    mutate(Policy="Proposed policy")
+  oadr_sim(aussim_df, filter(pension_age, Policy == "Approved")) %>%
+    mutate(Policy = "Current policy"),
+  oadr_sim(aussim_df, filter(pension_age, Policy == "Proposed")) %>%
+    mutate(Policy = "Proposed policy")
 ) %>%
   mutate(Policy = factor(Policy,
-    levels = c("Pension age 65","Current policy","Proposed policy")))
+    levels = c("Pension age 65", "Current policy", "Proposed policy")
+  ))
 df %>%
-  ggplot(aes(x=Year, y=OADR)) +
+  ggplot(aes(x = Year, y = OADR)) +
   geom_hline(yintercept = 0.21, col = "gray") +
-    geom_ribbon(aes(ymin=Lo, ymax=Hi, fill=Policy, group=Policy), alpha=0.5) +
-    geom_line(aes(col=Policy, group=Policy), size=.75) +
-    geom_line(col='black', size=.75, data=OADR_history) +
-    xlab("year") + ylab("ratio") +
+  geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy), alpha = 0.5) +
+  geom_line(aes(col = Policy, group = Policy), size = .75) +
+  geom_line(col = "black", size = .75, data = OADR_history) +
+  xlab("year") +
+  ylab("ratio") +
   ggtitle("OADR forecasts with pension age=65") +
-    scale_color_brewer(palette="Dark2") +
-    scale_fill_brewer(palette="Dark2")
+  scale_color_brewer(palette = "Dark2") +
+  scale_fill_brewer(palette = "Dark2")
 ```
@@
   migfs <- forecast(mig.fit.s, H)
-    aus.sim.s <- pop.sim(mort = mortfs, fert = fertfs, mig = migfs,
-                         firstyearpop = pop.short, N = 3)
+  aus.sim.s <- pop.sim(
+    mort = mortfs, fert = fertfs, mig = migfs,
+    firstyearpop = pop.short, N = 3
+  )
   # Combine simulation results into one tibble
@@
     rolling_sim,
-      as.tbl_cube(aus.sim.s[["male"]]/1e3, met_name = "Population") %>%
-        as_tibble() %>% mutate(Sex = "Male", id=i),
-      as.tbl_cube(aus.sim.s[["female"]]/1e3, met_name = "Population") %>%
-        as_tibble() %>% mutate(Sex = "Female", id=i)
+    as.tbl_cube(aus.sim.s[["male"]] / 1e3, met_name = "Population") %>%
+      as_tibble() %>% mutate(Sex = "Male", id = i),
+    as.tbl_cube(aus.sim.s[["female"]] / 1e3, met_name = "Population") %>%
+      as_tibble() %>% mutate(Sex = "Female", id = i)
   )
@@
 ```{r rmseplot, dependson="rollingtest"}
-oadr_rolling_sim(rolling_sim,
-    filter(pension_age, Policy=='Approved')) %>%
+oadr_rolling_sim(
+  rolling_sim,
+  filter(pension_age, Policy == "Approved")
+) %>%
   group_by(id) %>%
@@
   rename(Forecast = OADR) %>%
-  left_join(OADR_history, by="Year") %>%
-  mutate(e = OADR-Forecast) %>%
+  left_join(OADR_history, by = "Year") %>%
+  mutate(e = OADR - Forecast) %>%
   group_by(h) %>%
   summarise(RMSE = sqrt(mean(e^2))) %>%
-  ggplot(aes(x=h, y=RMSE)) +
+  ggplot(aes(x = h, y = RMSE)) +
   geom_point()
@@
 pension_age_lower <- pension_age %>%
-  filter(Policy == "Current", Year >= 2019) %>% select(-Policy)
-for (i in seq(5,50)) {
+  filter(Policy == "Current", Year >= 2019) %>%
+  select(-Policy)
+for (i in seq(5, 50)) {
   current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
   while ((current > target) &
-         (max(diff(pension_age_lower$Age[(i-1):50])) <= (1 - 1/12))) {
-    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1/12
+    (max(diff(pension_age_lower$Age[(i - 1):50])) <= (1 - 1 / 12))) {
+    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1 / 12
     current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
@@
 pension_age_optimal <- pension_age_lower
-for (i in seq(5,50)) {
+for (i in seq(5, 50)) {
   current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
   while ((current > target) &
-         (max(diff(pension_age_optimal$Age[(i-1):50])) <= (1 - 1/12))) {
-    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1/12
+    (max(diff(pension_age_optimal$Age[(i - 1):50])) <= (1 - 1 / 12))) {
+    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1 / 12
     current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
@@
 pension_age_upper <- pension_age_optimal
-for (i in seq(5,50)) {
+for (i in seq(5, 50)) {
   current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
   while ((current > target) &
-         (max(diff(pension_age_upper$Age[(i-1):50])) <= (1 - 1/12))) {
-    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1/12
+    (max(diff(pension_age_upper$Age[(i - 1):50])) <= (1 - 1 / 12))) {
+    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1 / 12
     current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
@@
     Month = round((Age - trunc(Age)) * 12),
-    Agestring = paste0(trunc(Age),"Y",
-      if_else(Month > 0, paste0("+", Month, "M"), "")),
+    Agestring = paste0(
+      trunc(Age), "Y",
+      if_else(Month > 0, paste0("+", Month, "M"), "")
+    ),
     Column = trunc((Year - 2019) / 10) + 1,
@@
   select(Year, Agestring, Column) %>%
-  nest(data=c(Year=Year, Age=Agestring)) %>%
-  pivot_wider(names_from=Column, values_from=data) %>%
-  unnest(cols=paste(1:5), names_repair='unique') %>%
+  nest(data = c(Year = Year, Age = Agestring)) %>%
+  pivot_wider(names_from = Column, values_from = data) %>%
+  unnest(cols = paste(1:5), names_repair = "unique") %>%
   knitr::kable(
-    format="latex",
-    col.names = rep(c("Year","Age"),5),
+    format = "latex",
+    col.names = rep(c("Year", "Age"), 5),
     booktabs = TRUE,
@@
     MonthHi = round((Hi80 - trunc(Hi80)) * 12),
-    AgeLo = paste0(trunc(Lo80),"Y",
-      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")),
-    AgeHi = paste0(trunc(Hi80),"Y",
-      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")),
+    AgeLo = paste0(
+      trunc(Lo80), "Y",
+      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
+    ),
+    AgeHi = paste0(
+      trunc(Hi80), "Y",
+      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
+    ),
     Column = trunc((Year - 2019) / 10) + 1,
@@
   select(Year, AgeLo, AgeHi, Column) %>%
-  nest(data=c(Year=Year, Lo=AgeLo, Hi = AgeHi)) %>%
-  pivot_wider(names_from=Column, values_from=data) %>%
-  unnest(cols=paste(1:5), names_repair='unique') %>%
+  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
+  pivot_wider(names_from = Column, values_from = data) %>%
+  unnest(cols = paste(1:5), names_repair = "unique") %>%
   knitr::kable(
-    format="latex",
-    col.names = rep(c("Year","Lo","Hi"),5),
+    format = "latex",
+    col.names = rep(c("Year", "Lo", "Hi"), 5),
     booktabs = TRUE,
@@
 OADR_optimal %>%
-  ggplot(aes(x=Year)) +
-  geom_ribbon(aes(ymin=Lo, ymax=Hi), fill="#7d7def") +
-
+  ggplot(aes(x = Year)) +
+  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
   autoplot(OADR.f.optimal$x) +
@@
   ggtitle("OADR forecast estimates for optimal pension ages") +
-  xlab("year") + ylab("ratio")
+  xlab("year") +
+  ylab("ratio")
 ```
@@
   autolayer(ts(c(rep(65, 50)), start = 1990), series = "Pension age at 65") +
-  xlab("Year") + ylab("Age of retirement")
+  xlab("Year") +
+  ylab("Age of retirement")
 ```
@@
 ```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}
+
 ```

### 2020-05-05 PensionAge.Rmd
Now compiling

@@
 OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
+OADR_lower <- oadr_sim(aussim_df, pension_age_lower)
+OADR_upper <- oadr_sim(aussim_df, pension_age_upper)
 pension_age_optimal <- pension_age_optimal %>%
@@
 
-```{r pensionagetables2, dependson="OADRat65"}
+```{r pensionagetables2, dependson="OADRat65", message=FALSE}
 pension_age_optimal %>%
@@
     caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
-  )
-kable_styling(kable_output, font_size = 7)
+  ) %>%
+  kable_styling(font_size = 7)
 ```
@@
   ggplot(aes(x = Year)) +
+  geom_hline(yintercept = target, col = "red") +
   geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  autoplot(OADR.f.optimal$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  autolayer(OADR.f.optimal) +
+  geom_line(aes(y=OADR), col="#0000cc") +
+  geom_line(data=OADR_history, aes(y=OADR)) +
   ggtitle("OADR forecast estimates for optimal pension ages") +
-  xlab("year") +
-  ylab("ratio")
+  ylab("Old age dependency ratio") 
 ```
@@
 ```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
-p1 <- autoplot(OADR.f.upper$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  autolayer(OADR.f.upper) +
-  ggtitle("OADR for upper boundary pension ages") +
-  xlab("Year") + ylab("ratio") +
-  ylim(0.07, 0.27)
-p2 <- autoplot(OADR.f.lower$x) +
-  geom_hline(yintercept = OADR.f$mean[4], col = "red") +
-  autolayer(OADR.f.lower) +
-  ggtitle("OADR for lower boundary pension ages") +
-  xlab("Year") + ylab("ratio") +
-  ylim(0.07, 0.27)
-gridExtra::grid.arrange(p1, p2, ncol = 2)
+bind_rows(
+    OADR_upper %>% mutate(Series="Upper boundary"),
+    OADR_lower %>% mutate(Series="Lower boundary"),
+  ) %>%
+  ggplot(aes(x = Year)) +
+  geom_hline(yintercept = target, col = "red") +
+  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
+  geom_line(aes(y=OADR), col="#0000cc") +
+  geom_line(data=OADR_history, aes(y=OADR)) +
+  facet_grid(. ~ Series) +
+  ggtitle("OADR forecasts for boundary pension age schemes") +
+  ylab("Old age dependency ratio") 
 ```
@@
 The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
+pension.fc <- structure(
+  list(mean=ts(pension_age_optimal$Age, start=min(pension_age_optimal$Year)),
+       lower=ts(pension_age_optimal$Lo80, start=min(pension_age_optimal$Year)),
+       upper=ts(pension_age_optimal$Hi80, start=min(pension_age_optimal$Year)),
+       level=80),
+  class="forecast")
 ggplot() +
   autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
-  #  geom_hline(yintercept=65, color='black') +
-  autolayer(ts(c(rep(65, 7), c(65.5, 65.5, 66.5, 66.5, 67, 67), rep(67, 37))[1:50],
-    start = 2015
-  ), series = "Approved change") +
-  autolayer(ts(c(rep(65, 50)), start = 1990), series = "Pension age at 65") +
-  xlab("Year") +
-  ylab("Age of retirement")
+  autolayer(
+    ts(pension_age %>% filter(Policy=="Approved", Year >= 1995) %>% pull(Age), 
+       start=1995), series = "Approved change"
+  ) +
+  autolayer(
+    ts(pension_age %>% filter(Policy=="Current", Year >= 1995) %>% pull(Age), 
+       start=1995), series = "Pension age at 65"
+  )  +
+  xlab("Year") + ylab("Age of retirement")
 ```

### 2020-05-05 PensionAge.tex
Now compiling

@@
 \def\cover{{\sffamily\setcounter{page}{0}
-        \thispagestyle{empty}%
-        \vspace*{-2cm}
-        \centerline{\raisebox{-1.8cm}{\includegraphics[width=5cm]{MBSportrait}}\hspace*{9cm} ISSN 1440-771X}\vspace{0.99cm}
+        \thispagestyle{empty}
+        \placefig{2}{1.5}{width=5cm}{monash2}
+        \placefig{16.9}{1.5}{width=2.1cm}{MBusSchool}
+        \begin{textblock}{4}(16.9,4)ISSN 1440-771X\end{textblock}
+        \begin{textblock}{7}(12.7,27.9)\hfill
+        \includegraphics[height=0.7cm]{AACSB}~~~
+        \includegraphics[height=0.7cm]{EQUIS}~~~
+        \includegraphics[height=0.7cm]{AMBA}
+        \end{textblock}
+        \vspace*{2cm}
         \begin{center}\Large
         Department of Econometrics and Business Statistics\\[.5cm]
-        \scriptsize http://business.monash.edu/econometrics-and-business-statistics/research/publications
+        \footnotesize http://monash.edu/business/ebs/research/publications
         \end{center}\vspace{2cm}
@@
                 Working Paper \@wp
-        \end{center}}}
+        \end{center}\vspace*{2cm}}}
 \def\pageone{{\sffamily\setstretch{1}%
@@
 
+\RequirePackage[absolute,overlay]{textpos}
+\setlength{\TPHorizModule}{1cm}
+\setlength{\TPVertModule}{1cm}
+\def\placefig#1#2#3#4{\begin{textblock}{.1}(#1,#2)\rlap{\includegraphics[#3]{#4}}\end{textblock}}
+
 \author{Rob J~Hyndman, Yijun~Zeng, Han Lin~Shang}
@@
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the current level, which is 21\%.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2014 level, which is 21\%.
 This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
@@
 
-This is consistent with the Australian Intergenerational Reports \autocites{IGR02}{IGR07}{Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
+This is consistent with the Australian Intergenerational Reports \autocite{IGR02,IGR07,Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
 To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
@@
 
-In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs \autocites{ARW07}{IGR02}{IGR07}.
+In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs \autocite{ARW07,IGR02,IGR07}.
 The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age \autocite{ARW07}.
@@
 \hypertarget{sec:litreview}{%
-\section{Background and Literature Review}\label{sec:litreview}}
+\section{Background}\label{sec:litreview}}
 
@@
 Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing.
-For example, it provides single home-owners with a real income of \$13653 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
+For example, it provides single home-owners with a real income of \$23,889 p.a and additional allowances to cover expenses such as rent or pharmaceuticals\footnote{The pension amount is adjusted every 6 months for inflation}.
 The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases.
@@
 
-Currently, the age pension is the primary source of income for 70\% -80\% of Australian residents over 64 years \autocite{ABS06}.
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the current average less than \$100,000 at retirement \autocite{ASFA07}.
+In 2006, the age pension was the primary source of income for 70--80\% of Australian residents over 64 years \autocite{ABS06}.
+Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the average less than \$100,000 at retirement \autocite{ASFA07}.
 It has been estimated by \textcite{PT08} that a retiree will need to have \$450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
@@
 Given children born today are expected to live up to their 90s on average, the \textcite{PC13} suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65).
-They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964}.
+They have predicted that a third of baby boomers are expected to spend all their money and assets before they die\footnote{Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964.}.
 This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects \autocite{IGR02}.
@@
 The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
-The current Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014-2015 to be confirmed by Australian Federal Government.
+The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014--2015 to be confirmed by Australian Federal Government.
 Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.
@@
 \hypertarget{deterministic-methods-used-by-the-abs}{%
-\subsubsection{Deterministic Methods Used by the ABS}\label{deterministic-methods-used-by-the-abs}}
+\subsubsection{Deterministic methods used by the ABS}\label{deterministic-methods-used-by-the-abs}}
 
@@
 In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
-Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for variety of population projections.
+Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for a variety of population projections.
 
 \hypertarget{lee-carter-method}{%
-\subsubsection{Lee-Carter Method}\label{lee-carter-method}}
+\subsubsection{Lee-Carter method}\label{lee-carter-method}}
 
@@
 \begin{equation}
-  \ln(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
+  \log(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
 \end{equation}
-where \(m_{x,t}\) is the central death rate\footnote{The central death rate is properly defined in Section~\ref{sec:data}} for age \(x\) in year \(t\).
+where \(m_{x,t}\) is the central death rate (properly defined in Section\textasciitilde\ref{sec:data}) for age \(x\) in year \(t\).
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(a_x\)\} and \{\(b_x\)\}, and a time-varying index \(k_t\).
@@
 \textcite{LC92} choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
-It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least square solution (Good, 1969).
-Therefore, the estimations of \(b_x\) and \(k_t\) are the first principal component and scores of \(\ln(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when \(\bm{X}=\ln(m_{x,t})-a_x\)).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the \(\ln\) transformation.
+It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least squares solution (Good, 1969).
+Therefore, the estimates of \(b_x\) and \(k_t\) are the first principal component and scores of \(\log(m_{x,t})-a_x\) (i.e., \(b_x=\bm{z_1}\) and \(k_t=\bm{u_1}'\) when \(\bm{X}=\log(m_{x,t})-a_x\)).
+However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the \(\log\) transformation.
 To overcome this problem, the LC method adjusts \(k_t\) such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted \(k_t\) is then extrapolated using random walk with drift models, which is equivalent to ARIMA (\(0,1,0\)) model with \(c\neq0\).
+The adjusted \(k_t\) is then extrapolated using random walk with drift models, which is equivalent to an ARIMA (\(0,1,0\)) model with \(c\neq0\).
 
 \hypertarget{hyndman-ullah-method}{%
-\subsubsection{\texorpdfstring{Hyndman-Ullah Method \label{sec:HU}}{Hyndman-Ullah Method }}\label{hyndman-ullah-method}}
+\subsubsection{\texorpdfstring{Hyndman-Ullah method \label{sec:HU}}{Hyndman-Ullah method }}\label{hyndman-ullah-method}}
 
@@
 \begin{enumerate}
-\item The rates are smoothed using penalized regression splines [@BHT14] before modeling.
-\item It uses functional principal components analysis, which is a continuous version of PCA.
-\item It uses more than one principal component, which address the main weakness of the LC method.
-\item The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  The rates are smoothed using penalized regression splines \autocite{BHT14} before modeling.
+\item
+  It uses functional principal components analysis, which is a continuous version of PCA.
+\item
+  It uses more than one principal component, which address the main weakness of the LC method.
+\item
+  The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
 \end{enumerate}
@@
 The model proposed by \textcite{HU07} is as follows:
-\vspace{-.3in}
 \begin{align}
@@
 In other words, we take singular value decomposition of \(s_t(x)-\mu(x)\), then \eqref{eq:HU_2} now becomes
-\vspace{-.2in}
-\begin{equation*}
+\[
   s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
-\end{equation*}
+\]
 We chose \(J\) in a way that we believe the majority of information for \(s_t(x)-\mu(x)\) has been captured by the first \(J\) components.
@@
 In terms of forecasting, by conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of log rate \(y_{n+h}(x)\) can be acquired by:
-\vspace{-.2in}
 \begin{equation}
@@
 The fitted process is given as follows:
-\vspace{-.3in}
-\begin{equation*}
+\[
   (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
-\end{equation*}
+\]
 where the parameters are estimated using maximum likelihood estimation.
@@
   P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}\\
+  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}
 \end{align*}
-\vspace{-.4in}where \(x\) denotes age and \(x=0,1,2,\dots,m^+\).
-\(m^+\) is the open-ended upper age group, which is 100 in this study.
-\(t\) denotes year and \(t=1,2,\dots,n\), where \(n\) is the horizon of historical data used.
-Therefore, all of those data points can be recorded in an \(m\times n\) matrix.
-The superscripts M and F denote male and female respectively.
+where \(x=0,1,2,\dots,p-1,p^+\) denotes age with \(p^+\) the open-ended upper age group, set to 100\(^+\) in this study.
+The years is denoted by \(t=1,2,\dots,n\), and superscripts \(M\) and \(F\) denote male and female respectively.
 
 We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
-\vspace{-.3in}
 \begin{align*}
   m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
 \end{align*}
 
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame} (denoted \(G\)) is estimated using a demographic growth-balance equation, which is an equation to summarize the relationship between population change and three factors: net migration, births and deaths.
-The equation is expressed as: \todo{Please define $p$ and $^+$}
-\vspace{-.3in}
+In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted \(G\)) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
+The equations are expressed as:
 \begin{align*}
-  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\text{~for~} x=0,1,2,\dots,p-2,\\
-  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+)\\
-  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0)
+  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
+  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
+  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
 \end{align*}
-where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p)\) \todo{should it be $p^+$} refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1), D_t(p-1^+,p^+), D_t(B,0)\).
+where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
 The deaths are estimated using the standard life table approach of population projection.
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0-99 and 100+ have been sourced from the \textcite{HMD} for 1921--2014.\todo{Han has updated the data period.} The start-year population for 2015 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15-49 over the period 1950-2014 was obtained from the \textcite{ABS12}.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the \textcite{HMD} for 1921--2014.
+The start-year population for 2015 is also used to estimate net migration.
+Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2014 was obtained from the \textcite{ABS12}.
 Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons.
-First, the period between 1921-1950 has very different mortality patterns from later years because of wars and epidemics \autocite{HB08}.
+First, the period between 1921--1950 has very different mortality patterns from later years because of wars and epidemics \autocite{HB08}.
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Secondly, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
+Second, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
 
 \hypertarget{sec:forecasting}{%
-\subsection{Forecasting Population Age Structure and OADR}\label{sec:forecasting}}
+\subsection{Forecasting population age structure and OADR}\label{sec:forecasting}}
 
@@
 In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by \(p_t(x)\)) and ratio series (denoted by \(r_t(x)\)), which are defined as follows:
-\vspace{-.4in}
 \begin{align}
@@
 Then, \textcite{HU07} was applied to these two new variables instead of male and female mortality rate as follows:
-\vspace{-.3in}
 \begin{align*}
-  \ln[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \ln[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
+  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
 \end{align*}
@@
 From here, obtaining \(h\)-step-ahead forecast of sex-specific coherent mortality rates (denoted \(m_{n+h\mid n,M}(x)\) and \(m_{n+h\mid n,F}(x)\)) was performed using a back-transformation:
-\vspace{-.3in}
 \begin{align*}
@@
 Recall that for \(h=1\), we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
-\begin{equation*}
+\[
   \bm{p}_{n+1}=[p_{n+1,m,i}] =
@@
       \end{bmatrix}.
-\end{equation*}
+\]
 When \(r=0\), then the simulation of a population aged 15 to pension age is a subset of the above matrix from \(15^{th}\) row to \(a-1^{th}\) row, which is:
@@
 When \(r\neq0\), the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
-\vspace{-.2in}
 \begin{equation}
@@
 After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of \(\bm{p}^{\text{work}}_{n+1}\) by the corresponding element of \(\bm{p}^{\text{aged}}_{n+1}\), i.e.:
-\vspace{-.3in}
 \begin{align*}
@@
 Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
-\begin{equation*}
+\[
   \bm{\text{OADR}}^{\text{forecast}}=\left[\text{OADR}_{h,i}\right] =
@@
   \end{bmatrix}.
-\end{equation*}
+\]
 
@@
 The first term (\(\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}\)) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of the first coefficient, estimated historical first principal component scores \(\widehat{\beta}_{t,1}\) are shown in black for 1950-2014.
+In the plot of the first coefficient, estimated historical first principal component scores \(\widehat{\beta}_{t,1}\) are shown in black for 1950--2014.
 It captures the general trend of fertility change over time.
-It indicates a sharp increase between 1950-1960, followed by a rapid decline of fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II}.
+It indicates a sharp increase between 1950--1960, followed by a rapid decline of fertility rates from 1961.
+This increase of fertility is linked to the Post-World War II baby boom\footnote{Between the years 1946 and 1964.} in Australia, resulting from the recovery from war and the Great Depression\footnote{The Great Depression was a severe economic depression in the decade before World War II.}.
 The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
 A noticeable further reduction of fertility rates in late 1960s may be due to a change in the law allowing abortion in some states in Australia.
+
+\begin{verbatim}
+## Loading required package: latex2exp
+\end{verbatim}
 
@@
 
-Both Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2034} show the forecast results of population.
+oth Figures \ref{fig:totalpopulationbyyears} and \ref{fig:totalpopulationin2034} show the forecast results of population.
 Figure \ref{fig:totalpopulationbyyears} shows the forecast of total population by gender over the prediction horizon, while Figure \ref{fig:totalpopulationin2028} shows the forecast of population age structure in a specific year, 2034.
@@
 \caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
-The actual OADRs for 1950-2014 are shown in black.}
+The actual OADRs for 1950--2014 are shown in black.}
 \end{figure}
@@
 Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \ref{fig:OADRat65} shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921-2014.
+Figure \ref{fig:OADRat65} shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921--2014.
 A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
@@
 \hypertarget{sec:accuracy}{%
-\subsection{Evaluating Forecast Accuracy}\label{sec:accuracy}}
+\subsection{Evaluating forecast accuracy}\label{sec:accuracy}}
 
@@
 
-The logic of a Cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need \(k\) years' observations to produce a reliable forecast\footnote{$k$ can't be too small}, we are interested in the \(H\) prediction horizon.
+The logic of a cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Suppose we need \(k\) years' observations to produce a reliable forecast\footnote{\(k\) can't be too small}, we are interested in the \(H\) prediction horizon.
 Then we are allowed to repeat the test \(n-H-k+1\) times, where \(n\) is the number of total years of observation.
@@
 
-Let \(\omega=1\), we first select historical data for a time interval of \([\omega,\omega+1,\dots,\omega+k-1]\) as ``in sample data'' to fit the model, and then forecast \(H\) years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test}.
+Let \(\omega=1\), we first select historical data for a time interval of \([\omega,\omega+1,\dots,\omega+k-1]\) as ``in sample data'' to fit the model, and then forecast \(H\) years' OADR\footnote{The OADR is generated based on a pension age equal to 65 for the purpose of test.}.
 Then, we can calculate the difference of forecasted OADR over the period \([\omega+k,\omega+k+1,\dots,\omega+k+H-1]\) from the real OADR for the same period, which is known as absolute error.
@@
 Then, we can summary the information into a matrix as follows:
-\begin{equation*}
+\[
   \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
@@
     \end{bmatrix}
-\end{equation*}
+\]
 where \(h\) denotes for the forecast horizon and \(\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|\).
@@
 
-In our sample, \(n=2014-1950+1=65\) and we set \(k=25\) and \(H=25\) to perform the test.
+n our sample, \(n=2014-1950+1=65\) and we set \(k=25\) and \(H=25\) to perform the test.
 The mean absolute error of \(h\)-step-ahead forecast of OADR for \(h=1,2,\dots,25\) is shown in Figure \ref{fig:rollingtest}.
@@
 
-\begin{verbatim}
-## Error in stats::arima(x = x, order = order, seasonal = seasonal, include.mean = include.mean,  : 
-##   non-stationary AR part from CSS
-## Error in stats::arima(x = x, order = order, seasonal = seasonal, include.mean = include.mean,  : 
-##   non-stationary AR part from CSS
-\end{verbatim}
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_files/figure-latex/rollingtest-1.pdf}
-\caption{\label{fig:rollingtest}The mean absolute error of \(h\)-step-ahead forecast for \(h=1,2,\dots,25\).}
-\end{figure}
+\includegraphics{PensionAge_files/figure-latex/rmseplot-1.pdf}
 
@@
 \hypertarget{sec:target}{%
-\section{Finding the Target Pension Age Scheme}\label{sec:target}}
+\section{Finding the target pension age scheme}\label{sec:target}}
 
@@
 for \(h=1,2,\dots,H\)
-\begin{equation*}
+\[
   \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-\end{equation*}
+\]
 \begin{align*}
@@
 For \(h=1,2,\dots,H\), we keep increasing pension age vector \([\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]\) by a month at a time, unless we find that
-\vspace{-.2in}
 \begin{align*}
@@
 \hypertarget{plausible-pension-age-schemes}{%
-\subsection{Plausible Pension Age Schemes}\label{plausible-pension-age-schemes}}
+\subsection{Plausible pension age schemes}\label{plausible-pension-age-schemes}}
 
@@
 Figure \ref{fig:OADRwithoptimal} provides a visible comparison of the desired OADR level of 21\% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.\todo{In the table, I set the beginning year to 2015 instead of 2016.}
+Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
 
@@
 \centering
-\begin{tabular}[t]{llllllllll}
+\begin{tabular}[t]{rlrlrlrlrl}
 \toprule
@@
 \midrule
-2017 & 65Y & 2027 & 66Y+8M & 2037 & 69Y+2M & 2047 & 71Y+2M & 2057 & 71Y+2M\\
-2018 & 65Y & 2028 & 67Y+2M & 2038 & 69Y+8M & 2048 & 71Y+2M & 2058 & 71Y+2M\\
-2019 & 65Y & 2029 & 67Y+2M & 2039 & 69Y+8M & 2049 & 71Y+2M & 2059 & 71Y+2M\\
-2020 & 65Y & 2030 & 67Y+8M & 2040 & 70Y+2M & 2050 & 71Y+2M & 2060 & 71Y+2M\\
-2021 & 65Y & 2031 & 67Y+8M & 2041 & 70Y+2M & 2051 & 71Y+2M & 2061 & 71Y+2M\\
+2019 & 65Y & 2029 & 68Y+1M & 2039 & 70Y+1M & 2049 & 70Y+1M & 2059 & 71Y+1M\\
+2020 & 65Y & 2030 & 68Y+1M & 2040 & 70Y+1M & 2050 & 70Y+1M & 2060 & 71Y+1M\\
+2021 & 65Y & 2031 & 68Y+1M & 2041 & 70Y+1M & 2051 & 70Y+1M & 2061 & 71Y+1M\\
+2022 & 65Y & 2032 & 68Y+1M & 2042 & 70Y+1M & 2052 & 70Y+1M & 2062 & 71Y+1M\\
+2023 & 65Y+12M & 2033 & 68Y+1M & 2043 & 70Y+1M & 2053 & 70Y+1M & 2063 & 71Y+1M\\
 \addlinespace
-2022 & 65Y+5M & 2032 & 68Y+2M & 2042 & 70Y+8M & 2052 & 71Y+2M & 2062 & 71Y+2M\\
-2023 & 65Y+8M & 2033 & 68Y+2M & 2043 & 70Y+8M & 2053 & 71Y+2M & 2063 & 71Y+2M\\
-2024 & 65Y+11M & 2034 & 68Y+8M & 2044 & 71Y+2M & 2054 & 71Y+2M & 2064 & 71Y+2M\\
-2025 & 66Y+2M & 2035 & 68Y+8M & 2045 & 71Y+2M & 2055 & 71Y+2M & 2065 & 71Y+2M\\
-2026 & 66Y+8M & 2036 & 69Y+2M & 2046 & 71Y+2M & 2056 & 71Y+2M & 2066 & 71Y+3M\\
+2024 & 66Y+12M & 2034 & 68Y+1M & 2044 & 70Y+1M & 2054 & 70Y+1M & 2064 & 71Y+1M\\
+2025 & 67Y+1M & 2035 & 68Y+1M & 2045 & 70Y+1M & 2055 & 70Y+1M & 2065 & 72Y+1M\\
+2026 & 67Y+1M & 2036 & 69Y+1M & 2046 & 70Y+1M & 2056 & 70Y+1M & 2066 & 72Y+1M\\
+2027 & 67Y+1M & 2037 & 69Y+1M & 2047 & 70Y+1M & 2057 & 71Y+1M & 2067 & 72Y+1M\\
+2028 & 67Y+1M & 2038 & 69Y+1M & 2048 & 70Y+1M & 2058 & 71Y+1M & 2068 & 72Y+1M\\
 \bottomrule
@@
 \fontsize{7}{9}\selectfont
-\begin{tabular}[t]{lllllllllllllll}
+\begin{tabular}[t]{rllrllrllrllrll}
 \toprule
@@
 \midrule
-2017 & 65Y & 65Y & 2027 & 66Y+4M & 67Y & 2037 & 68Y & 69Y+7M & 2047 & 70Y & 71Y+7M & 2057 & 70Y & 71Y+11M\\
-2018 & 65Y & 65Y & 2028 & 66Y+10M & 67Y+6M & 2038 & 68Y+6M & 70Y+1M & 2048 & 70Y & 71Y+7M & 2058 & 70Y & 72Y+2M\\
-2019 & 65Y & 65Y & 2029 & 66Y+10M & 67Y+7M & 2039 & 68Y+6M & 70Y+1M & 2049 & 70Y & 71Y+7M & 2059 & 70Y & 72Y+4M\\
-2020 & 65Y & 65Y & 2030 & 67Y+4M & 68Y+1M & 2040 & 69Y & 70Y+7M & 2050 & 70Y & 71Y+7M & 2060 & 70Y & 72Y+7M\\
-2021 & 65Y & 65Y & 2031 & 67Y+4M & 68Y+1M & 2041 & 69Y & 70Y+7M & 2051 & 70Y & 71Y+7M & 2061 & 70Y & 72Y+9M\\
+2019 & 65Y & 65Y & 2029 & 68Y+1M & 68Y+1M & 2039 & 69Y+1M & 70Y+1M & 2049 & 69Y+1M & 70Y+1M & 2059 & 69Y+1M & 71Y+1M\\
+2020 & 65Y & 65Y & 2030 & 68Y+1M & 68Y+1M & 2040 & 69Y+1M & 70Y+1M & 2050 & 69Y+1M & 70Y+1M & 2060 & 69Y+1M & 71Y+1M\\
+2021 & 65Y & 65Y & 2031 & 68Y+1M & 68Y+1M & 2041 & 69Y+1M & 70Y+1M & 2051 & 69Y+1M & 70Y+1M & 2061 & 69Y+1M & 71Y+1M\\
+2022 & 65Y & 65Y & 2032 & 68Y+1M & 68Y+1M & 2042 & 69Y+1M & 70Y+1M & 2052 & 69Y+1M & 70Y+1M & 2062 & 69Y+1M & 71Y+1M\\
+2023 & 65Y+12M & 65Y+12M & 2033 & 68Y+1M & 68Y+1M & 2043 & 69Y+1M & 70Y+1M & 2053 & 69Y+1M & 70Y+1M & 2063 & 69Y+1M & 71Y+1M\\
 \addlinespace
-2022 & 65Y+4M & 65Y+7M & 2032 & 67Y+10M & 68Y+7M & 2042 & 69Y+6M & 71Y+1M & 2052 & 70Y & 71Y+7M & 2062 & 70Y & 73Y\\
-2023 & 65Y+6M & 65Y+10M & 2033 & 67Y+10M & 68Y+7M & 2043 & 69Y+6M & 71Y+1M & 2053 & 70Y & 71Y+7M & 2063 & 70Y & 73Y+2M\\
-2024 & 65Y+7M & 66Y+2M & 2034 & 68Y+4M & 69Y+1M & 2044 & 70Y & 71Y+7M & 2054 & 70Y & 71Y+7M & 2064 & 70Y & 73Y+4M\\
-2025 & 65Y+10M & 66Y+5M & 2035 & 68Y+4M & 69Y+1M & 2045 & 70Y & 71Y+7M & 2055 & 70Y & 71Y+7M & 2065 & 70Y & 73Y+6M\\
-2026 & 66Y+4M & 66Y+11M & 2036 & 68Y+10M & 69Y+7M & 2046 & 70Y & 71Y+7M & 2056 & 70Y & 71Y+8M & 2066 & 70Y & 73Y+9M\\
+2024 & 66Y+12M & 66Y+12M & 2034 & 68Y+1M & 68Y+1M & 2044 & 69Y+1M & 70Y+1M & 2054 & 69Y+1M & 70Y+1M & 2064 & 69Y+1M & 71Y+1M\\
+2025 & 67Y+1M & 67Y+1M & 2035 & 68Y+1M & 68Y+1M & 2045 & 69Y+1M & 70Y+1M & 2055 & 69Y+1M & 70Y+1M & 2065 & 69Y+1M & 72Y+1M\\
+2026 & 67Y+1M & 67Y+1M & 2036 & 69Y+1M & 69Y+1M & 2046 & 69Y+1M & 70Y+1M & 2056 & 69Y+1M & 70Y+1M & 2066 & 69Y+1M & 73Y+1M\\
+2027 & 67Y+1M & 67Y+1M & 2037 & 69Y+1M & 69Y+1M & 2047 & 69Y+1M & 70Y+1M & 2057 & 69Y+1M & 71Y+1M & 2067 & 69Y+1M & 73Y+1M\\
+2028 & 67Y+1M & 67Y+1M & 2038 & 69Y+1M & 69Y+1M & 2048 & 69Y+1M & 70Y+1M & 2058 & 69Y+1M & 71Y+1M & 2068 & 69Y+1M & 74Y+1M\\
 \bottomrule
@@
 When we allow 1\% more in desired OADR, the real pension age becomes plausible.
-Figure \ref{fig:OADR_realpensionage} shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023-2035, we assume it follows increase rate for 2017-2023, which increase half year pension age in every two years}.
+Figure @ref(fig:OADR\_realpensionage) shows simulated OADR associated with proposed pension age scheme\footnote{Since we don't know the change rate set by government for 2023--2035, we assume it follows increase rate for 2017--2023, which increase half year pension age in every two years.}.
 It confirms that OADR is stable around a level higher than current level of OADR before 2035.

### 2020-08-24 PensionAge.Rmd
Added renv lock, updated all packages and recompiled

@@
 knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
-library(tidyverse)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
 library(demography)
-# remotes::install_github("robjhyndman/addb")
-library(addb)
 library(patchwork)
-library(kableExtra)
 source("functions-v4.R")
@@
 # Get fertility data for 1921-2006
-aus.fert <- aus.fertility
+aus.fert <- addb::aus.fertility
 births <- aus.fert$rate$female * aus.fert$pop$female
@@
   ) %>%
-  kable_styling(font_size = 7)
+  kableExtra::kable_styling(font_size = 7)
 ```
@@
 For instance, the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.
+
+\newpage
+
+### Colophon {-}
+
+This report was generated on `r Sys.time()`.
+
+The current Git commit details are:
+
+```{r}
+## Which commit is this file at?
+git2r::repository(here::here())
+```
+
+We used the following computational environment and dependencies:
+
+```{r colophon, cache=FALSE}
+options(width=100)
+## Which R packages and versions?
+devtools::session_info()
+```
+
+\newpage

### 2020-08-24 PensionAge.tex
Added renv lock, updated all packages and recompiled

@@
 
+\newpage
+
+\hypertarget{colophon}{%
+\subsubsection*{Colophon}\label{colophon}}
+\addcontentsline{toc}{subsubsection}{Colophon}
+
+This report was generated on 2020-08-24 15:26:49.
+
+The current Git commit details are:
+
+\begin{verbatim}
+## Local:    master /home/robjhyndman/git/Research/PensionAge
+## Remote:   master @ origin (git@github.com:robjhyndman/PensionAge.git)
+## Head:     [e16a85d] 2020-05-05: [ImgBot] Optimize images
+\end{verbatim}
+
+We used the following computational environment and dependencies:
+
+\begin{verbatim}
+## - Session info -----------------------------------------------------------------------------------
+##  setting  value                       
+##  version  R version 4.0.2 (2020-06-22)
+##  os       Ubuntu 20.04.1 LTS          
+##  system   x86_64, linux-gnu           
+##  ui       X11                         
+##  language en_AU:en                    
+##  collate  en_AU.UTF-8                 
+##  ctype    en_AU.UTF-8                 
+##  tz       Australia/Melbourne         
+##  date     2020-08-24                  
+## 
+## - Packages ---------------------------------------------------------------------------------------
+##  ! package            * version  date       lib source                                         
+##  P abind                1.4-5    2016-07-21 [?] CRAN (R 4.0.0)                                 
+##  P assertthat           0.2.1    2019-03-21 [?] CRAN (R 4.0.0)                                 
+##  P backports            1.1.6    2020-04-05 [?] CRAN (R 4.0.0)                                 
+##    bookdown             0.18     2020-03-05 [1] CRAN (R 4.0.0)                                 
+##  P callr                3.4.3    2020-03-28 [?] CRAN (R 4.0.0)                                 
+##  P cli                  2.0.2    2020-02-28 [?] CRAN (R 4.0.0)                                 
+##  P cluster              2.1.0    2019-06-19 [?] CRAN (R 4.0.0)                                 
+##  P cobs                 1.3-4    2020-01-24 [?] CRAN (R 4.0.0)                                 
+##    codetools            0.2-16   2018-12-24 [1] CRAN (R 4.0.0)                                 
+##  P colorspace           1.4-1    2019-03-18 [?] CRAN (R 4.0.0)                                 
+##  P crayon               1.3.4    2017-09-16 [?] CRAN (R 4.0.0)                                 
+##  P curl                 4.3      2019-12-02 [?] CRAN (R 4.0.0)                                 
+##  P demography         * 1.22     2019-04-22 [?] CRAN (R 4.0.0)                                 
+##  P desc                 1.2.0    2018-05-01 [?] CRAN (R 4.0.0)                                 
+##    devtools             2.3.0    2020-04-10 [1] CRAN (R 4.0.0)                                 
+##  P digest               0.6.25   2020-02-23 [?] CRAN (R 4.0.0)                                 
+##  P dplyr              * 0.8.5    2020-03-07 [?] CRAN (R 4.0.0)                                 
+##  P ellipsis             0.3.0    2019-09-20 [?] CRAN (R 4.0.0)                                 
+##  P evaluate             0.14     2019-05-28 [?] CRAN (R 4.0.0)                                 
+##  P fansi                0.4.1    2020-01-08 [?] CRAN (R 4.0.0)                                 
+##  P farver               2.0.3    2020-01-16 [?] CRAN (R 4.0.0)                                 
+##  P fda                  5.1.4    2020-04-20 [?] CRAN (R 4.0.0)                                 
+##  P forecast           * 8.12     2020-03-31 [?] CRAN (R 4.0.0)                                 
+##  P fracdiff             1.5-1    2020-01-24 [?] CRAN (R 4.0.0)                                 
+##  P fs                   1.4.1    2020-04-04 [?] CRAN (R 4.0.0)                                 
+##  P ftsa                 5.6      2020-04-23 [?] CRAN (R 4.0.0)                                 
+##  P geometry             0.4.5    2019-12-04 [?] CRAN (R 4.0.0)                                 
+##  P ggplot2            * 3.3.0    2020-03-05 [?] CRAN (R 4.0.0)                                 
+##  P git2r                0.27.1   2020-05-03 [?] CRAN (R 4.0.0)                                 
+##  P glue                 1.4.0    2020-04-03 [?] CRAN (R 4.0.0)                                 
+##  P gtable               0.3.0    2019-03-25 [?] CRAN (R 4.0.0)                                 
+##  P hdrcde               3.3      2018-12-21 [?] CRAN (R 4.0.0)                                 
+##    here                 0.1      2017-05-28 [1] CRAN (R 4.0.0)                                 
+##  P highr                0.8      2019-03-20 [?] CRAN (R 4.0.0)                                 
+##  P hms                  0.5.3    2020-01-08 [?] CRAN (R 4.0.0)                                 
+##  P htmltools            0.4.0    2019-10-04 [?] CRAN (R 4.0.0)                                 
+##  P httr                 1.4.1    2019-08-05 [?] CRAN (R 4.0.0)                                 
+##  P kableExtra           1.1.0    2019-03-16 [?] CRAN (R 4.0.0)                                 
+##  P KernSmooth           2.23-17  2020-04-26 [?] CRAN (R 4.0.0)                                 
+##  P knitr                1.28     2020-02-06 [?] CRAN (R 4.0.0)                                 
+##  P ks                   1.11.7   2020-02-11 [?] CRAN (R 4.0.0)                                 
+##  P labeling             0.3      2014-08-23 [?] CRAN (R 4.0.0)                                 
+##  P latex2exp          * 0.4.0    2015-11-30 [?] CRAN (R 4.0.0)                                 
+##  P lattice              0.20-41  2020-04-02 [?] RSPM (R 4.0.0)                                 
+##  P lifecycle            0.2.0    2020-03-06 [?] CRAN (R 4.0.0)                                 
+##  P lmtest               0.9-37   2019-04-30 [?] CRAN (R 4.0.0)                                 
+##  P magic                1.5-9    2018-09-17 [?] CRAN (R 4.0.0)                                 
+##  P magrittr             1.5      2014-11-22 [?] CRAN (R 4.0.0)                                 
+##  P MASS                 7.3-51.6 2020-04-26 [?] CRAN (R 4.0.0)                                 
+##  P Matrix               1.2-18   2019-11-27 [?] CRAN (R 4.0.0)                                 
+##  P MatrixModels         0.4-1    2015-08-22 [?] CRAN (R 4.0.0)                                 
+##  P mclust               5.4.6    2020-04-11 [?] CRAN (R 4.0.0)                                 
+##    memoise              1.1.0    2017-04-21 [1] CRAN (R 4.0.0)                                 
+##  P mgcv                 1.8-31   2019-11-09 [?] CRAN (R 4.0.0)                                 
+##    MonashEBSTemplates   0.2      2020-05-04 [1] Github (robjhyndman/MonashEBSTemplates@dc32000)
+##  P munsell              0.5.0    2018-06-12 [?] CRAN (R 4.0.0)                                 
+##  P mvtnorm              1.1-0    2020-02-24 [?] RSPM (R 4.0.0)                                 
+##  P nlme                 3.1-147  2020-04-13 [?] RSPM (R 4.0.0)                                 
+##  P nnet                 7.3-14   2020-04-26 [?] CRAN (R 4.0.0)                                 
+##  P patchwork          * 1.0.0    2019-12-01 [?] CRAN (R 4.0.0)                                 
+##  P pcaPP                1.9-73   2018-01-14 [?] CRAN (R 4.0.0)                                 
+##  P pdfCluster           1.0-3    2018-12-04 [?] CRAN (R 4.0.0)                                 
+##  P pillar               1.4.3    2019-12-20 [?] CRAN (R 4.0.0)                                 
+##  P pkgbuild             1.0.7    2020-04-25 [?] CRAN (R 4.0.0)                                 
+##  P pkgconfig            2.0.3    2019-09-22 [?] CRAN (R 4.0.0)                                 
+##  P pkgload              1.0.2    2018-10-29 [?] CRAN (R 4.0.0)                                 
+##  P prettyunits          1.1.1    2020-01-24 [?] CRAN (R 4.0.0)                                 
+##  P processx             3.4.2    2020-02-09 [?] CRAN (R 4.0.0)                                 
+##  P ps                   1.3.2    2020-02-13 [?] CRAN (R 4.0.0)                                 
+##  P purrr                0.3.4    2020-04-17 [?] RSPM (R 4.0.0)                                 
+##  P quadprog             1.5-8    2019-11-20 [?] CRAN (R 4.0.0)                                 
+##  P quantmod             0.4.17   2020-03-31 [?] CRAN (R 4.0.0)                                 
+##  P quantreg             5.55     2020-04-01 [?] CRAN (R 4.0.0)                                 
+##  P R6                   2.4.1    2019-11-12 [?] CRAN (R 4.0.0)                                 
+##  P rainbow              3.6      2019-01-29 [?] CRAN (R 4.0.0)                                 
+##  P RColorBrewer         1.1-2    2014-12-07 [?] CRAN (R 4.0.0)                                 
+##  P Rcpp                 1.0.4.6  2020-04-09 [?] CRAN (R 4.0.0)                                 
+##  P readr                1.3.1    2018-12-21 [?] CRAN (R 4.0.0)                                 
+##  P remotes              2.1.1    2020-02-15 [?] CRAN (R 4.0.0)                                 
+##    renv                 0.9.3    2020-02-10 [1] CRAN (R 4.0.0)                                 
+##    rlang                0.4.6    2020-05-02 [1] CRAN (R 4.0.0)                                 
+##  P rmarkdown            2.1      2020-01-20 [?] CRAN (R 4.0.0)                                 
+##  P rprojroot            1.3-2    2018-01-03 [?] CRAN (R 4.0.0)                                 
+##  P rstudioapi           0.11     2020-02-07 [?] CRAN (R 4.0.0)                                 
+##  P rvest                0.3.5    2019-11-08 [?] CRAN (R 4.0.0)                                 
+##  P scales               1.1.0    2019-11-18 [?] CRAN (R 4.0.0)                                 
+##  P sde                  2.0.15   2016-04-13 [?] CRAN (R 4.0.0)                                 
+##    sessioninfo          1.1.1    2018-11-05 [1] CRAN (R 4.0.0)                                 
+##  P SparseM              1.78     2019-12-13 [?] RSPM (R 4.0.0)                                 
+##  P stringi              1.4.6    2020-02-17 [?] CRAN (R 4.0.0)                                 
+##  P stringr              1.4.0    2019-02-10 [?] CRAN (R 4.0.0)                                 
+##  P testthat             2.3.2    2020-03-02 [?] CRAN (R 4.0.0)                                 
+##  P tibble               3.0.1    2020-04-20 [?] CRAN (R 4.0.0)                                 
+##  P tidyr              * 1.0.2    2020-01-24 [?] CRAN (R 4.0.0)                                 
+##  P tidyselect           1.0.0    2020-01-27 [?] CRAN (R 4.0.0)                                 
+##  P timeDate             3043.102 2018-02-21 [?] CRAN (R 4.0.0)                                 
+##  P tseries              0.10-47  2019-06-05 [?] CRAN (R 4.0.0)                                 
+##  P TTR                  0.23-6   2019-12-15 [?] CRAN (R 4.0.0)                                 
+##  P urca                 1.3-0    2016-09-06 [?] CRAN (R 4.0.0)                                 
+##    usethis              1.6.1    2020-04-29 [1] CRAN (R 4.0.0)                                 
+##  P vctrs                0.2.4    2020-03-10 [?] CRAN (R 4.0.0)                                 
+##  P viridisLite          0.3.0    2018-02-01 [?] CRAN (R 4.0.0)                                 
+##  P webshot              0.5.2    2019-11-22 [?] CRAN (R 4.0.0)                                 
+##  P withr                2.2.0    2020-04-20 [?] CRAN (R 4.0.0)                                 
+##  P xfun                 0.13     2020-04-13 [?] CRAN (R 4.0.0)                                 
+##  P xml2                 1.3.2    2020-04-23 [?] CRAN (R 4.0.0)                                 
+##  P xts                  0.12-0   2020-01-19 [?] CRAN (R 4.0.0)                                 
+##  P yaml                 2.2.1    2020-02-01 [?] CRAN (R 4.0.0)                                 
+##  P zoo                  1.8-7    2020-01-10 [?] CRAN (R 4.0.0)                                 
+## 
+## [1] /home/robjhyndman/git/Research/PensionAge/renv/library/R-4.0/x86_64-pc-linux-gnu
+## [2] /tmp/RtmpYSnVGN/renv-system-library
+## 
+##  P -- Loaded and on-disk path mismatch.
+\end{verbatim}
+
+\newpage
+
 \printbibliography

### 2020-09-10 PensionAge.Rmd
Hanlin's changes

@@
   othernames: Han Lin
-  address: Australian National University
+  address: Macquarie University
 abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
@@
 We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2014 level, which is 21%.
-This approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "functional time series model, coherent forecasts, demographic components, pension and insurance"
+This approach can easily be extended to other target levels of the old-aged dependency ratio and other countries."
+keywords: "coherent forecasts, demographic components, functional time series model, pension and insurance"
 wpnumber: no/yr
@@
 The research presented in this paper contributes to the discussion by forecasting the age structure of the population, quantifying the effects of changing the pension age on financial burdens, and hence finding an appropriate pension age scheme which is economically viable for Australia.
-The analysis of economic impact of increasing pension age can be complicated.
-In this paper, we will focus on only one aspect: the impact on the burden of future working age generations.
-
-In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
+The analysis of the economic impact of increasing pension age can be complicated.
+In this paper, we will focus on only one aspect: the impact on the burden of future working-age generations.
+
+In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
 The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07].
@@
 By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
-Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at a desired level in the future.
-It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2014.
+Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at the desired level in the future.
+It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2018.
 Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
-This paper concentrates on providing a framework for policy makers to find a target pension age for a given desired level of OADR.
-
-Some may argue that using OADR as a measure of financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
+This paper concentrates on providing a framework for policymakers to find a target pension age for a given desired level of OADR.
+
+Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
 However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14].
-Therefore, the proportion of people over working age is still a good representation of financial burden on future working generations.
+Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
 Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
@@
 
-Age pension in Australia is an income support and provides access to a range of concessions for older Australians who have passed means testing.
+Age pension in Australia is income support and provides access to a range of concessions for older Australians who have passed means-testing.
 For example, it provides single home-owners with a real income of $23,889 p.a and additional allowances to cover expenses such as rent or pharmaceuticals^[The pension amount is adjusted every 6 months for inflation].
-The means test ensures that retirees with enough personal savings will become ineligible for public provision by reducing the pension at fixed levels of pay as personal wealth increases.
+The means test ensures that retirees with enough personal savings will become ineligible for the public provision by reducing the pension at fixed levels of pay as personal wealth increases.
 The age pension in Australia is very generous, even with the means test.
@@
 The ageing trend in Australia, along with retirees' dependence on the age pension, has dramatically increased the fiscal cost of the age pension.
-For instance, the fiscal cost of the age pension is currently around at 2.5% of Gross Domestic Profit (GDP), but is expected to increase to 4.4% by the 2050s (Australian Government, 2007).
+For instance, the fiscal cost of the age pension is currently around at 2.5% of Gross Domestic Profit (GDP), but is expected to increase to 4.4% by the 2050s (Australian government, 2007).
 The @PC13 also indicates the government will need to raise taxes by 21% to pay for extra aged care and health costs, which is caused by longer life expectancies in newer generations.
@@
 While the pension age for females was 60 years until 1994, it has steadily increased to 65 years, in line with that of males.
-The previous Labor government announced in 2009 that the pension age will increase six months every two years until 2017, capping at 67 in July 2023.
-This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because pension age is regarded as a normal age for retirement in Australia.
-However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and elderly people are capable of continuing work.
+The previous Labor government announced in 2009 that the pension age would increase six months every two years until 2017, capping at 67 in July 2023.
+This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because the pension age is regarded as a normal age for retirement in Australia.
+However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and older people are capable of continuing work.
 The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
-The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014--2015 to be confirmed by Australian Federal Government.
+The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014--2015 to be confirmed by the Australian Federal Government.
 Figure \@ref(fig:changespension) illustrates the process of the adjustments on pension age scheme.
 This announcement received overwhelmingly negative responses in the media.
-@Guest14 argues from an economic prospective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is  less than half of the OECD average.
+@Guest14 argues from an economic perspective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is  less than half of the OECD average.
 He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time.
-Further, @Power14 contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more a complex social problem.
-
-In fact, all supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age.
+Further, @Power14 contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more complex social problem.
+
+All supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age.
 No justification on the pace or degree of the change has been provided.
@@
 However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-Our study suggests an approach, linking the pension age with the the aged dependency ratio, based on forecasts of future mortality and fertility rates.
+Our study suggests an approach, linking the pension age with the aged dependency ratio, based on forecasts of future mortality and fertility rates.
 Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
@@
 It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour [@PC13].
-In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method, which now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method [see, e.g., @SBH11].
+In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method.
+It now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method [see, e.g., @SBH11].
 Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates [@PC13].
@@
 Therefore, some official agencies decide to mix the two approaches in their forecasts in order to provide a supplement to both approaches.
-For instance, the most recent forecast of population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
+For instance, the most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
 The approach of forecasting used in this study is very similar to the @PC13.
-The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of Lee-Carter method.
+The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of the Lee-Carter method.
 In addition, an adapted product-ratio method is used to eliminate the potential long-term divergence between female and male mortality rates.
@@
 \end{equation}
-where $m_{x,t}$ is the central death rate (properly defined in Section~\@ref(sec:data)) for age $x$ in year $t$.
+where $m_{x,t}$ is the central death rate (properly defined in Section \@ref(sec:data)) for age $x$ in year $t$.
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
 $b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$.
-$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
+$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across the age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
 
@@
 \end{equation}
-Also, we normally seek the least squares solution when estimating parameters.
+Also, we normally seek the least-squares solution when estimating parameters.
 However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation.
 @LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
-It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least squares solution (Good, 1969).
+It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least squares solution [@Good1969].
 Therefore, the estimates of $b_x$ and $k_t$ are the first principal component and scores of $\log(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$  when $\bm{X}=\log(m_{x,t})-a_x$).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of actual number of deaths because of the $\log$ transformation.
+However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of the actual number of deaths because of the $\log$ transformation.
 To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to an ARIMA ($0,1,0$) model with $c\neq0$.
+The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
 
@@
 
-  1. The rates are smoothed using penalized regression splines [@BHT14] before modeling.
+  1. The demographic rates are smoothed using penalized regression splines [@BHT14] before modeling.
   2. It uses functional principal components analysis, which is a continuous version of PCA.
-  3. It uses more than one principal component, which address the main weakness of the LC method.
-  4. The forecasting models for the principal component scores are more complex than the Random walk with drift model used in LC model.
+  3. It uses more than one principal component, which addresses the main weakness of the LC method.
+  4. The forecasting models for the principal component scores are more complex than the random walk with drift model used in the LC model.
 
@@
 $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14].
-$\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ are independent identical distributed standard normal error terms.
+$\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ is independent and identically distributed standard normal error terms.
 Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
 It describes the dynamics of $s_t(x)$ over time.
-The $\beta_{t,j}$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\phi_j(x)$ for every $j$ is a time-varying index.
+The $\phi_j(x)$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\beta_{t,j}$ for every $j$ is a time-varying index.
 The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation.
@@
 For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
-The fitted process is given as follows:
+The fitting process is given as follows:
 $$
-  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
+  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c_0+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
 $$
-where the parameters are estimated using maximum likelihood estimation.
+where the parameters are estimated using conditional maximum likelihood estimation.
 
@@
 We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method.
-The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., population of age $x$ at 30 June) for each year.
+The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., the population of age $x$ at 30 June) for each year.
 The notations are as follows:
@@
 where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
-The years is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
+The years is denoted by $t=1,2,\dots,n$, and superscripts M and F denote male and female respectively.
 
@@
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
 The deaths are estimated using the standard life table approach of population projection.
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the @HMD for 1921--2014.
-The start-year population for 2015 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2014 was obtained from the @ABS12.
-Even though annual mortality rates are available from 1921 to 2014, only data collected after 1950 is used for two reasons.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the @HMD for 1921--2018.
+The start-year population for 2019 is also used to estimate net migration.
+Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the @ABS12.
+Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
 First, the period between 1921--1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
@@
 Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula.
-Even though the process seems complicated, it is relatively resy to implement using \textit{R} [@Team18].
+Even though the process seems complicated, it is relatively easy to implement using \textit{R} [@Team18].
 The detailed explanation of each step is as follows.
@@
 
-The main procedure for forecasting the population age structure follows @HB08, except that the data is updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
+The main procedure for forecasting the population age structure follows @HB08, except that the data are updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
 The @HU07 model, introduced in section \@ref(sec:HU), is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
 Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
-However, for mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13].
+However, for the mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13].
 In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
@@
 
-After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value were simulated using the demographic growth-balance equations over the prediction horizon.
-The future deaths and births in this equation are assumed to follow Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
+After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value was simulated using the demographic growth-balance equations over the prediction horizon.
+The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
 Hence, we can simulate $h$-step-ahead age- and gender-specific births and deaths based on simulated mortality and fertility rates.
@@
 This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population.
-The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in these research).
+The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in this research).
 It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
@@
 Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
-We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in year 2015), given a specific pension age.
+We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in the year 2019), given a specific pension age.
 The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
@@
 
-Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and and $r$ is the reminder of pension age.
+Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and $r$ is the remainder of pension age.
 Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
@@
 \end{equation}
-To calculate the total number of working age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of total number of work age become a vector:
+To calculate the total number of working-age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of the total number of working-age become a vector:
 \begin{equation}
@@
 \end{equation}
-Using the same method, the simulations of total number of aged pensioners in the population can be shown as:
+Using the same method, the simulations of the total number of aged pensioners in the population can be shown as:
 \begin{equation}
@@
 
-When $r\neq0$, the vector of total number of working age population in \eqref{eq:work} is added, and the vector of total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
+When $r\neq0$, the vector of the total number of working-age population in \eqref{eq:work} is added, and the vector of the total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
 \begin{equation}
@@
 \end{equation}
-This adjustment is based on the assumption that the birthday of population is uniformly distributed over the year.
-Then, $r\times100\%$ of population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age.
-In other words, $(1-r\times100\%)$ of population with recorded integer age $a$ at beginning of the year is actually older than $a.r$, so they should be counted as the aged population.
+This adjustment is based on the assumption that the birthday of the population is uniformly distributed over the year.
+Then, $r\times100\%$ of the population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age.
+In other words, $(1-r\times100\%)$ of the population with recorded integer age $a$ at the beginning of the year is older than $a.r$, so they should be counted as the aged population.
 The simulation vectors of total work age population and total aged population should then be:
@@
 
-The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2015 to 2064).
-Simulations of OADR over a 50 year prediction horizon by the matrix is summarised below, with the forecast year in rows and simulation in the columns:
+The same algorithm is applied to the simulation matrix of the population age structure to obtain  $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2019 to 2068).
+Simulations of OADR over a 50 year prediction horizon by the matrix is summarized below, with the forecast year in rows and simulation in the columns:
 $$
@@
 It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
-Figure \@ref(fig:componentsfertility) above shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
+Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
 The first term ($\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950--2014.
+In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950--2018.
 It captures the general trend of fertility change over time.
-It indicates a sharp increase between 1950--1960, followed by a rapid decline of fertility rates from 1961.
+It indicates a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
 This increase of fertility is linked to the Post-World War II baby boom^[Between the years 1946 and 1964.] in Australia, resulting from the recovery from war and the Great Depression^[The Great Depression was a severe economic depression in the decade before World War II.].
 The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
-A noticeable further reduction of fertility rates in late 1960s may be due to a change in the law allowing abortion in some states in Australia.
+A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the law allowing abortion in some states in Australia.
 
@@
 It indicates the general pattern of fertility has very little effect on females of age 15.
-This makes intuitive sense because most early pregnancies are accidental, therefore, any of previously discussed events has no effect on early pregnancies.
+This makes intuitive sense because most early pregnancies are accidental.
+Therefore, any of the previously discussed events has no effect on early pregnancies.
 In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
 Furthermore, the blue line is the fitted value of future coefficients (i.e., $\widehat{\beta}_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% pointwise prediction interval according to the fitted ARIMA model of first coefficients $\left\{\widehat{\beta}_{t,1}\right\}$.
-Other terms further explain variation that has not been captured by first term, but less economic explanations can be given for them.
-
-oth Figures \@ref(fig:totalpopulationbyyears) and \@ref(fig:totalpopulationin2034) show the forecast results of population.
-Figure \@ref(fig:totalpopulationbyyears) shows the forecast of total population by gender over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2034.
-Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 23 million by 2064.
-Since the fertility rate is expected to remain low, the possible reason of the significant increase in population size is net migration.
-We can also observe that the further the projected year is, the bigger the forecast variation of population.
+Other terms further explain variation that has not been captured by the first term, but less economic explanations can be given for them.
+
+Figures \@ref(fig:totalpopulationbyyears) and \@ref(fig:totalpopulationin2034) show the forecast results of population.
+Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by gender over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2038.
+Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 27 million by 2068.
+Since the fertility rate is expected to remain low, the possible reason for the significant increase in population size is net migration.
+We can also observe that the further the projected year is, the bigger the forecast variation of a population.
 This increase in variation shows that we have less relevant information for further apart prediction horizons.
@@
 
-```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of total population for each sex, along with 80% prediction intervals.
-The actually population from 1950 to 2015 is shown using circles.", fig.height=4, dependson='simulationresults'}
+```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.
+The actual population from 1950 to 2019 is shown using circles.", fig.height=4, dependson='simulationresults'}
 future_tot_pop <- aussim_df %>%
@@
 
-```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2034, along with 80% pointwise prediction intervals.
-The actual pyramid for 2015 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
+```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals.
+The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
 pyramid <- function(history, future) {
@@
 
-Figure \@ref(fig:totalpopulationin2034) shows the mean and the 80% pointwise prediction interval of simulated population paths for year 2034, along with the 2015 base population.
-It can be observed that overall population size is expected to increase substantially.
-The uncertainty of population of infant is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates.
+Figure \@ref(fig:totalpopulationin2034) shows the mean and the 80% pointwise prediction interval of simulated population paths for the year 2038, along with the 2019 base population.
+It can be observed that the overall population size is expected to increase substantially.
+The uncertainty of the infant population is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates.
 The uncertainty of the young age population is mainly due to migration [@HB08].
 
-```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
+```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with the assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
 OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
@@
 ```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
-The actual OADRs for 1950--2014 are shown in black.", dependson='OADRat65'}
+The actual OADRs for 1921--2018 are shown in black.", dependson='OADRat65'}
 df <- bind_rows(
@@
 
-Analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
+The analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with the approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
 Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \@ref(fig:OADRat65) shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921--2014.
+Figure \@ref(fig:OADRat65) shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921--2018.
 A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
-This is consistent with the prediction by inter-generation reports in 2002 [@IGR02] and in 2007 [@IGR07].
+This is consistent with the prediction by inter-generation reports in 2002 [@IGR02] and 2007 [@IGR07].
 According to former Australian Treasurer @Costello04, this could be a result of better health care and low fertility rates.
@@
 
-Figure \@ref(fig:OADRcurrent) presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with approved change, along with comparison of both forecasts with desired level of OADR, which has been set at 21%.
+Figure \@ref(fig:OADRcurrent) presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with the approved change, along with a comparison of both forecasts with the desired level of OADR, which has been set at 21%.
 It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment.
-However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at nearly same rate as the OADR of a pension age equal of 65.
+However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at the nearly same rate as the OADR of a pension age equal of 65.
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
@@
 However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
-This answer will allow us to respond to the recent proposal of further increasing pension age to 70 by 2035.
+This answer will allow us to respond to the recent proposal of further increasing the pension age to 70 by 2035.
 
@@
 We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
-Therefore, we will use a Cross-Validation procedure (Hyndman and Athanasopoulos, 2013) to evaluate the accuracy of the models used in this paper.
-
-The logic of a cross-Validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
+
+The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
 Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
@@
 We repeat the following steps for $\omega=1,2,\dots,n-k-H+1$.
-Then, we can summary the information into a matrix as follows:
+Then, we can summarize the information into a matrix as follows:
 $$
@@
 
-n our sample, $n=2014-1950+1=65$ and we set $k=25$ and $H=25$ to perform the test.
+n our sample, $n=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
 The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
-From this figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
+From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
 Overall, the mean absolute error is very small.
@@
 
-It would normally be ideal to compare the mean absolute error of the forecast from our model to other available models to measure the accuracy.
+It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
 For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
-However, we are not able to actually perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
+However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
 
@@
 In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
-It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though pension age for males and females is 65.5 in mid-2017.
-The same pension age for males and females was set to simplify the calculations.
+It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though the pension age for males and females is 65.5 in mid-2017, the same pension age for males and females was set to simplify the calculations.
 This simplification is reasonable because the pension age will be same in mid-2017 onward}, which is:
@@
 In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
-To be more specific, "plausible", means finding a range of pension age schemes that could possibly lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
+To be more specific, "plausible", means finding a range of pension age schemes that could lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
 Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
 Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as 80% confidence interval of pension age scheme where we are 80% sure that there will be a desired outcome.
+The range of plausible pension age schemes can be thought of as a 80% confidence interval of pension age scheme where we are 80% sure that there will be the desired outcome.
 In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.
@@
 The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR is replaced by the boundary of the 80% prediction interval.
-Mean is replaced by the upper (lower) limit of the 80% prediction interval to find upper (lower) boundary for pension age schemes.
+Mean is replaced by the upper (lower) limit of the 80% prediction interval to find the upper (lower) boundary for pension age schemes.
 
@@
 Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
-It is assumed that it is impractical to change the pension age during 2011--2014, so the pension age has to be set at 65 for those years.
+It is assumed that it is impractical to change the pension age during 2011--2018, so the pension age has to be set at 65 for those years.
 Figure \@ref(fig:OADRwithoptimal) provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
@@
 
-```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2014).
+```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018).
 The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
@@
 
-```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with upper and lower boundary of plausible pension age schemes (listed in Table.2), along with desired OADR level (in red).", dependson="OADRat65"}
+```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red).", dependson="OADRat65"}
 bind_rows(
@@
 
-```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.
-The red solid line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
+```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade.
+The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
 pension.fc <- structure(
@@
 The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \@ref(fig:OADRboundaries).
-It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
+It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with the lower (upper) boundary of the 80% confidence interval  pension age scheme is entirely stable around the desired level.
 Note the negative relationship between OADR and pension age.
-It suggests, on one hand, that any pension age higher than the upper boundary in table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
+It suggests, on the one hand, that any pension age higher than the upper boundary in Table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
 On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
@@
 Figure \@ref(fig:comparisonofpensionages) compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
-It was found that the target pension age increases at higher rate than the proposed new pension age scheme.
+It was found that the target pension age increases at a higher rate than the proposed new pension age scheme.
 Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
-Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than desired level.
-From this result, it is concluded that government will need to adjust  pension age slightly quicker than proposed pace to ensure we have a stable OADR around desired level at 21%.
-
-However, it is interesting to note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
+Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than the desired level.
+From this result, it is concluded that the government will need to adjust  pension age slightly quicker than the proposed pace to ensure we have a stable OADR around the desired level at 21%.
+
+Note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
 Therefore, it is worth performing a sensitivity test on the desired level here.
 
-Using the approach suggested in this paper, the target pension age associated with desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with real pension age scheme in Figure \@ref(fig:ComparisonwithOADR22).
+Using the approach suggested in this paper, the target pension age associated with the desired OADR equal to current level plus 1% has been found.
+We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with a real pension age scheme in Figure \@ref(fig:ComparisonwithOADR22).
 When we allow 1% more in desired OADR, the real pension age becomes plausible.
@@
 
-The ageing of population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers.
+The ageing of the population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers.
 The fiscal cost of the age pension is projected to sharply increase as a result.
@@
 In this paper, we have suggested a statistical and demographic approach to address the issue.
-We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of financial burden on Australian society.
+We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of the financial burden on Australian society.
 The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable OADR around the desired level.
-To forecast population age structure, three demographic components of population were modelled separately using @HU07 functional time series method, with an extension of the product-ratio method [@HBY13].
-Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than desired level.
-This approach is proposed to find target pension age scheme based on a given desired level of OADR.
-
-We undertake the approach based on assuming the desired level of OADR is at current level of 21%.
-Using the historical data from 1950 to 2010, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
+To forecast the population age structure, three demographic components of the population were modeled separately using functional time series method [@HU07], with an extension of the product-ratio method [@HBY13].
+Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than the desired level.
+This approach is proposed to find a target pension age scheme based on a given desired level of OADR.
+
+We undertake the approach based on assuming the desired level of OADR is at the current level of 21%.
+Using the historical data from 1950 to 2018, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
 It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
 Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
-It was concluded that the pension age set by government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.
+It was concluded that the pension age set by the government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.
 
@@
 Therefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
-This approach has been used to calculate the target pension age from now until 2060 and its 80% confidence interval.
+This approach has been used to calculate the target pension age from now until 2068 and its 80% confidence interval.
 The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
@@
 It is possible to include an economic perspective.
-For example, the economic implications of retaining older workers in workforce can be considered.
-Second, Our research uses an OADR as a single measurement of financial burden.
+For example, the economic implications of retaining older workers in the workforce can be considered.
+Second, Our research uses an OADR as a single measurement of the financial burden.
 Further research should allow the effect of other economic factors to be taken into account.

### 2020-09-10 PensionAge.Rmd
Update based on Hanlin's email comments

@@
 
+\todo[inline]{Adjust numbers in abstract as per Figure 9}
+
 # Introduction
@@
 The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$.
-The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal component and scores of $s_t(x)-\mu(x)$ respectively.
+The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal component and scores of $s_t(x)-\mu(x)$ respectively.
 In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
@@
 We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
+
+\todo[inline]{Add comment on choosing $J$}
 
@@
 
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models'}
+```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models', message=FALSE}
 autoplot(fertf)

### 2020-09-10 PensionAge.Rmd
proselint and styler

@@
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2014 level, which is 21%.
+We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2018 level, which is 21%.
 This approach can easily be extended to other target levels of the old-aged dependency ratio and other countries."
@@
 The means test ensures that retirees with enough personal savings will become ineligible for the public provision by reducing the pension at fixed levels of pay as personal wealth increases.
-The age pension in Australia is very generous, even with the means test.
+The age pension in Australia is generous, even with the means test.
 For instance, a couple holding assets of more than one million dollars is still eligible for a partial age pension.
@@
 Our study suggests an approach, linking the pension age with the aged dependency ratio, based on forecasts of future mortality and fertility rates.
-Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with our ultimate goal of a stable financial burden for the public.
+Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.
 
@@
 
-In population forecasting, two very different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
+In population forecasting, two different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
 For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
@@
 For instance, the most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The approach of forecasting used in this study is very similar to the @PC13.
+The approach of forecasting used in this study is similar to the @PC13.
 The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of the Lee-Carter method.
@@
 Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
-First, the period between 1921--1950 has very different mortality patterns from later years because of wars and epidemics [@HB08].
+First, the period between 1921--1950 has different mortality patterns from later years because of wars and epidemics [@HB08].
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
@@
 The first estimated basis function $\widehat{\phi}_1(x)$ measures the different effects of the trend over time across ages.
-It indicates the general pattern of fertility has very little effect on females of age 15.
+It indicates the general pattern of fertility has little effect on females of age 15.
 This makes intuitive sense because most early pregnancies are accidental.
@@
 From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is very small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is very small if compared to the desired level of OADR, which is at 21%.
+Overall, the mean absolute error is small.
+For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 21%.
 
@@
   geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  geom_line(aes(y=OADR), col="#0000cc") +
-  geom_line(data=OADR_history, aes(y=OADR)) +
+  geom_line(aes(y = OADR), col = "#0000cc") +
+  geom_line(data = OADR_history, aes(y = OADR)) +
   ggtitle("OADR forecast estimates for optimal pension ages") +
@@
 bind_rows(
-    OADR_upper %>% mutate(Series="Upper boundary"),
-    OADR_lower %>% mutate(Series="Lower boundary"),
+  OADR_upper %>% mutate(Series = "Upper boundary"),
+  OADR_lower %>% mutate(Series = "Lower boundary"),
 ) %>%
@@
   geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  geom_line(aes(y=OADR), col="#0000cc") +
-  geom_line(data=OADR_history, aes(y=OADR)) +
+  geom_line(aes(y = OADR), col = "#0000cc") +
+  geom_line(data = OADR_history, aes(y = OADR)) +
   facet_grid(. ~ Series) +
@@
 pension.fc <- structure(
-  list(mean=ts(pension_age_optimal$Age, start=min(pension_age_optimal$Year)),
-       lower=ts(pension_age_optimal$Lo80, start=min(pension_age_optimal$Year)),
-       upper=ts(pension_age_optimal$Hi80, start=min(pension_age_optimal$Year)),
-       level=80),
-  class="forecast")
+  list(
+    mean = ts(pension_age_optimal$Age, start = min(pension_age_optimal$Year)),
+    lower = ts(pension_age_optimal$Lo80, start = min(pension_age_optimal$Year)),
+    upper = ts(pension_age_optimal$Hi80, start = min(pension_age_optimal$Year)),
+    level = 80
+  ),
+  class = "forecast"
+)
 ggplot() +
@@
   autolayer(
-    ts(pension_age %>% filter(Policy=="Approved", Year >= 1995) %>% pull(Age),
-       start=1995), series = "Approved change"
+    ts(pension_age %>% filter(Policy == "Approved", Year >= 1995) %>% pull(Age),
+      start = 1995
+    ),
+    series = "Approved change"
   ) +
   autolayer(
-    ts(pension_age %>% filter(Policy=="Current", Year >= 1995) %>% pull(Age),
-       start=1995), series = "Pension age at 65"
+    ts(pension_age %>% filter(Policy == "Current", Year >= 1995) %>% pull(Age),
+      start = 1995
+    ),
+    series = "Pension age at 65"
   ) +
-  xlab("Year") + ylab("Age of retirement")
+  xlab("Year") +
+  ylab("Age of retirement")
 ```
@@
 It suggests, on the one hand, that any pension age higher than the upper boundary in Table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
-On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a very generous age pension immediately.
+On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a generous age pension immediately.
 
@@
 ```{r colophon, cache=FALSE}
-options(width=100)
+options(width = 100)
 ## Which R packages and versions?

### 2020-09-10 PensionAge.Rmd
Edited Sections 1 and 2

@@
     citation_package: biblatex
-    includes:
-      in_header: preamble.tex
+header-includes:
+  - \usepackage{todonotes, xcolor}
 ---
@@
 This announcement received overwhelmingly negative responses in the media.
-@Guest14 argues from an economic perspective that Australia currently has much better circumstances than other OECD countries in terms of age pension pressure, because spending on the age pension in Australia is less than half of the OECD average.
+@Guest14 argues from an economic perspective that Australia currently has much less age pension pressure than other OECD countries, because spending on the age pension in Australia is less than half of the OECD average.
 He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time.
@@
 
-In population forecasting, two different approaches: a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) are frequently used.
+In population forecasting, two different approaches --- a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) --- are frequently used.
 For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
@@
 
-### Deterministic methods used by the ABS
+### Deterministic methods used by the ABS {-}
 
@@
 
-### Lee-Carter method
+### Lee-Carter method {-}
 
@@
 
-The model proposed by @LC92 is as follows:
-\begin{equation}
-  \log(m_{x,t})=a_x+b_xk_t+\epsilon_{x,t}
+The model proposed by @LC92 is
+\begin{equation}\label{eq:lc}
+  \log(m_{x,t})=a_x+b_xk_t+\varepsilon_{x,t},
 \end{equation}
@@
 $b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$.
-$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across the age of the log mortality rate and $\epsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
-
-The model is under-determined in terms of estimation of parameters.
+$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across the age of the log mortality rate and $\varepsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
+
+The model is over-parameterised.
 For example, if the vector $a,b,k$ is one solution, then for any scalar $c$, $a, b/c, kc$ or $a - bc, b, k+c$ also must be two possible solutions.
@@
 \end{equation}
-Also, we normally seek the least-squares solution when estimating parameters.
-However, in this case, the model cannot be estimated using simple regression methods because there is no regressor on the right side of the equation.
-@LC92 choose a singular value decomposition (SVD) method to undertake principal component analysis (PCA), and hence find the least squares solution.
-It has been shown that applying SVD method to a matrix of the logarithms of the rates after subtracting the average over time of the log age-specific rates can find the least squares solution [@Good1969].
-Therefore, the estimates of $b_x$ and $k_t$ are the first principal component and scores of $\log(m_{x,t})-a_x$ (i.e., $b_x=\bm{z_1}$ and $k_t=\bm{u_1}'$ when $\bm{X}=\log(m_{x,t})-a_x$).
-However, the empirical results suggest that the resulting fitted number of deaths are biased estimates of the actual number of deaths because of the $\log$ transformation.
-To overcome this problem, the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $k_t$ is then extrapolated using random walk with drift models, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
-
-### Hyndman-Ullah method \label{sec:HU}
-
-@HU07 proposed a nonparametric method for demographic modelling and forecasting. It extended the LC model in four ways:
+@LC92 use a singular value decomposition (SVD) method to find the least squares solution of \eqref{eq:lc} [@Good1969].
+The estimates of $b_x$ and $k_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{x_i,t})-a_{x_i}]$, where $a_{x_i}$ is the sample mean of $\log(m_{x_i,t})$ over $t$.
+The log transformation introduces some bias, so the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
+The adjusted $k_t$ is then extrapolated using a random walk with drift model, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
+
+### Hyndman-Ullah method \label{sec:HU} {-}
+
+@HU07 proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:
 
@@
 \begin{align}
-  y_t(x) & = s_t(x) + \sigma_t(x)\epsilon_{t,x}\label{eq:HU_1}\\
+  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
   s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
@@
 $y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14].
-$\sigma_t(x)$ allows the variance to be a function of time and age; and $\epsilon_{t,x}$ is independent and identically distributed standard normal error terms.
+$\sigma_t(x)$ allows the variance to be a function of time and age; and $\varepsilon_{t,x}$ is independent and identically distributed standard normal error terms.
 Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
@@
 $$
-We chose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
-
-\todo[inline]{Add comment on choosing $J$}
-
-In terms of forecasting, by conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ can be acquired by:
+We choose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
+Following @HB08, we select $J=6$ which has been found empirically to be large enough for demographic applications.
+
+Ty conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ are given by
 \begin{equation}
-  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j}
+  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j},
 \end{equation}
 where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$.
-Because of the time-varying property of $\left\{\beta_{t,j}\right\}$, it controls the dynamics of the process.
-For every component series $\left\{\beta_{t,j}\right\}$, we fit them with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion (Booth, Hyndman \& Tickle, 2014).
-The fitting process is given as follows:
-$$
-  (1-\phi_1B-\dots-\phi_{p_j}B^{p_j})(1-B)^{d_j}\beta_{t,j}=c_0+(1+\theta_1B+\dots+\theta_{q_j}B^{q_j})e_t, \quad ~\forall j=1,2,\dots,J,
-$$
-where the parameters are estimated using conditional maximum likelihood estimation.
+Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process.
+Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion [@forecastpackage], and the parameters are estimated using maximum likelihood estimation.
 
@@
 
-We use the same notation and similar procedures to construct data as in @HB08, because the fundamental model for forecasting population for this study is the @HU07 method.
+We use the same notation and similar procedures to construct data as in @HB08.
 The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., the population of age $x$ at 30 June) for each year.

### 2020-09-11 PensionAge.Rmd
Moved product-ratio to section 2

@@
 
-In population forecasting, two different approaches --- a deterministic approach (sometimes called a quasi-statistical approach) and a stochastic approach (a purely statistical approach) --- are frequently used.
-For instance, the Australian Bureau of Statistics (ABS) is using a deterministic approach for its demographic projection, while some other countries or institutes forecast demographic trends based on purely statistical approaches such as Statistics New Zealand and the United States Census Bureau.
-In the deterministic approach, experts project future demographic changes using judgement-based scenarios.
-It ignores the non-demographic factors such as major pandemics or wars, although historically they are important factors that affect demographic behaviour [@PC13].
-In stochastic approaches, the Lee-Carter (LC) method [@LC92] is the most prominent demographic forecasting method.
-It now has several variants and extensions that relax some of the assumptions of the basic Lee-Carter method [see, e.g., @SBH11].
-Although statistical forecasting models are rigorous, they still leave a basis for judgment-based adaptation, as they sometimes produce unrealistic projections of demographic factors such as long-run projections of mortality rates [@PC13].
-
-Therefore, some official agencies decide to mix the two approaches in their forecasts in order to provide a supplement to both approaches.
-For instance, the most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
+Variants of the Lee-Carter method [@LC92] are frequently used for demographic forecasting [see, e.g., @SBH11].
+The most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
 The approach of forecasting used in this study is similar to the @PC13.
 The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of the Lee-Carter method.
-In addition, an adapted product-ratio method is used to eliminate the potential long-term divergence between female and male mortality rates.
-A more detailed review of forecasting methods is given below.
-
-### Deterministic methods used by the ABS {-}
-
-The deterministic method is judgment-based.
-The Australian Bureau of Statistics formulates assumptions on the basis of demographic trends, in conjunction with advice from individual experts or government departments.
-The projections are not predictions or forecasts, "but are simply illustrations of the growth and change in population which would occur if certain assumptions about future levels of fertility, mortality, internal migration and overseas migration were to prevail over the projection period" [@ABS12, p.2].
-In addition, they do not attempt to take into account of non-demographic factors, such as major government policy changes and catastrophes.
-Therefore, they normally report multiple (usually three) series based on different levels of assumptions of demographic factors to allow for a variety of population projections.
+In addition, an adapted product-ratio method [@HBY13] is used to eliminate the potential long-term divergence between female and male mortality rates.
 
@@
 
-The Lee-Carter method [@LC92] is a significant milestone in demographic forecasting. It has been widely used to forecast mortality rates across various countries, including Australia.
-
-The model proposed by @LC92 is
+The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 is
 \begin{equation}\label{eq:lc}
@@
 For example, if the vector $a,b,k$ is one solution, then for any scalar $c$, $a, b/c, kc$ or $a - bc, b, k+c$ also must be two possible solutions.
-Therefore, Lee and Carter (1992) impose the following constraints:
+Therefore,  the constraints
 \begin{equation}
-  \sum_{t=1}^{n}k_t=0, \qquad \sum_{x=x_1}^{x_m}b_x=1
+  \sum_{t=1}^{n}k_t=0, \qquad\text{and}\qquad \sum_{x=x_1}^{x_m}b_x=1
 \end{equation}
-@LC92 use a singular value decomposition (SVD) method to find the least squares solution of \eqref{eq:lc} [@Good1969].
+are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969].
 The estimates of $b_x$ and $k_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{x_i,t})-a_{x_i}]$, where $a_{x_i}$ is the sample mean of $\log(m_{x_i,t})$ over $t$.
@@
 
-  1. The demographic rates are smoothed using penalized regression splines [@BHT14] before modeling.
+  1. The demographic rates are smoothed before modeling.
   2. It uses functional principal components analysis, which is a continuous version of PCA.
@@
 
-The model proposed by @HU07 is as follows:
+The Hyndman-Ullah (HU) model can be written as
 \begin{align}
   y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
-  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2}
+  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
 \end{align}
-Equation \eqref{eq:HU_1} describes the smoothing process.
-$y_t(x)$ is the observed data in year $t$ and age $x$, and $s_t(x)$ is the smoothed function of $y_t(x)$, estimated by constrained weighted penalized regression splines [@BHT14].
-$\sigma_t(x)$ allows the variance to be a function of time and age; and $\varepsilon_{t,x}$ is independent and identically distributed standard normal error terms.
-Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it incorporates more than one principal component and score.
-It describes the dynamics of $s_t(x)$ over time.
-The $\phi_j(x)$ for every $j$ and $\mu(x)$ are sets of age-specific constants, and $\beta_{t,j}$ for every $j$ is a time-varying index.
-The $e_t(x)$ is the model error, which is the residual function with mean zero and no serial correlation.
-The $\mu(x)$ is estimated by the average of $s_t(x)$ across years, which measures the general shape of the observed data $y_t(x)$.
-The estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal component and scores of $s_t(x)-\mu(x)$ respectively.
-In other words, we take singular value decomposition of $s_t(x)-\mu(x)$, then \eqref{eq:HU_2} now becomes
-$$
-  s_t(x)-\mu(x) = \phi_1(x)\beta_{t,1}+\phi_2(x)\beta_{t,2}+\dots+\phi_J(x)\beta_{t,J}
-$$
-We choose $J$ in a way that we believe the majority of information for $s_t(x)-\mu(x)$ has been captured by the first $J$ components.
-Following @HB08, we select $J=6$ which has been found empirically to be large enough for demographic applications.
-
-Ty conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of log rate $y_{n+h}(x)$ are given by
+where $y_t(x)$ may be log mortality, log fertility or net migration [@HB08] in year $t$ and age $x$.
+Here $s_t(x)$ is a smoothed version of the observed data $y_t(x)$, smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and $\{\varepsilon_{t,x}\}$ are independent and identically distributed standard normal error terms.
+Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score.
+The $e_t(x)$ is the model error having mean zero and no serial correlation, while $\mu(x)$ is estimated as the average of $s_t(x)$ across years.
+Estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal components and scores of $s_t(x)-\mu(x)$ respectively.
+Following @HB08, we select $J=6$ which we have found to be large enough for demographic applications.
+
+By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{n+h}(x)$ are given by
 \begin{equation}
@@
 Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion [@forecastpackage], and the parameters are estimated using maximum likelihood estimation.
+
+## Product-ratio method
+
+When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge [@HBY13].
+In the product-ratio method, we apply the HU model to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
+That is, we define
+\begin{align}
+  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
+  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
+\end{align}
+Then, the HU method is applied to these two new variables instead of male and female series:
+\begin{align*}
+  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
+  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+\end{align*}
+where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$).
+It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge.
+Then, forecasts of sex-specific data are obtained using
+\begin{align*}
+  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
+  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
+\end{align*}
+The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.
 
@@
 The main procedure for forecasting the population age structure follows @HB08, except that the data are updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
-The @HU07 model, introduced in section \@ref(sec:HU), is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
+
+, introduced in section \@ref(sec:HU), is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
 Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
-However, for the mortality rate by sex, the product-ratio method is used to ensure the forecast of females and males are non-divergent or coherent [@HBY13].
-In the product-ratio method, after smoothing the female and male mortality rates, two other series were created: product series (denoted by $p_t(x)$) and ratio series (denoted by $r_t(x)$), which are defined as follows:
-\begin{align}
-  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
-  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
-\end{align}
-Then, @HU07 was applied to these two new variables instead of male and female mortality rate as follows:
-\begin{align*}
-  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
-\end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$).
-It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecast of male and female do not diverge.
-Then, simulating $h$-step-ahead forecast values of product variable and ratio variable was performed (denoted by $p_{n+h\mid n}(x)$ and $r_{n+h\mid n}(x)$ respectively) according to \eqref{eq:coherent_1} and \eqref{eq:coherent_2}.
-From here, obtaining $h$-step-ahead forecast of sex-specific coherent mortality rates (denoted $m_{n+h\mid n,M}(x)$ and $m_{n+h\mid n,F}(x)$) was performed using a back-transformation:
-\begin{align*}
-  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
-  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
-\end{align*}
-The method for simulating $h$-step-ahead values of net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration.
-A stationary constraint was imposed on the ARIMA model for net migration to make sure the difference between sexes did not diverge.
 

### 2020-09-11 PensionAge.Rmd
Finished section 2

@@
 One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
-Forecasts of population structure have been built on forecasts of age- and gender-specific mortality rates, fertility rates and net migration using this method.
+Forecasts of population structure have been built on forecasts of age- and sex-specific mortality rates, fertility rates and net migration using this method.
 These forecasts presuppose that the historical trends of past years will continue.
-Historical data of those rates have thus been used as input to simulate future paths of age- and gender-specific population structure.
+Historical data of those rates have thus been used as input to simulate future paths of age- and sex-specific population structure.
 
@@
 
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 is
+The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 (but using our notation) is
 \begin{equation}\label{eq:lc}
-  \log(m_{x,t})=a_x+b_xk_t+\varepsilon_{x,t},
+  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
 \end{equation}
-where $m_{x,t}$ is the central death rate (properly defined in Section \@ref(sec:data)) for age $x$ in year $t$.
-This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$a_x$} and {$b_x$}, and a time-varying index $k_t$.
-$b_x$ is a set of parameters that tell us the rate at which each age responds to changes in $k_t$.
-$k_t$ measures the general level of the log death rates; $a_x$ is the general pattern across the age of the log mortality rate and $\varepsilon_{x,t}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
-
-The model is over-parameterised.
-For example, if the vector $a,b,k$ is one solution, then for any scalar $c$, $a, b/c, kc$ or $a - bc, b, k+c$ also must be two possible solutions.
-Therefore,  the constraints
+where $m_{t}(x)$ is the central death rate (properly defined in Section \@ref(sec:data)) for age $x$ in year $t$.
+This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$\mu(x)$} and {$\phi(x)$}, and a time-varying index $\beta_{t}$.
+$\phi(x)$ is a set of parameters that tell us the rate at which each age responds to changes in $\beta_{t}$.
+$\beta_{t}$ measures the general level of the log death rates; $\mu(x)$ is the general pattern across the age of the log mortality rate and $\varepsilon_{t,x}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
+
+The model is over-parameterised. Therefore, the constraints
 \begin{equation}
-  \sum_{t=1}^{n}k_t=0, \qquad\text{and}\qquad \sum_{x=x_1}^{x_m}b_x=1
+  \sum_{t=1}^{n}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
 \end{equation}
 are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969].
-The estimates of $b_x$ and $k_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{x_i,t})-a_{x_i}]$, where $a_{x_i}$ is the sample mean of $\log(m_{x_i,t})$ over $t$.
-The log transformation introduces some bias, so the LC method adjusts $k_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $k_t$ is then extrapolated using a random walk with drift model, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
+The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\mu(x)]$, where $\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$.
+The log transformation introduces some bias, so the LC method adjusts $\beta_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
+The adjusted $\beta_t$ is then extrapolated using a random walk with drift model, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
 
@@
 
-When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge [@HBY13].
-In the product-ratio method, we apply the HU model to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
+When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
+In the product-ratio method [@HBY13], we apply the HU model to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
 That is, we define
@@
 \end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., $d$ in ARIMA($p,d,q$) constrained to $0<d<\frac{1}{2}$).
+where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$).
 It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge.
@@
 
-# Data {#sec:data}
-
-We use the same notation and similar procedures to construct data as in @HB08.
-The data used to construct population age structure included: age- and gender-specific birth and death numbers of each calendar year, age- and gender-specific population members on 1\ January of each year, and age- and gender-specific exposures to risk (i.e., the population of age $x$ at 30 June) for each year.
-The notations are as follows:
+## Stochastic population forecasting
+
+We follow the general procedure proposed in @HB08, except that we use the product-ratio method rather than the HU method for mortality and net-migration.
+
+The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
+Let
 \begin{align*}
-  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$}\\
-  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$}\\
-  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$}\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$}
+  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
+  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
+  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
+  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
 \end{align*}
 where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
-The years is denoted by $t=1,2,\dots,n$, and superscripts M and F denote male and female respectively.
+The year is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
 
@@
 
+A stochastic functional data model was applied to the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components into the future.
+
+We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
+From these models, sample paths are simulated for age-specific fertility rates, age- and sex-specific mortality rates and age- and sex-specific net migration.
+Then future population values are simulated using the demographic growth-balance equations.
+The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates.
+We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see @HB08 for the details).
+Hence, we can simulate $h$-step-ahead age- and sex-specific population numbers based on simulated births, deaths and net-migrants.
+
+This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a sample path of the age-specific population. Many simulated population paths were obtained in this way.
+
+It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores, and randomness from the Poisson distribution for births and deaths or the bootstrap for migrants.
+
+# Data {#sec:data}
+
 Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the @HMD for 1921--2018.
@@
 
-## Forecasting population age structure and OADR {#sec:forecasting}
-
-In this study, three steps were taken to simulate OADR associated with a specific pension age scheme.
-A stochastic functional data model was applied to five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components over the prediction horizon (which is 50 years in this study).
-Age- and gender-specific population paths over the prediction horizon were simulated using the demographic growth-balance equation.
-The Monte Carlo simulation method was used consistently in this research.
-Finally, calculation of OADR associated with a specific pension age scheme was performed by applying the OADR formula.
-Even though the process seems complicated, it is relatively easy to implement using \textit{R} [@Team18].
-The detailed explanation of each step is as follows.
-The corresponding R code is attached as a supplement.
-
-### Step 1 {-}
-
-The main procedure for forecasting the population age structure follows @HB08, except that the data are updated, and we incorporate the product-ratio method [@HBY13] to improve the accuracy of the forecast.
-
-, introduced in section \@ref(sec:HU), is applied to the mortality rate, fertility rate and net migration separately, based on the assumption that they behave independently.
-Therefore, to fit the model to historical fertility rates, let $y_t(x)$ in equation \eqref{eq:HU_1} denote the observed historical fertility data.
-
-### Step 2 {-}
-
-After simulating paths for age-specific fertility rate, age- and gender-specific mortality rate and age- and gender-specific net migration, future population value was simulated using the demographic growth-balance equations over the prediction horizon.
-The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates (see Hyndman and Booth, 2008 for the details of the functions).
-Hence, we can simulate $h$-step-ahead age- and gender-specific births and deaths based on simulated mortality and fertility rates.
-According to the demographic growth-balance equation, one-step-ahead net migrations, deaths, births and population in the last year were simulated, allowing for the generation of one-step-ahead population predictions by sex and age.
-This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a path of population.
-The process was repeated and simulated $i$ paths of population based on Monte Carlo simulation method were created (we set $i=1000$ in this research).
-It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores and randomness from the Poisson distribution.
-It should be noted that the simulated population will be an array with three dimensions: age, year and simulation.
-
-### Step 3 {-}
+## Forecasting OADR {#sec:forecasting}
 
@@
 Figures \@ref(fig:totalpopulationbyyears) and \@ref(fig:totalpopulationin2034) show the forecast results of population.
-Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by gender over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2038.
+Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by sex over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2038.
 Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 27 million by 2068.

### 2020-09-14 PensionAge.Rmd
Reorganized some material and rewrote some sections

@@
 
-## Population forecasting
+## Demographic growth-balance equations
+
+The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
+Let
+\begin{align*}
+  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
+  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
+  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
+  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
+\end{align*}
+where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
+The year is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
+
+We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
+\begin{align*}
+  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
+\end{align*}
+
+In addition, the net migration^[Net migration is the difference between immigration and emigration in a certain area during a specified time frame.] (denoted $G$) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
+The equations are expressed as:
+\begin{align*}
+  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
+  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
+  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
+\end{align*}
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
+The deaths are estimated using the standard life table approach of population projection.
+It should be noted that the estimated net migration includes errors in data recording.
+
+## Old-Age Dependency Ratio
+
+Using this notation, the OADR in year $t$ is given by
+\begin{equation}\label{eq:oadr}
+\text{OADR}_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
+\end{equation}
+where $a_t$ is the pension age and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$.
+This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.
+
+## Forecasting demographic components
 
@@
 \end{equation}
-where $m_{t}(x)$ is the central death rate (properly defined in Section \@ref(sec:data)) for age $x$ in year $t$.
+where $m_{t}(x)$ is the central death rate for age $x$ in year $t$.
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$\mu(x)$} and {$\phi(x)$}, and a time-varying index $\beta_{t}$.
@@
 
-## Product-ratio method
+### Product-ratio method {-}
 
@@
 
-## Stochastic population forecasting
-
-We follow the general procedure proposed in @HB08, except that we use the product-ratio method rather than the HU method for mortality and net-migration.
-
-The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
-Let
-\begin{align*}
-  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
-  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
-  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
-\end{align*}
-where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
-The year is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
-
-We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
-\begin{align*}
-  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
-\end{align*}
-
-In addition, the net migration^[Net migration is the difference between immigration and emigration in a certain area during a specified time frame.] (denoted $G$) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
-The equations are expressed as:
-\begin{align*}
-  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
-  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
-  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
-\end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
-The deaths are estimated using the standard life table approach of population projection.
-It should be noted that the estimated net migration includes errors in data recording.
-
-A stochastic functional data model was applied to the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates to simulate these five components into the future.
-
-We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
+## Forecasting OADR
+
+Following the general procedure proposed in @HB08, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
+
+We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration (whereas @HB08 used the HU method for all five components).
+
 From these models, sample paths are simulated for age-specific fertility rates, age- and sex-specific mortality rates and age- and sex-specific net migration.
@@
 
-This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a sample path of the age-specific population. Many simulated population paths were obtained in this way.
+This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a sample path of the age-specific population.
+Many simulated population paths were obtained in this way.
+For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.
 
@@
 
-# Data {#sec:data}
+# Results
+
+## Data
 
@@
 The start-year population for 2019 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the @ABS12.
+Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the @ABSBirths.
 Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
@@
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Second, fertility rates are only available from 1950, so the mortality rate was cut to fit the same period.
-
-## Forecasting OADR {#sec:forecasting}
-
-Even though the OADR is a simple function of the population age structure and pension age, the formula can't be directly applied to the simulated population array because the pension age changes over time.
-To overcome this problem, we assume that the pension age can only be adjusted at the beginning of a year for these calculations.
-Therefore, one pension age is applicable for a whole year and hence OADR is generated at the beginning of each year to show the trend.
-We will show the process of obtaining a one-step-ahead OADR (i.e., forecast of OADR in the year 2019), given a specific pension age.
-The same method can be applied to all years over the prediction horizon, given their corresponding pension age.
-Further, the fractional pension age causes practical issues in calculating OADR, since ages are recorded as integers.
-We will also show how this issue was handled in the example below.
-
-Suppose the pension age for $n+1$ is $a.r$ where $a$ is the integer and $r$ is the remainder of pension age.
-Recall that for $h=1$, we can express the simulated population paths as a matrix with age in the row and simulation in the column as follows:
-$$
-  \bm{p}_{n+1}=[p_{n+1,m,i}] =
-    \begin{bmatrix}
-       p_{1,1} & \cdots\cdots & p_{1,1000} \\
-      \vdots & \ddots & \vdots \\
-      p_{100^+,1} & \cdots\cdots &p_{100^+,1000}
-      \end{bmatrix}.
-$$
-When $r=0$, then the simulation of a population aged 15 to pension age is a subset of the above matrix from $15^{th}$ row to $a-1^{th}$ row, which is:
-\begin{equation}
-  \begin{bmatrix}
-    p_{15,1} & \cdots\cdots & p_{15,1000} \\
-    \vdots & \ddots & \vdots \\
-    p_{a-1,1} & \cdots\cdots &p_{a-1,1000}
-  \end{bmatrix}. \label{eq:population_mat}
-\end{equation}
-To calculate the total number of working-age, we take a column sum of the trimmed matrix \eqref{eq:population_mat}. The simulations of the total number of working-age become a vector:
-\begin{equation}
-  \bm{p}^{\text{work}}_{n+1} = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right] \label{eq:work}
-\end{equation}
-Using the same method, the simulations of the total number of aged pensioners in the population can be shown as:
-\begin{equation}
-  \bm{p}^{\text{aged}}_{n+1} = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]\label{eq:aged}
-\end{equation}
-
-When $r\neq0$, the vector of the total number of working-age population in \eqref{eq:work} is added, and the vector of the total number of aged population in \eqref{eq:aged} is subtracted with an adjustment:
-\begin{equation}
-  \text{adjustment}=0.r\times100\%[p_{a,1},p_{a,2},\dots,p_{a,1000}]
-\end{equation}
-This adjustment is based on the assumption that the birthday of the population is uniformly distributed over the year.
-Then, $r\times100\%$ of the population with a recorded integer age of $a$ at beginning of the year is actually younger than $a.r$, so they are still under the pension age.
-In other words, $(1-r\times100\%)$ of the population with recorded integer age $a$ at the beginning of the year is older than $a.r$, so they should be counted as the aged population.
-The simulation vectors of total work age population and total aged population should then be:
-\begin{align*}
-  \bm{p}^{\text{work}}_{n+1}
-    & = \left[p^{\text{work}}_{n+1,1},p^{\text{work}}_{n+1,2},\dots,p^{\text{work}}_{n+1,1000}\right]\\
-    & = \left[\sum_{m=15}^{a-1}p_{m,1},\sum_{m=15}^{a-1}p_{m,2},\dots,\sum_{m=15}^{a-1}p_{m,1000}\right]+0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]   \\
-  \bm{p}^{\text{aged}}_{n+1}
-    & = \left[p^{\text{aged}}_{n+1,1},p^{\text{aged}}_{n+1,2},\dots,p^{\text{aged}}_{n+1,1000}\right]\\
-    & = \left[\sum_{m=a}^{100^+}p_{m,1},\sum_{m=a}^{100^+}p_{m,2},\dots,\sum_{m=a}^{100^+}p_{m,1000}\right]-0.r\times100\%\left[p_{a,1},p_{a,2},\dots,p_{a,1000}\right]
-\end{align*}
-
-After the adjustment, we can generate simulation vectors of the one-step-ahead OADR by dividing every element of $\bm{p}^{\text{work}}_{n+1}$ by the corresponding element of $\bm{p}^{\text{aged}}_{n+1}$, i.e.:
-\begin{align*}
-  \bm{\text{OADR}}_{n+1} & = \left[\text{OADR}_{n+1,1},\text{OADR}_{n+1,2},\dots,\text{OADR}_{n+1,1000}\right]\\
-                  & = \left[\frac{p^{\text{work}}_{n+1,1}}{p^{\text{aged}}_{n+1,1}},\dots,\frac{p^{\text{work}}_{n+1,1000}}{p^{\text{aged}}_{n+1,1000}}\right]
-\end{align*}
-The average value of elements of $\bm{\text{OADR}}_{n+1}$ is the mean prediction of one-step-ahead OADR.
-
-The same algorithm is applied to the simulation matrix of the population age structure to obtain $h$-step-ahead simulation vectors of OADR for $h=1,2,\dots,H$, where $H=50$ for this study (i.e., a prediction horizon of 2019 to 2068).
-Simulations of OADR over a 50 year prediction horizon by the matrix is summarized below, with the forecast year in rows and simulation in the columns:
-$$
-  \bm{\text{OADR}}^{\text{forecast}}=\left[\text{OADR}_{h,i}\right] =
-  \begin{bmatrix}
-    \text{OADR}_{n+1,1} & \cdots\cdots & \text{OADR}_{n+1,1000} \\
-    \vdots & \ddots & \vdots \\
-    \text{OADR}_{n+50,1} & \cdots\cdots & \text{OADR}_{n+50,1000}
-  \end{bmatrix}.
-$$
-
-## Results
+Second, fertility rates are only available from 1950, so the mortality rates were also truncated to the same period.
 
@@
 
+## Component forecasts
+
 We use the fitted model of fertility rates as an example to interpret the results of fitted models.
-It should be noted that models fitted to product and ratio series are less likely to be interpreted in an economic sense.
-Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two estimated basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and first two estimated coefficients (i.e., estimated principal component scores $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
-The first term ($\widehat{\phi}_1(x)\times \widehat{\beta}_{t,1}$) accounts for the most variation in fertility, so a relatively sensible interpretation can be given to the first term.
-In the plot of the first coefficient, estimated historical first principal component scores $\widehat{\beta}_{t,1}$ are shown in black for 1950--2018.
-It captures the general trend of fertility change over time.
-It indicates a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom^[Between the years 1946 and 1964.] in Australia, resulting from the recovery from war and the Great Depression^[The Great Depression was a severe economic depression in the decade before World War II.].
+It should be noted that models fitted to product and ratio series are less able to be interpreted in an economic sense.
+Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and the first two principal component scores, $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
+The first term ($\widehat{\phi}_1(x) \widehat{\beta}_{t,1}$) accounts for the most variation in fertility.
+The first principal component scores $\widehat{\beta}_{t,1}$, shown in black for 1950--2018, display a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
+This increase of fertility is linked to the Post-World War II baby boom in Australia, resulting from the recovery from war and the Great Depression.
 The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
@@
 
-The first estimated basis function $\widehat{\phi}_1(x)$ measures the different effects of the trend over time across ages.
-It indicates the general pattern of fertility has little effect on females of age 15.
-This makes intuitive sense because most early pregnancies are accidental.
-Therefore, any of the previously discussed events has no effect on early pregnancies.
-In addition, there are two spikes in the first basic function, which suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-Furthermore, the blue line is the fitted value of future coefficients (i.e., $\widehat{\beta}_{n+h,1}$, for $h=1,2,\dots,50$) and the yellow shading shows their 80% pointwise prediction interval according to the fitted ARIMA model of first coefficients $\left\{\widehat{\beta}_{t,1}\right\}$.
-Other terms further explain variation that has not been captured by the first term, but less economic explanations can be given for them.
+The first basis function $\widehat{\phi}_1(x)$ measures the different effects of the time-trend across ages.
+It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception.
+The two "bumps" in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
+The second basis function largely concerns mothers aged over 30.
+The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80% pointwise prediction intervals shown as blue shaded regions.
+These forecasts are obtained using automatically selected ARIMA models.
+In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts and are much harder to interpret.
+
+Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.
+
+## Population forecasts
 

### 2020-09-15 PensionAge.Rmd
Revised Section 3

@@
 
-```{r changespension, echo=FALSE, fig.cap="Government's adjustments on pension age scheme.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
+```{r changespension, echo=FALSE, fig.cap="Australian pension age policies.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
 # Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
@@
   geom_line() +
-  ylab("Age of retirement") +
+  ylab("Minimum pension age") +
   scale_color_brewer(
@@
 The most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The approach of forecasting used in this study is similar to the @PC13.
-The Hyndman-Ullah method (2007) is used as a basic forecasting approach, which is a comprehensive extension of the Lee-Carter method.
-In addition, an adapted product-ratio method [@HBY13] is used to eliminate the potential long-term divergence between female and male mortality rates.
+The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
+In addition, the product-ratio method [@HBY13] is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
 
@@
 are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969].
-The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\mu(x)]$, where $\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$.
+The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\widehat\mu(x)]$, where $\widehat\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$.
 The log transformation introduces some bias, so the LC method adjusts $\beta_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $\beta_t$ is then extrapolated using a random walk with drift model, which is equivalent to an ARIMA ($0,1,0$) model with a drift parameter.
+The adjusted $\beta_t$ is then extrapolated using a random walk with drift model.
 
@@
 Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process.
-Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are determined by minimizing the Akaike Information Criterion [@forecastpackage], and the parameters are estimated using maximum likelihood estimation.
+Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are selected using the automated algorithm of @forecastpackage, and the parameters are estimated using maximum likelihood estimation.
 
@@
 When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
-In the product-ratio method [@HBY13], we apply the HU model to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
-That is, we define
+In the product-ratio method [@HBY13], the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
+That is, define
 \begin{align}
@@
 \end{align}
-Then, the HU method is applied to these two new variables instead of male and female series:
+Then, the HU method is applied to these two new variables:
 \begin{align*}
@@
 \end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with an ARIMA model while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA model (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$).
+where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$).
 It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge.
@@
 Following the general procedure proposed in @HB08, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
-
-We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration (whereas @HB08 used the HU method for all five components).
+We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
 
@@
 
-It should be noted that there are three types of randomness in the simulation: randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}), randomness from the ARIMA model fitted to principal component scores, and randomness from the Poisson distribution for births and deaths or the bootstrap for migrants.
+There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
 
@@
 Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
-First, the period between 1921--1950 has different mortality patterns from later years because of wars and epidemics [@HB08].
+First, the period between 1921--1950 has different mortality patterns from later years because of wars [@HB08].
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
@@
 
-We use the fitted model of fertility rates as an example to interpret the results of fitted models.
-It should be noted that models fitted to product and ratio series are less able to be interpreted in an economic sense.
-Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and the first two principal component scores, $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for fertility rates.
-The first term ($\widehat{\phi}_1(x) \widehat{\beta}_{t,1}$) accounts for the most variation in fertility.
+We illustrate the component model forecasts using fertility rates.
+Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and the first two principal component scores, $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for log fertility rates.
+The first term, $\widehat{\phi}_1(x) \widehat{\beta}_{t,1}$, accounts for `r round(fert.fit$varprop[1]*100,1)`% of the variation in the log fertility rates.
 The first principal component scores $\widehat{\beta}_{t,1}$, shown in black for 1950--2018, display a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
-This increase of fertility is linked to the Post-World War II baby boom in Australia, resulting from the recovery from war and the Great Depression.
-The dramatic decrease from 1960 was due to the availability of contraception pills in Australia.
-A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the law allowing abortion in some states in Australia.
+This increase of fertility is linked to the post-World War II baby boom, while the dramatic decrease from 1960 was due to the availability of contraception pills.
+A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the abortion laws in some states.
 
@@
 The two "bumps" in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-The second basis function largely concerns mothers aged over 30.
+The second basis function, accounting for `r round(fert.fit$varprop[2]*100,1)`% of the variation, largely concerns mothers aged over 30.
 The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80% pointwise prediction intervals shown as blue shaded regions.
 These forecasts are obtained using automatically selected ARIMA models.
-In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts and are much harder to interpret.
+In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for `r round(sum(fert.fit$varprop[3:6])*100,1)`% of the variation, and are much harder to interpret.
 
@@
 
-Figures \@ref(fig:totalpopulationbyyears) and \@ref(fig:totalpopulationin2034) show the forecast results of population.
-Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by sex over the prediction horizon, while Figure \@ref(fig:totalpopulationin2028) shows the forecast of population age structure in a specific year, 2038.
+Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by sex over the prediction horizon, while Figure \@ref(fig:totalpopulationin2038) shows the 20-year forecast of population age structure in 2038.
 Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 27 million by 2068.
-Since the fertility rate is expected to remain low, the possible reason for the significant increase in population size is net migration.
-We can also observe that the further the projected year is, the bigger the forecast variation of a population.
-This increase in variation shows that we have less relevant information for further apart prediction horizons.
 
@@
 ############### SIMULATION STEP #################
+if(file.exists("aus_sim.rds")) {
+  aus.sim <- readRDS("aus_sim.rds")
+} else {
   # This takes a while!
   set.seed(2020 - 05 - 02)
-nsim <- 20 # Change to 2000 or higher to get better estimates
+  nsim <- 2000 # Change to 2000 or higher to get better estimates
   aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)
-
+  saveRDS(aus.sim, "aus_sim.rds")
+}
+```
+
+```{r sim_tibbles, dependson='simulation'}
 # Combine simulation results into one tibble
@@
   Age = dimnames(aus.sim[[1]])[[1]],
-  Year = dimnames(aus.sim[[1]])[[2]],
+  Year = as.numeric(dimnames(aus.sim[[1]])[[2]]) + 1,
   Rep = dimnames(aus.sim[[1]])[[3]]
@@
   )
-# rm(aus.sim)
+
 # Combine simulations to create means and quantiles of future years
@@
 
-```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.
-The actual population from 1950 to 2019 is shown using circles.", fig.height=4, dependson='simulationresults'}
+```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4, dependson='simulationresults'}
 future_tot_pop <- aussim_df %>%
@@
 
-```{r totalpopulationin2034, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals.
+```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals.
 The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
@@
 
-Figure \@ref(fig:totalpopulationin2034) shows the mean and the 80% pointwise prediction interval of simulated population paths for the year 2038, along with the 2019 base population.
-It can be observed that the overall population size is expected to increase substantially.
-The uncertainty of the infant population is much higher than other ages, which reflects the higher forecast variation of fertility rates than mortality rates.
-The uncertainty of the young age population is mainly due to migration [@HB08].
-
-```{r OADRat65, fig.cap="Fifty-year forecasts of the OADR with the assumption of pension age equal to 65 for both sexes, along with 80% pointwise prediction interval.", dependson='simulationresults'}
+Figure \@ref(fig:totalpopulationin2038) shows the mean and the 80% pointwise prediction interval of simulated population paths for the year 2038 (a 20-year forecast), along with the 2019 base population.
+The uncertainty of the population below aged 20 is largely due to higher forecast variation of fertility rates compared to other components.
+
+Historical OADR values are shown in Figure \@ref(fig:OADRcurrent) for 1921--2019.
+The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07].
+The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2.
+We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise 6 months every two years until it reaches 70 in 2035.
+
+```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
+The actual OADRs for 1921--2019 are shown in black.", dependson='OADRcurrent'}
 OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
@@
   mutate(Policy = "Pension age 65")
-OADR.65 %>%
-  ggplot(aes(x = Year, y = OADR)) +
-  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  geom_line(col = "#0000aa", size = .75) +
-  geom_line(col = "black", size = .75, data = OADR_history) +
-  xlab("year") +
-  ylab("ratio") +
-  ggtitle("OADR forecasts with pension age=65")
-```
-
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green line) and equal to the pension age scheme with approved change (orange line) respectively, along with the desired OADR level in purple.
-The actual OADRs for 1921--2018 are shown in black.", dependson='OADRat65'}
 df <- bind_rows(
@@
   ggplot(aes(x = Year, y = OADR)) +
-  geom_hline(yintercept = 0.21, col = "gray") +
+  geom_hline(yintercept = 0.25, col = "gray") +
   geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy), alpha = 0.5) +
@@
 
-The analysis was performed by first generating an OADR associated with a fixed pension age of 65 and an OADR associated with pension age scheme with the approved change, gradually increasing the pension age from 65 to 67 by mid-2023.
-Even though the government might further increase the pension age in future, we kept the pension age at 67 from 2024 to see what would happen if no further action was taken.
-Figure \@ref(fig:OADRat65) shows the mean forecast and pointwise prediction interval of the OADR with a pension age of 65, along with the historical OADR for 1921--2018.
-A strong positive trend was observed, which indicates an increasing burden on the next working-age generation if the pension age is fixed at 65.
-This is consistent with the prediction by inter-generation reports in 2002 [@IGR02] and 2007 [@IGR07].
-According to former Australian Treasurer @Costello04, this could be a result of better health care and low fertility rates.
-These two reasons could be regarded as permanent change and therefore a persistent trend.
-In addition, there is a big jump from actual data to predicted data.
-This jump is possibly a result of the Baby Boomers’ retirement.
-Those born in 1946, the start of the baby boom, would begin retiring in 2011 when the pension age was 65.
-
-Figure \@ref(fig:OADRcurrent) presents a comparison of the mean forecast of OADR with the pension age equal to 65 and a pension age equal to the pension age scheme with the approved change, along with a comparison of both forecasts with the desired level of OADR, which has been set at 21%.
-It should be noted that OADR corresponding to pension age scheme with approved change is approaching the desired level, which suggests that the approved change does achieve the aim of providing an affordable financial burden, at least for a moment.
-However, once the pension age reaches 67, the OADR of the pension scheme with approved adjustment grows at the nearly same rate as the OADR of a pension age equal of 65.
+Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65.
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Therefore, Figure \@ref(fig:OADRcurrent) demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
-However, the questions of when the action needs to be taken and how much of an adjustment needs to be made remain to be answered.
-This answer will allow us to respond to the recent proposal of further increasing the pension age to 70 by 2035.
-
-## Evaluating forecast accuracy {#sec:accuracy}
-
-Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
-It is not valid to assess the model's fit in terms of historical data.
-We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
-Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
-
-The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
-Then we are allowed to repeat the test $n-H-k+1$ times, where $n$ is the number of total years of observation.
-The procedure is as follows:
-
-Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
-Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
-We repeat the following steps for $\omega=1,2,\dots,n-k-H+1$.
-Then, we can summarize the information into a matrix as follows:
-$$
-  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
-    \begin{bmatrix}
-      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,n-k-H+1} \\
-      \vdots          & \ddots       & \vdots \\
-      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,n-k-H+1}
-    \end{bmatrix}
-$$
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
-This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
-We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.
-
-n our sample, $n=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
-From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 21%.
-
-```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
-######## Run a rolling forecast origin
-t <- 2014 - 1950 + 1
-H <- 25 ## forecast horizon for test
-k <- 25 ## years of data required to make a forecast
-rolling_sim <- NULL
-for (i in seq(t - k - H))
-{
-  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
-  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
-  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
-  pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
-  mort.fit.s <- coherentfdm(ausmort.short)
-  mortfs <- forecast(mort.fit.s, H)
-  fert.fit.s <- fdm(ausfert.short)
-  # Fix problem
-  #  miss <- is.na(fert.fit.s$residuals$y)
-  #  fert.fit.s$residuals$y[miss] <- 0
-  # End fix
-  fertfs <- forecast(fert.fit.s, H)
-  mig.fit.s <- coherentfdm(ausmig.short)
-  migfs <- forecast(mig.fit.s, H)
-  aus.sim.s <- pop.sim(
-    mort = mortfs, fert = fertfs, mig = migfs,
-    firstyearpop = pop.short, N = 3
-  )
-  # Combine simulation results into one tibble
-  dimnames(aus.sim.s[["male"]]) <-
-    dimnames(aus.sim.s[["female"]]) <-
-    list(
-      Age = dimnames(aus.sim.s[[1]])[[1]],
-      Year = dimnames(aus.sim.s[[1]])[[2]],
-      Rep = dimnames(aus.sim.s[[1]])[[3]]
-    )
-  rolling_sim <- bind_rows(
-    rolling_sim,
-    as.tbl_cube(aus.sim.s[["male"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Male", id = i),
-    as.tbl_cube(aus.sim.s[["female"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Female", id = i)
-  )
-}
-```
-
-```{r rmseplot, dependson="rollingtest"}
-oadr_rolling_sim(
-  rolling_sim,
-  filter(pension_age, Policy == "Approved")
-) %>%
-  group_by(id) %>%
-  mutate(h = row_number()) %>%
-  ungroup() %>%
-  select(Year, h, OADR) %>%
-  rename(Forecast = OADR) %>%
-  left_join(OADR_history, by = "Year") %>%
-  mutate(e = OADR - Forecast) %>%
-  group_by(h) %>%
-  summarise(RMSE = sqrt(mean(e^2))) %>%
-  ggplot(aes(x = h, y = RMSE)) +
-  geom_point()
-```
-
-It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
-For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
-However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
+Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035.
+Figure \@ref(fig:OADRcurrent) demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
 
@@
 
-```{r optimal_pension, dependson="OADRat65"}
+```{r optimal_pension, dependson="OADRcurrent"}
 ### find the pension.age scheme with OADR closest to target
@@
 # Chosen target OADR
-target <- 0.22
+target <- 0.25
 
@@
 
-Table 1 shows the target pension age scheme, which is properly defined in section 3.2.2.
-It is assumed that it is impractical to change the pension age during 2011--2018, so the pension age has to be set at 65 for those years.
+Table 1 shows the target pension age scheme, which is properly defined in section ??.
 Figure \@ref(fig:OADRwithoptimal) provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
@@
 
-```{r pensionagetables2, dependson="OADRat65", message=FALSE}
+```{r pensionagetables2, dependson="OADRcurrent", message=FALSE}
 pension_age_optimal %>%
@@
 ```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018).
-The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRat65"}
+The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRcurrent"}
 ## plots of OADR with plausible pension age schemes
@@
 
-```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red).", dependson="OADRat65"}
+```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red).", dependson="OADRcurrent"}
 bind_rows(
@@
 ```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade.
-The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRat65"}
+The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRcurrent"}
 pension.fc <- structure(
@@
 ggplot() +
-  autolayer(pension.fc, series = "Pension age to give OADR=0.21") +
+  autolayer(pension.fc, series = "Pension age to give OADR=0.25") +
   autolayer(
@@
   xlab("Year") +
-  ylab("Age of retirement")
-```
-
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRat65"}
+  ylab("Minimum pension age")
+```
+
+```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRcurrent"}
 
@@
 ```{r OADR_realpensionage, fig.cap="The mean forecast of OADR associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRat65"}
+The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRcurrent"}
 ```
@@
 This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
+
+## Evaluating forecast accuracy {#sec:accuracy}
+
+Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
+It is not valid to assess the model's fit in terms of historical data.
+We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
+Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
+
+The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
+Then we are allowed to repeat the test $n-H-k+1$ times, where $n$ is the number of total years of observation.
+The procedure is as follows:
+
+Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
+Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
+We repeat the following steps for $\omega=1,2,\dots,n-k-H+1$.
+Then, we can summarize the information into a matrix as follows:
+$$
+  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
+    \begin{bmatrix}
+      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,n-k-H+1} \\
+      \vdots          & \ddots       & \vdots \\
+      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,n-k-H+1}
+    \end{bmatrix}
+$$
+where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
+This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
+We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.
+
+In our sample, $n=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
+The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
+From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
+Overall, the mean absolute error is small.
+For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 25%.
+
+```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
+######## Run a rolling forecast origin
+t <- 2014 - 1950 + 1
+H <- 25 ## forecast horizon for test
+k <- 25 ## years of data required to make a forecast
+rolling_sim <- NULL
+for (i in seq(t - k - H))
+{
+  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
+  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
+  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
+  pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
+  mort.fit.s <- coherentfdm(ausmort.short)
+  mortfs <- forecast(mort.fit.s, H)
+  fert.fit.s <- fdm(ausfert.short)
+  # Fix problem
+  #  miss <- is.na(fert.fit.s$residuals$y)
+  #  fert.fit.s$residuals$y[miss] <- 0
+  # End fix
+  fertfs <- forecast(fert.fit.s, H)
+  mig.fit.s <- coherentfdm(ausmig.short)
+  migfs <- forecast(mig.fit.s, H)
+  aus.sim.s <- pop.sim(
+    mort = mortfs, fert = fertfs, mig = migfs,
+    firstyearpop = pop.short, N = 3
+  )
+  # Combine simulation results into one tibble
+  dimnames(aus.sim.s[["male"]]) <-
+    dimnames(aus.sim.s[["female"]]) <-
+    list(
+      Age = dimnames(aus.sim.s[[1]])[[1]],
+      Year = dimnames(aus.sim.s[[1]])[[2]],
+      Rep = dimnames(aus.sim.s[[1]])[[3]]
+    )
+  rolling_sim <- bind_rows(
+    rolling_sim,
+    as.tbl_cube(aus.sim.s[["male"]] / 1e3, met_name = "Population") %>%
+      as_tibble() %>% mutate(Sex = "Male", id = i),
+    as.tbl_cube(aus.sim.s[["female"]] / 1e3, met_name = "Population") %>%
+      as_tibble() %>% mutate(Sex = "Female", id = i)
+  )
+}
+```
+
+```{r rmseplot, dependson="rollingtest"}
+oadr_rolling_sim(
+  rolling_sim,
+  filter(pension_age, Policy == "Approved")
+) %>%
+  group_by(id) %>%
+  mutate(h = row_number()) %>%
+  ungroup() %>%
+  select(Year, h, OADR) %>%
+  rename(Forecast = OADR) %>%
+  left_join(OADR_history, by = "Year") %>%
+  mutate(e = OADR - Forecast) %>%
+  group_by(h) %>%
+  summarise(RMSE = sqrt(mean(e^2))) %>%
+  ggplot(aes(x = h, y = RMSE)) +
+  geom_point()
+```
+
+It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
+For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
+However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
 

### 2020-09-17 PensionAge.Rmd
Refactored to use drake

@@
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-We apply these ideas to Australian historical demographic data and the results suggest that the pension age should be increased to 67 by 2021, 70 by 2032 and 75 by 2058 in order to maintain the old-age dependency ratio at the 2018 level, which is 21%.
-This approach can easily be extended to other target levels of the old-aged dependency ratio and other countries."
+Our results suggest that the Australian pension age should be increased to 68 by 2028 and 69 by 2034 in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
+Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
 keywords: "coherent forecasts, demographic components, functional time series model, pension and insurance"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
-library(dplyr)
-library(tidyr)
+knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = FALSE)
+
+# Set up drake plan
+source("_drake.R")
+
+# Run all code required
+drake::r_make()
+
+# Load results
+drake::loadd()
+
+# Load additional packages for graphs and tables
 library(ggplot2)
-library(demography)
 library(patchwork)
-source("functions-v4.R")
 ```
@@
 # History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
-pension_age <- tibble(
-  Year = 1920:2068,
-  Current = 65
-) %>%
-  mutate(
-    Proposed = pmin(70, Current + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
-    Approved = pmin(Proposed, 67),
-  ) %>%
-  pivot_longer(-Year, values_to = "Age", names_to = "Policy")
-
 pension_age %>%
-  filter(Year >= 2008, Year <= 2050) %>%
+  filter(Year >= 2014) %>%
   ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
@@
       palette = "Dark2",
-    breaks = c("Proposed", "Approved", "Current"),
-    labels = c("Proposed further change", "Approved change", "Pension age at 65")
+      breaks = c("Proposed", "Current", "Age65"),
+      labels = c("Proposed further change", "Current policy", "Pension age at 65")
     )
@@
 where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
-The year is denoted by $t=1,2,\dots,n$, and superscripts $M$ and $F$ denote male and female respectively.
+The year is denoted by $t=1,2,\dots,T$, and superscripts $M$ and $F$ denote male and female respectively.
 
@@
 \begin{equation}\label{eq:oadr}
-\text{OADR}_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
+O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
 \end{equation}
-where $a_t$ is the pension age and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$.
+where $a_t$ is the pension age in year $t$ and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$.
 This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.
@@
 \begin{equation}
-  \sum_{t=1}^{n}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
+  \sum_{t=1}^{T}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
 \end{equation}
@@
 
-By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{n+h}(x)$ are given by
+By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{T+h}(x)$ are given by
 \begin{equation}
-  \widehat{y}_{n+h\mid n}(x)=\widehat{s}_{n+h\mid n}(x) = \text{E}[\widehat{s}_{n+h\mid n}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{n+h\mid n,j},
+  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
 \end{equation}
-where $\widehat{\beta}_{n+h\mid n,j}$ denotes the $h$-step-ahead forecast of $\beta_{n+h\mid n,j}$.
+where $\widehat{\beta}_{T+h\mid T,j}$ denotes the $h$-step-ahead forecast of $\beta_{T+h\mid T,j}$.
 Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process.
@@
 \begin{align*}
-  m_{n+h\mid n}^{\text{M}}(x) & = p_{n+h\mid n}(x)r_{n+h\mid n}(x)\\
-  m_{n+h\mid n}^{\text{F}}(x) & = p_{n+h\mid n}(x)/r_{n+h\mid n}(x)
+  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
+  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
 \end{align*}
@@
 
-This simulation was repeated for years $t=n+1,\dots,n+h$ to obtain a sample path of the age-specific population.
+This simulation was repeated for years $t=T+1,\dots,T+h$ to obtain a sample path of the age-specific population.
 Many simulated population paths were obtained in this way.
@@
 
-```{r getdata, eval=FALSE}
-################################################
-################### DATA STEP ##################
-################################################
-
-# Get population data to 1 Jan 2019
-source("hmd.R") # File only stores username and password
-aus.pop <- hmd.pop(
-  country = "AUS", username = username, password = password,
-  label = "Australia"
-)
-aus.pop <- extract.ages(aus.pop, ages = 0:100)
-
-# Get mortality data to 2018
-aus.mort <- hmd.mx("AUS", username, password, "Australia")
-aus.mort <- aus.mort %>%
-  extract.ages(ages = 0:100, combine.upper = FALSE) %>%
-  extract.years(years = 1950:max(aus.mort$year))
-
-# Get fertility data for 1921-2006
-aus.fert <- addb::aus.fertility
-births <- aus.fert$rate$female * aus.fert$pop$female
-# Get latest fertility data from ABS (downloaded 30 April 2020)
-ausf <- readr::read_csv("FERTILITY_AGE_STATE_30042020143630412.csv") %>%
-  filter(
-    Region == "Australia",
-    Age %in% paste(15:49),
-  ) %>%
-  mutate(
-    Year = Time,
-    Age = as.numeric(Age)
-  ) %>%
-  select(Year, Age, Measure, Value)
-# Extract births and population values
-newbirths <- ausf %>%
-  filter(Measure == "Births") %>%
-  mutate(Value = Value * 1000) %>%
-  select(-Measure) %>%
-  pivot_wider(names_from = Year, values_from = Value) %>%
-  select(-Age) %>%
-  as.matrix()
-newpop <- ausf %>%
-  filter(Measure == "Female population") %>%
-  mutate(Value = Value) %>%
-  select(-Measure) %>%
-  pivot_wider(names_from = Year, values_from = Value) %>%
-  select(-Age) %>%
-  as.matrix()
-rownames(newbirths) <- rownames(newpop) <- 15:49
-
-# Use ABS data where available
-births <- cbind(births[, 1:54], newbirths)
-fpop <- cbind(aus.fert$pop$female[, 1:54], newpop)
-# Use populations in ausf rather than aus.pop to get the same rates
-aus.fert$rate$female <- births / fpop
-aus.fert$pop$female <- fpop
-aus.fert$year <- 1920 + seq(NCOL(births))
-
-# Compute migration data
-aus.mig <- netmigration(
-  mort = aus.mort, fert = aus.fert,
-  startyearpop = aus.pop, mfratio = 1.05
-)
-save(aus.fert, aus.mort, aus.mig, aus.pop, file = "ausdata.Rdata")
-rm(ausf, births, fpop, newbirths, newpop)
-```
-
-```{r maketibble}
-load("ausdata.Rdata")
-
-auspop_df <- bind_rows(
-  as_tibble(aus.pop$pop$male / 1000) %>%
-    mutate(
-      Age = aus.pop$age,
-      Sex = "Male"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-  as_tibble(aus.pop$pop$female / 1000) %>%
-    mutate(
-      Age = aus.pop$age,
-      Sex = "Female"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-)
-```
-
-```{r smoothing}
-################################################
-################ SMOOTHING STEP ################
-################################################
-
-ausmort.sm <- smooth.demogdata(aus.mort, obs.var = "theoretical")
-ausfert.sm <- smooth.demogdata(aus.fert, obs.var = "theoretical")
-ausmig.sm <- smooth.demogdata(aus.mig)
-```
-
-```{r models, dependson='smoothing'}
-################################################
-################ MODELLING STEP ################
-################################################
-
-# MORTALITY
-mort.fit <- coherentfdm(ausmort.sm)
-mortf <- forecast(mort.fit, h = 50)
-
-# FERTILITY
-fert.fit <- fdm(ausfert.sm)
-fertf <- forecast(fert.fit, h = 50)
-
-# MIGRATION
-mig.fit <- coherentfdm(ausmig.sm)
-migf <- forecast(mig.fit, h = 50)
-```
-
 ## Component forecasts
@@
 
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", dependson='models', message=FALSE}
-autoplot(fertf)
+```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", message=FALSE}
+autoplot.fmforecast(fertf)
 ```
@@
 
-```{r simulation, dependson='models'}
-############### SIMULATION STEP #################
-if(file.exists("aus_sim.rds")) {
-  aus.sim <- readRDS("aus_sim.rds")
-} else {
-  # This takes a while!
-  set.seed(2020 - 05 - 02)
-  nsim <- 2000 # Change to 2000 or higher to get better estimates
-  aus.sim <- pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = nsim)
-  saveRDS(aus.sim, "aus_sim.rds")
-}
-```
-
-```{r sim_tibbles, dependson='simulation'}
-# Combine simulation results into one tibble
-dimnames(aus.sim[["male"]]) <- dimnames(aus.sim[["female"]]) <- list(
-  Age = dimnames(aus.sim[[1]])[[1]],
-  Year = as.numeric(dimnames(aus.sim[[1]])[[2]]) + 1,
-  Rep = dimnames(aus.sim[[1]])[[3]]
-)
-aussim_df <- bind_rows(
-    as.tbl_cube(aus.sim[["male"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Male"),
-    as.tbl_cube(aus.sim[["female"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Female")
-  )
-
-# Combine simulations to create means and quantiles of future years
-future_pop <- aussim_df %>%
-  group_by(Sex, Age, Year) %>%
-  summarise(
-    Mean = mean(Population),
-    Lower = quantile(Population, prob = 0.1),
-    Upper = quantile(Population, prob = 0.9)
-  ) %>%
-  ungroup()
-# Historical data as a tibble
-history_pop <- bind_rows(
-  as_tibble(aus.pop$pop$male / 1000) %>%
-    mutate(
-      Age = aus.pop$age,
-      Sex = "Male"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-  as_tibble(aus.pop$pop$female / 1000) %>%
-    mutate(
-      Age = aus.pop$age,
-      Sex = "Female"
-    ) %>%
-    pivot_longer(c(-Age, -Sex), names_to = "Year", values_to = "Population"),
-) %>%
-  mutate(Year = as.numeric(Year))
-```
-
-```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4, dependson='simulationresults'}
-future_tot_pop <- aussim_df %>%
-  group_by(Rep, Sex, Year) %>%
-  summarise(Population = sum(Population) / 1e3) %>%
-  group_by(Sex, Year) %>%
-  summarise(
-    Mean = mean(Population),
-    Median = median(Population),
-    Lo95 = quantile(Population, prob = 0.025),
-    Up95 = quantile(Population, prob = 0.975),
-    Lo80 = quantile(Population, prob = 0.1),
-    Up80 = quantile(Population, prob = 0.9)
-  ) %>%
-  ungroup()
+```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4}
 history_pop %>%
@@
 
-```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals.
-The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE, dependson='simulationresults'}
-pyramid <- function(history, future) {
-  data <- bind_rows(history, future)
-  p_male <- data %>%
-    filter(Sex == "Male") %>%
-    ggplot(aes(x = Age, y = Population, group = Year)) +
-    labs(y = "Population ('000)") +
-    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
-    geom_line(linetype = 2) +
-    geom_line(aes(y = Mean), col = "#0000cc") +
-    coord_flip() +
-    scale_y_reverse(expand = c(0.012, 0.012)) +
-    scale_x_continuous(expand = c(0.012, 0.012)) +
-    facet_grid(. ~ Sex)
-  p_female <- data %>%
-    filter(Sex == "Female") %>%
-    ggplot(aes(x = Age, y = Population, group = Year)) +
-    labs(y = "Population ('000)") +
-    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
-    geom_line(linetype = 2) +
-    geom_line(aes(y = Mean), col = "#0000cc") +
-    coord_flip() +
-    scale_y_continuous(expand = c(0.012, 0.012)) +
-    theme(
-      axis.title.y.left = element_blank(),
-      axis.text.y.left = element_blank(),
-      axis.ticks.y.left = element_blank()
-    ) +
-    scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
-    facet_grid(. ~ Sex)
-
-  (p_male | p_female)
-}
+```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE}
 pyramid(
@@
 
-Historical OADR values are shown in Figure \@ref(fig:OADRcurrent) for 1921--2019.
+Historical OADR values are shown in black in Figure \@ref(fig:OADRcurrent) for 1921--2019.
 The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07].
 The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2.
-We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise 6 months every two years until it reaches 70 in 2035.
+We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.
 
 ```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
-The actual OADRs for 1921--2019 are shown in black.", dependson='OADRcurrent'}
-OADR_history <- oadr(history_pop, filter(pension_age, Policy == "Current"))
-OADR.65 <- oadr_sim(aussim_df, filter(pension_age, Policy == "Current")) %>%
-  mutate(Policy = "Pension age 65")
-df <- bind_rows(
-  OADR.65,
-  oadr_sim(aussim_df, filter(pension_age, Policy == "Approved")) %>%
-    mutate(Policy = "Current policy"),
-  oadr_sim(aussim_df, filter(pension_age, Policy == "Proposed")) %>%
-    mutate(Policy = "Proposed policy")
-) %>%
-  mutate(Policy = factor(Policy,
-    levels = c("Pension age 65", "Current policy", "Proposed policy")
-  ))
-df %>%
+The actual OADRs for 1921--2019 are shown in black."}
+OADR_future %>%
   ggplot(aes(x = Year, y = OADR)) +
-  geom_hline(yintercept = 0.25, col = "gray") +
-  geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy), alpha = 0.5) +
+    geom_hline(yintercept = target, col = "gray") +
+    geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy),
+      alpha = 0.5) +
     geom_line(aes(col = Policy, group = Policy), size = .75) +
@@
 
-# Finding the target pension age scheme {#sec:target}
+# Sustainable pension age scheme
 
-The goal of this research is to keep the pension age low, as long as OADR is lower than or equal to the desired OADR level.
-According to the formula of OADR, OADR at a given time can be written as a function of pension age, when the population age structure is given.
-Suppose we denote pension age (PA) schemes over the prediction horizon by $\bm{\text{PA}}=[\text{PA}_{n+1}, \text{PA}_{n+2},\dots,\text{PA}_{n+H}]$.
-The OADR function of pension age over the prediction horizon is denoted as $\text{OADR}_h(\text{PA}_{n+h})$ for $h=1,2,\dots,H$.
-There is a negative relationship between pension age and OADR.
-The negative relationship implies that the higher the pension age, the lower the OADR.
-Therefore, our goal becomes finding the minimum pension age which has an OADR lower than desired OADR level.
-Several practical issues need to be considered to achieve this goal.
-First, only simulated forecasting values of future OADR are available, so it is assumed that the mean value of the simulated OADR is a good estimate of true underlying OADR.
-Second, pension age cannot be increased by more than one within a year or decreased because either one of the two actions will force some retirees back to the workforce, which is unreasonable in practical applications.
-Therefore, the target pension age scheme $\bm{\text{PA}}^{\text{target}}$ can be defined in the following way:
-for $h=1,2,\dots,H$
-$$
-  \text{minimise~} \text{PA}_{n+h}  \text{~such that~} \text{OADR}_h(\text{PA}_{n+h})\leq \text{OADR}^{\text{desired}}
-$$
-\begin{align*}
-  \text{subject to the constraint~} 0\leq \text{PA}_{n+h}-\text{PA}_{n+h-1}\leq 1
-\end{align*}
-In order to achieve this maximization subject to constraint, these calculations assume that the adjustment unit of pension age is one month for practical convenience.
-It is also supposed that the set starting value of pension age is at 65 for all years\footnote{Even though the pension age for males and females is 65.5 in mid-2017, the same pension age for males and females was set to simplify the calculations.
-This simplification is reasonable because the pension age will be same in mid-2017 onward}, which is:
-\begin{align*}
-  \bm{\text{PA}}=\left[\text{PA}_{n+1},\text{PA}_{n+2},\dots,\text{PA}_{n+H}\right] = \left[65,65,\dots,65\right]
-\end{align*}
-We take the following algorithm:
-For $h=1,2,\dots,H$, we keep increasing pension age vector $[\text{PA}_{n+h},\text{PA}_{n+h+1},\dots,\text{PA}_{n+H}]$ by a month at a time, unless we find that
-\begin{align*}
-  \text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})> \text{OADR}^{\text{desired}} \quad \text{~or~}\quad  \text{PA}_{n+h}-\text{PA}_{n+h-1}\geq 1
-\end{align*}
-where $\text{OADR}^{\text{mean}}_h(\text{PA}_{n+h})$ is the mean value of $h$-step-ahead forecast of OADR with a pension age at the time $n+h$ equal to $\text{PA}_{n+h}$.
+Our aim is to determine a pension age scheme that would lead to the OADR being below a desired threshold, thus imposing a sustainability constraint.
 
-In addition to finding the target pension age based on the mean value of OADR, the aim is to find plausible pension age schemes that could give the desired OADR level.
-To be more specific, "plausible", means finding a range of pension age schemes that could lead to the desired OADR, contained by 80% prediction intervals of simulated OADR.
-Because of the monotonic relationship between pension age and OADR, we only need to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
+Let $a_t$ denote the pension age in year $t$, and we denote a pension age scheme over the prediction horizon by $\bm{P}=[a_{T+1},\dots,a_{T+H}]'$, with the corresponding OADR values given by $O_{T+1},\dots,O_{T+H}$.
+Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.
+We impose the constraint $0 \le a_t - a_{t-1} < 1$ to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension.
+We also assume that the adjustment unit of the pension age is one month, for easier implementation.
+
+## Finding the target pension age scheme {#sec:target}
+
+Let $O^*$ denote the desired OADR threshold.
+Because we do not observe the population in future years, we must estimate $O_{T+h}$ from the simulated populations.
+Then we compute the pension age scheme $\bm{P}$ using the following algorithm.
+Starting with $h=1$:
+
+  1. Set $a_{T+h}=a_{T+h-1}$.
+  2.
+Increment $a_{T+h}$ by one-month intervals until either $\widehat{O}_{T+h|T} > O^*$ or $a_{T+1} - a_{T}=$ 1 month, where $\widehat{O}_{T+h|T}$ denotes the mean of the simulated $O_{T+h|T}$ values.
+
+We repeat these steps for $h=2,\dots,H$.
+
+In addition to finding the target pension age based on the mean value of OADR, we also find "plausible" pension age schemes that could give the desired OADR level.
+Specifically, we find a range of pension age schemes for which $O^*$ is contained within the 80% prediction intervals of the simulated $O_{T+H|T}$ values.
+Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
 Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as a 80% confidence interval of pension age scheme where we are 80% sure that there will be the desired outcome.
-In other words, any pension age scheme outside the range is undesirable to use, because we are 80% certain that the corresponding OADR will deviate from the desired level of OADR.
+The range of plausible pension age schemes can be thought of as an 80% confidence interval of pension age schemes where we are 80% sure that they will give the desired outcome.
 
-The algorithm to find the upper and lower boundary of plausible pension age schemes is similar to the algorithm to find the target pension age scheme, except that the mean value of OADR is replaced by the boundary of the 80% prediction interval.
-Mean is replaced by the upper (lower) limit of the 80% prediction interval to find the upper (lower) boundary for pension age schemes.
+The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but mean of $O_{T+H|T}$ is replaced by the 10% and 90% quantiles.
 
-## Plausible pension age schemes
+```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade.
+The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009."}
+pension.fc <- structure(
+  list(
+    mean = ts(pension_age_optimal$Age, start = min(pension_age_optimal$Year)),
+    lower = ts(as.matrix(pension_age_lower$Age), start = min(pension_age_optimal$Year)),
+    upper = ts(as.matrix(pension_age_upper$Age), start = min(pension_age_optimal$Year)),
+    level = 80
+  ),
+  class = "forecast"
+)
+ggplot() +
+  autolayer(pension.fc, series = paste("Pension age to give OADR =", target)) +
+  autolayer(
+    ts(pension_age %>% filter(Policy == "Current", Year >= 1995) %>% pull(Age),
+       start = 1995),
+    series = "Approved change"
+  ) +
+  autolayer(
+    ts(pension_age %>% filter(Policy == "Age65", Year >= 1995) %>% pull(Age),
+      start = 1995),
+    series = "Pension age at 65"
+  ) +
+  xlab("Year") +
+  ylab("Minimum pension age")
+```
 
-```{r optimal_pension, dependson="OADRcurrent"}
-### find the pension.age scheme with OADR closest to target
-### find upper boundary of pension ages whose OADR PI contains target
-### find Lower boundary of pension ages whose OADR PI contains target
-### Constrained such that solution is in minimum jumps of 1 month
-### and the pension age can't change until 2023
+```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018).
+The 80% prediction interval of the forecast of OADR is shown as blue shading."}
+## plots of OADR with plausible pension age schemes
+OADR_optimal %>%
+  ggplot(aes(x = Year)) +
+    geom_hline(yintercept = target, col = "red") +
+    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
+    geom_line(aes(y = OADR), col = "#0000cc") +
+    geom_line(data = OADR_history, aes(y = OADR)) +
+    ggtitle("OADR forecast estimates for optimal pension ages") +
+    ylab("Old age dependency ratio")
+```
 
-# Chosen target OADR
-target <- 0.25
-
-# Lower bound (starting at age 65)
-pension_age_lower <- pension_age %>%
-  filter(Policy == "Current", Year >= 2019) %>%
-  select(-Policy)
-for (i in seq(5, 50)) {
-  current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
-  while ((current > target) &
-    (max(diff(pension_age_lower$Age[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension_age_lower$Age[i:50] <- pension_age_lower$Age[i:50] + 1 / 12
-    current <- oadr_sim(aussim_df, pension_age_lower)$Lo[i]
-  }
-}
-# Mean (start at lower bound)
-pension_age_optimal <- pension_age_lower
-for (i in seq(5, 50)) {
-  current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
-  while ((current > target) &
-    (max(diff(pension_age_optimal$Age[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension_age_optimal$Age[i:50] <- pension_age_optimal$Age[i:50] + 1 / 12
-    current <- oadr_sim(aussim_df, pension_age_optimal)$OADR[i]
-  }
-}
-# Upper bound (start at mean)
-pension_age_upper <- pension_age_optimal
-for (i in seq(5, 50)) {
-  current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
-  while ((current > target) &
-    (max(diff(pension_age_upper$Age[(i - 1):50])) <= (1 - 1 / 12))) {
-    pension_age_upper$Age[i:50] <- pension_age_upper$Age[i:50] + 1 / 12
-    current <- oadr_sim(aussim_df, pension_age_upper)$Hi[i]
-  }
-}
-# Final results
-OADR_optimal <- oadr_sim(aussim_df, pension_age_optimal)
-OADR_lower <- oadr_sim(aussim_df, pension_age_lower)
-OADR_upper <- oadr_sim(aussim_df, pension_age_upper)
-pension_age_optimal <- pension_age_optimal %>%
-  mutate(
-    Lo80 = pension_age_lower$Age,
-    Hi80 = pension_age_upper$Age
-  )
+```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red)."}
+bind_rows(
+    OADR_upper %>% mutate(Series = "Upper boundary"),
+    OADR_lower %>% mutate(Series = "Lower boundary"),
+  ) %>%
+  ggplot(aes(x = Year)) +
+    geom_hline(yintercept = target, col = "red") +
+    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
+    geom_line(aes(y = OADR), col = "#0000cc") +
+    geom_line(data = OADR_history, aes(y = OADR)) +
+    facet_grid(. ~ Series) +
+    ggtitle("OADR forecasts for boundary pension age schemes") +
+    ylab("Old age dependency ratio")
 ```
@@
 
-```{r pensionagetables, dependson="optimal_pension", message=FALSE}
+```{r pensionagetables, message=FALSE, eval=FALSE}
 pension_age_optimal %>%
@@
     Agestring = paste0(
-      trunc(Age), "Y",
-      if_else(Month > 0, paste0("+", Month, "M"), "")
-    ),
+      trunc(Age), "Y", if_else(Month > 0, paste0("+", Month, "M"), "")),
     Column = trunc((Year - 2019) / 10) + 1,
@@
   pivot_wider(names_from = Column, values_from = data) %>%
-  unnest(cols = paste(1:5), names_repair = "unique") %>%
+  unnest(cols = c(`1`, `2`, `3`, `4`), names_repair = "unique") %>%
   knitr::kable(
     format = "latex",
-    col.names = rep(c("Year", "Age"), 5),
+    col.names = rep(c("Year", "Age"), 4),
     booktabs = TRUE,
@@
 
-```{r pensionagetables2, dependson="OADRcurrent", message=FALSE}
+```{r pensionagetables2, message=FALSE, eval=FALSE}
 pension_age_optimal %>%
@@
 
-```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018).
-The 80% prediction interval of the forecast of OADR is shown as blue shading.", dependson="OADRcurrent"}
-## plots of OADR with plausible pension age schemes
-OADR_optimal %>%
-  ggplot(aes(x = Year)) +
-  geom_hline(yintercept = target, col = "red") +
-  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  geom_line(aes(y = OADR), col = "#0000cc") +
-  geom_line(data = OADR_history, aes(y = OADR)) +
-  ggtitle("OADR forecast estimates for optimal pension ages") +
-  ylab("Old age dependency ratio")
-```
-
-```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red).", dependson="OADRcurrent"}
-bind_rows(
-  OADR_upper %>% mutate(Series = "Upper boundary"),
-  OADR_lower %>% mutate(Series = "Lower boundary"),
-) %>%
-  ggplot(aes(x = Year)) +
-  geom_hline(yintercept = target, col = "red") +
-  geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-  geom_line(aes(y = OADR), col = "#0000cc") +
-  geom_line(data = OADR_history, aes(y = OADR)) +
-  facet_grid(. ~ Series) +
-  ggtitle("OADR forecasts for boundary pension age schemes") +
-  ylab("Old age dependency ratio")
-```
-
-```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade.
-The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009.", dependson="OADRcurrent"}
-pension.fc <- structure(
-  list(
-    mean = ts(pension_age_optimal$Age, start = min(pension_age_optimal$Year)),
-    lower = ts(pension_age_optimal$Lo80, start = min(pension_age_optimal$Year)),
-    upper = ts(pension_age_optimal$Hi80, start = min(pension_age_optimal$Year)),
-    level = 80
-  ),
-  class = "forecast"
-)
-ggplot() +
-  autolayer(pension.fc, series = "Pension age to give OADR=0.25") +
-  autolayer(
-    ts(pension_age %>% filter(Policy == "Approved", Year >= 1995) %>% pull(Age),
-      start = 1995
-    ),
-    series = "Approved change"
-  ) +
-  autolayer(
-    ts(pension_age %>% filter(Policy == "Current", Year >= 1995) %>% pull(Age),
-      start = 1995
-    ),
-    series = "Pension age at 65"
-  ) +
-  xlab("Year") +
-  ylab("Minimum pension age")
-```
-
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade.", dependson="OADRcurrent"}
+```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade."}
 
@@
 ```{r OADR_realpensionage, fig.cap="The mean forecast of OADR associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading.", dependson="OADRcurrent"}
+The 80% prediction interval of the forecast of OADR is shown as shading."}
 ```
@@
 This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
-
-## Evaluating forecast accuracy {#sec:accuracy}
-
-Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
-It is not valid to assess the model's fit in terms of historical data.
-We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
-Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
-
-The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
-Then we are allowed to repeat the test $n-H-k+1$ times, where $n$ is the number of total years of observation.
-The procedure is as follows:
-
-Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
-Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
-We repeat the following steps for $\omega=1,2,\dots,n-k-H+1$.
-Then, we can summarize the information into a matrix as follows:
-$$
-  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
-    \begin{bmatrix}
-      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,n-k-H+1} \\
-      \vdots          & \ddots       & \vdots \\
-      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,n-k-H+1}
-    \end{bmatrix}
-$$
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
-This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
-We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.
-
-In our sample, $n=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
-From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 25%.
-
-```{r rollingtest, fig.cap="The mean absolute error of $h$-step-ahead forecast for $h=1,2,\\dots,25$.", warning=FALSE, message=FALSE, dependson='simulationresults'}
-######## Run a rolling forecast origin
-t <- 2014 - 1950 + 1
-H <- 25 ## forecast horizon for test
-k <- 25 ## years of data required to make a forecast
-rolling_sim <- NULL
-for (i in seq(t - k - H))
-{
-  ausmort.short <- extract.years(ausmort.sm, years = 1949 + i + (0:(k - 1)))
-  ausfert.short <- extract.years(ausfert.sm, years = 1949 + i + (0:(k - 1)))
-  ausmig.short <- extract.years(ausmig.sm, years = 1949 + i + (0:(k - 1)))
-  pop.short <- extract.years(aus.pop, years = 1949 + i + (0:k))
-  mort.fit.s <- coherentfdm(ausmort.short)
-  mortfs <- forecast(mort.fit.s, H)
-  fert.fit.s <- fdm(ausfert.short)
-  # Fix problem
-  #  miss <- is.na(fert.fit.s$residuals$y)
-  #  fert.fit.s$residuals$y[miss] <- 0
-  # End fix
-  fertfs <- forecast(fert.fit.s, H)
-  mig.fit.s <- coherentfdm(ausmig.short)
-  migfs <- forecast(mig.fit.s, H)
-  aus.sim.s <- pop.sim(
-    mort = mortfs, fert = fertfs, mig = migfs,
-    firstyearpop = pop.short, N = 3
-  )
-  # Combine simulation results into one tibble
-  dimnames(aus.sim.s[["male"]]) <-
-    dimnames(aus.sim.s[["female"]]) <-
-    list(
-      Age = dimnames(aus.sim.s[[1]])[[1]],
-      Year = dimnames(aus.sim.s[[1]])[[2]],
-      Rep = dimnames(aus.sim.s[[1]])[[3]]
-    )
-  rolling_sim <- bind_rows(
-    rolling_sim,
-    as.tbl_cube(aus.sim.s[["male"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Male", id = i),
-    as.tbl_cube(aus.sim.s[["female"]] / 1e3, met_name = "Population") %>%
-      as_tibble() %>% mutate(Sex = "Female", id = i)
-  )
-}
-```
-
-```{r rmseplot, dependson="rollingtest"}
-oadr_rolling_sim(
-  rolling_sim,
-  filter(pension_age, Policy == "Approved")
-) %>%
-  group_by(id) %>%
-  mutate(h = row_number()) %>%
-  ungroup() %>%
-  select(Year, h, OADR) %>%
-  rename(Forecast = OADR) %>%
-  left_join(OADR_history, by = "Year") %>%
-  mutate(e = OADR - Forecast) %>%
-  group_by(h) %>%
-  summarise(RMSE = sqrt(mean(e^2))) %>%
-  ggplot(aes(x = h, y = RMSE)) +
-  geom_point()
-```
-
-It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
-For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
-However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
 
@@
 
-### Colophon {-}
+# Appendix: Evaluating forecast accuracy {#sec:accuracy}
 
-This report was generated on `r Sys.time()`.
+Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
+It is not valid to assess the model's fit in terms of historical data.
+We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
+Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
 
-The current Git commit details are:
+The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
+Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
+Then we are allowed to repeat the test $T-H-k+1$ times, where $T$ is the number of total years of observation.
+The procedure is as follows:
 
-```{r}
-## Which commit is this file at?
-git2r::repository(here::here())
+Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
+Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
+We repeat the following steps for $\omega=1,2,\dots,T-k-H+1$.
+Then, we can summarize the information into a matrix as follows:
+$$
+  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
+    \begin{bmatrix}
+      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,T-k-H+1} \\
+      \vdots          & \ddots       & \vdots \\
+      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,T-k-H+1}
+    \end{bmatrix}
+$$
+where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
+This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
+We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.
+
+In our sample, $T=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
+The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
+From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
+Overall, the mean absolute error is small.
+For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 25%.
+
+```{r rmseplot}
+oadr_rolling_sim %>%
+  group_by(id) %>%
+  mutate(h = row_number()) %>%
+  ungroup() %>%
+  select(Year, h, OADR) %>%
+  rename(Forecast = OADR) %>%
+  left_join(OADR_history, by = "Year") %>%
+  mutate(e = OADR - Forecast) %>%
+  group_by(h) %>%
+  summarise(RMSE = sqrt(mean(e^2))) %>%
+  ggplot(aes(x = h, y = RMSE)) +
+    geom_point()
 ```
 
-We used the following computational environment and dependencies:
-
-```{r colophon, cache=FALSE}
-options(width = 100)
-## Which R packages and versions?
-devtools::session_info()
-```
-
-\newpage
+It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
+For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
+However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.

### 2020-09-17 R/autoplot.fmforecast.R

@@ -1,0 +1,28 @@
+# Autoplot for fmforecast objects
+autoplot.fmforecast <- function(data) {
+  require(latex2exp)
+  p1 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 1])) +
+    geom_line() +
+    xlab("Age (x)") +
+    ylab(TeX("$\\mu(x)"))
+  p2 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 2])) +
+    geom_line() +
+    xlab("Age (x)") +
+    ylab(TeX("$\\phi_1(x)$"))
+  p3 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 3])) +
+    geom_line() +
+    xlab("Age (x)") +
+    ylab(TeX("$\\phi_2(x)$"))
+  # Fix bug in fertf output
+  for(i in 2:3) {
+    data$coeff[[i]]$lower <- ts(as.matrix(data$coeff[[i]]$lower))
+    data$coeff[[i]]$upper <- ts(as.matrix(data$coeff[[i]]$upper))
+    tsp(data$coeff[[i]]$lower) <- tsp(data$coeff[[i]]$upper) <- tsp(data$coeff[[i]]$mean)
+  }
+  p4 <- autoplot(data$coeff[[2]]) +
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{1,t}$"))
+  p5 <- autoplot(data$coeff[[3]]) +
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{2,t}$"))
+
+  print((p1 | p2 | p3) / (plot_spacer() | p4 | p5))
+}

### 2020-09-17 R/oadr_future.R

@@ -1,0 +1,13 @@
+estimate_oadr_future <- function(sim, pension_age) {
+  bind_rows(
+    oadr_sim(sim, filter(pension_age, Policy == "Age65")) %>%
+      mutate(Policy = "Pension age 65"),
+    oadr_sim(sim, filter(pension_age, Policy == "Current")) %>%
+      mutate(Policy = "Current policy"),
+    oadr_sim(sim, filter(pension_age, Policy == "Proposed")) %>%
+      mutate(Policy = "Proposed policy")
+  ) %>%
+  mutate(Policy = factor(Policy,
+                         levels = c("Pension age 65", "Current policy", "Proposed policy"))
+  )
+}

### 2020-09-17 R/plan.R

@@ -1,0 +1,128 @@
+the_plan <-
+  drake_plan(
+
+  ## Pension age schemes
+  pension_age = tibble(Year = 1920:2050, Age65 = 65) %>%
+    mutate(
+      Proposed = pmin(70, Age65 + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
+      Current = pmin(Proposed, 67),
+    ) %>%
+    pivot_longer(-Year, values_to = "Age", names_to = "Policy"),
+
+  # Get population data to 1 Jan 2019
+  aus.pop = hmd.pop(country = "AUS",
+                    username = username,
+                    password = password,
+                    label = "Australia") %>%
+      extract.ages(ages = 0:100),
+
+  # Get mortality data to 2018
+  aus.mort = hmd.mx("AUS", username, password, "Australia") %>%
+      extract.ages(ages = 0:100, combine.upper = FALSE) %>%
+      extract.years(years = 1950:2100),
+
+  # Get fertility data to 2018
+  abs_fertility_file = "./data/FERTILITY_AGE_STATE_30042020143630412.csv",
+  aus.fert = get_aus_fert(abs_fertility_file),
+
+  # Compute migration data
+  aus.mig = netmigration(mort = aus.mort, fert = aus.fert,
+    startyearpop = aus.pop, mfratio = 1.05),
+
+  # Population data frame
+  auspop_df = aus_pop_df(aus.pop),
+
+  # SMOOTHING
+  ausmort.sm = smooth.demogdata(aus.mort, obs.var = "theoretical"),
+  ausfert.sm = smooth.demogdata(aus.fert, obs.var = "theoretical"),
+  ausmig.sm = smooth.demogdata(aus.mig),
+
+  # MORTALITY model
+  mort.fit = coherentfdm(ausmort.sm),
+  mortf = forecast(mort.fit, h = 33),
+
+  # FERTILITY model
+  fert.fit = fdm(ausfert.sm),
+  fertf = forecast(fert.fit, h = 33),
+
+  # MIGRATION
+  mig.fit = coherentfdm(ausmig.sm),
+  migf = forecast(mig.fit, h = 33),
+
+  # SIMULATED populations
+  aus.sim = pop.sim(mort = mortf, fert = fertf, mig = migf, firstyearpop = aus.pop, N = 2000),
+  # Convert to tibble
+  aussim_df = make_aussim_df(aus.sim, 2050),
+
+  # Combine simulations to create means and quantiles of future years
+  future_pop = aussim_df %>%
[…]

### 2020-09-17 R/pyramid.R

@@ -1,0 +1,32 @@
+pyramid <- function(history, future) {
+  data <- bind_rows(history, future)
+  p_male <- data %>%
+    filter(Sex == "Male") %>%
+    ggplot(aes(x = Age, y = Population, group = Year)) +
+    labs(y = "Population ('000)") +
+    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
+    geom_line(linetype = 2) +
+    geom_line(aes(y = Mean), col = "#0000cc") +
+    coord_flip() +
+    scale_y_reverse(expand = c(0.012, 0.012)) +
+    scale_x_continuous(expand = c(0.012, 0.012)) +
+    facet_grid(. ~ Sex)
+  p_female <- data %>%
+    filter(Sex == "Female") %>%
+    ggplot(aes(x = Age, y = Population, group = Year)) +
+    labs(y = "Population ('000)") +
+    geom_ribbon(aes(x = Age, ymin = Lower, ymax = Upper, y = Mean), fill = "#7d7def") +
+    geom_line(linetype = 2) +
+    geom_line(aes(y = Mean), col = "#0000cc") +
+    coord_flip() +
+    scale_y_continuous(expand = c(0.012, 0.012)) +
+    theme(
+      axis.title.y.left = element_blank(),
+      axis.text.y.left = element_blank(),
+      axis.ticks.y.left = element_blank()
+    ) +
+    scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
+    facet_grid(. ~ Sex)
+
+  (p_male | p_female)
+}

### 2020-09-17 functions-v4.R

@@ -1,73 +1,0 @@
-# Autoplot for fmforecast objects
-autoplot.fmforecast <- function(data) {
-  require(latex2exp)
-  p1 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,1])) +
-    geom_line() + xlab("Age (x)") + ylab(TeX("$\\mu(x)"))
-  p2 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,2])) +
-    geom_line() + xlab("Age (x)") + ylab(TeX("$\\phi_1(x)$"))
-  p3 <- ggplot(mapping=aes(x=data$age, y=data$model$basis[,3])) +
-    geom_line() + xlab("Age (x)") + ylab(TeX("$\\phi_2(x)$"))
-  p4 <- autoplot(data$coeff[[2]]) +
-    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{1,t}$"))
-  p5 <- autoplot(data$coeff[[3]]) +
-    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{2,t}$"))
-
-  print((p1 | p2 | p3) / ( plot_spacer() | p4 | p5))
-}
-
-# Function to produce old age dependency ratio using tibbles
-# df is data frame with columns Age, Sex, Year, Population
-# pension_age is dataframe with columns Year, Age.
-oadr <- function(df, pension) {
-  pension <- pension %>%
-    select(Year, Age) %>%
-    rename(Pension = Age)
-  df %>%
-    left_join(pension, by="Year") %>%
-    mutate(
-      # Fill historical years with minimum pension age
-      Pension = replace_na(Pension, min(Pension, na.rm=TRUE)),
-      # Divide population into three groups
-      Group = case_when(
-        (Age >= 15 & Age < Pension) ~ "Workers",
-        (Age >= Pension) ~ "Pension",
-        TRUE ~ "Child"
-      )
-    ) %>%
-    group_by(Year, Group) %>%
-    summarise(Population = sum(Population)) %>%
-    ungroup() %>%
-    pivot_wider(Year, names_from=Group, values_from=Population) %>%
-    mutate(OADR = Pension / Workers) %>%
-    select(Year, OADR)
-}
-
-# As above but df now contains Reps.
-oadr_sim <- function(df, pension, level=80) {
-  # Simulated OADR
-  df %>%
-    group_by(Rep) %>%
[…]

### 2020-09-17 packages.R

@@ -1,0 +1,9 @@
+## library() calls go here
+library(conflicted)
+library(dotenv)
+library(drake)
+
+library(dplyr)
+library(cubelyr)
+library(tidyr)
+library(demography)

### 2020-09-18 PensionAge.Rmd
Nearly there

@@
 ---
-title: "Forecasting the old-age dependency ratio to determine the best pension age"
+title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
 author:
@@
 Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
-Our results suggest that the Australian pension age should be increased to 68 by 2028 and 69 by 2034 in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
+Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
 Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
@@
 
-# Set up drake plan
+# Set up plan
 source("_drake.R")
@@
 
-# Load results
-drake::loadd()
-
-# Load additional packages for graphs and tables
-library(ggplot2)
-library(patchwork)
+loadd(oadr_target)
 ```
-
-\todo[inline]{Adjust numbers in abstract as per Figure 9}
 
@@
 Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at the desired level in the future.
-It should be noted that the desired level has been set at 21%, the estimated level of OADR in 2018.
+It should be noted that the desired level has been set at `r 100*oadr_target`%, just above the level of OADR in 2018.
 Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
@@
 Section \@ref(sec:litreview) reviews key literature on population forecasting and the pension age in Australia.
-Section \@ref(sec:data) describes the data and modelling framework we use in this study.
+Section \@ref(sec:results) describes the data and modelling framework we use in this study.
 We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \@ref(sec:target).
@@
 # History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
-pension_age %>%
-  filter(Year >= 2014) %>%
-  ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
-    geom_line() +
-    ylab("Minimum pension age") +
-    scale_color_brewer(
-      palette = "Dark2",
-      breaks = c("Proposed", "Current", "Age65"),
-      labels = c("Proposed further change", "Current policy", "Pension age at 65")
-    )
+loadd(pension_age_plot)
+pension_age_plot
 ```
@@
 
-# Results
+# Application to Australia {#sec:results}
 
@@
 
+```{r loadfertfit}
+loadd(fert.fit)
+```
+
 We illustrate the component model forecasts using fertility rates.
@@
 ```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", message=FALSE}
-autoplot.fmforecast(fertf)
+loadd(fertf_plot)
+fertf_plot
 ```
@@
 ```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4}
-history_pop %>%
-  group_by(Sex, Year) %>%
-  summarise(Population = sum(Population) / 1e3) %>%
-  ggplot(aes(x = Year, y = Population, group = Sex)) +
-    geom_line(size = 1) +
-    ylab("Population (millions)") +
-    ggtitle("Total population") +
-    facet_grid(. ~ Sex) +
-    geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
-    geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1)
+loadd(population_plot)
+population_plot
 ```
@@
 ```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE}
-pyramid(
-  history_pop %>% filter(Year == max(Year)),
-  future_pop %>% filter(Year == max(history_pop$Year) + 20)
-)
+loadd(pyramid_plot)
+pyramid_plot
 ```
@@
 The actual OADRs for 1921--2019 are shown in black."}
-OADR_future %>%
-  ggplot(aes(x = Year, y = OADR)) +
-    geom_hline(yintercept = target, col = "gray") +
-    geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy),
-      alpha = 0.5) +
-    geom_line(aes(col = Policy, group = Policy), size = .75) +
-    geom_line(col = "black", size = .75, data = OADR_history) +
-    xlab("year") +
-    ylab("ratio") +
-    ggtitle("OADR forecasts with pension age=65") +
-    scale_color_brewer(palette = "Dark2") +
-    scale_fill_brewer(palette = "Dark2")
+loadd(oadr_plots)
+oadr_plots
 ```
@@
 Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035.
+This proposal also leads to a slow decline in the OADR over the next 15 years.
 Figure \@ref(fig:OADRcurrent) demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
 
-# Sustainable pension age scheme
+# Sustainable pension age schemes
 
@@
 
-The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but mean of $O_{T+H|T}$ is replaced by the 10% and 90% quantiles.
+The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but the mean of $O_{T+H|T}$ is replaced by the 10% and 90% quantiles.
 
-```{r comparisonofpensionages, fig.cap="The comparison between the target pension age scheme (in green) and real pension age scheme that has been set or proposed by the government, along with the 80% confidence interval of the target pension age shown in the green shade.
-The solid red line indicates the changes to the pension age from 65 to 67, announced in 2009."}
-pension.fc <- structure(
-  list(
-    mean = ts(pension_age_optimal$Age, start = min(pension_age_optimal$Year)),
-    lower = ts(as.matrix(pension_age_lower$Age), start = min(pension_age_optimal$Year)),
-    upper = ts(as.matrix(pension_age_upper$Age), start = min(pension_age_optimal$Year)),
-    level = 80
-  ),
-  class = "forecast"
-)
-ggplot() +
-  autolayer(pension.fc, series = paste("Pension age to give OADR =", target)) +
-  autolayer(
-    ts(pension_age %>% filter(Policy == "Current", Year >= 1995) %>% pull(Age),
-       start = 1995),
-    series = "Approved change"
-  ) +
-  autolayer(
-    ts(pension_age %>% filter(Policy == "Age65", Year >= 1995) %>% pull(Age),
-      start = 1995),
-    series = "Pension age at 65"
-  ) +
-  xlab("Year") +
-  ylab("Minimum pension age")
+Figure \@ref(fig:comparisonofpensionages) shows (in blue) the pension scheme produced by this algorithm, along with 80% confidence intervals.
+In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.
+
+```{r comparisonofpensionages, fig.cap="The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
+The blue shaded region shows 80% confidence intervals for the target pension age."}
+loadd(proposed_pension_scheme_plot)
+proposed_pension_scheme_plot
 ```
 
-```{r OADRwithoptimal, fig.cap="The mean forecast of OADR associated with target pension age scheme (listed in Table 1) shown in blue, along with the desired OADR level in red (i.e., mean forecast of OADR in 2018).
-The 80% prediction interval of the forecast of OADR is shown as blue shading."}
+```{r OADRwithoptimal, fig.cap="The mean forecast and 80% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray."}
 ## plots of OADR with plausible pension age schemes
-OADR_optimal %>%
-  ggplot(aes(x = Year)) +
-    geom_hline(yintercept = target, col = "red") +
-    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-    geom_line(aes(y = OADR), col = "#0000cc") +
-    geom_line(data = OADR_history, aes(y = OADR)) +
-    ggtitle("OADR forecast estimates for optimal pension ages") +
-    ylab("Old age dependency ratio")
+loadd(proposed_oadr_plot)
+proposed_oadr_plot
 ```
 
-```{r OADRboundaries, fig.cap="The 80% prediction interval forecast of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes (listed in Table 2), along with desired OADR level (in red)."}
-bind_rows(
-    OADR_upper %>% mutate(Series = "Upper boundary"),
-    OADR_lower %>% mutate(Series = "Lower boundary"),
-  ) %>%
-  ggplot(aes(x = Year)) +
-    geom_hline(yintercept = target, col = "red") +
-    geom_ribbon(aes(ymin = Lo, ymax = Hi), fill = "#7d7def") +
-    geom_line(aes(y = OADR), col = "#0000cc") +
-    geom_line(data = OADR_history, aes(y = OADR)) +
-    facet_grid(. ~ Series) +
-    ggtitle("OADR forecasts for boundary pension age schemes") +
-    ylab("Old age dependency ratio")
+```{r OADRboundaries, fig.cap="The 80% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.", fig.height=3}
+loadd(oadr_upper_lower_plot)
+oadr_upper_lower_plot
 ```
 
-Table 1 shows the target pension age scheme, which is properly defined in section ??.
-Figure \@ref(fig:OADRwithoptimal) provides a visible comparison of the desired OADR level of 21% and the mean forecast of the OADR corresponding to the target pension age.
-Note that the OADR associated with target pension age scheme has nearly overlapped the desired OADR level, which indicates that we have successfully found the pension age with stable OADR at the desired levels.
+Figure \@ref(fig:OADRwithoptimal) shows the OADR forecasts as a result of using the target age pension scheme shown in Figure \@ref(fig:comparisonofpensionages).
+The target level of `r oadr_target*100`% and the mean forecast of the OADR corresponding to the target pension age almost overlap.
+Figure \@ref(fig:OADRboundaries) shows the OADR forecasts corresponding to the upper and lower limits of the 80% confidence intervals shown in Figure \@ref(fig:comparisonofpensionages), demonstrating that they correspond to having OADR forecast prediction interval boundaries that lie very close to the target OADR value.
 
 ```{r pensionagetables, message=FALSE, eval=FALSE}
+loadd(pension_age_optimal)
 pension_age_optimal %>%
@@
 
-```{r ComparisonwithOADR22, fig.cap="The comparison between the target pension age scheme (in green) associated with desired level equal to current level plus $1%$ (i.e., 22%) and real pension age scheme that has been set or proposed by government, along with the 80% confidence interval of the target pension age shown in green shade."}
+Thus any pension age higher than the upper boundary shown in Figure \@ref(fig:comparisonofpensionages) will give an OADR value that is significantly lower than the target value, while any pension age scheme lower than the lower boundary of the pension age reported in Figure \@ref(fig:comparisonofpensionages) will give an OADR value that is significantly higher than the target value.
 
-```
-
-```{r OADR_realpensionage, fig.cap="The mean forecast of OADR associated with different pension age schemes under investigation, along with the desired OADR level in grey (i.e., mean forecast of OADR in 2014).
-The 80% prediction interval of the forecast of OADR is shown as shading."}
-```
-
-The upper and lower boundaries of the plausible pension age schemes (also called the 80 % confidence interval of the target pension age scheme in this paper) are reported in Table 2, and their corresponding OADR simulation results are shown in Figure \@ref(fig:OADRboundaries).
-It can be seen that the lower (upper) limit of the 80% prediction interval of OADR associated with the lower (upper) boundary of the 80% confidence interval pension age scheme is entirely stable around the desired level.
-Note the negative relationship between OADR and pension age.
-It suggests, on the one hand, that any pension age higher than the upper boundary in Table 2 is deemed to be undesirable because the age is too high to allow the age pension to provide enough welfare support or insurance to the aged.
-On the other hand, any pension age scheme lower than the lower boundary of the pension age reported in Table 2 will also be regarded as unreasonable, because it sacrifices the interests of the next generation to provide a generous age pension immediately.
-
-Figure \@ref(fig:comparisonofpensionages) compares the target pension age scheme and its 80% confidence interval with the pension age scheme with proposed further change.
-It was found that the target pension age increases at a higher rate than the proposed new pension age scheme.
-Reported in Table 1, the target pension age is supposed to reach 67 by 2021 and 70 by 2032, while pension age has been proposed to change to 67 by 2023 and 70 by 2035.
-Moreover, the proposed pension age scheme is below the lower boundary of plausible pension age schemes, which means we are 80% sure that it will cause an OADR higher than the desired level.
-From this result, it is concluded that the government will need to adjust pension age slightly quicker than the proposed pace to ensure we have a stable OADR around the desired level at 21%.
-
-Note that the proposed pension age scheme does not diverge too far from the plausible pension age schemes, suggesting proposed new pension age scheme may be appropriate if we can afford slightly higher OADR.
-Therefore, it is worth performing a sensitivity test on the desired level here.
-
-Using the approach suggested in this paper, the target pension age associated with the desired OADR equal to current level plus 1% has been found.
-We have shown the comparison of it \todo{code are missing for two figures} and its 80% confidence level with a real pension age scheme in Figure \@ref(fig:ComparisonwithOADR22).
-When we allow 1% more in desired OADR, the real pension age becomes plausible.
-Figure \@ref(fig:OADR_realpensionage) shows simulated OADR associated with proposed pension age scheme^[Since we don't know the change rate set by government for 2023--2035, we assume it follows increase rate for 2017--2023, which increase half year pension age in every two years.].
-It confirms that OADR is stable around a level higher than current level of OADR before 2035.
-This results suggest that pension age scheme with proposed change could be suitable if the government are targeting a slightly higher financial pressure than current level.
+Figure \@ref(fig:comparisonofpensionages) also compares the target pension age scheme and its 80% confidence interval with the pension age scheme that has been proposed but not yet enacted.
+Clearly, it is outside the 80% confidence interval and so is too high for our targeted OADR value of `r oadr_target*100`%.
+Under our proposed scheme, the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at `r oadr_target*100`%.
 
@@
 
-The ageing of the population is expected to become a critical issue in Australia due to the increase in life expectancy and the retirement of baby boomers.
+The ageing of the population is an increasingly critical issue in Australia (and many other countries) due to the increase in life expectancy and the retirement of baby boomers.
 The fiscal cost of the age pension is projected to sharply increase as a result.
-For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023 and 70 in 2035 to reduce the financial burden on society.
+For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023, with a proposal to increase it to 70 by 2035 in order to reduce the financial burden on society.
+Our analysis suggests that this increase is too rapid unless the aim is to reduce the OADR to below 2018 values.
 
@@
 
-We undertake the approach based on assuming the desired level of OADR is at the current level of 21%.
-Using the historical data from 1950 to 2018, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
+We undertake the approach based on assuming the desired level of OADR is around the 2018 level of `r oadr_target*100`%.
+Using historical data from 1950 to 2019, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
 It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
 Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
-It was concluded that the pension age set by the government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around 21%.
+It was concluded that the pension age set by the government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around `r oadr_target*100`%.
 
-The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at 21%.
+The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at `r oadr_target*100`%.
 However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
@@
 This approach has been used to calculate the target pension age from now until 2068 and its 80% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 70 by 2032 and 75 by 2058.
+The target pension age found in this research increases to 67 by 2023, 70 by 2050.
 This generates a stable OADR of around 21%.
@@
 
-\newpage
-
-# Appendix: Evaluating forecast accuracy {#sec:accuracy}
-
-Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast.
-It is not valid to assess the model's fit in terms of historical data.
-We are concerned with how well a model performs on out-of-sample data, which is known but not used to fit the model.
-Therefore, we will use a cross-validation procedure [@fpp] to evaluate the accuracy of the models used in this paper.
-
-The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test.
-Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon.
-Then we are allowed to repeat the test $T-H-k+1$ times, where $T$ is the number of total years of observation.
-The procedure is as follows:
-
-Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.].
-Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error.
-We repeat the following steps for $\omega=1,2,\dots,T-k-H+1$.
-Then, we can summarize the information into a matrix as follows:
-$$
-  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
-    \begin{bmatrix}
-      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,T-k-H+1} \\
-      \vdots          & \ddots       & \vdots \\
-      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,T-k-H+1}
-    \end{bmatrix}
-$$
-where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$.
-This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time.
-We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.
-
-In our sample, $T=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test.
-The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rollingtest).
-From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR.
-Overall, the mean absolute error is small.
-For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 25%.
-
-```{r rmseplot}
-oadr_rolling_sim %>%
-  group_by(id) %>%
-  mutate(h = row_number()) %>%
-  ungroup() %>%
-  select(Year, h, OADR) %>%
-  rename(Forecast = OADR) %>%
-  left_join(OADR_history, by = "Year") %>%
-  mutate(e = OADR - Forecast) %>%
-  group_by(h) %>%
-  summarise(RMSE = sqrt(mean(e^2))) %>%
-  ggplot(aes(x = h, y = RMSE)) +
-    geom_point()
-```
-
-It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy.
-For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years.
-However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.
+\clearpage

### 2020-09-18 appendix.Rmd
Nearly there

# Appendix: Evaluating forecast accuracy {-}

Since all the results and implications are dependent on the forecast accuracy, it is important to evaluate the accuracy of our forecast. We will use a cross-validation procedure [@fpp2] to evaluate the accuracy of the models used in this paper.

The logic of a cross-validation test is to use a portion of available data for fitting, and use the remaining data to test. Suppose we need $k$ years' observations to produce a reliable forecast^[$k$ can't be too small], we are interested in the $H$ prediction horizon. Then we are allowed to repeat the test $T-H-k+1$ times, where $T$ is the number of total years of observation. The procedure is as follows:

  Let $\omega=1$, we first select historical data for a time interval of $[\omega,\omega+1,\dots,\omega+k-1]$ as "in sample data" to fit the model, and then forecast $H$ years' OADR^[The OADR is generated based on a pension age equal to 65 for the purpose of test.]. Then, we can calculate the difference of forecasted OADR over the period $[\omega+k,\omega+k+1,\dots,\omega+k+H-1]$ from the real OADR for the same period, which is known as absolute error. We repeat the following steps for $\omega=1,2,\dots,T-k-H+1$. Then, we can summarize the information into a matrix as follows:
$$
  \text{\textbf{Absolute Error}} = [\text{AE}_{h,\omega}] =
    \begin{bmatrix}
      \text{AE}_{1,1} & \cdots\cdots & \text{AE}_{1,T-k-H+1} \\
      \vdots          & \ddots       & \vdots \\
      \text{AE}_{H,1} & \cdots\cdots & \text{AE}_{H,T-k-H+1}
    \end{bmatrix}
$$
where $h$ denotes for the forecast horizon and $\text{AE}_{h,\omega}=\left|\text{OADR}^{\text{mean}}_{h,\omega}-\text{OADR}^{\text{real}}_{h,\omega}\right|$. This process is also known as "rolling forecasting origin", because the "origin" ($k+\omega-1$) at which the forecast is based rolls forward in time. We take the average of each row to obtain an absolute mean error of $h$-step-ahead forecast of OADR where $h=1,2,\dots,H$.

In our sample, $T=2018-1950+1=69$ and we set $k=25$ and $H=25$ to perform the test. The mean absolute error of $h$-step-ahead forecast of OADR for $h=1,2,\dots,25$ is shown in Figure \@ref(fig:rmseplot). From this Figure, we observe that the mean absolute error is increasing as $h$ increases, which is reasonable as we have less relevant information to make a forecast for further apart OADR. Overall, the mean absolute error is small. For example, the mean absolute error for 25-step-ahead forecast is 1.6%, which is small if compared to the desired level of OADR, which is at 25%.

```{r rmseplot}
loadd(oadr_rolling_rmse_plot)
oadr_rolling_rmse_plot
```

It would normally be ideal for comparing the mean absolute error of the forecast from our model to other available models to measure the accuracy. For example, suppose we can take the population projections from ABS reports over the last few decades, their projection of population age structure reported in different years can be used to mimic the rolling origin test of OADR, because we now have the real OADR for those projected years. However, we are not able to perform it because full projection data is no longer available online and ABS projections have not used a consistent and replicate methodology.

### 2020-09-18 R/oadr_future.R

@@ -1,13 +1,13 @@
 estimate_oadr_future <- function(sim, pension_age) {
   bind_rows(
     oadr_sim(sim, filter(pension_age, Policy == "Age65")) %>%
-      mutate(Policy = "Pension age 65"),
+      mutate(Policy = "Age65"),
     oadr_sim(sim, filter(pension_age, Policy == "Current")) %>%
-      mutate(Policy = "Current policy"),
+      mutate(Policy = "Current"),
     oadr_sim(sim, filter(pension_age, Policy == "Proposed")) %>%
-      mutate(Policy = "Proposed policy")
+      mutate(Policy = "Proposed")
   ) %>%
-  mutate(Policy = factor(Policy,
-                         levels = c("Pension age 65", "Current policy", "Proposed policy"))
+  mutate(
+    Policy = factor(Policy, levels = c("Proposed","Current","Age65"), ordered = TRUE)
   )
 }

### 2020-09-18 R/optimal_pension_scheme_plot.R

@@ -1,0 +1,33 @@
+optimal_pension_scheme_plot <- function(pension_age, pension.fc, pension_colors, oadr_target) {
+  pension_schemes <- pension_age %>%
+    bind_rows(
+      tibble(Year = time(pension.fc$mean),
+             Age = pension.fc$mean,
+             Policy="Optimal")
+    ) %>%
+    mutate(
+      Policy = factor(Policy, levels = c("Optimal","Proposed","Current","Age65"), ordered = TRUE)
+    ) %>%
+    filter(Year >= 2005)
+  pension.fc$x <- ts(rep(65,3), start=2016)
+  autoplot(pension.fc, fcol=pension_colors["Optimal"]) +
+    geom_line(data= pension_schemes, mapping=aes(x=Year, y=Age, col=Policy, group=Policy)) +
+    xlab("Year") +
+    ylab("Minimum pension age") +
+    scale_color_manual(
+      values = pension_colors,
+      labels = c(paste("Pension age to give OADR =",oadr_target),
+                 "Proposed policy",
+                 "Current policy",
+                 "Pension age 65")
+    ) +
+    scale_fill_manual(
+      values = pension_colors,
+      labels = c(paste("Pension age to give OADR =",oadr_target),
+                 "Proposed policy",
+                 "Current policy",
+                 "Pension age 65")
+    ) +
+    guides(col = guide_legend("Policy")) +
+    ggtitle("")
+}

### 2020-09-18 R/plan.R

@@ -7,7 +7,31 @@ the_plan <-
       Proposed = pmin(70, Age65 + 0.5 * pmax(0, trunc((Year - 2015) / 2))),
       Current = pmin(Proposed, 67),
     ) %>%
-    pivot_longer(-Year, values_to = "Age", names_to = "Policy"),
+    pivot_longer(-Year, values_to = "Age", names_to = "Policy") %>%
+    mutate(
+      Policy = factor(Policy, levels = c("Proposed","Current","Age65"), ordered = TRUE)
+    ),
+
+  # Okabe-Ito colors for pension age schemes
+  pension_colors = c(
+    Optimal = "#0072B2",
+    Proposed = "#E69F00",
+    Current = "#D55E00",
+    Age65 = "#009E73"
+  ),
+
+  # Pension age scheme plot
+  pension_age_plot = pension_age %>%
+    filter(Year >= 2014) %>%
+    ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
+    geom_line() +
+    ylab("Minimum pension age") +
+    scale_color_manual(
+      values = pension_colors,
+      labels = c("Proposed further change",
+                 "Current policy",
+                 "Pension age at 65")
+    ),
 
   # Get population data to 1 Jan 2019
   aus.pop = hmd.pop(country = "AUS",
@@ -44,6 +68,7 @@ the_plan <-
   # FERTILITY model
   fert.fit = fdm(ausfert.sm),
   fertf = forecast(fert.fit, h = 33),
+  fertf_plot = autoplot.fmforecast(fertf),
 
   # MIGRATION
   mig.fit = coherentfdm(ausmig.sm),
@@ -86,7 +111,7 @@ the_plan <-
   # Future population simulation
   future_tot_pop = aussim_df %>%
     group_by(Rep, Sex, Year) %>%
-    summarise(Population = sum(Population) / 1e3, .groups="keep") %>%
+    summarise(Population = sum(Population) / 1e3, .groups = "keep") %>%
     group_by(Sex, Year) %>%
     summarise(
       Mean = mean(Population),
@@ -99,12 +124,53 @@ the_plan <-
     ) %>%
     ungroup(),
 
+  population_plot = history_pop %>%
+    group_by(Sex, Year) %>%
+    summarise(Population = sum(Population) / 1e3) %>%
+    ggplot(aes(x = Year, y = Population, group = Sex)) +
+    geom_line(size = 1) +
+    ylab("Population (millions)") +
[…]

### 2020-09-18 packages.R

@@ -1,9 +1,14 @@
-## library() calls go here
+# Drake standard package loads
 library(conflicted)
 library(dotenv)
 library(drake)
 
+# Data wrangling and computation
 library(dplyr)
 library(cubelyr)
 library(tidyr)
 library(demography)
+
+# Packages for graphs and tables
+library(ggplot2)
+library(patchwork)

### 2020-09-20 PensionAge.Rmd
Rewritten intro and conclusion

@@
   othernames: Yijun
-  address: Monash University
+  address: Shanghai, China
 - familyname: Shang
   othernames: Han Lin
-  address: Macquarie University
+  address: Macquarie University, Sydney, Australia
 abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate future age-structures of the population.
+Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population.
 Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
 Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "coherent forecasts, demographic components, functional time series model, pension and insurance"
+keywords: "coherent forecasts, demographic components, functional time series, pension age"
 wpnumber: no/yr
-jelcodes: C10,C14,C22
+jelcodes: J11,J14,C22
 blind: false
@@
 
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past twenty or so years [@Fehr2008].
+Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past thirty years [@Fehr2008].
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
-Similar demographic challenges face many other countries.
+Many other countries face similar demographic challenges.
 One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age [@Walker1982].
@@
 This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014.
-In this paper, we investigate the effect of these changes in the pension age on the forecast OADR.
+We investigate the effect of these changes in the pension age on the forecasts of the OADR.
 
-The research presented in this paper contributes to the discussion by forecasting the age structure of the population, quantifying the effects of changing the pension age on financial burdens, and hence finding an appropriate pension age scheme which is economically viable for Australia.
-The analysis of the economic impact of increasing pension age can be complicated.
-In this paper, we will focus on only one aspect: the impact on the burden of future working-age generations.
-
-In this paper, we use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
-The OADR is defined as the ratio of the number of people aged over the pension age to the number of people of working age [@ARW07].
-This can be expressed using the formula below:
+The OADR can be expressed as
 \begin{equation}
@@
 \end{equation}
-We provide forecasts of future population age structures over the next 50 years.
-We then use those forecasts to compute the OADR associated with pension age both before and after the adjustments.
-One contribution of the current study is the combined use of the Hyndman-Ullah forecasting method [@HU07] and the product-ratio method [@HBY13] to forecast a population age structure.
-Forecasts of population structure have been built on forecasts of age- and sex-specific mortality rates, fertility rates and net migration using this method.
+We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
+We provide forecasts of future population age structures over the next 50 years, and use those forecasts to compute the OADR that would result under various pension age schemes.
+
+We then invert the analysis by finding a pension age scheme that would lead to a specified OADR value.
+For our analysis, the specified OADR value has been set at `r 100*oadr_target`%, just above the level of OADR in 2018.
+Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
+Instead, we provide a methodology for policymakers to find a target pension age that leads to a given OADR value.
+
+Forecasts of population structure depend on forecasts of age- and sex-specific mortality rates, fertility rates and net migration.
+To this end, we combine the functional demographic models of @HU07 and the product-ratio method of @HBY13 within the general stochastic population forecasting framework of @HB08, to forecast a population age structure.
 These forecasts presuppose that the historical trends of past years will continue.
 Historical data of those rates have thus been used as input to simulate future paths of age- and sex-specific population structure.
-
-Using these predicted population paths, we can calculate the average OADR and predict the levels of old-age dependency that correspond to different pension age schemes.
-By testing different pension age schemes, we aim to find the pension age with the desired OADR outcome.
-Therefore, other contributions of this research are (1) to examine the effect of adjusting pension ages by comparing OADR before and after adjustment; and (2) to suggest a suitable pension age scheme to ensure that the economic burden will remain relatively constant at the desired level in the future.
-It should be noted that the desired level has been set at `r 100*oadr_target`%, just above the level of OADR in 2018.
-Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
-This paper concentrates on providing a framework for policymakers to find a target pension age for a given desired level of OADR.
 
@@
 We do not consider these here.
-Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables.
+Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables if required.
 
@@
 
-Age pension in Australia is income support and provides access to a range of concessions for older Australians who have passed means-testing.
-For example, it provides single home-owners with a real income of $23,889 p.a and additional allowances to cover expenses such as rent or pharmaceuticals^[The pension amount is adjusted every 6 months for inflation].
-The means test ensures that retirees with enough personal savings will become ineligible for the public provision by reducing the pension at fixed levels of pay as personal wealth increases.
-The age pension in Australia is generous, even with the means test.
-For instance, a couple holding assets of more than one million dollars is still eligible for a partial age pension.
+The age pension in Australia provides income support and access to a range of concessions and additional allowances for older Australians who have passed a means test.
 
-In 2006, the age pension was the primary source of income for 70--80% of Australian residents over 64 years [@ABS06].
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with the average less than $100,000 at retirement [@ASFA07].
-It has been estimated by @PT08 that a retiree will need to have $450,000 at 65 in order to support a pension-equivalent income and this is more than eight times of the average retirement accumulation of Australians.
-The required wealth to comply with personal-funded retirement savings requirements is too high for most Australians, suggesting that retirees will continue to rely on the age pension in the coming decades.
+In 2018, 67% of Australian residents aged 65 and over received income support payments [@AIHW19].
+Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances [@data61].
 
-The ageing trend in Australia, along with retirees' dependence on the age pension, has dramatically increased the fiscal cost of the age pension.
-For instance, the fiscal cost of the age pension is currently around at 2.5% of Gross Domestic Profit (GDP), but is expected to increase to 4.4% by the 2050s (Australian government, 2007).
-The @PC13 also indicates the government will need to raise taxes by 21% to pay for extra aged care and health costs, which is caused by longer life expectancies in newer generations.
-
-The issue is not only a problem for the government, but also for future retirees.
-Given children born today are expected to live up to their 90s on average, the @PC13 suggests that Australians won't be able to afford to spend 35 years in retirement (i.e., retire around 65).
-They have predicted that a third of baby boomers are expected to spend all their money and assets before they die^[Baby Boomers are people born during the Post-World War II baby boom between the years 1946 and 1964.].
-This problem might eventually deteriorate the sustainability of the age pension, although the welfare system works well at the moment, because demographic changes often have delayed effects [@IGR02].
+The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7% of Gross Domestic Profit.
+With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.
 
@@
 
-The Australian government is trying to take early intervention in relation to the pension age to balance between providing social support and fiscal cost.
-The pension age for males has been set at 65 for over a century.
-While the pension age for females was 60 years until 1994, it has steadily increased to 65 years, in line with that of males.
-The previous Labor government announced in 2009 that the pension age would increase six months every two years until 2017, capping at 67 in July 2023.
-This change is expected to have a significant impact on labor force participation and to decrease the retirement duration of residents because the pension age is regarded as a normal age for retirement in Australia.
-However, the @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and older people are capable of continuing work.
-The National Commission of Audit (NCOA) (2014) holds the same opinion, and recommended lifting the pension age to 70 from 2053.
-The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 from 2035, which is proposed in the Federal Budget Statement for 2014--2015 to be confirmed by the Australian Federal Government.
+The pension age for males was set at 65 for over a century.
+While the pension age for females was 60 years until 1994, it has steadily increased to 65 years in 2014, in line with that of males.
+From July 2017, pension eligibility ages for both males and females have been increasing by six months every two years and will reach 67 in July 2023.
+The @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and older people are capable of continuing work.
+The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 by 2035, and this was proposed in the Federal Budget Statement for 2014--2015, although it has never been legislated by the Australian Federal Government.
 Figure \@ref(fig:changespension) illustrates the process of the adjustments on pension age scheme.
-This announcement received overwhelmingly negative responses in the media.
-@Guest14 argues from an economic perspective that Australia currently has much less age pension pressure than other OECD countries, because spending on the age pension in Australia is less than half of the OECD average.
-He also claims that Australia has a higher consumption of all other goods and services, and so why are they not allowed to have more leisure time.
-Further, @Power14 contends that many Australians are not physically able to work full-time to 70, so that recommendations made by the PC and NCOA are simplistic solutions to a more complex social problem.
 
-All supportive arguments for increasing the pension age in Australia have only justified the need to increase the pension age.
-No justification on the pace or degree of the change has been provided.
-Also, the government has not disclosed the method it used to determine the new pension age.
-It is therefore not surprising that the adjustment of the pension age has been questioned by the public.
-A consistent method to determine the appropriate pension age would be more persuasive in general.
-For example, it is preferred by OECD countries that pension age should be linked to life expectancy [@OECD12].
-There is a practical issue as to how to link life expectancy with pension ages given that there is no information on future mortality rates [@PC13].
+The government has not disclosed the method it used to determine the new pension age.
 @CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that "pension age should increase by approximately 50% of any increase in life expectancy".
 However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-Our study suggests an approach, linking the pension age with the aged dependency ratio, based on forecasts of future mortality and fertility rates.
+We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates.
 Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.
@@
 
-The data used are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
+The data required for our proposal are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
 Let
@@
 The ageing of the population is an increasingly critical issue in Australia (and many other countries) due to the increase in life expectancy and the retirement of baby boomers.
-The fiscal cost of the age pension is projected to sharply increase as a result.
-For the purpose of sustainability of the welfare system in Australia, the government has announced an increase in the pension age to 67 in 2023, with a proposal to increase it to 70 by 2035 in order to reduce the financial burden on society.
+The fiscal cost of the age pension has increased as a result, and is likely to continue to be a financial burden unless there are changes in age pension schemes.
+Under current Australian government policy, the pension age will rise to 67 in 2023, and there is a proposal to further increase it to 70 by 2035.
 Our analysis suggests that this increase is too rapid unless the aim is to reduce the OADR to below 2018 values.
@@
 In this paper, we have suggested a statistical and demographic approach to address the issue.
-We attempt to quantify the effects of changes in the pension age on financial burdens using an OADR as a measure of the financial burden on Australian society.
-The quantification process involves applying stochastic models to forecast future population age structure and then using those future age structure projections to find the most appropriate pension age scheme that will ensure stable OADR around the desired level.
-To forecast the population age structure, three demographic components of the population were modeled separately using functional time series method [@HU07], with an extension of the product-ratio method [@HBY13].
-Next, future age structures were used to simulate OADR associated with different pension age schemes until the minimum pension age scheme was found, which ensures the OADR no greater than the desired level.
-This approach is proposed to find a target pension age scheme based on a given desired level of OADR.
+We attempt to quantify the effects of changes in the pension age on the OADR, which we take as a crude measure of the financial burden of the age pension.
+We have applied stochastic models to forecast the future population age structure and then used those future age structure projections to find the most appropriate pension age scheme that will ensure a stable OADR around the desired level.
+To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods [@HU07], along with an extension of the product-ratio method [@HBY13].
+Then the framework of @HB08 was used to simulate future populations by age and sex.
+These were then used to simulate OADR values associated with different pension age schemes.
+Finally, we inverted the process to find a pension age scheme that leads to a specified OADR value.
 
-We undertake the approach based on assuming the desired level of OADR is around the 2018 level of `r oadr_target*100`%.
-Using historical data from 1950 to 2019, the forecast of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
+We illustrate the approach based on assuming the desired level of OADR is around the 2018 level of `r oadr_target*100`%.
+Using historical data from 1950 to 2019, the forecasts of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
 It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
-Findings indicate that the pension age scheme with proposed change was not too high, as it is still lower than the target pension age scheme and outside its confidence interval.
-It was concluded that the pension age set by the government should be adjusted slight quicker to be in line with our target pension age, which ensures a stable OADR of around `r oadr_target*100`%.
 
-The empirical analysis presented in this paper shows the adjustment of the pension age announced in 2009 was effective in reducing the financial burden to the desired level, which was set at `r oadr_target*100`%.
+The empirical analysis presented in this paper shows the adjustment of the pension age to age 67 has been effective in stopping the increasing trend in the OADR values.
 However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
-Therefore, we recommend consistently reviewing the pension age according to the presented statistical approach.
-This approach has been used to calculate the target pension age from now until 2068 and its 80% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 70 by 2050.
-This generates a stable OADR of around 21%.
-The rate of growth in the pension age as proposed by the government in 2014 is slightly lower than the target pension age found in this study, which suggests that the government may need to slightly accelerate the growth of the pension age to maintain an OADR at the current level.
+Therefore, we recommend consistently reviewing the pension age according to the proposed statistical approach.
+This approach has been used to calculate the target pension age from now until 2050 along with its 80% confidence interval.
+The target pension age found in this research increases to 67 by 2023, 68 by 2030, 69 by 2036 and 70 by 2050.
+This generates a stable OADR of around `r oadr_target*100`%.
 
-Although our results are promising, there are still grounds for further research.
-First, our research results are based on forecasts from one particular model.
-Further studies can apply the same approach but with different models of population forecasting, which allows for enhanced credibility of results.
-Moreover, our research addresses the issue from a purely demographic perspective.
-It is possible to include an economic perspective.
-For example, the economic implications of retaining older workers in the workforce can be considered.
-Second, Our research uses an OADR as a single measurement of the financial burden.
-Further research should allow the effect of other economic factors to be taken into account.
-For instance, the effect of growth in superannuation can be considered in a way that the effects of high OADR can be offset by the growth in superannuation.
+This research addresses the pension age issue from a purely demographic perspective.
+Further analysis should include an economic perspective as well including the impact of the superannuation guarantee and other economic measures to offset the fiscal burden of the age pension.
 
-\clearpage
+Finally, we have not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures.
+It is known that the mortality rates from COVID-19 are greater amongst older people, so it should lead to a decrease in the OADR.
+However, the relatively small number of deaths in Australia mean that the effect of the pandemic will probably not substantially change our recommendations.

### 2020-09-20 PensionAge.Rmd
Added reproducibility statement and cleaned up references

@@
 In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010].
-In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035.
-This new proposal is in line with the recommendations from the @PC13 and the @NCOA2014.
+In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the @PC13.
 We investigate the effect of these changes in the pension age on the forecasts of the OADR.
@@
 However, the relatively small number of deaths in Australia mean that the effect of the pandemic will probably not substantially change our recommendations.
+
+## Reproducibility {-}
+
+The data and code to fully reproduce our results is available at [`https://github.com/robjhyndman/PensionAge`](https://github.com/robjhyndman/PensionAge).
+We used R [@RCore], along with the drake [@Rdrake], tidyverse [@Rtidyverse], demography [@Rdemography] and forecast [@Rforecast] packages.

### 2020-09-20 PensionAge.Rmd
Fixed heading of reproducibility section
Minor fixes

@@
     citation_package: biblatex
-header-includes:
-  - \usepackage{todonotes, xcolor}
 ---
@@
 
-# Sustainable pension age schemes
+# Sustainable pension age schemes {#sec:target}
 
@@
 
-## Finding the target pension age scheme {#sec:target}
+## Finding the target pension age scheme
 
@@
 
-## Reproducibility {-}
+# Reproducibility {-}
 

### 2020-09-20 PensionAge_anzjs.Rmd
ANZJS version

--- 2020-09-20 PensionAge.Rmd
@@
 title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
-author:
-- familyname: Hyndman
-  othernames: Rob J
-  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
-  email: Rob.Hyndman@monash.edu
-  correspondingauthor: true
-- familyname: Zeng
-  othernames: Yijun
-  address: Shanghai, China
-- familyname: Shang
-  othernames: Han Lin
-  address: Macquarie University, Sydney, Australia
-abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population.
-Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "coherent forecasts, demographic components, functional time series, pension age"
-wpnumber: no/yr
-jelcodes: J11,J14,C22
-blind: false
-cover: true
+author: Rob J Hyndman$^{1*}$, Yijun Zeng^2, Hanlin Shang^3
+documentclass: anzsauth
+classoption: doublespace
+bibliography: pensionage.bib
+biblio-style: anzsj
 toc: false
-bibliography: pensionage.bib
-biblio-style: authoryear-comp
 output:
-  MonashEBSTemplates::workingpaper:
+  bookdown::pdf_document2:
     fig_caption: yes
+    citation_package: natbib
     fig_height: 5
@@
     number_sections: yes
-    citation_package: biblatex
+    includes:
+      in_header: anzjs_preamble.tex
 ---
@@
 ```
+
+# Summary {-}
+
+We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
+Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population.
+Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
+Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
+
+**Keywords:** coherent forecasts, demographic components, functional time series, pension age.
 

### 2020-09-20 PensionAge_anzjs.tex
ANZJS version

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  doublespace]{anzsauth}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Forecasting the old-age dependency ratio to determine a sustainable pension age},
  pdfauthor={Rob J Hyndman\^{}\{1*\}, Yijun Zeng\^{}2, Hanlin Shang\^{}3},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%% Any special functions or other packages can be loaded here.
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{float, bm}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
\usepackage[UKenglish]{isodate}
\usepackage{hyperref}

\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[tbp]
} {
    \endorigfigure
}

\let\origtable\table
\let\endorigtable\endtable
\renewenvironment{table}[1][2] {
    \expandafter\origtable\expandafter[tbp]
} {
    \endorigtable
}

\runningheads{Forecasting the OADR to determine a sustainable pension age}{HYNDMAN, ZENG, SHANG}

\def\volumeyear{2020}
\let\oldmaketitle\maketitle
\def\maketitle{\cleanlookdateon\oldmaketitle}
\linenumbers

\usepackage{titling}
\pretitle{\begin{center}\Large\bfseries}
\posttitle{\end{center}\vspace{0.5cm}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\begin{center}
$^1$\emph{Department of Econometrics \& Business Statistics, Monash University, Clayton, Australia}\\
$^2$\emph{Shanghai, China}\\
$^3$\emph{Macquarie University, Sydney, Australia}
\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}}\end{center}}

\usepackage{mathptmx}
\usepackage[]{natbib}
\bibliographystyle{anzsj}

\title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Hanlin Shang\^{}3}
\date{}

\begin{document}
\maketitle

\hypertarget{summary}{%
\section*{Summary}\label{summary}}
\addcontentsline{toc}{section}{Summary}

We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."

\textbf{Keywords:} coherent forecasts, demographic components, functional time series, pension age.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}. Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Many other countries face similar demographic challenges. One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \citep{Walker1982}. The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

This is consistent with the Australian Intergenerational Reports \citep{IGR02, IGR07, Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations. To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time). In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 \citep{Nielson2010}. In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the \citet{PC13}. We investigate the effect of these changes in the pension age on the forecasts of the OADR.

The OADR can be expressed as
\begin{equation}
  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
\end{equation}
We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs \citep{ARW07, IGR02, IGR07}.
We provide forecasts of future population age structures over the next 50 years, and use those forecasts to compute the OADR that would result under various pension age schemes.

We then invert the analysis by finding a pension age scheme that would lead to a specified OADR value. For our analysis, the specified OADR value has been set at 23\%, just above the level of OADR in 2018. Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper. Instead, we provide a methodology for policymakers to find a target pension age that leads to a given OADR value.

Forecasts of population structure depend on forecasts of age- and sex-specific mortality rates, fertility rates and net migration. To this end, we combine the functional demographic models of \citet{HU07} and the product-ratio method of \citet{HBY13} within the general stochastic population forecasting framework of \citet{HB08}, to forecast a population age structure. These forecasts presuppose that the historical trends of past years will continue. Historical data of those rates have thus been used as input to simulate future paths of age- and sex-specific population structure.

Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation. However, 80\% of Australians over pension age rely fully or partly on the age pension \citep{Power14}. Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations. Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and \citet{HY12} have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance. We do not consider these here. Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables if required.

The remainder of this paper proceeds as follows. Section \ref{sec:litreview} reviews key literature on population forecasting and the pension age in Australia. Section \ref{sec:results} describes the data and modelling framework we use in this study. We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \ref{sec:target}. Finally, Section \ref{sec:conclusions} gives concluding remarks as well as identifies the scope for future research.

\hypertarget{sec:litreview}{%
\section{Background}\label{sec:litreview}}

\hypertarget{the-age-pension-in-australia}{%
\subsection{The age pension in Australia}\label{the-age-pension-in-australia}}

The age pension in Australia provides income support and access to a range of concessions and additional allowances for older Australians who have passed a means test.

In 2018, 67\% of Australian residents aged 65 and over received income support payments \citep{AIHW19}. Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances \citep{data61}.

The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7\% of Gross Domestic Profit. With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/changespension-1.pdf}
\caption{\label{fig:changespension}Australian pension age policies.}
\end{figure}

The pension age for males was set at 65 for over a century. While the pension age for females was 60 years until 1994, it has steadily increased to 65 years in 2014, in line with that of males. From July 2017, pension eligibility ages for both males and females have been increasing by six months every two years and will reach 67 in July 2023. The \citet{PC13} proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and older people are capable of continuing work. The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 by 2035, and this was proposed in the Federal Budget Statement for 2014--2015, although it has never been legislated by the Australian Federal Government. Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.

The government has not disclosed the method it used to determine the new pension age. \citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''. However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term. We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates. Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.

\hypertarget{demographic-growth-balance-equations}{%
\subsection{Demographic growth-balance equations}\label{demographic-growth-balance-equations}}

The data required for our proposal are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1~January of each year, and age- and sex-specific exposures to risk (i.e., the population of age \(x\) at 30~June) for each year. Let
\begin{align*}
  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
\end{align*}
where \(x=0,1,2,\dots,p-1,p^+\) denotes age with \(p^+\) the open-ended upper age group, set to 100\(^+\) in this study. The year is denoted by \(t=1,2,\dots,T\), and superscripts \(M\) and \(F\) denote male and female respectively.

We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted \(G\)) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths. The equations are expressed as:
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
\end{align*}
where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\). The deaths are estimated using the standard life table approach of population projection. It should be noted that the estimated net migration includes errors in data recording.

\hypertarget{old-age-dependency-ratio}{%
\subsection{Old-Age Dependency Ratio}\label{old-age-dependency-ratio}}

Using this notation, the OADR in year \(t\) is given by
\begin{equation}\label{eq:oadr}
O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
\end{equation}
where \(a_t\) is the pension age in year \(t\) and \(r_t = a_t - \lfloor a_t \rfloor\) is the non-integer part of \(a_t\). This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.

\hypertarget{forecasting-demographic-components}{%
\subsection{Forecasting demographic components}\label{forecasting-demographic-components}}

Variants of the Lee-Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}. The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture. The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study. In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.

\hypertarget{lee-carter-method}{%
\subsubsection*{Lee-Carter method}\label{lee-carter-method}}
\addcontentsline{toc}{subsubsection}{Lee-Carter method}

The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
\begin{equation}\label{eq:lc}
  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
\end{equation}
where \(m_{t}(x)\) is the central death rate for age \(x\) in year \(t\). This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(\mu(x)\)\} and \{\(\phi(x)\)\}, and a time-varying index \(\beta_{t}\). \(\phi(x)\) is a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\). \(\beta_{t}\) measures the general level of the log death rates; \(\mu(x)\) is the general pattern across the age of the log mortality rate and \(\varepsilon_{t,x}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

The model is over-parameterised. Therefore, the constraints
\begin{equation}
  \sum_{t=1}^{T}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
\end{equation}
are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} \citep{Good1969}. The estimates of \(\phi(x)\) and \(\beta_t\) are therefore the first principal component and scores of \(\bm{X}\) with \((i,t)\)th element \([\log(m_{t}(x))-\widehat\mu(x)]\), where \(\widehat\mu(x)\) is the sample mean of \(\log(m_{t}(x))\) over \(t\). The log transformation introduces some bias, so the LC method adjusts \(\beta_t\) such that for each year, the implied number of deaths will be equal to the actual number of deaths. The adjusted \(\beta_t\) is then extrapolated using a random walk with drift model.

\hypertarget{hyndman-ullah-method}{%
\subsubsection*{\texorpdfstring{Hyndman-Ullah method \label{sec:HU}}{Hyndman-Ullah method }}\label{hyndman-ullah-method}}
\addcontentsline{toc}{subsubsection}{Hyndman-Ullah method \label{sec:HU}}

\citet{HU07} proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The demographic rates are smoothed before modeling.
\item
  It uses functional principal components analysis, which is a continuous version of PCA.
\item
  It uses more than one principal component, which addresses the main weakness of the LC method.
\item
  The forecasting models for the principal component scores are more complex than the random walk with drift model used in the LC model.
\end{enumerate}

The Hyndman-Ullah (HU) model can be written as
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
\end{align}
where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\). Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score. The \(e_t(x)\) is the model error having mean zero and no serial correlation, while \(\mu(x)\) is estimated as the average of \(s_t(x)\) across years. Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j^{th}\) principal components and scores of \(s_t(x)-\mu(x)\) respectively. Following \citet{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.

By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) are given by
\begin{equation}
  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
\end{equation}
where \(\widehat{\beta}_{T+h\mid T,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{T+h\mid T,j}\). Because \(\left\{\beta_{t,j}\right\}\) is time-varying, it controls the dynamics of the process. Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \citet{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.

\hypertarget{product-ratio-method}{%
\subsubsection*{Product-ratio method}\label{product-ratio-method}}
\addcontentsline{toc}{subsubsection}{Product-ratio method}

When we apply the \citet{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge. In the product-ratio method \citep{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently. That is, define
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, the HU method is applied to these two new variables:
\begin{align*}
  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0<d<\frac{1}{2}\)). It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecasts of male and female do not diverge. Then, forecasts of sex-specific data are obtained using
\begin{align*}
  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
\end{align*}
The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.

\hypertarget{forecasting-oadr}{%
\subsection{Forecasting OADR}\label{forecasting-oadr}}

Following the general procedure proposed in \citet{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future. We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.

From these models, sample paths are simulated for age-specific fertility rates, age- and sex-specific mortality rates and age- and sex-specific net migration. Then future population values are simulated using the demographic growth-balance equations. The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates. We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see \citet{HB08} for the details). Hence, we can simulate \(h\)-step-ahead age- and sex-specific population numbers based on simulated births, deaths and net-migrants.

This simulation was repeated for years \(t=T+1,\dots,T+h\) to obtain a sample path of the age-specific population. Many simulated population paths were obtained in this way. For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.

There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.

\hypertarget{sec:results}{%
\section{Application to Australia}\label{sec:results}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the \citet{HMD} for 1921--2018. The start-year population for 2019 is also used to estimate net migration. Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the \citet{ABSBirths}. Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons. First, the period between 1921--1950 has different mortality patterns from later years because of wars \citep{HB08}. Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them. Second, fertility rates are only available from 1950, so the mortality rates were also truncated to the same period.

\hypertarget{component-forecasts}{%
\subsection{Component forecasts}\label{component-forecasts}}

We illustrate the component model forecasts using fertility rates. Figure \ref{fig:componentsfertility} shows the estimated mean age pattern \(\widehat{\mu}(x)\), the first two basis functions, \(\widehat{\phi}_1(x)\) and \(\widehat{\phi}_2(x)\), and the first two principal component scores, \(\widehat{\beta}_{t,1}\) and \(\widehat{\beta}_{t,2}\)) for log fertility rates. The first term, \(\widehat{\phi}_1(x) \widehat{\beta}_{t,1}\), accounts for 63.7\% of the variation in the log fertility rates. The first principal component scores \(\widehat{\beta}_{t,1}\), shown in black for 1950--2018, display a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961. This increase of fertility is linked to the post-World War II baby boom, while the dramatic decrease from 1960 was due to the availability of contraception pills. A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the abortion laws in some states.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/componentsfertility-1.pdf}
\caption{\label{fig:componentsfertility}Fitted basis functions and coefficients for Australian age-specific fertility rates.}
\end{figure}

The first basis function \(\widehat{\phi}_1(x)\) measures the different effects of the time-trend across ages. It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception. The two ``bumps'' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s. The second basis function, accounting for 31.5\% of the variation, largely concerns mothers aged over 30. The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80\% pointwise prediction intervals shown as blue shaded regions. These forecasts are obtained using automatically selected ARIMA models. In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for 4.6\% of the variation, and are much harder to interpret.

Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.

\hypertarget{population-forecasts}{%
\subsection{Population forecasts}\label{population-forecasts}}

Figure \ref{fig:totalpopulationbyyears} shows the forecast of the total population by sex over the prediction horizon, while Figure \ref{fig:totalpopulationin2038} shows the 20-year forecast of population age structure in 2038. Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 27 million by 2068.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationbyyears-1.pdf}
\caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of the total population for each sex, along with 80\% prediction intervals.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationin2038-1.pdf}
\caption{\label{fig:totalpopulationin2038}Forecast population pyramid for 2038, along with 80\% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.}
\end{figure}

Figure \ref{fig:totalpopulationin2038} shows the mean and the 80\% pointwise prediction interval of simulated population paths for the year 2038 (a 20-year forecast), along with the 2019 base population. The uncertainty of the population below aged 20 is largely due to higher forecast variation of fertility rates compared to other components.

Historical OADR values are shown in black in Figure \ref{fig:OADRcurrent} for 1921--2019. The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}. The increased trend from 2010 is due to the retirements of ``Baby Boomers'', born after WW2. We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple). The actual OADRs for 1921--2019 are shown in black.}
\end{figure}

Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65. This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care. Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035. This proposal also leads to a slow decline in the OADR over the next 15 years. Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.

\hypertarget{sec:target}{%
\section{Sustainable pension age schemes}\label{sec:target}}

Our aim is to determine a pension age scheme that would lead to the OADR being below a desired threshold, thus imposing a sustainability constraint.

Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]'\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\). Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold. We impose the constraint \(0 \le a_t - a_{t-1} < 1\) to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension. We also assume that the adjustment unit of the pension age is one month, for easier implementation.

\hypertarget{finding-the-target-pension-age-scheme}{%
\subsection{Finding the target pension age scheme}\label{finding-the-target-pension-age-scheme}}

Let \(O^*\) denote the desired OADR threshold. Because we do not observe the population in future years, we must estimate \(O_{T+h}\) from the simulated populations. Then we compute the pension age scheme \(\bm{P}\) using the following algorithm. Starting with \(h=1\):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Set \(a_{T+h}=a_{T+h-1}\).
\item
  Increment \(a_{T+h}\) by one-month intervals until either \(\widehat{O}_{T+h|T} > O^*\) or \(a_{T+1} - a_{T}=\) 1 month, where \(\widehat{O}_{T+h|T}\) denotes the mean of the simulated \(O_{T+h|T}\) values.
\end{enumerate}

We repeat these steps for \(h=2,\dots,H\).

In addition to finding the target pension age based on the mean value of OADR, we also find ``plausible'' pension age schemes that could give the desired OADR level. Specifically, we find a range of pension age schemes for which \(O^*\) is contained within the 80\% prediction intervals of the simulated \(O_{T+H|T}\) values. Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80\% prediction intervals of OADR is equal to the desired OADR level. Hence, any pension age scheme within those two boundaries is plausible. The range of plausible pension age schemes can be thought of as an 80\% confidence interval of pension age schemes where we are 80\% sure that they will give the desired outcome.

The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but the mean of \(O_{T+H|T}\) is replaced by the 10\% and 90\% quantiles.

Figure \ref{fig:comparisonofpensionages} shows (in blue) the pension scheme produced by this algorithm, along with 80\% confidence intervals. In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
\caption{\label{fig:comparisonofpensionages}The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government. The blue shaded region shows 80\% confidence intervals for the target pension age.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.}
\end{figure}

Figure \ref{fig:OADRwithoptimal} shows the OADR forecasts as a result of using the target age pension scheme shown in Figure \ref{fig:comparisonofpensionages}. The target level of 23\% and the mean forecast of the OADR corresponding to the target pension age almost overlap. Figure \ref{fig:OADRboundaries} shows the OADR forecasts corresponding to the upper and lower limits of the 80\% confidence intervals shown in Figure \ref{fig:comparisonofpensionages}, demonstrating that they correspond to having OADR forecast prediction interval boundaries that lie very close to the target OADR value.

Thus any pension age higher than the upper boundary shown in Figure \ref{fig:comparisonofpensionages} will give an OADR value that is significantly lower than the target value, while any pension age scheme lower than the lower boundary of the pension age reported in Figure \ref{fig:comparisonofpensionages} will give an OADR value that is significantly higher than the target value.

Figure \ref{fig:comparisonofpensionages} also compares the target pension age scheme and its 80\% confidence interval with the pension age scheme that has been proposed but not yet enacted. Clearly, it is outside the 80\% confidence interval and so is too high for our targeted OADR value of 23\%. Under our proposed scheme, the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%.

\hypertarget{sec:conclusions}{%
\section{Conclusions}\label{sec:conclusions}}

The ageing of the population is an increasingly critical issue in Australia (and many other countries) due to the increase in life expectancy and the retirement of baby boomers. The fiscal cost of the age pension has increased as a result, and is likely to continue to be a financial burden unless there are changes in age pension schemes. Under current Australian government policy, the pension age will rise to 67 in 2023, and there is a proposal to further increase it to 70 by 2035. Our analysis suggests that this increase is too rapid unless the aim is to reduce the OADR to below 2018 values.

In this paper, we have suggested a statistical and demographic approach to address the issue. We attempt to quantify the effects of changes in the pension age on the OADR, which we take as a crude measure of the financial burden of the age pension. We have applied stochastic models to forecast the future population age structure and then used those future age structure projections to find the most appropriate pension age scheme that will ensure a stable OADR around the desired level. To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods \citep{HU07}, along with an extension of the product-ratio method \citep{HBY13}. Then the framework of \citet{HB08} was used to simulate future populations by age and sex. These were then used to simulate OADR values associated with different pension age schemes. Finally, we inverted the process to find a pension age scheme that leads to a specified OADR value.

We illustrate the approach based on assuming the desired level of OADR is around the 2018 level of 23\%. Using historical data from 1950 to 2019, the forecasts of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend. It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.

The empirical analysis presented in this paper shows the adjustment of the pension age to age 67 has been effective in stopping the increasing trend in the OADR values. However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure. Therefore, we recommend consistently reviewing the pension age according to the proposed statistical approach. This approach has been used to calculate the target pension age from now until 2050 along with its 80\% confidence interval. The target pension age found in this research increases to 67 by 2023, 68 by 2030, 69 by 2036 and 70 by 2050. This generates a stable OADR of around 23\%.

This research addresses the pension age issue from a purely demographic perspective. Further analysis should include an economic perspective as well including the impact of the superannuation guarantee and other economic measures to offset the fiscal burden of the age pension.

Finally, we have not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures. It is known that the mortality rates from COVID-19 are greater amongst older people, so it should lead to a decrease in the OADR. However, the relatively small number of deaths in Australia mean that the effect of the pandemic will probably not substantially change our recommendations.

\hypertarget{reproducibility}{%
\section*{Reproducibility}\label{reproducibility}}
\addcontentsline{toc}{section}{Reproducibility}

The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}. We used R \citep{RCore}, along with the drake \citep{Rdrake}, tidyverse \citep{Rtidyverse}, demography \citep{Rdemography} and forecast \citep{Rforecast} packages.

  \bibliography{pensionage.bib}

\end{document}

### 2020-09-20 anzjs_preamble.tex
ANZJS version

--- 2020-09-20 PensionAge_anzjs.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  doublespace]{anzsauth}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Forecasting the old-age dependency ratio to determine a sustainable pension age},
-  pdfauthor={Rob J Hyndman\^{}\{1*\}, Yijun Zeng\^{}2, Hanlin Shang\^{}3},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
 %% Any special functions or other packages can be loaded here.
@@
 \usepackage{mathptmx}
-\usepackage[]{natbib}
-\bibliographystyle{anzsj}
-
-\title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
-\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Hanlin Shang\^{}3}
-\date{}
-
-\begin{document}
-\maketitle
-
-\hypertarget{summary}{%
-\section*{Summary}\label{summary}}
-\addcontentsline{toc}{section}{Summary}
-
-We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population.
-Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-
-\textbf{Keywords:} coherent forecasts, demographic components, functional time series, pension age.
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}.
-Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
-Many other countries face similar demographic challenges.
-One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \citep{Walker1982}.
-The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
-
-This is consistent with the Australian Intergenerational Reports \citep{IGR02, IGR07, Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
-To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
-In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 \citep{Nielson2010}.
-In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the \citet{PC13}.
-We investigate the effect of these changes in the pension age on the forecasts of the OADR.
-
-The OADR can be expressed as
-\begin{equation}
-  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
-\end{equation}
-We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs \citep{ARW07, IGR02, IGR07}.
-We provide forecasts of future population age structures over the next 50 years, and use those forecasts to compute the OADR that would result under various pension age schemes.
-
-We then invert the analysis by finding a pension age scheme that would lead to a specified OADR value.
-For our analysis, the specified OADR value has been set at 23\%, just above the level of OADR in 2018.
-Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
-Instead, we provide a methodology for policymakers to find a target pension age that leads to a given OADR value.
-
-Forecasts of population structure depend on forecasts of age- and sex-specific mortality rates, fertility rates and net migration.
-To this end, we combine the functional demographic models of \citet{HU07} and the product-ratio method of \citet{HBY13} within the general stochastic population forecasting framework of \citet{HB08}, to forecast a population age structure.
-These forecasts presuppose that the historical trends of past years will continue.
-Historical data of those rates have thus been used as input to simulate future paths of age- and sex-specific population structure.
-
-Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80\% of Australians over pension age rely fully or partly on the age pension \citep{Power14}.
-Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
-Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and \citet{HY12} have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
-We do not consider these here.
-Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables if required.
-
-The remainder of this paper proceeds as follows.
-Section \ref{sec:litreview} reviews key literature on population forecasting and the pension age in Australia.
-Section \ref{sec:results} describes the data and modelling framework we use in this study.
-We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \ref{sec:target}.
-Finally, Section \ref{sec:conclusions} gives concluding remarks as well as identifies the scope for future research.
-
-\hypertarget{sec:litreview}{%
-\section{Background}\label{sec:litreview}}
-
-\hypertarget{the-age-pension-in-australia}{%
-\subsection{The age pension in Australia}\label{the-age-pension-in-australia}}
-
-The age pension in Australia provides income support and access to a range of concessions and additional allowances for older Australians who have passed a means test.
-
-In 2018, 67\% of Australian residents aged 65 and over received income support payments \citep{AIHW19}.
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances \citep{data61}.
-
-The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7\% of Gross Domestic Profit.
-With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/changespension-1.pdf}
-\caption{\label{fig:changespension}Australian pension age policies.}
-\end{figure}
-
-The pension age for males was set at 65 for over a century.
-While the pension age for females was 60 years until 1994, it has steadily increased to 65 years in 2014, in line with that of males.
-From July 2017, pension eligibility ages for both males and females have been increasing by six months every two years and will reach 67 in July 2023.
-The \citet{PC13} proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and older people are capable of continuing work.
-The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 by 2035, and this was proposed in the Federal Budget Statement for 2014--2015, although it has never been legislated by the Australian Federal Government.
-Figure \ref{fig:changespension} illustrates the process of the adjustments on pension age scheme.
-
-The government has not disclosed the method it used to determine the new pension age.
-\citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''.
-However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates.
-Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.
-
-\hypertarget{demographic-growth-balance-equations}{%
-\subsection{Demographic growth-balance equations}\label{demographic-growth-balance-equations}}
-
-The data required for our proposal are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1~January of each year, and age- and sex-specific exposures to risk (i.e., the population of age \(x\) at 30~June) for each year.
-Let
-\begin{align*}
-  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
-  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
-  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
-\end{align*}
-where \(x=0,1,2,\dots,p-1,p^+\) denotes age with \(p^+\) the open-ended upper age group, set to 100\(^+\) in this study.
-The year is denoted by \(t=1,2,\dots,T\), and superscripts \(M\) and \(F\) denote male and female respectively.
-
-We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
-\begin{align*}
-  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
-\end{align*}
-
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted \(G\)) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
-The equations are expressed as:
-\begin{align*}
-  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
-  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
-  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
-\end{align*}
-where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
-The deaths are estimated using the standard life table approach of population projection.
-It should be noted that the estimated net migration includes errors in data recording.
-
-\hypertarget{old-age-dependency-ratio}{%
-\subsection{Old-Age Dependency Ratio}\label{old-age-dependency-ratio}}
-
-Using this notation, the OADR in year \(t\) is given by
-\begin{equation}\label{eq:oadr}
-O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
-\end{equation}
-where \(a_t\) is the pension age in year \(t\) and \(r_t = a_t - \lfloor a_t \rfloor\) is the non-integer part of \(a_t\).
-This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.
-
-\hypertarget{forecasting-demographic-components}{%
-\subsection{Forecasting demographic components}\label{forecasting-demographic-components}}
-
-Variants of the Lee-Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}.
-The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
-In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
-
-\hypertarget{lee-carter-method}{%
-\subsubsection*{Lee-Carter method}\label{lee-carter-method}}
-\addcontentsline{toc}{subsubsection}{Lee-Carter method}
-
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
-\begin{equation}\label{eq:lc}
-  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
-\end{equation}
-where \(m_{t}(x)\) is the central death rate for age \(x\) in year \(t\).
-This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(\mu(x)\)\} and \{\(\phi(x)\)\}, and a time-varying index \(\beta_{t}\).
-\(\phi(x)\) is a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\).
-\(\beta_{t}\) measures the general level of the log death rates; \(\mu(x)\) is the general pattern across the age of the log mortality rate and \(\varepsilon_{t,x}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
-
-The model is over-parameterised. Therefore, the constraints
-\begin{equation}
-  \sum_{t=1}^{T}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
-\end{equation}
-are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} \citep{Good1969}.
-The estimates of \(\phi(x)\) and \(\beta_t\) are therefore the first principal component and scores of \(\bm{X}\) with \((i,t)\)th element \([\log(m_{t}(x))-\widehat\mu(x)]\), where \(\widehat\mu(x)\) is the sample mean of \(\log(m_{t}(x))\) over \(t\).
-The log transformation introduces some bias, so the LC method adjusts \(\beta_t\) such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted \(\beta_t\) is then extrapolated using a random walk with drift model.
-
-\hypertarget{hyndman-ullah-method}{%
-\subsubsection*{\texorpdfstring{Hyndman-Ullah method \label{sec:HU}}{Hyndman-Ullah method }}\label{hyndman-ullah-method}}
-\addcontentsline{toc}{subsubsection}{Hyndman-Ullah method \label{sec:HU}}
-
-\citet{HU07} proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  The demographic rates are smoothed before modeling.
-\item
-  It uses functional principal components analysis, which is a continuous version of PCA.
-\item
-  It uses more than one principal component, which addresses the main weakness of the LC method.
-\item
-  The forecasting models for the principal component scores are more complex than the random walk with drift model used in the LC model.
-\end{enumerate}
-
-The Hyndman-Ullah (HU) model can be written as
-\begin{align}
-  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
-  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
-\end{align}
-where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\).
-Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms.
-Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score.
-The \(e_t(x)\) is the model error having mean zero and no serial correlation, while \(\mu(x)\) is estimated as the average of \(s_t(x)\) across years.
-Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j^{th}\) principal components and scores of \(s_t(x)-\mu(x)\) respectively.
-Following \citet{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.
-
-By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) are given by
-\begin{equation}
-  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
-\end{equation}
-where \(\widehat{\beta}_{T+h\mid T,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{T+h\mid T,j}\).
-Because \(\left\{\beta_{t,j}\right\}\) is time-varying, it controls the dynamics of the process.
-Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \citet{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.
-
-\hypertarget{product-ratio-method}{%
-\subsubsection*{Product-ratio method}\label{product-ratio-method}}
-\addcontentsline{toc}{subsubsection}{Product-ratio method}
-
-When we apply the \citet{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
-In the product-ratio method \citep{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
-That is, define
-\begin{align}
-  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
-  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
-\end{align}
-Then, the HU method is applied to these two new variables:
-\begin{align*}
-  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
-\end{align*}
-where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0<d<\frac{1}{2}\)).
-It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecasts of male and female do not diverge.
-Then, forecasts of sex-specific data are obtained using
-\begin{align*}
-  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
-  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
-\end{align*}
-The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.
-
-\hypertarget{forecasting-oadr}{%
-\subsection{Forecasting OADR}\label{forecasting-oadr}}
-
-Following the general procedure proposed in \citet{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
-We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
-
-From these models, sample paths are simulated for age-specific fertility rates, age- and sex-specific mortality rates and age- and sex-specific net migration.
-Then future population values are simulated using the demographic growth-balance equations.
-The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates.
-We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see \citet{HB08} for the details).
-Hence, we can simulate \(h\)-step-ahead age- and sex-specific population numbers based on simulated births, deaths and net-migrants.
-
-This simulation was repeated for years \(t=T+1,\dots,T+h\) to obtain a sample path of the age-specific population.
-Many simulated population paths were obtained in this way.
-For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.
-
-There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
-
-\hypertarget{sec:results}{%
-\section{Application to Australia}\label{sec:results}}
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
-
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the \citet{HMD} for 1921--2018.
-The start-year population for 2019 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the \citet{ABSBirths}.
-Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
-First, the period between 1921--1950 has different mortality patterns from later years because of wars \citep{HB08}.
-Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Second, fertility rates are only available from 1950, so the mortality rates were also truncated to the same period.
-
-\hypertarget{component-forecasts}{%
-\subsection{Component forecasts}\label{component-forecasts}}
-
-We illustrate the component model forecasts using fertility rates.
-Figure \ref{fig:componentsfertility} shows the estimated mean age pattern \(\widehat{\mu}(x)\), the first two basis functions, \(\widehat{\phi}_1(x)\) and \(\widehat{\phi}_2(x)\), and the first two principal component scores, \(\widehat{\beta}_{t,1}\) and \(\widehat{\beta}_{t,2}\)) for log fertility rates.
-The first term, \(\widehat{\phi}_1(x) \widehat{\beta}_{t,1}\), accounts for 63.7\% of the variation in the log fertility rates.
-The first principal component scores \(\widehat{\beta}_{t,1}\), shown in black for 1950--2018, display a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
-This increase of fertility is linked to the post-World War II baby boom, while the dramatic decrease from 1960 was due to the availability of contraception pills.
-A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the abortion laws in some states.
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/componentsfertility-1.pdf}
-\caption{\label{fig:componentsfertility}Fitted basis functions and coefficients for Australian age-specific fertility rates.}
-\end{figure}
-
-The first basis function \(\widehat{\phi}_1(x)\) measures the different effects of the time-trend across ages.
-It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception.
-The two ``bumps'' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-The second basis function, accounting for 31.5\% of the variation, largely concerns mothers aged over 30.
-The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80\% pointwise prediction intervals shown as blue shaded regions.
-These forecasts are obtained using automatically selected ARIMA models.
-In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for 4.6\% of the variation, and are much harder to interpret.
-
-Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.
-
-\hypertarget{population-forecasts}{%
-\subsection{Population forecasts}\label{population-forecasts}}
-
-Figure \ref{fig:totalpopulationbyyears} shows the forecast of the total population by sex over the prediction horizon, while Figure \ref{fig:totalpopulationin2038} shows the 20-year forecast of population age structure in 2038.
-Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 27 million by 2068.
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationbyyears-1.pdf}
-\caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of the total population for each sex, along with 80\% prediction intervals.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationin2038-1.pdf}
-\caption{\label{fig:totalpopulationin2038}Forecast population pyramid for 2038, along with 80\% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.}
-\end{figure}
-
-Figure \ref{fig:totalpopulationin2038} shows the mean and the 80\% pointwise prediction interval of simulated population paths for the year 2038 (a 20-year forecast), along with the 2019 base population.
-The uncertainty of the population below aged 20 is largely due to higher forecast variation of fertility rates compared to other components.
-
-Historical OADR values are shown in black in Figure \ref{fig:OADRcurrent} for 1921--2019.
-The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}.
-The increased trend from 2010 is due to the retirements of ``Baby Boomers'', born after WW2.
-We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
-\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
-The actual OADRs for 1921--2019 are shown in black.}
-\end{figure}
-
-Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65.
-This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035.
-This proposal also leads to a slow decline in the OADR over the next 15 years.
-Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
-
-\hypertarget{sec:target}{%
-\section{Sustainable pension age schemes}\label{sec:target}}
-
-Our aim is to determine a pension age scheme that would lead to the OADR being below a desired threshold, thus imposing a sustainability constraint.
-
-Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]'\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\).
-Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.
-We impose the constraint \(0 \le a_t - a_{t-1} < 1\) to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension.
-We also assume that the adjustment unit of the pension age is one month, for easier implementation.
-
-\hypertarget{finding-the-target-pension-age-scheme}{%
-\subsection{Finding the target pension age scheme}\label{finding-the-target-pension-age-scheme}}
-
-Let \(O^*\) denote the desired OADR threshold.
-Because we do not observe the population in future years, we must estimate \(O_{T+h}\) from the simulated populations.
-Then we compute the pension age scheme \(\bm{P}\) using the following algorithm.
-Starting with \(h=1\):
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Set \(a_{T+h}=a_{T+h-1}\).
-\item
-  Increment \(a_{T+h}\) by one-month intervals until either \(\widehat{O}_{T+h|T} > O^*\) or \(a_{T+1} - a_{T}=\) 1 month, where \(\widehat{O}_{T+h|T}\) denotes the mean of the simulated \(O_{T+h|T}\) values.
-\end{enumerate}
-
-We repeat these steps for \(h=2,\dots,H\).
-
-In addition to finding the target pension age based on the mean value of OADR, we also find ``plausible'' pension age schemes that could give the desired OADR level.
-Specifically, we find a range of pension age schemes for which \(O^*\) is contained within the 80\% prediction intervals of the simulated \(O_{T+H|T}\) values.
-Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80\% prediction intervals of OADR is equal to the desired OADR level.
-Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as an 80\% confidence interval of pension age schemes where we are 80\% sure that they will give the desired outcome.
-
-The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but the mean of \(O_{T+H|T}\) is replaced by the 10\% and 90\% quantiles.
-
-Figure \ref{fig:comparisonofpensionages} shows (in blue) the pension scheme produced by this algorithm, along with 80\% confidence intervals.
-In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
-\caption{\label{fig:comparisonofpensionages}The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
-The blue shaded region shows 80\% confidence intervals for the target pension age.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
-\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
-\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.}
-\end{figure}
-
-Figure \ref{fig:OADRwithoptimal} shows the OADR forecasts as a result of using the target age pension scheme shown in Figure \ref{fig:comparisonofpensionages}.
-The target level of 23\% and the mean forecast of the OADR corresponding to the target pension age almost overlap.
-Figure \ref{fig:OADRboundaries} shows the OADR forecasts corresponding to the upper and lower limits of the 80\% confidence intervals shown in Figure \ref{fig:comparisonofpensionages}, demonstrating that they correspond to having OADR forecast prediction interval boundaries that lie very close to the target OADR value.
-
-Thus any pension age higher than the upper boundary shown in Figure \ref{fig:comparisonofpensionages} will give an OADR value that is significantly lower than the target value, while any pension age scheme lower than the lower boundary of the pension age reported in Figure \ref{fig:comparisonofpensionages} will give an OADR value that is significantly higher than the target value.
-
-Figure \ref{fig:comparisonofpensionages} also compares the target pension age scheme and its 80\% confidence interval with the pension age scheme that has been proposed but not yet enacted.
-Clearly, it is outside the 80\% confidence interval and so is too high for our targeted OADR value of 23\%.
-Under our proposed scheme, the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%.
-
-\hypertarget{sec:conclusions}{%
-\section{Conclusions}\label{sec:conclusions}}
-
-The ageing of the population is an increasingly critical issue in Australia (and many other countries) due to the increase in life expectancy and the retirement of baby boomers.
-The fiscal cost of the age pension has increased as a result, and is likely to continue to be a financial burden unless there are changes in age pension schemes.
-Under current Australian government policy, the pension age will rise to 67 in 2023, and there is a proposal to further increase it to 70 by 2035.
-Our analysis suggests that this increase is too rapid unless the aim is to reduce the OADR to below 2018 values.
-
-In this paper, we have suggested a statistical and demographic approach to address the issue.
-We attempt to quantify the effects of changes in the pension age on the OADR, which we take as a crude measure of the financial burden of the age pension.
-We have applied stochastic models to forecast the future population age structure and then used those future age structure projections to find the most appropriate pension age scheme that will ensure a stable OADR around the desired level.
-To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods \citep{HU07}, along with an extension of the product-ratio method \citep{HBY13}.
-Then the framework of \citet{HB08} was used to simulate future populations by age and sex.
-These were then used to simulate OADR values associated with different pension age schemes.
-Finally, we inverted the process to find a pension age scheme that leads to a specified OADR value.
-
-We illustrate the approach based on assuming the desired level of OADR is around the 2018 level of 23\%.
-Using historical data from 1950 to 2019, the forecasts of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
-It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
-
-The empirical analysis presented in this paper shows the adjustment of the pension age to age 67 has been effective in stopping the increasing trend in the OADR values.
-However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
-Therefore, we recommend consistently reviewing the pension age according to the proposed statistical approach.
-This approach has been used to calculate the target pension age from now until 2050 along with its 80\% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 68 by 2030, 69 by 2036 and 70 by 2050.
-This generates a stable OADR of around 23\%.
-
-This research addresses the pension age issue from a purely demographic perspective.
-Further analysis should include an economic perspective as well including the impact of the superannuation guarantee and other economic measures to offset the fiscal burden of the age pension.
-
-Finally, we have not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures.
-It is known that the mortality rates from COVID-19 are greater amongst older people, so it should lead to a decrease in the OADR.
-However, the relatively small number of deaths in Australia mean that the effect of the pandemic will probably not substantially change our recommendations.
-
-\hypertarget{reproducibility}{%
-\section*{Reproducibility}\label{reproducibility}}
-\addcontentsline{toc}{section}{Reproducibility}
-
-The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}.
-We used R \citep{RCore}, along with the drake \citep{Rdrake}, tidyverse \citep{Rtidyverse}, demography \citep{Rdemography} and forecast \citep{Rforecast} packages.
-
-  \bibliography{pensionage.bib}
-
-\end{document}

### 2020-09-20 PensionAge_anzjs.Rmd
Final changes and submitted

@@
 title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
-author: Rob J Hyndman$^{1*}$, Yijun Zeng^2, Hanlin Shang^3
+author: Rob J Hyndman$^{1*}$, Yijun Zeng^2, Han Lin Shang^3
 documentclass: anzsauth
@@
 Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
+Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
 

### 2020-09-20 PensionAge_anzjs.tex
Final changes and submitted

@@
   pdftitle={Forecasting the old-age dependency ratio to determine a sustainable pension age},
-  pdfauthor={Rob J Hyndman\^{}\{1*\}, Yijun Zeng\^{}2, Hanlin Shang\^{}3},
+  pdfauthor={Rob J Hyndman\^{}\{1*\}, Yijun Zeng\^{}2, Han Lin Shang\^{}3},
   hidelinks,
@@
 \title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
-\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Hanlin Shang\^{}3}
+\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Han Lin Shang\^{}3}
 \date{}
@@
 Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
+Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
 

### 2020-09-20 PensionAge.Rmd
Added wp number

@@
 keywords: "coherent forecasts, demographic components, functional time series, pension age"
-wpnumber: no/yr
+wpnumber: 31/20
 jelcodes: J11,J14,C22

### 2021-03-03 Response_to_reviewers.Rmd
Started revision

---
title: Response to reviewers
author: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
output: MonashEBSTemplates::memo
---

We thank the reviewers for their careful reading of our paper; their comments have led to several improvements and corrections.

# Reviewer 1

> What this paper has done is to calculate the right pension age to lead to a given OADR. The calculation is based on a careful and skillful projection on future population, which is described nicely in the first half of the title “Forecasting the old-age dependency ratio”. This part seems to be the main contribution of the paper.

> However, it is dubious whether this calculation help “to determine a sustainable pension age”, as stated in the second half of the title. The main problem is, even if the targeted pension age keeps the OADR from rising above the current level at 23%, the fiscal burden may or may not stay acceptable, or “sustainable”. The reasons are elaborated below.

> First, the calculated pension age is based on number of those above a certain age. A related question is how many of those above 65 years old receive Age Pension, and whether the ratio is expected to remain stable. In Power (2014), as cited on p.3, the portion of Australians over pension age receive age pension was 80%. But the number was 67% in 2018 (p.3) according to Australian Institute of Health and Welfare (2019). This portion may have gone further down to 45% since December 2018, due perhaps to the success of Superannuation, by the estimate of a private firm (https://www.nestegg.com.au/retirement/planning/australians-super-ready). If this figure indeed goes down over time, the financial burden will be lighter and the rise of the target pension age can be slower. The authors may want to check and discuss whether the percentage of Age Pensioners is expected to stabilize around 67% in the future.

> Second, what does “sustainable” mean here? In Australia, the age pension is financed by general taxes. Therefore, growth of GDP, which finances the pension, seems important. In fact, the percentage of total pension payment in GDP may be a more meaningful policy target to examine than the percentage of elderly in total population for policy makers. The authors may want to give some thoughts here.

> Third, do labor force participation and technological growth matter at all? In most rich countries, the long-term growth rate of per capita GDP is lower over time. Hence even if the pension age is raised, the burden of pension payment, which comes from general taxes, may still become heavier if GDP does not grow as fast in the future. A decline in labor force participation rate may have similar effects. The authors may want to consider these extra factors, though they have stated that the approach of this paper is to “illustrate how population forecasting can be used to explore the pension age issue in a simple context” (p.3), and “whether this OADR is the most appropriate level for Australia remains to be examined and is not the focus of this paper” (p.2).

> A minor point here. there are some typos to correct, such as (1) The definitions of OADR are opposite in Eq. 1 and Eq. 2. (2) Should “Gross Domestic Profit” on p.3 be “Gross Domestic Product”?

> To sum up, the technical parts are nicely done, and the calculation of pension age to keep OADR constant can serve as a nice first step for policy decision. But more have to be done to improve the contribution of the paper.

# Reviewer 2

### 2021-03-03 Reviews/Response_to_reviewers.Rmd
Started revision

--- 2021-03-03 Response_to_reviewers.Rmd
@@
 # Reviewer 1
+
+> This paper applies functional data models to mortality, fertility and net migration, and
+use the models to simulate future age-structure of the population. The paper then forecast
+old-age dependency ratio for Australia under various pension age schemes, and propose
+some pension age schemes with given targets. The application is interesting.
+
+> Comments:
+
+> 1. Page 5, 2nd to last line. $G_t(B, 0)$ should refer to net migration rather than deaths?
+> 2. Last line of Page 5 and first line of Page 6. What does the following sentence mean
+in its context: “The deaths are estimated using the standard life table approach of
+population projection.”
+> 3. Page 6, the numerator and denominator of equation (2) should be flipped?
+> 4. Page 8, after equation (9), it is mentioned that “the HU method is applied to these
+two new variables.” In the previous description of the HU method, smoothed version
+of $y_t(x)$ is modelled in the form of equation (6), whereas here the non-smoothed
+$\log[p_t(x)]$ and $\log[r_t(x)]$ are modelled in the form of equation (6). Please clarify.
+> 5. Page 9. It is mentioned that “The future deaths and births in this equation are
+assumed to follow a Poisson distribution, with parameters as a function of future
+mortality and fertility rates.” In the observed data, is the Poisson variation in the
+deaths and births modelled?
+> 6. Page 14. In the second step of computing the pension age scheme $P$, what does “or
+$a_{T+1} - a_T = 1$” mean? Why is $h$ not involved?
+
+# Reviewer 2
 
@@
 But more have to be done to improve the contribution of the paper.
-
-# Reviewer 2

### 2021-03-03 PensionAge.Rmd
Started revision

@@
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
-The deaths are estimated using the standard life table approach of population projection.
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to migration in calendar year $t$ of persons born during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
+The deaths are estimated using the standard life table approach of population projection [@Preston2000].
 It should be noted that the estimated net migration includes errors in data recording.
@@
 \begin{equation}\label{eq:oadr}
-O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
+O_t = \frac{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)},
 \end{equation}

### 2021-03-03 PensionAge_anzjs.Rmd
Started revision

@@
 title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
-author: Rob J Hyndman$^{1*}$, Yijun Zeng^2, Han Lin Shang^3
+author: Rob J Hyndman$^{1*}$, Yijun Zeng$^2$, Han Lin Shang$^3$
 documentclass: anzsauth
@@
 \end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to deaths in calendar year $t$ of births during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
-The deaths are estimated using the standard life table approach of population projection.
+where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to migration in calendar year $t$ of persons born during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
+The deaths are estimated using the standard life table approach of population projection [@Preston2001].
 It should be noted that the estimated net migration includes errors in data recording.

### 2021-03-03 PensionAge_anzjs.tex
Started revision

@@
   doublespace]{anzsauth}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
 % Correct order of tables after \paragraph or \subparagraph
@@
 \usepackage{mathptmx}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \usepackage[]{natbib}
@@
 \end{align*}
-where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to deaths in calendar year \(t\) of births during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
-The deaths are estimated using the standard life table approach of population projection.
+where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to migration in calendar year \(t\) of persons born during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
+The deaths are estimated using the standard life table approach of population projection \citep{Preston2001}.
 It should be noted that the estimated net migration includes errors in data recording.

### 2021-03-03 PensionAge.Rmd
Created yaml header files for different versions

@@
----
-title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
-author:
-- familyname: Hyndman
-  othernames: Rob J
-  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
-  email: Rob.Hyndman@monash.edu
-  correspondingauthor: true
-- familyname: Zeng
-  othernames: Yijun
-  address: Shanghai, China
-- familyname: Shang
-  othernames: Han Lin
-  address: Macquarie University, Sydney, Australia
-abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
-Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population.
-Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
-keywords: "coherent forecasts, demographic components, functional time series, pension age"
-wpnumber: 31/20
-jelcodes: J11,J14,C22
-blind: false
-cover: true
-toc: false
-bibliography: pensionage.bib
-biblio-style: authoryear-comp
-output:
-  MonashEBSTemplates::workingpaper:
-    fig_caption: yes
-    fig_height: 5
-    fig_width: 8
-    keep_tex: yes
-    number_sections: yes
-    citation_package: biblatex
----
-
 ```{r setup, include=FALSE}

### 2021-03-03 PensionAge_anzjs.Rmd
Created yaml header files for different versions

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = FALSE)
-
-# Set up plan
-source("_drake.R")
-
-# Run all code required
-drake::r_make()
-
-loadd(oadr_target)
-```
-
 # Summary {-}
@@
 
-# Introduction
-
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past thirty years [@Fehr2008].
-Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
-Many other countries face similar demographic challenges.
-One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age [@Walker1982].
-The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
-
-This is consistent with the Australian Intergenerational Reports [@IGR02; @IGR07; @Swan2010] that explored the extent to which existing age-related policies would affect the burden of future working generations.
-To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
-In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 [@Nielson2010].
-In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the @PC13.
-We investigate the effect of these changes in the pension age on the forecasts of the OADR.
-
-The OADR can be expressed as
-\begin{equation}
-  \text{OADR} = \frac{\text{number of people aged over pension age}}{\text{number of people aged 15 to pension age}}*100\%
-\end{equation}
-We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs [@ARW07; @IGR02; @IGR07].
-We provide forecasts of future population age structures over the next 50 years, and use those forecasts to compute the OADR that would result under various pension age schemes.
-
-We then invert the analysis by finding a pension age scheme that would lead to a specified OADR value.
-For our analysis, the specified OADR value has been set at `r 100*oadr_target`%, just above the level of OADR in 2018.
-Whether this OADR level is the most appropriate level for Australia remains to be examined and is not the focus of this paper.
-Instead, we provide a methodology for policymakers to find a target pension age that leads to a given OADR value.
-
-Forecasts of population structure depend on forecasts of age- and sex-specific mortality rates, fertility rates and net migration.
-To this end, we combine the functional demographic models of @HU07 and the product-ratio method of @HBY13 within the general stochastic population forecasting framework of @HB08, to forecast a population age structure.
-These forecasts presuppose that the historical trends of past years will continue.
-Historical data of those rates have thus been used as input to simulate future paths of age- and sex-specific population structure.
-
-Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14].
-Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
-Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and @HY12 have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
-We do not consider these here.
-Our approach is intended to illustrate how population forecasting can be used to explore the pension age issue in a simple context, and it could be extended to take into account other variables if required.
-
-The remainder of this paper proceeds as follows.
-Section \@ref(sec:litreview) reviews key literature on population forecasting and the pension age in Australia.
-Section \@ref(sec:results) describes the data and modelling framework we use in this study.
-We show how our framework can be used to estimate a pension age scheme that leads to a target OADR in Section \@ref(sec:target).
-Finally, Section \@ref(sec:conclusions) gives concluding remarks as well as identifies the scope for future research.
-
-# Background {#sec:litreview}
-
-## The age pension in Australia
-
-The age pension in Australia provides income support and access to a range of concessions and additional allowances for older Australians who have passed a means test.
-
-In 2018, 67% of Australian residents aged 65 and over received income support payments [@AIHW19].
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances [@data61].
-
-The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7% of Gross Domestic Profit.
-With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.
-
-```{r changespension, echo=FALSE, fig.cap="Australian pension age policies.", fig.height=4, fig.width=8, message=FALSE, warning=FALSE}
-# Policies obtained from https://www.dss.gov.au/seniors/benefits-payments/age-pension
-# Law: https://guides.dss.gov.au/guide-social-security-law/3/4/1/10
-# History: https://nationalseniors.com.au/news/campaign/a-short-history-of-the-age-pension-section
-loadd(pension_age_plot)
-pension_age_plot
+```{r child='PensionAge.Rmd'}
 ```
-
-The pension age for males was set at 65 for over a century.
-While the pension age for females was 60 years until 1994, it has steadily increased to 65 years in 2014, in line with that of males.
-From July 2017, pension eligibility ages for both males and females have been increasing by six months every two years and will reach 67 in July 2023.
-The @PC13 proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers $150 billion in welfare costs and health spending, and older people are capable of continuing work.
-The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 by 2035, and this was proposed in the Federal Budget Statement for 2014--2015, although it has never been legislated by the Australian Federal Government.
-Figure \@ref(fig:changespension) illustrates the process of the adjustments on pension age scheme.
-
-The government has not disclosed the method it used to determine the new pension age.
-@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that "pension age should increase by approximately 50% of any increase in life expectancy".
-However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
-We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates.
-Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.
-
-## Demographic growth-balance equations
-
-The data required for our proposal are age- and sex-specific birth and death numbers of each calendar year, age- and sex-specific population members on 1&nbsp;January of each year, and age- and sex-specific exposures to risk (i.e., the population of age $x$ at 30&nbsp;June) for each year.
-Let
-\begin{align*}
-  B_t(x) &= \text{Births in calendar year $t$ to females of age $x$},\\
-  D_t(x) &= \text{Deaths in calendar year $t$ of persons of age $x$},\\
-  P_t(x) &= \text{Population of age $x$ at 1 January of year $t$},\\
-  E_t(x) &= \text{Population of age $x$ exposed to risk at 30 June of year $t$},
-\end{align*}
-where $x=0,1,2,\dots,p-1,p^+$ denotes age with $p^+$ the open-ended upper age group, set to 100$^+$ in this study.
-The year is denoted by $t=1,2,\dots,T$, and superscripts $M$ and $F$ denote male and female respectively.
-
-We can obtain historical mortality rates $m_t(x)$ (also called central death rates) and fertility rates $f_t(x)$ as follows:
-\begin{align*}
-  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
-\end{align*}
-
-In addition, the net migration^[Net migration is the difference between immigration and emigration in a certain area during a specified time frame.] (denoted $G$) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
-The equations are expressed as:
-\begin{align*}
-  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
-  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
-  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
-\end{align*}
-where $G_t(x,x+1)$ refers to net migration in calendar year $t$ of persons aged $x$ at the beginning of year $t$, $G_t(p-1^+,p^+)$ refers to migration in calendar year $t$ of persons aged $p-1$ and older at the beginning of year $t$, and $G_t(B,0)$ refers to migration in calendar year $t$ of persons born during year $t$; and similarly for deaths, $D_t(x,x+1)$, $D_t(p-1^+,p^+)$, and $D_t(B,0)$.
-The deaths are estimated using the standard life table approach of population projection [@Preston2001].
-It should be noted that the estimated net migration includes errors in data recording.
-
-## Old-Age Dependency Ratio
-
-Using this notation, the OADR in year $t$ is given by
-\begin{equation}\label{eq:oadr}
-O_t = \frac{\displaystyle\sum_{x=15}^{\lfloor a_t\rfloor-1} P_t(x) + r_t P_t(\lfloor a_t\rfloor)}{\displaystyle\sum_{x\ge \lfloor a_t\rfloor} P_t(x) - r_t P_t(\lfloor a_t\rfloor)},
-\end{equation}
-where $a_t$ is the pension age in year $t$ and $r_t = a_t - \lfloor a_t \rfloor$ is the non-integer part of $a_t$.
-This assumes that the pension age can only be adjusted at the beginning of a year, and that the birthday of the population is uniformly distributed over the year.
-
-## Forecasting demographic components
-
-Variants of the Lee-Carter method [@LC92] are frequently used for demographic forecasting [see, e.g., @SBH11].
-The most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
-In addition, the product-ratio method [@HBY13] is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
-
-### Lee-Carter method {-}
-
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 (but using our notation) is
-\begin{equation}\label{eq:lc}
-  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
-\end{equation}
-where $m_{t}(x)$ is the central death rate for age $x$ in year $t$.
-This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$\mu(x)$} and {$\phi(x)$}, and a time-varying index $\beta_{t}$.
-$\phi(x)$ is a set of parameters that tell us the rate at which each age responds to changes in $\beta_{t}$.
-$\beta_{t}$ measures the general level of the log death rates; $\mu(x)$ is the general pattern across the age of the log mortality rate and $\varepsilon_{t,x}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
-
-The model is over-parameterised. Therefore, the constraints
-\begin{equation}
-  \sum_{t=1}^{T}\beta_t=0, \qquad\text{and}\qquad \int_x \phi(x)=1
-\end{equation}
-are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} [@Good1969].
-The estimates of $\phi(x)$ and $\beta_t$ are therefore the first principal component and scores of $\bm{X}$ with $(i,t)$th element $[\log(m_{t}(x))-\widehat\mu(x)]$, where $\widehat\mu(x)$ is the sample mean of $\log(m_{t}(x))$ over $t$.
-The log transformation introduces some bias, so the LC method adjusts $\beta_t$ such that for each year, the implied number of deaths will be equal to the actual number of deaths.
-The adjusted $\beta_t$ is then extrapolated using a random walk with drift model.
-
-### Hyndman-Ullah method \label{sec:HU} {-}
-
-@HU07 proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:
-
-  1. The demographic rates are smoothed before modeling.
-  2. It uses functional principal components analysis, which is a continuous version of PCA.
-  3. It uses more than one principal component, which addresses the main weakness of the LC method.
-  4. The forecasting models for the principal component scores are more complex than the random walk with drift model used in the LC model.
-
-The Hyndman-Ullah (HU) model can be written as
-\begin{align}
-  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
-  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
-\end{align}
-where $y_t(x)$ may be log mortality, log fertility or net migration [@HB08] in year $t$ and age $x$.
-Here $s_t(x)$ is a smoothed version of the observed data $y_t(x)$, smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and $\{\varepsilon_{t,x}\}$ are independent and identically distributed standard normal error terms.
-Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score.
-The $e_t(x)$ is the model error having mean zero and no serial correlation, while $\mu(x)$ is estimated as the average of $s_t(x)$ across years.
-Estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal components and scores of $s_t(x)-\mu(x)$ respectively.
-Following @HB08, we select $J=6$ which we have found to be large enough for demographic applications.
-
-By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{T+h}(x)$ are given by
-\begin{equation}
-  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
-\end{equation}
-where $\widehat{\beta}_{T+h\mid T,j}$ denotes the $h$-step-ahead forecast of $\beta_{T+h\mid T,j}$.
-Because $\left\{\beta_{t,j}\right\}$ is time-varying, it controls the dynamics of the process.
-Each component series $\left\{\beta_{t,j}\right\}$ is modelled with an ARIMA$(p_j,d_j,q_j)$ process, where $p_j,d_j,q_j$ are selected using the automated algorithm of @forecastpackage, and the parameters are estimated using maximum likelihood estimation.
-
-### Product-ratio method {-}
-
-When we apply the @HU07 model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
-In the product-ratio method [@HBY13], the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
-That is, define
-\begin{align}
-  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
-  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
-\end{align}
-Then, the HU method is applied to these two new variables:
-\begin{align*}
-  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
-\end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$).
-It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge.
-Then, forecasts of sex-specific data are obtained using
-\begin{align*}
-  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
-  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
-\end{align*}
-The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.
-
-## Forecasting OADR
-
-Following the general procedure proposed in @HB08, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
-We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
-
-From these models, sample paths are simulated for age-specific fertility rates, age- and sex-specific mortality rates and age- and sex-specific net migration.
-Then future population values are simulated using the demographic growth-balance equations.
-The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates.
-We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see @HB08 for the details).
-Hence, we can simulate $h$-step-ahead age- and sex-specific population numbers based on simulated births, deaths and net-migrants.
-
-This simulation was repeated for years $t=T+1,\dots,T+h$ to obtain a sample path of the age-specific population.
-Many simulated population paths were obtained in this way.
-For each simulated population path, and each proposed set of pension age changes, we can simulate future OADR values using \eqref{eq:oadr}.
-
-There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
-
-# Application to Australia {#sec:results}
-
-## Data
-
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the @HMD for 1921--2018.
-The start-year population for 2019 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the @ABSBirths.
-Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
-First, the period between 1921--1950 has different mortality patterns from later years because of wars [@HB08].
-Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
-Second, fertility rates are only available from 1950, so the mortality rates were also truncated to the same period.
-
-## Component forecasts
-
-```{r loadfertfit}
-loadd(fert.fit)
-```
-
-We illustrate the component model forecasts using fertility rates.
-Figure \@ref(fig:componentsfertility) shows the estimated mean age pattern $\widehat{\mu}(x)$, the first two basis functions, $\widehat{\phi}_1(x)$ and $\widehat{\phi}_2(x)$, and the first two principal component scores, $\widehat{\beta}_{t,1}$ and $\widehat{\beta}_{t,2}$) for log fertility rates.
-The first term, $\widehat{\phi}_1(x) \widehat{\beta}_{t,1}$, accounts for `r round(fert.fit$varprop[1]*100,1)`% of the variation in the log fertility rates.
-The first principal component scores $\widehat{\beta}_{t,1}$, shown in black for 1950--2018, display a sharp increase between 1950--1960, followed by a rapid decline in fertility rates from 1961.
-This increase of fertility is linked to the post-World War II baby boom, while the dramatic decrease from 1960 was due to the availability of contraception pills.
-A noticeable further reduction of fertility rates in the late 1960s may be due to a change in the abortion laws in some states.
-
-```{r componentsfertility, fig.cap="Fitted basis functions and coefficients for Australian age-specific fertility rates.", message=FALSE}
-loadd(fertf_plot)
-fertf_plot
-```
-
-The first basis function $\widehat{\phi}_1(x)$ measures the different effects of the time-trend across ages.
-It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception.
-The two "bumps" in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
-The second basis function, accounting for `r round(fert.fit$varprop[2]*100,1)`% of the variation, largely concerns mothers aged over 30.
-The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80% pointwise prediction intervals shown as blue shaded regions.
-These forecasts are obtained using automatically selected ARIMA models.
-In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for `r round(sum(fert.fit$varprop[3:6])*100,1)`% of the variation, and are much harder to interpret.
-
-Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.
-
-## Population forecasts
-
-Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by sex over the prediction horizon, while Figure \@ref(fig:totalpopulationin2038) shows the 20-year forecast of population age structure in 2038.
-Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 27 million by 2068.
-
-```{r totalpopulationbyyears, fig.cap="Fifty-year forecasts of the total population for each sex, along with 80% prediction intervals.", fig.height=4}
-loadd(population_plot)
-population_plot
-```
-
-```{r totalpopulationin2038, fig.cap="Forecast population pyramid for 2038, along with 80% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.", warnings=FALSE}
-loadd(pyramid_plot)
-pyramid_plot
-```
-
-Figure \@ref(fig:totalpopulationin2038) shows the mean and the 80% pointwise prediction interval of simulated population paths for the year 2038 (a 20-year forecast), along with the 2019 base population.
-The uncertainty of the population below aged 20 is largely due to higher forecast variation of fertility rates compared to other components.
-
-Historical OADR values are shown in black in Figure \@ref(fig:OADRcurrent) for 1921--2019.
-The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07].
-The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2.
-We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.
-
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
-The actual OADRs for 1921--2019 are shown in black."}
-loadd(oadr_plots)
-oadr_plots
-```
-
-Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65.
-This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
-Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035.
-This proposal also leads to a slow decline in the OADR over the next 15 years.
-Figure \@ref(fig:OADRcurrent) demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.
-
-# Sustainable pension age schemes {#sec:target}
-
-Our aim is to determine a pension age scheme that would lead to the OADR being below a desired threshold, thus imposing a sustainability constraint.
-
-Let $a_t$ denote the pension age in year $t$, and we denote a pension age scheme over the prediction horizon by $\bm{P}=[a_{T+1},\dots,a_{T+H}]'$, with the corresponding OADR values given by $O_{T+1},\dots,O_{T+H}$.
-Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.
-We impose the constraint $0 \le a_t - a_{t-1} < 1$ to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension.
-We also assume that the adjustment unit of the pension age is one month, for easier implementation.
-
-## Finding the target pension age scheme
-
-Let $O^*$ denote the desired OADR threshold.
-Because we do not observe the population in future years, we must estimate $O_{T+h}$ from the simulated populations.
-Then we compute the pension age scheme $\bm{P}$ using the following algorithm.
-Starting with $h=1$:
-
-  1. Set $a_{T+h}=a_{T+h-1}$.
-  2.
-Increment $a_{T+h}$ by one-month intervals until either $\widehat{O}_{T+h|T} > O^*$ or $a_{T+1} - a_{T}=$ 1 month, where $\widehat{O}_{T+h|T}$ denotes the mean of the simulated $O_{T+h|T}$ values.
-
-We repeat these steps for $h=2,\dots,H$.
-
-In addition to finding the target pension age based on the mean value of OADR, we also find "plausible" pension age schemes that could give the desired OADR level.
-Specifically, we find a range of pension age schemes for which $O^*$ is contained within the 80% prediction intervals of the simulated $O_{T+H|T}$ values.
-Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80% prediction intervals of OADR is equal to the desired OADR level.
-Hence, any pension age scheme within those two boundaries is plausible.
-The range of plausible pension age schemes can be thought of as an 80% confidence interval of pension age schemes where we are 80% sure that they will give the desired outcome.
-
-The algorithm to find the upper and lower boundary of plausible pension age schemes is the same as above, but the mean of $O_{T+H|T}$ is replaced by the 10% and 90% quantiles.
-
-Figure \@ref(fig:comparisonofpensionages) shows (in blue) the pension scheme produced by this algorithm, along with 80% confidence intervals.
-In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.
-
-```{r comparisonofpensionages, fig.cap="The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
-The blue shaded region shows 80% confidence intervals for the target pension age."}
-loadd(proposed_pension_scheme_plot)
-proposed_pension_scheme_plot
-```
-
-```{r OADRwithoptimal, fig.cap="The mean forecast and 80% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray."}
-## plots of OADR with plausible pension age schemes
-loadd(proposed_oadr_plot)
-proposed_oadr_plot
-```
-
-```{r OADRboundaries, fig.cap="The 80% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.", fig.height=3}
-loadd(oadr_upper_lower_plot)
-oadr_upper_lower_plot
-```
-
-Figure \@ref(fig:OADRwithoptimal) shows the OADR forecasts as a result of using the target age pension scheme shown in Figure \@ref(fig:comparisonofpensionages).
-The target level of `r oadr_target*100`% and the mean forecast of the OADR corresponding to the target pension age almost overlap.
-Figure \@ref(fig:OADRboundaries) shows the OADR forecasts corresponding to the upper and lower limits of the 80% confidence intervals shown in Figure \@ref(fig:comparisonofpensionages), demonstrating that they correspond to having OADR forecast prediction interval boundaries that lie very close to the target OADR value.
-
-```{r pensionagetables, message=FALSE, eval=FALSE}
-loadd(pension_age_optimal)
-pension_age_optimal %>%
-  mutate(
-    Month = round((Age - trunc(Age)) * 12),
-    Agestring = paste0(
-      trunc(Age), "Y", if_else(Month > 0, paste0("+", Month, "M"), "")),
-    Column = trunc((Year - 2019) / 10) + 1,
-  ) %>%
-  select(Year, Agestring, Column) %>%
-  nest(data = c(Year = Year, Age = Agestring)) %>%
-  pivot_wider(names_from = Column, values_from = data) %>%
-  unnest(cols = c(`1`, `2`, `3`, `4`), names_repair = "unique") %>%
-  knitr::kable(
-    format = "latex",
-    col.names = rep(c("Year", "Age"), 4),
-    booktabs = TRUE,
-    caption = "Fifty-year target pension age scheme with stable OADR around desired OADR. Y denotes years and M denotes months."
-  )
-```
-
-```{r pensionagetables2, message=FALSE, eval=FALSE}
-pension_age_optimal %>%
-  mutate(
-    MonthLo = round((Lo80 - trunc(Lo80)) * 12),
-    MonthHi = round((Hi80 - trunc(Hi80)) * 12),
-    AgeLo = paste0(
-      trunc(Lo80), "Y",
-      if_else(MonthLo > 0, paste0("+", MonthLo, "M"), "")
-    ),
-    AgeHi = paste0(
-      trunc(Hi80), "Y",
-      if_else(MonthHi > 0, paste0("+", MonthHi, "M"), "")
-    ),
-    Column = trunc((Year - 2019) / 10) + 1,
-  ) %>%
-  select(Year, AgeLo, AgeHi, Column) %>%
-  nest(data = c(Year = Year, Lo = AgeLo, Hi = AgeHi)) %>%
-  pivot_wider(names_from = Column, values_from = data) %>%
-  unnest(cols = paste(1:5), names_repair = "unique") %>%
-  knitr::kable(
-    format = "latex",
-    col.names = rep(c("Year", "Lo", "Hi"), 5),
-    booktabs = TRUE,
-    caption = "Fifty-year lower and higher boundary of pension age scheme with 80\\% confidence. Y denotes years and M denotes months."
-  ) %>%
-  kableExtra::kable_styling(font_size = 7)
-```
-
-Thus any pension age higher than the upper boundary shown in Figure \@ref(fig:comparisonofpensionages) will give an OADR value that is significantly lower than the target value, while any pension age scheme lower than the lower boundary of the pension age reported in Figure \@ref(fig:comparisonofpensionages) will give an OADR value that is significantly higher than the target value.
-
-Figure \@ref(fig:comparisonofpensionages) also compares the target pension age scheme and its 80% confidence interval with the pension age scheme that has been proposed but not yet enacted.
-Clearly, it is outside the 80% confidence interval and so is too high for our targeted OADR value of `r oadr_target*100`%.
-Under our proposed scheme, the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at `r oadr_target*100`%.
-
-# Conclusions {#sec:conclusions}
-
-The ageing of the population is an increasingly critical issue in Australia (and many other countries) due to the increase in life expectancy and the retirement of baby boomers.
-The fiscal cost of the age pension has increased as a result, and is likely to continue to be a financial burden unless there are changes in age pension schemes.
-Under current Australian government policy, the pension age will rise to 67 in 2023, and there is a proposal to further increase it to 70 by 2035.
-Our analysis suggests that this increase is too rapid unless the aim is to reduce the OADR to below 2018 values.
-
-In this paper, we have suggested a statistical and demographic approach to address the issue.
-We attempt to quantify the effects of changes in the pension age on the OADR, which we take as a crude measure of the financial burden of the age pension.
-We have applied stochastic models to forecast the future population age structure and then used those future age structure projections to find the most appropriate pension age scheme that will ensure a stable OADR around the desired level.
-To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods [@HU07], along with an extension of the product-ratio method [@HBY13].
-Then the framework of @HB08 was used to simulate future populations by age and sex.
-These were then used to simulate OADR values associated with different pension age schemes.
-Finally, we inverted the process to find a pension age scheme that leads to a specified OADR value.
-
-We illustrate the approach based on assuming the desired level of OADR is around the 2018 level of `r oadr_target*100`%.
-Using historical data from 1950 to 2019, the forecasts of future populations suggests a substantial increase in total population, and confirms the inherent ageing trend.
-It was found that pension age should not be fixed, but instead should grow at a rate that will ensure a stable OADR at a level which can be affordable to Australians of working age.
-
-The empirical analysis presented in this paper shows the adjustment of the pension age to age 67 has been effective in stopping the increasing trend in the OADR values.
-However, a one-time adjustment is not sufficient to ensure a stable OADR in the long term, due to ongoing changes in the population age structure.
-Therefore, we recommend consistently reviewing the pension age according to the proposed statistical approach.
-This approach has been used to calculate the target pension age from now until 2050 along with its 80% confidence interval.
-The target pension age found in this research increases to 67 by 2023, 68 by 2030, 69 by 2036 and 70 by 2050.
-This generates a stable OADR of around `r oadr_target*100`%.
-
-This research addresses the pension age issue from a purely demographic perspective.
-Further analysis should include an economic perspective as well including the impact of the superannuation guarantee and other economic measures to offset the fiscal burden of the age pension.
-
-Finally, we have not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures.
-It is known that the mortality rates from COVID-19 are greater amongst older people, so it should lead to a decrease in the OADR.
-However, the relatively small number of deaths in Australia mean that the effect of the pandemic will probably not substantially change our recommendations.
-
-# Reproducibility {-}
-
-The data and code to fully reproduce our results is available at [`https://github.com/robjhyndman/PensionAge`](https://github.com/robjhyndman/PensionAge).
-We used R [@RCore], along with the drake [@Rdrake], tidyverse [@Rtidyverse], demography [@Rdemography] and forecast [@Rforecast] packages.

### 2021-03-03 PensionAge_wp.Rmd
Created yaml header files for different versions

---
title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Shanghai, China
- familyname: Shang
  othernames: Han Lin
  address: Macquarie University, Sydney, Australia
abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "coherent forecasts, demographic components, functional time series, pension age"
wpnumber: 31/20
jelcodes: J11,J14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

```{r child='PensionAge.Rmd'}
```

### 2021-03-03 PensionAge_wp.tex
Recompiled both versions

--- 2021-03-03 PensionAge_anzjs.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  doublespace]{anzsauth}
-\usepackage{amsmath,amssymb}
+\documentclass[11pt,a4paper,]{article}
 \usepackage{lmodern}
+
+\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
 \hypersetup{
             pdftitle={Forecasting the old-age dependency ratio to determine a sustainable pension age},
-  pdfauthor={Rob J Hyndman\^{}\{1*\}, Yijun Zeng\^{}2, Han Lin Shang\^{}3},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
+            pdfkeywords={coherent forecasts, demographic components, functional time series, pension age},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{geometry}
+\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
+\usepackage[style=authoryear-comp,]{biblatex}
+\addbibresource{pensionage.bib}
+\usepackage{longtable,booktabs}
+% Fix footnotes in tables (requires footnote package)
+\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \setcounter{secnumdepth}{5}
-%% Any special functions or other packages can be loaded here.
+
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+\title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
+
+%% MONASH STUFF
+
+%% CAPTIONS
+\RequirePackage{caption}
+\DeclareCaptionStyle{italic}[justification=centering]
+ {labelfont={bf},textfont={it},labelsep=colon}
+\captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
+\captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
+
+%% FONT
+\RequirePackage{bera}
+\RequirePackage{mathpazo}
+
+%% HEADERS AND FOOTERS
+\RequirePackage{fancyhdr}
+\pagestyle{fancy}
+\rfoot{\Large\sffamily\raisebox{-0.1cm}{\textbf{\thepage}}}
+\makeatletter
+\lhead{\textsf{\expandafter{\@title}}}
+\makeatother
+\rhead{}
+\cfoot{}
+\setlength{\headheight}{15pt}
+\renewcommand{\headrulewidth}{0.4pt}
+\renewcommand{\footrulewidth}{0.4pt}
+\fancypagestyle{plain}{%
+\fancyhf{} % clear all header and footer fields
+\fancyfoot[C]{\sffamily\thepage} % except the center
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrulewidth}{0pt}}
+
+%% MATHS
+\RequirePackage{bm,amsmath}
+\allowdisplaybreaks
+
+%% GRAPHICS
+\RequirePackage{graphicx}
+\setcounter{topnumber}{2}
+\setcounter{bottomnumber}{2}
+\setcounter{totalnumber}{4}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.15}
+\renewcommand{\floatpagefraction}{0.8}
+
+%\RequirePackage[section]{placeins}
+
+%% SECTION TITLES
+\RequirePackage[compact,sf,bf]{titlesec}
+\titleformat{\section}[block]
+  {\fontsize{15}{17}\bfseries\sffamily}
+  {\thesection}
+  {0.4em}{}
+\titleformat{\subsection}[block]
+  {\fontsize{12}{14}\bfseries\sffamily}
+  {\thesubsection}
+  {0.4em}{}
+\titlespacing{\section}{0pt}{*5}{*1}
+\titlespacing{\subsection}{0pt}{*2}{*0.2}
+
+%% TITLE PAGE
+\def\Date{\number\day}
+\def\Month{\ifcase\month\or
+ January\or February\or March\or April\or May\or June\or
+ July\or August\or September\or October\or November\or December\fi}
+\def\Year{\number\year}
+
+\makeatletter
+\def\wp#1{\gdef\@wp{#1}}\def\@wp{??/??}
+\def\jel#1{\gdef\@jel{#1}}\def\@jel{??}
+\def\showjel{{\large\textsf{\textbf{JEL classification:}}~\@jel}}
+\def\nojel{\def\showjel{}}
+\def\addresses#1{\gdef\@addresses{#1}}\def\@addresses{??}
+\def\cover{{\sffamily\setcounter{page}{0}
+        \thispagestyle{empty}
+        \placefig{2}{1.5}{width=5cm}{monash2}
+        \placefig{16.9}{1.5}{width=2.1cm}{MBusSchool}
+        \begin{textblock}{4}(16.9,4)ISSN 1440-771X\end{textblock}
+        \begin{textblock}{7}(12.7,27.9)\hfill
+        \includegraphics[height=0.7cm]{AACSB}~~~
+        \includegraphics[height=0.7cm]{EQUIS}~~~
+        \includegraphics[height=0.7cm]{AMBA}
+        \end{textblock}
+        \vspace*{2cm}
+        \begin{center}\Large
+        Department of Econometrics and Business Statistics\\[.5cm]
+        \footnotesize http://monash.edu/business/ebs/research/publications
+        \end{center}\vspace{2cm}
+        \begin{center}
+        \fbox{\parbox{14cm}{\begin{onehalfspace}\centering\Huge\vspace*{0.3cm}
+                \textsf{\textbf{\expandafter{\@title}}}\vspace{1cm}\par
+                \LARGE\@author\end{onehalfspace}
+        }}
+        \end{center}
+        \vfill
+                \begin{center}\Large
+                \Month~\Year\\[1cm]
+                Working Paper \@wp
+        \end{center}\vspace*{2cm}}}
+\def\pageone{{\sffamily\setstretch{1}%
+        \thispagestyle{empty}%
+        \vbox to \textheight{%
+        \raggedright\baselineskip=1.2cm
+     {\fontsize{24.88}{30}\sffamily\textbf{\expandafter{\@title}}}
+        \vspace{2cm}\par
+        \hspace{1cm}\parbox{14cm}{\sffamily\large\@addresses}\vspace{1cm}\vfill
+        \hspace{1cm}{\large\Date~\Month~\Year}\\[1cm]
+        \hspace{1cm}\showjel\vss}}}
+\def\blindtitle{{\sffamily
+     \thispagestyle{plain}\raggedright\baselineskip=1.2cm
+     {\fontsize{24.88}{30}\sffamily\textbf{\expandafter{\@title}}}\vspace{1cm}\par
+        }}
+\def\titlepage{{\cover\newpage\pageone\newpage\blindtitle}}
+
+\def\blind{\def\titlepage{{\blindtitle}}\let\maketitle\blindtitle}
+\def\titlepageonly{\def\titlepage{{\pageone\end{document}}}}
+\def\nocover{\def\titlepage{{\pageone\newpage\blindtitle}}\let\maketitle\titlepage}
+\let\maketitle\titlepage
+\makeatother
+
+%% SPACING
+\RequirePackage{setspace}
+\spacing{1.5}
+
+%% LINE AND PAGE BREAKING
+\sloppy
+\clubpenalty = 10000
+\widowpenalty = 10000
+\brokenpenalty = 10000
+\RequirePackage{microtype}
+
+%% PARAGRAPH BREAKS
+\setlength{\parskip}{1.4ex}
+\setlength{\parindent}{0em}
+
+%% HYPERLINKS
+\RequirePackage{xcolor} % Needed for links
+\definecolor{darkblue}{rgb}{0,0,.6}
+\RequirePackage{url}
+
+\makeatletter
+\@ifpackageloaded{hyperref}{}{\RequirePackage{hyperref}}
+\makeatother
+\hypersetup{
+     citecolor=0 0 0,
+     breaklinks=true,
+     bookmarksopen=true,
+     bookmarksnumbered=true,
+     linkcolor=darkblue,
+     urlcolor=blue,
+     citecolor=darkblue,
+     colorlinks=true}
+
+%% KEYWORDS
+\newenvironment{keywords}{\par\vspace{0.5cm}\noindent{\sffamily\textbf{Keywords:}}}{\vspace{0.25cm}\par\hrule\vspace{0.5cm}\par}
+
+%% ABSTRACT
+\renewenvironment{abstract}{\begin{minipage}{\textwidth}\parskip=1.4ex\noindent
+\hrule\vspace{0.1cm}\par{\sffamily\textbf{\abstractname}}\newline}
+  {\end{minipage}}
+
 \usepackage[T1]{fontenc}
@@
 
-\usepackage{float, bm}
-\usepackage{moreverb}
-\usepackage{url}
-\usepackage{grffile}
-\usepackage{lineno}
-\usepackage[UKenglish]{isodate}
-\usepackage{hyperref}
+\usepackage[showonlyrefs]{mathtools}
+\usepackage[no-weekday]{eukdate}
 
-\let\origfigure\figure
-\let\endorigfigure\endfigure
-\renewenvironment{figure}[1][2] {
-    \expandafter\origfigure\expandafter[tbp]
-} {
-    \endorigfigure
+%% BIBLIOGRAPHY
+
+\makeatletter
+\@ifpackageloaded{biblatex}{}{\usepackage[style=authoryear-comp, backend=biber, natbib=true]{biblatex}}
+\makeatother
+\ExecuteBibliographyOptions{bibencoding=utf8,minnames=1,maxnames=3, maxbibnames=99,dashed=false,terseinits=true,giveninits=true,uniquename=false,uniquelist=false,doi=false, isbn=false,url=true,sortcites=false}
+
+\DeclareFieldFormat{url}{\texttt{\url{#1}}}
+\DeclareFieldFormat[article]{pages}{#1}
+\DeclareFieldFormat[inproceedings]{pages}{\lowercase{pp.}#1}
+\DeclareFieldFormat[incollection]{pages}{\lowercase{pp.}#1}
+\DeclareFieldFormat[article]{volume}{\mkbibbold{#1}}
+\DeclareFieldFormat[article]{number}{\mkbibparens{#1}}
+\DeclareFieldFormat[article]{title}{\MakeCapital{#1}}
+\DeclareFieldFormat[inproceedings]{title}{#1}
+\DeclareFieldFormat{shorthandwidth}{#1}
+% No dot before number of articles
+\usepackage{xpatch}
+\xpatchbibmacro{volume+number+eid}{\setunit*{\adddot}}{}{}{}
+% Remove In: for an article.
+\renewbibmacro{in:}{%
+  \ifentrytype{article}{}{%
+  \printtext{\bibstring{in}\intitlepunct}}}
+
+\makeatletter
+\DeclareDelimFormat[cbx@textcite]{nameyeardelim}{\addspace}
+\makeatother
+\renewcommand*{\finalnamedelim}{%
+  %\ifnumgreater{\value{liststop}}{2}{\finalandcomma}{}% there really should be no funny Oxford comma business here
+  \addspace\&\space}
+
+\wp{31/20}
+\jel{J11,J14,C22}
+
+\RequirePackage[absolute,overlay]{textpos}
+\setlength{\TPHorizModule}{1cm}
+\setlength{\TPVertModule}{1cm}
+\def\placefig#1#2#3#4{\begin{textblock}{.1}(#1,#2)\rlap{\includegraphics[#3]{#4}}\end{textblock}}
+
+\author{Rob J~Hyndman, Yijun~Zeng, Han Lin~Shang}
+\addresses{\textbf{Rob J Hyndman}\newline
+Department of Econometrics \& Business Statistics\newline Monash University, Clayton VIC 3800, Australia
+\newline{Email: \href{mailto:Rob.Hyndman@monash.edu}{\nolinkurl{Rob.Hyndman@monash.edu}}}\newline Corresponding author\\[1cm]
+\textbf{Yijun Zeng}\newline
+Shanghai, China
+\\[1cm]
+\textbf{Han Lin Shang}\newline
+Macquarie University, Sydney, Australia
+\\[1cm]
 }
 
-\let\origtable\table
-\let\endorigtable\endtable
-\renewenvironment{table}[1][2] {
-    \expandafter\origtable\expandafter[tbp]
-} {
-    \endorigtable
-}
-
-\runningheads{Forecasting the OADR to determine a sustainable pension age}{HYNDMAN, ZENG, SHANG}
-
-\def\volumeyear{2020}
-\let\oldmaketitle\maketitle
-\def\maketitle{\cleanlookdateon\oldmaketitle}
-\linenumbers
-
-\usepackage{titling}
-\pretitle{\begin{center}\Large\bfseries}
-\posttitle{\end{center}\vspace{0.5cm}}
-\preauthor{\begin{center}\large}
-\postauthor{\end{center}\begin{center}
-$^1$\emph{Department of Econometrics \& Business Statistics, Monash University, Clayton, Australia}\\
-$^2$\emph{Shanghai, China}\\
-$^3$\emph{Macquarie University, Sydney, Australia}
-\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}}\end{center}}
-
-\usepackage{mathptmx}
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\usepackage[]{natbib}
-\bibliographystyle{anzsj}
-
-\title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
-\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Han Lin Shang\^{}3}
-\date{}
+\date{\sf\Date~\Month~\Year}
+\makeatletter
+ \lfoot{\sf Hyndman, Zeng, Shang: \@date}
+\makeatother
 
@@
 \maketitle
-
-\hypertarget{summary}{%
-\section*{Summary}\label{summary}}
-\addcontentsline{toc}{section}{Summary}
-
+\begin{abstract}
 We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level.
@@
 Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
-
-\textbf{Keywords:} coherent forecasts, demographic components, functional time series, pension age.
+\end{abstract}
+\begin{keywords}
+coherent forecasts, demographic components, functional time series, pension age
+\end{keywords}
 
@@
 
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}.
+Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \autocite{Fehr2008}.
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
 Many other countries face similar demographic challenges.
-One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \citep{Walker1982}.
+One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \autocite{Walker1982}.
 The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.
 
-This is consistent with the Australian Intergenerational Reports \citep{IGR02, IGR07, Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
+This is consistent with the Australian Intergenerational Reports \autocite{IGR02,IGR07,Swan2010} that explored the extent to which existing age-related policies would affect the burden of future working generations.
 To date, the Australian government has addressed the problem through a variety of approaches including modifications to compulsory superannuation policies, instigating work incentives for older people, and increasing the pension age (defined as the age at which eligible residents can access the age pension for the first time).
-In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 \citep{Nielson2010}.
-In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the \citet{PC13}.
+In 2009, the federal government announced an increase in pension age from 65 to 67 by 2023 \autocite{Nielson2010}.
+In May 2014, the Federal Treasurer proposed a further increase in the pension age to 70 by 2035, in line with the recommendations from the \textcite{PC13}.
 We investigate the effect of these changes in the pension age on the forecasts of the OADR.
@@
 \end{equation}
-We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs \citep{ARW07, IGR02, IGR07}.
+We use the OADR as a measure of the financial burden on the Australian workforce because a rise in the OADR will reduce the ability of working-age population to finance pensions and health costs \autocite{ARW07,IGR02,IGR07}.
 We provide forecasts of future population age structures over the next 50 years, and use those forecasts to compute the OADR that would result under various pension age schemes.
@@
 Forecasts of population structure depend on forecasts of age- and sex-specific mortality rates, fertility rates and net migration.
-To this end, we combine the functional demographic models of \citet{HU07} and the product-ratio method of \citet{HBY13} within the general stochastic population forecasting framework of \citet{HB08}, to forecast a population age structure.
+To this end, we combine the functional demographic models of \textcite{HU07} and the product-ratio method of \textcite{HBY13} within the general stochastic population forecasting framework of \textcite{HB08}, to forecast a population age structure.
 These forecasts presuppose that the historical trends of past years will continue.
@@
 Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80\% of Australians over pension age rely fully or partly on the age pension \citep{Power14}.
+However, 80\% of Australians over pension age rely fully or partly on the age pension \autocite{Power14}.
 Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
-Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and \citet{HY12} have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
+Nevertheless, using OADR as a single measurement of financial burden may overlook some important economic factors, and \textcite{HY12} have suggested the use of an adjusted OADR that takes account of some of these factors in analyzing pension finance.
 We do not consider these here.
@@
 
-In 2018, 67\% of Australian residents aged 65 and over received income support payments \citep{AIHW19}.
-Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances \citep{data61}.
+In 2018, 67\% of Australian residents aged 65 and over received income support payments \autocite{AIHW19}.
+Even though the government has promoted self-financed retirement by introducing the Superannuation Guarantee in 1992, the Superannuation Guarantee accumulations are still modest, with many retirees having no superannuation or very modest balances \autocite{data61}.
 
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/changespension-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/changespension-1.pdf}
 \caption{\label{fig:changespension}Australian pension age policies.}
@@
 From July 2017, pension eligibility ages for both males and females have been increasing by six months every two years and will reach 67 in July 2023.
-The \citet{PC13} proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and older people are capable of continuing work.
+The \textcite{PC13} proposed further lifting of the pension age to 70 on the grounds that increasing the pension age to 70 would save taxpayers \$150 billion in welfare costs and health spending, and older people are capable of continuing work.
 The former Treasurer Joe Hockey announced that the government would increase the pension age to 70 by 2035, and this was proposed in the Federal Budget Statement for 2014--2015, although it has never been legislated by the Australian Federal Government.
@@
 The government has not disclosed the method it used to determine the new pension age.
-\citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''.
+\textcite[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''.
 However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term.
@@
 where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to migration in calendar year \(t\) of persons born during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
-The deaths are estimated using the standard life table approach of population projection \citep{Preston2001}.
+The deaths are estimated using the standard life table approach of population projection \autocite{Preston2000}.
 It should be noted that the estimated net migration includes errors in data recording.
@@
 
-Variants of the Lee-Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}.
-The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
+Variants of the Lee-Carter method \autocite{LC92} are frequently used for demographic forecasting \autocite[see, e.g.,][]{SBH11}.
+The most recent forecast of the population in Australia by the \textcite{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
 The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
-In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
+In addition, the product-ratio method \autocite{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
 
@@
 
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
+The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \textcite{LC92} (but using our notation) is
 \begin{equation}\label{eq:lc}
@@
 \end{equation}
-are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} \citep{Good1969}.
+are imposed, and a singular value decomposition is used to find the least squares solution of \eqref{eq:lc} \autocite{Good1969}.
 The estimates of \(\phi(x)\) and \(\beta_t\) are therefore the first principal component and scores of \(\bm{X}\) with \((i,t)\)th element \([\log(m_{t}(x))-\widehat\mu(x)]\), where \(\widehat\mu(x)\) is the sample mean of \(\log(m_{t}(x))\) over \(t\).
@@
 
-\citet{HU07} proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:
+\textcite{HU07} proposed a nonparametric method for demographic modelling and forecasting that extended the LC model in four ways:
 
@@
 \end{align}
-where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\).
+where \(y_t(x)\) may be log mortality, log fertility or net migration \autocite{HB08} in year \(t\) and age \(x\).
 Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms.
@@
 Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j^{th}\) principal components and scores of \(s_t(x)-\mu(x)\) respectively.
-Following \citet{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.
+Following \textcite{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.
 
@@
 Because \(\left\{\beta_{t,j}\right\}\) is time-varying, it controls the dynamics of the process.
-Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \citet{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.
+Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \textcite{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.
 
@@
 
-When we apply the \citet{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
-In the product-ratio method \citep{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
+When we apply the \textcite{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge.
+In the product-ratio method \autocite{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently.
 That is, define
@@
 
-Following the general procedure proposed in \citet{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
+Following the general procedure proposed in \textcite{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future.
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
@@
 The future deaths and births in this equation are assumed to follow a Poisson distribution, with parameters as a function of future mortality and fertility rates.
-We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see \citet{HB08} for the details).
+We bootstrap the residuals of the net-migration model to simulate future net-migration numbers (see \textcite{HB08} for the details).
 Hence, we can simulate \(h\)-step-ahead age- and sex-specific population numbers based on simulated births, deaths and net-migrants.
@@
 
-Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the \citet{HMD} for 1921--2018.
+Historical central death rates and start-year and mid-year populations of residents in Australia by sex and age in single years for age group 0--99 and 100+ have been sourced from the \textcite{HMD} for 1921--2018.
 The start-year population for 2019 is also used to estimate net migration.
-Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the \citet{ABSBirths}.
+Data for age-specific annual fertility rates by single years of age for 15--49 over the period 1950--2018 was obtained from the \textcite{ABSBirths}.
 Even though annual mortality rates are available from 1921 to 2018, only data collected after 1950 is used for two reasons.
-First, the period between 1921--1950 has different mortality patterns from later years because of wars \citep{HB08}.
+First, the period between 1921--1950 has different mortality patterns from later years because of wars \autocite{HB08}.
 Since the model for this study is valid under the assumption that extrapolative methods can be used, it seemed best to delete the less relevant data, which might influence estimations of parameters if we include them.
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/componentsfertility-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/componentsfertility-1.pdf}
 \caption{\label{fig:componentsfertility}Fitted basis functions and coefficients for Australian age-specific fertility rates.}
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationbyyears-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/totalpopulationbyyears-1.pdf}
 \caption{\label{fig:totalpopulationbyyears}Fifty-year forecasts of the total population for each sex, along with 80\% prediction intervals.}
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/totalpopulationin2038-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/totalpopulationin2038-1.pdf}
 \caption{\label{fig:totalpopulationin2038}Forecast population pyramid for 2038, along with 80\% pointwise prediction intervals. The actual pyramid for 2019 is shown using dashed lines.}
@@
 Historical OADR values are shown in black in Figure \ref{fig:OADRcurrent} for 1921--2019.
-The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}.
+The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \autocite{IGR02} and 2007 \autocite{IGR07}.
 The increased trend from 2010 is due to the retirements of ``Baby Boomers'', born after WW2.
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/OADRcurrent-1.pdf}
 \caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/comparisonofpensionages-1.pdf}
 \caption{\label{fig:comparisonofpensionages}The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/OADRwithoptimal-1.pdf}
 \caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray.}
@@
 \centering
-\includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
+\includegraphics{PensionAge_wp_files/figure-latex/OADRboundaries-1.pdf}
 \caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.}
@@
 We have applied stochastic models to forecast the future population age structure and then used those future age structure projections to find the most appropriate pension age scheme that will ensure a stable OADR around the desired level.
-To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods \citep{HU07}, along with an extension of the product-ratio method \citep{HBY13}.
-Then the framework of \citet{HB08} was used to simulate future populations by age and sex.
+To forecast the population age structure, three demographic components of the population were modeled separately using functional time series methods \autocite{HU07}, along with an extension of the product-ratio method \autocite{HBY13}.
+Then the framework of \textcite{HB08} was used to simulate future populations by age and sex.
 These were then used to simulate OADR values associated with different pension age schemes.
@@
 The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}.
-We used R \citep{RCore}, along with the drake \citep{Rdrake}, tidyverse \citep{Rtidyverse}, demography \citep{Rdemography} and forecast \citep{Rforecast} packages.
+We used R \autocite{RCore}, along with the drake \autocite{Rdrake}, tidyverse \autocite{Rtidyverse}, demography \autocite{Rdemography} and forecast \autocite{Rforecast} packages.
 
-  \bibliography{pensionage.bib}
+\printbibliography
 

### 2021-03-03 Reviews/Response_to_reviewers.Rmd
Working on responses

@@
 author: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
-output: MonashEBSTemplates::memo
+bibliography: ../pensionage.bib
+output: 
+  MonashEBSTemplates::memo:
+    includes:
+      in_header: preamble.tex
 ---
 
-We thank the reviewers for their careful reading of our paper; their comments have led to several improvements and corrections.
+We thank the reviewers for their careful reading of our paper; their comments have led to several improvements and corrections. Reviewer comments are in black, our responses are in green.
 
@@
 
-> This paper applies functional data models to mortality, fertility and net migration, and
+This paper applies functional data models to mortality, fertility and net migration, and
 use the models to simulate future age-structure of the population. The paper then forecast
@@
 
-> Comments:
+Comments:
 
-> 1. Page 5, 2nd to last line. $G_t(B, 0)$ should refer to net migration rather than deaths?
-> 2. Last line of Page 5 and first line of Page 6. What does the following sentence mean
+1. Page 5, 2nd to last line. $G_t(B, 0)$ should refer to net migration rather than deaths?
+
+> Thanks. Now fixed.
+
+2. Last line of Page 5 and first line of Page 6. What does the following sentence mean
 in its context: “The deaths are estimated using the standard life table approach of
 population projection.”
-> 3. Page 6, the numerator and denominator of equation (2) should be flipped?
-> 4. Page 8, after equation (9), it is mentioned that “the HU method is applied to these
+
+> We have added a reference to @Preston2000 who discuss this method.
+
+3. Page 6, the numerator and denominator of equation (2) should be flipped?
+4. Page 8, after equation (9), it is mentioned that “the HU method is applied to these
 two new variables.” In the previous description of the HU method, smoothed version
@@
 $\log[p_t(x)]$ and $\log[r_t(x)]$ are modelled in the form of equation (6). Please clarify.
-> 5. Page 9. It is mentioned that “The future deaths and births in this equation are
+5. Page 9. It is mentioned that “The future deaths and births in this equation are
 assumed to follow a Poisson distribution, with parameters as a function of future
@@
 deaths and births modelled?
-> 6. Page 14. In the second step of computing the pension age scheme $P$, what does “or
+6. Page 14. In the second step of computing the pension age scheme $P$, what does “or
 $a_{T+1} - a_T = 1$” mean? Why is $h$ not involved?
@@
 
-> What this paper has done is to calculate the right pension age to lead to a given OADR.
+What this paper has done is to calculate the right pension age to lead to a given OADR.
 The calculation is based on a careful and skillful projection on future population, which is described nicely in the first half of the title “Forecasting the old-age dependency ratio”.
@@
 
-> However, it is dubious whether this calculation help “to determine a sustainable pension age”, as stated in the second half of the title.
+However, it is dubious whether this calculation help “to determine a sustainable pension age”, as stated in the second half of the title.
 The main problem is, even if the targeted pension age keeps the OADR from rising above the current level at 23%, the fiscal burden may or may not stay acceptable, or “sustainable”.
@@
 
-> First, the calculated pension age is based on number of those above a certain age.
+First, the calculated pension age is based on number of those above a certain age.
 A related question is how many of those above 65 years old receive Age Pension, and whether the ratio is expected to remain stable.
@@
 
-> Second, what does “sustainable” mean here?
+Second, what does “sustainable” mean here?
 In Australia, the age pension is financed by general taxes.
@@
 
-> Third, do labor force participation and technological growth matter at all?
+Third, do labor force participation and technological growth matter at all?
 In most rich countries, the long-term growth rate of per capita GDP is lower over time.
@@
 
-> A minor point here. there are some typos to correct, such as (1) The definitions of OADR are opposite in Eq. 1 and Eq. 2. (2) Should “Gross Domestic Profit” on p.3 be “Gross Domestic Product”?
+A minor point here. there are some typos to correct, such as (1) The definitions of OADR are opposite in Eq. 1 and Eq. 2. (2) Should “Gross Domestic Profit” on p.3 be “Gross Domestic Product”?
 
-> To sum up, the technical parts are nicely done, and the calculation of pension age to keep OADR constant can serve as a nice first step for policy decision.
+To sum up, the technical parts are nicely done, and the calculation of pension age to keep OADR constant can serve as a nice first step for policy decision.
 But more have to be done to improve the contribution of the paper.

### 2021-03-09 PensionAge_anzjs.tex
Updated Makefile

@@
   doublespace]{anzsauth}
-\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
+\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
+\usepackage{longtable,booktabs}
 \usepackage{calc} % for calculating minipage widths
@@
 \title{Forecasting the old-age dependency ratio to determine a sustainable pension age}
-\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\^{}2, Han Lin Shang\^{}3}
+\author{Rob J Hyndman\(^{1*}\), Yijun Zeng\(^2\), Han Lin Shang\(^3\)}
 \date{}
@@
 where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to migration in calendar year \(t\) of persons born during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\).
-The deaths are estimated using the standard life table approach of population projection \citep{Preston2001}.
+The deaths are estimated using the standard life table approach of population projection \citep{Preston2000}.
 It should be noted that the estimated net migration includes errors in data recording.

### 2021-03-15 Reviews/Response_to_reviewers.Rmd
Revision submitted

@@
 
-# Reviewer 1
+# Reviewer 1 {-}
 
@@
 3. Page 6, the numerator and denominator of equation (2) should be flipped?
+
+> Thanks. Now fixed.
+
 4. Page 8, after equation (9), it is mentioned that “the HU method is applied to these
@@
 $\log[p_t(x)]$ and $\log[r_t(x)]$ are modelled in the form of equation (6). Please clarify.
+
+> No, we only apply the HU method to smoothed functions: $p_t(x)$ and $r_t(x)$ are functions of $s_t^M(x)$ and $s_t^F(x)$ which are both smooth.
+
 5. Page 9. It is mentioned that “The future deaths and births in this equation are
@@
 deaths and births modelled?
+
+> Yes, the Poisson variation is used in the weighted smoothing. This information has now been added to end of the first paragraph in Section 2.5.
+
 6. Page 14. In the second step of computing the pension age scheme $P$, what does “or
@@
 
-# Reviewer 2
+> Thanks you for spotting this error.
+It has now been corrected to $a_{T+h} - a_{T+h-1}=12$ months.
+It means that the pension age should not jump more than 12 months between years, to prevent pension-age people losing their pension.
+We have also added this explanation to the paper.
+
+# Reviewer 2 {-}
 
@@
 
+> Thank you for these helpful comments.
+We had previously stated this very briefly in the second last paragraph of the conclusion.
+We have now extended that to incorporate some of the points you have made.
+
+> AIHW (2019) states that the proportion of the aged population receiving the pension has remained relatively stable from 2001 to 2018, so we think it is likely that Power (2014) and the private superannuation firms are counting the numbers differently.
+So we have now removed the citation to Power (2014) and just refer to AIHW (2019).
+
+> The GDP is much more difficult to forecast than age structure, so it is problematic to use it as a target.
+
 A minor point here. there are some typos to correct, such as (1) The definitions of OADR are opposite in Eq. 1 and Eq. 2. (2) Should “Gross Domestic Profit” on p.3 be “Gross Domestic Product”?
+
+> Thanks. Both now fixed.
 
@@
 But more have to be done to improve the contribution of the paper.
+
+> Thank you for your comments.

### 2021-03-15 PensionAge.Rmd
Added a Makefile and caching
Revision submitted

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = FALSE)
+knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
 
@@
 Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80% of Australians over pension age rely fully or partly on the age pension [@Power14].
+However, approximately two-thirds of Australians over pension age rely fully or partly on the age pension [@AIHW19], and this figure has remained relatively constant over the last 20 years.
 Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
@@
 
-The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7% of Gross Domestic Profit.
+The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7% of Gross Domestic Product.
 With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.
@@
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
+We used weighted penalized splines [@HU07] when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
+We use loess when estimating the net-migration curves.
 
@@
   2.
-Increment $a_{T+h}$ by one-month intervals until either $\widehat{O}_{T+h|T} > O^*$ or $a_{T+1} - a_{T}=$ 1 month, where $\widehat{O}_{T+h|T}$ denotes the mean of the simulated $O_{T+h|T}$ values.
+Increment $a_{T+h}$ by one-month intervals until either $\widehat{O}_{T+h|T} \le O^*$ or $a_{T+h} - a_{T+h-1}=12$ months, where $\widehat{O}_{T+h|T}$ denotes the mean of the simulated $O_{T+h|T}$ values.
 
 We repeat these steps for $h=2,\dots,H$.
+The second limit in Step 2 arises because the pension age should not jump more than 12 months between years, to prevent pension-age people losing their pension.
 
@@
 Further analysis should include an economic perspective as well including the impact of the superannuation guarantee and other economic measures to offset the fiscal burden of the age pension.
+There are several issues to be considered here.
+First, not all people aged above the pension age will receive the pension, and the ratio of those receiving the pension may decrease as more retiring people can access superannuation.
+Second, labour force participation is probably related to age as self-funded retirees may opt out of paid employment before they reach pension age.
+Hence, raising the pension age may not have as large an effect on OADR as we have estimated.
+Third, we have not considered the effect of changing per capita GDP which helps fund the pension.
+If per capita GDP declines, the fiscal burden of the pension may increase even with a stable OADR.
 
-Finally, we have not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures.
+We have also not allowed for the impact of COVID-19 in this analysis as it is too early to properly estimate its impact on mortality rates and future age structures.
 It is known that the mortality rates from COVID-19 are greater amongst older people, so it should lead to a decrease in the OADR.

### 2021-03-15 PensionAge_anzjs.tex
Revision submitted

@@
   doublespace]{anzsauth}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \usepackage{mathptmx}
+
+\raggedbottom
 \ifluatex
@@
 Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80\% of Australians over pension age rely fully or partly on the age pension \citep{Power14}.
+However, approximately two-thirds of Australians over pension age rely fully or partly on the age pension \citep{AIHW19}, and this figure has remained relatively constant over the last 20 years.
 Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
@@
 
-The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7\% of Gross Domestic Profit.
+The ageing trend in Australia, along with retirees' dependence on the age pension, means the cost of the age pension is currently around at 2.7\% of Gross Domestic Product.
 With an ageing population, the pension age will need to increase or the fiscal burden will become unsustainable.
@@
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
+We used weighted penalized splines \citep{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
+We use loess when estimating the net-migration curves.
 
@@
 \item
-  Increment \(a_{T+h}\) by one-month intervals until either \(\widehat{O}_{T+h|T} > O^*\) or \(a_{T+1} - a_{T}=\) 1 month, where \(\widehat{O}_{T+h|T}\) denotes the mean of the simulated \(O_{T+h|T}\) values.
+  Increment \(a_{T+h}\) by one-month intervals until either \(\widehat{O}_{T+h|T} \le O^*\) or \(a_{T+h} - a_{T+h-1}=12\) months, where \(\widehat{O}_{T+h|T}\) denotes the mean of the simulated \(O_{T+h|T}\) values.
 \end{enumerate}
@@
 We repeat these steps for \(h=2,\dots,H\).
+The second limit in Step 2 arises because the pension age should not jump more than 12 months between years, to prevent pension-age people losing their pension.
 

### 2021-03-15 PensionAge_wp.tex
Revision submitted

@@
 Some may argue that using OADR as a measure of a financial burden for the next generation could be biased, with a large number of retirees able to rely on self-financed retirement income, such as superannuation.
-However, 80\% of Australians over pension age rely fully or partly on the age pension \autocite{Power14}.
+However, approximately two-thirds of Australians over pension age rely fully or partly on the age pension \autocite{AIHW19}, and this figure has remained relatively constant over the last 20 years.
 Therefore, the proportion of people over working age is still a good representation of the financial burden on future working generations.
@@
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
+We used weighted penalized splines \autocite{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
+We use loess when estimating the net-migration curves.
 

### 2021-05-05 PensionAge.Rmd
Satisfying ANZJS style rules

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = TRUE)
+knitr::opts_chunk$set(echo = FALSE, messages = FALSE, warning = FALSE, cache = FALSE)
 
@@
 
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the "baby-boomer" generation; and (3) a large decline in fertility rates over the past thirty years [@Fehr2008].
+Australia's ageing population is a result of three factors: 1) significant technological advances in medical care leading to longer life spans; 2) high fertility rates after World War II resulting in the 'baby-boomer' generation; and 3) a large decline in fertility rates over the past thirty years [@Fehr2008].
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
@@
 The government has not disclosed the method it used to determine the new pension age.
-@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that "pension age should increase by approximately 50% of any increase in life expectancy".
-However, using a "rule of thumb" approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
+@CEDA07 [p7] proposed directly linking pension age with life expectancy in the way that 'pension age should increase by approximately 50% of any increase in life expectancy'.
+However, using a 'rule of thumb' approach might not be ideal, as 50% of the change in life expectancy may not be a good adjustment to pension age in the long term.
 We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates.
@@
 \begin{align*}
-  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
+  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year $t$};\\
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year $t$}.
 \end{align*}
 
-In addition, the net migration^[Net migration is the difference between immigration and emigration in a certain area during a specified time frame.] (denoted $G$) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
+The net migration is the difference between immigration and emigration in a certain area during a specified time frame.
+We denote net migration by $G$, and estimate it using demographic growth-balance equations, which summarise the relationship between population change and three factors: net migration, births and deaths.
 The equations are expressed as:
@@
 
-Variants of the Lee-Carter method [@LC92] are frequently used for demographic forecasting [see, e.g., @SBH11].
-The most recent forecast of the population in Australia by the @PC13 was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
+Variants of the Lee--Carter method [@LC92] are frequently used for demographic forecasting [see, e.g., @SBH11].
+The most recent forecast of the population in Australia by the @PC13 was based on basic Lee--Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee--Carter method failed to capture.
+The Hyndman--Ullah method (2007) is a generalisation of the Lee--Carter method and is used as the basis for forecasting demographic components in this study.
 In addition, the product-ratio method [@HBY13] is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
 
-### Lee-Carter method {-}
+### Lee--Carter method {-}
 
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 (but using our notation) is
+The Lee--Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by @LC92 (but using our notation) is
 \begin{equation}\label{eq:lc}
@@
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, {$\mu(x)$} and {$\phi(x)$}, and a time-varying index $\beta_{t}$.
-$\phi(x)$ is a set of parameters that tell us the rate at which each age responds to changes in $\beta_{t}$.
+The notation $\phi(x)$ denotes a set of parameters that tell us the rate at which each age responds to changes in $\beta_{t}$.
 $\beta_{t}$ measures the general level of the log death rates; $\mu(x)$ is the general pattern across the age of the log mortality rate and $\varepsilon_{t,x}$ is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
@@
 
-### Hyndman-Ullah method \label{sec:HU} {-}
+### Hyndman--Ullah method \label{sec:HU} {-}
 
@@
 
-The Hyndman-Ullah (HU) model can be written as
+The Hyndman--Ullah (HU) model can be written as
 \begin{align}
-  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
+  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1},\\
   s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
@@
 where $y_t(x)$ may be log mortality, log fertility or net migration [@HB08] in year $t$ and age $x$.
-Here $s_t(x)$ is a smoothed version of the observed data $y_t(x)$, smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and $\{\varepsilon_{t,x}\}$ are independent and identically distributed standard normal error terms.
+Here $s_t(x)$ is a smoothed version of the observed data $y_t(x)$, smoothed over age but not time, and estimated by constrained weighted penalised regression splines; and $\{\varepsilon_{t,x}\}$ are independent and identically distributed standard normal error terms.
 Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score.
 The $e_t(x)$ is the model error having mean zero and no serial correlation, while $\mu(x)$ is estimated as the average of $s_t(x)$ across years.
-Estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j^{th}$ principal components and scores of $s_t(x)-\mu(x)$ respectively.
-Following @HB08, we select $J=6$ which we have found to be large enough for demographic applications.
+Estimates of $\phi_j(x)$ and $\beta_{t,j}$ are the $j$th principal components and scores of $s_t(x)-\mu(x)$ respectively.
+Following @HB08, we select $J=6$, which we have found to be large enough for demographic applications.
 
-By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{T+h}(x)$ are given by
+By conditioning on the observed data $\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}$ and the set of functional principal components $\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}$, the $h$-step-ahead forecast of $y_{T+h}(x)$ is given by
 \begin{equation}
@@
 \begin{align*}
-  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x),\\
+  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x),
 \end{align*}
-where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0<d<\frac{1}{2}$).
+where time series $\left\{\beta_{t,j}\right\}$ are fitted with ARIMA models, while $\left\{\gamma_{t,l}\right\}$ are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to $0< d < 1/2$).
 It is the stationary constraint on $\gamma_{t,l}$ that ensures the forecasts of male and female do not diverge.
@@
 \begin{align*}
-  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
-  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
+  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x),\\
+  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x).
 \end{align*}
@@
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
-We used weighted penalized splines [@HU07] when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
+We used weighted penalised splines [@HU07] when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
 We use loess when estimating the net-migration curves.
@@
 
-There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
+There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman--Ullah specification (i.e., $e_t(x)$ in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
 
@@
 It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception.
-The two "bumps" in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
+The two 'bumps' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
 The second basis function, accounting for `r round(fert.fit$varprop[2]*100,1)`% of the variation, largely concerns mothers aged over 30.
-The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80% pointwise prediction intervals shown as blue shaded regions.
+The forecasts of future coefficients are shown in the lower panels with their 80% pointwise prediction intervals shown as shaded regions.
 These forecasts are obtained using automatically selected ARIMA models.
@@
 
-Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.
+Similar models are used for the product and ratio of mortality rates, and sum and difference of net migration rates.
 
@@
 Figure \@ref(fig:totalpopulationbyyears) shows the forecast of the total population by sex over the prediction horizon, while Figure \@ref(fig:totalpopulationin2038) shows the 20-year forecast of population age structure in 2038.
-Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to around 27 million by 2068.
+Figure \@ref(fig:totalpopulationbyyears) indicates that both the female and male population are expected to increase to almost 20 million by 2050.
 
@@
 The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 [@IGR02] and 2007 [@IGR07].
-The increased trend from 2010 is due to the retirements of "Baby Boomers", born after WW2.
+The increased trend from 2010 is due to the retirements of 'Baby Boomers', born after WW2.
 We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.
 
-```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
-The actual OADRs for 1921--2019 are shown in black."}
+```{r OADRcurrent, fig.cap="Fifty-year forecasts of the OADR associated with a pension age equal to 65, the current approved pension age scheme, and the proposed scheme with the pension age rising to 70 in 2035.
+The actual OADRs for 1921--2019 are also shown."}
 loadd(oadr_plots)
@@
 
-Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65.
+Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal to 65.
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
@@
 
-Let $a_t$ denote the pension age in year $t$, and we denote a pension age scheme over the prediction horizon by $\bm{P}=[a_{T+1},\dots,a_{T+H}]'$, with the corresponding OADR values given by $O_{T+1},\dots,O_{T+H}$.
+Let $a_t$ denote the pension age in year $t$, and we denote a pension age scheme over the prediction horizon by $\bm{P}=[a_{T+1},\dots,a_{T+H}]^\top$, with the corresponding OADR values given by $O_{T+1},\dots,O_{T+H}$.
 Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.
@@
 
-In addition to finding the target pension age based on the mean value of OADR, we also find "plausible" pension age schemes that could give the desired OADR level.
+In addition to finding the target pension age based on the mean value of OADR, we also find 'plausible' pension age schemes that could give the desired OADR level.
 Specifically, we find a range of pension age schemes for which $O^*$ is contained within the 80% prediction intervals of the simulated $O_{T+H|T}$ values.
@@
 
-Figure \@ref(fig:comparisonofpensionages) shows (in blue) the pension scheme produced by this algorithm, along with 80% confidence intervals.
-In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.
+Figure \@ref(fig:comparisonofpensionages) shows the pension scheme produced by this algorithm, along with 80% confidence intervals.
+In comparison, the previous, current and proposed schemes are also shown.
 
-```{r comparisonofpensionages, fig.cap="The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
-The blue shaded region shows 80% confidence intervals for the target pension age."}
+```{r comparisonofpensionages, fig.cap="The target pension age scheme along with the pension age schemes that have been set and proposed by the government.
+The shaded region shows 80% confidence intervals for the target pension age."}
 loadd(proposed_pension_scheme_plot)
@@
 
-```{r OADRwithoptimal, fig.cap="The mean forecast and 80% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray."}
+```{r OADRwithoptimal, fig.cap="The mean forecast and 80% prediction intervals for the OADR associated with the target pension age scheme, along with the desired OADR level at 0.23."}
 ## plots of OADR with plausible pension age schemes
@@
 
-```{r OADRboundaries, fig.cap="The 80% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.", fig.height=3}
+```{r OADRboundaries, fig.cap="The 80% prediction intervals of OADR associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level at 0.23.", fig.height=3}
 loadd(oadr_upper_lower_plot)
@@
 The data and code to fully reproduce our results is available at [`https://github.com/robjhyndman/PensionAge`](https://github.com/robjhyndman/PensionAge).
-We used R [@RCore], along with the drake [@Rdrake], tidyverse [@Rtidyverse], demography [@Rdemography] and forecast [@Rforecast] packages.
+We used \textsf{R} [@RCore], along with the \textsf{drake} [@Rdrake], \textsf{tidyverse} [@Rtidyverse], \textsf{demography} [@Rdemography] and \textsf{forecast} [@Rforecast] packages.

### 2021-05-05 PensionAge_anzjs.tex
Satisfying ANZJS style rules

@@
 \usepackage{hyperref}
+\usepackage{mathtools}
+\mathtoolsset{showonlyrefs}
 
@@
 $^3$\emph{Macquarie University, Sydney, Australia}
-\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}}\end{center}}
+\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}. This work is supported by the ARC Centre of Excellence for Mathematical and Statistical Frontiers.}\end{center}}
 
@@
 Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level.
-Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.
+Our general approach can easily be extended to other target levels of the old-age dependency ratio and to other countries.
 
@@
 
-Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}.
+Australia's ageing population is a result of three factors: 1) significant technological advances in medical care leading to longer life spans; 2) high fertility rates after World War II resulting in the `baby-boomer' generation; and 3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}.
 Consequently, there are many older people leaving the workforce, and fewer workers replacing them.
@@
 The government has not disclosed the method it used to determine the new pension age.
-\citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''.
-However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term.
+\citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that `pension age should increase by approximately 50\% of any increase in life expectancy'.
+However, using a `rule of thumb' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term.
 We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates.
@@
 \begin{align*}
-  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
-  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
+  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year $t$};\\
+  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year $t$}.
 \end{align*}
 
-In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted \(G\)) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths.
+The net migration is the difference between immigration and emigration in a certain area during a specified time frame.
+We denote net migration by \(G\), and estimate it using demographic growth-balance equations, which summarise the relationship between population change and three factors: net migration, births and deaths.
 The equations are expressed as:
@@
 
-Variants of the Lee-Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}.
-The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture.
-The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study.
+Variants of the Lee--Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}.
+The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee--Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee--Carter method failed to capture.
+The Hyndman--Ullah method (2007) is a generalisation of the Lee--Carter method and is used as the basis for forecasting demographic components in this study.
 In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.
 
-\hypertarget{lee-carter-method}{%
-\subsubsection*{Lee-Carter method}\label{lee-carter-method}}
-\addcontentsline{toc}{subsubsection}{Lee-Carter method}
+\hypertarget{leecarter-method}{%
+\subsubsection*{Lee--Carter method}\label{leecarter-method}}
+\addcontentsline{toc}{subsubsection}{Lee--Carter method}
 
-The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
+The Lee--Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
 \begin{equation}\label{eq:lc}
@@
 This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(\mu(x)\)\} and \{\(\phi(x)\)\}, and a time-varying index \(\beta_{t}\).
-\(\phi(x)\) is a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\).
+The notation \(\phi(x)\) denotes a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\).
 \(\beta_{t}\) measures the general level of the log death rates; \(\mu(x)\) is the general pattern across the age of the log mortality rate and \(\varepsilon_{t,x}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.
@@
 
-\hypertarget{hyndman-ullah-method}{%
-\subsubsection*{\texorpdfstring{Hyndman-Ullah method \label{sec:HU}}{Hyndman-Ullah method }}\label{hyndman-ullah-method}}
-\addcontentsline{toc}{subsubsection}{Hyndman-Ullah method \label{sec:HU}}
+\hypertarget{hyndmanullah-method}{%
+\subsubsection*{\texorpdfstring{Hyndman--Ullah method \label{sec:HU}}{Hyndman--Ullah method }}\label{hyndmanullah-method}}
+\addcontentsline{toc}{subsubsection}{Hyndman--Ullah method \label{sec:HU}}
 
@@
 where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\).
-Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms.
+Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalised regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms.
 Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score.
 The \(e_t(x)\) is the model error having mean zero and no serial correlation, while \(\mu(x)\) is estimated as the average of \(s_t(x)\) across years.
-Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j^{th}\) principal components and scores of \(s_t(x)-\mu(x)\) respectively.
-Following \citet{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.
+Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j\)th principal components and scores of \(s_t(x)-\mu(x)\) respectively.
+Following \citet{HB08}, we select \(J=6\), which we have found to be large enough for demographic applications.
 
-By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) are given by
+By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) is given by
 \begin{equation}
@@
 \begin{align*}
-  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
-  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
+  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x),\\
+  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x),
 \end{align*}
-where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0<d<\frac{1}{2}\)).
+where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models, while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0< d < 1/2\)).
 It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecasts of male and female do not diverge.
@@
 We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration.
-We used weighted penalized splines \citep{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
+We used weighted penalised splines \citep{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births.
 We use loess when estimating the net-migration curves.
@@
 
-There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
+There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman--Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.
 
@@
 It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception.
-The two ``bumps'' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
+The two `bumps' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s.
 The second basis function, accounting for 31.5\% of the variation, largely concerns mothers aged over 30.
-The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80\% pointwise prediction intervals shown as blue shaded regions.
+The forecasts of future coefficients are shown in the lower panels with their 80\% pointwise prediction intervals shown as shaded regions.
 These forecasts are obtained using automatically selected ARIMA models.
@@
 Figure \ref{fig:totalpopulationbyyears} shows the forecast of the total population by sex over the prediction horizon, while Figure \ref{fig:totalpopulationin2038} shows the 20-year forecast of population age structure in 2038.
-Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 27 million by 2068.
+Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to almost 20 million by 2050.
 
@@
 The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}.
-The increased trend from 2010 is due to the retirements of ``Baby Boomers'', born after WW2.
+The increased trend from 2010 is due to the retirements of `Baby Boomers', born after WW2.
 We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.
@@
 \includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
-\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple).
-The actual OADRs for 1921--2019 are shown in black.}
+\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65, the current approved pension age scheme, and the proposed scheme with the pension age rising to 70 in 2035.
+The actual OADRs for 1921--2019 are also shown.}
 \end{figure}
 
-Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65.
+Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal to 65.
 This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care.
@@
 
-Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]'\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\).
+Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]^\top\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\).
 Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold.
@@
 
-In addition to finding the target pension age based on the mean value of OADR, we also find ``plausible'' pension age schemes that could give the desired OADR level.
+In addition to finding the target pension age based on the mean value of OADR, we also find `plausible' pension age schemes that could give the desired OADR level.
 Specifically, we find a range of pension age schemes for which \(O^*\) is contained within the 80\% prediction intervals of the simulated \(O_{T+H|T}\) values.
@@
 
-Figure \ref{fig:comparisonofpensionages} shows (in blue) the pension scheme produced by this algorithm, along with 80\% confidence intervals.
-In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.
+Figure \ref{fig:comparisonofpensionages} shows the pension scheme produced by this algorithm, along with 80\% confidence intervals.
+In comparison, the previous, current and proposed schemes are also shown.
 
@@
 \includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
-\caption{\label{fig:comparisonofpensionages}The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government.
-The blue shaded region shows 80\% confidence intervals for the target pension age.}
+\caption{\label{fig:comparisonofpensionages}The target pension age scheme along with the pension age schemes that have been set and proposed by the government.
+The shaded region shows 80\% confidence intervals for the target pension age.}
 \end{figure}
@@
 \includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
-\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray.}
+\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme, along with the desired OADR level at 0.23.}
 \end{figure}
@@
 \includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
-\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.}
+\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level at 0.23.}
 \end{figure}
@@
 The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}.
-We used R \citep{RCore}, along with the drake \citep{Rdrake}, tidyverse \citep{Rtidyverse}, demography \citep{Rdemography} and forecast \citep{Rforecast} packages.
+We used \textsf{R} \citep{RCore}, along with the \textsf{drake} \citep{Rdrake}, \textsf{tidyverse} \citep{Rtidyverse}, \textsf{demography} \citep{Rdemography} and \textsf{forecast} \citep{Rforecast} packages.
 

### 2021-05-05 R/autoplot.fmforecast.R

@@ -4,15 +4,18 @@ autoplot.fmforecast <- function(data) {
   p1 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 1])) +
     geom_line() +
     xlab("Age (x)") +
-    ylab(TeX("$\\mu(x)"))
+    ylab(TeX("$\\mu(x)")) +
+    theme_bw()
   p2 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 2])) +
     geom_line() +
     xlab("Age (x)") +
-    ylab(TeX("$\\phi_1(x)$"))
+    ylab(TeX("$\\phi_1(x)$")) +
+    theme_bw()
   p3 <- ggplot(mapping = aes(x = data$age, y = data$model$basis[, 3])) +
     geom_line() +
     xlab("Age (x)") +
-    ylab(TeX("$\\phi_2(x)$"))
+    ylab(TeX("$\\phi_2(x)$")) +
+    theme_bw()
   # Fix bug in fertf output
   for(i in 2:3) {
     data$coeff[[i]]$lower <- ts(as.matrix(data$coeff[[i]]$lower))
@@ -20,9 +23,11 @@ autoplot.fmforecast <- function(data) {
     tsp(data$coeff[[i]]$lower) <- tsp(data$coeff[[i]]$upper) <- tsp(data$coeff[[i]]$mean)
   }
   p4 <- autoplot(data$coeff[[2]]) +
-    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{1,t}$"))
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{1,t}$")) +
+    theme_bw()
   p5 <- autoplot(data$coeff[[3]]) +
-    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{2,t}$"))
+    ggtitle("") + xlab("Year (t)") + ylab(TeX("$\\beta_{2,t}$")) +
+    theme_bw()
 
   print((p1 | p2 | p3) / (plot_spacer() | p4 | p5))
 }

### 2021-05-05 R/optimal_pension_scheme_plot.R

@@ -11,9 +11,16 @@ optimal_pension_scheme_plot <- function(pension_age, pension.fc, pension_colors,
     filter(Year >= 2005)
   pension.fc$x <- ts(rep(65,3), start=2016)
   autoplot(pension.fc, fcol=pension_colors["Optimal"]) +
-    geom_line(data= pension_schemes, mapping=aes(x=Year, y=Age, col=Policy, group=Policy)) +
+    geom_line(data= pension_schemes, mapping=aes(x=Year, y=Age, lty=Policy, col=Policy, group=Policy)) +
     xlab("Year") +
     ylab("Minimum pension age") +
+    scale_linetype_manual(
+      values = as.integer(factor(pension_colors)),
+      labels = c(paste("Pension age to give OADR =",oadr_target),
+                 "Proposed policy",
+                 "Current policy",
+                 "Pension age 65")
+    ) +
     scale_color_manual(
       values = pension_colors,
       labels = c(paste("Pension age to give OADR =",oadr_target),
@@ -28,6 +35,7 @@ optimal_pension_scheme_plot <- function(pension_age, pension.fc, pension_colors,
                  "Current policy",
                  "Pension age 65")
     ) +
-    guides(col = guide_legend("Policy")) +
-    ggtitle("")
+    guides(col=FALSE, lty = guide_legend("Policy")) +
+    ggtitle("") +
+    theme_bw()
 }

### 2021-05-05 R/plan.R

@@ -23,7 +23,7 @@ the_plan <-
   # Pension age scheme plot
   pension_age_plot = pension_age %>%
     filter(Year >= 2014) %>%
-    ggplot(aes(x = Year, y = Age, group = Policy, col = Policy)) +
+    ggplot(aes(x = Year, y = Age, group = Policy, lty= Policy)) +
     geom_line() +
     ylab("Minimum pension age") +
     scale_color_manual(
@@ -31,7 +31,7 @@ the_plan <-
       labels = c("Proposed further change",
                  "Current policy",
                  "Pension age at 65")
-    ),
+    ) + theme_bw(),
 
   # Get population data to 1 Jan 2019
   aus.pop = hmd.pop(country = "AUS",
@@ -133,7 +133,8 @@ the_plan <-
     ggtitle("Total population") +
     facet_grid(. ~ Sex) +
     geom_ribbon(aes(y = Mean, ymin = Lo80, ymax = Up80), fill = "#7d7def", data = future_tot_pop) +
-    geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1),
+    geom_line(data = future_tot_pop, col = "#0000cc", mapping = aes(y = Mean), size = 1) +
+    theme_bw(),
 
   pyramid_plot = pyramid(
     history_pop %>% filter(Year == max(Year)),
@@ -152,7 +153,7 @@ the_plan <-
     #geom_hline(yintercept = oadr_target, col = "gray") +
     geom_ribbon(aes(ymin = Lo, ymax = Hi, fill = Policy, group = Policy),
                 alpha = 0.5) +
-    geom_line(aes(col = Policy, group = Policy), size = .75) +
+    geom_line(aes(lty=Policy, col = Policy, group = Policy), size = .75) +
     geom_line(col = "black", size = .75, data = OADR_history) +
     xlab("year") +
     ylab("ratio") +
@@ -167,7 +168,8 @@ the_plan <-
                       labels = c("Pension age 65",
                                  "Current policy",
                                  "Proposed policy")
-    ),
+    ) + theme_bw() +
+    guides(fill=FALSE, col=FALSE) + theme(legend.position="bottom"),
 
   # Target OADR
   oadr_target = 0.23,
@@ -208,7 +210,7 @@ the_plan <-
     geom_line(aes(y = OADR), col = pension_colors["Optimal"]) +
[…]

### 2021-05-05 R/pyramid.R

@@ -10,7 +10,8 @@ pyramid <- function(history, future) {
     coord_flip() +
     scale_y_reverse(expand = c(0.012, 0.012)) +
     scale_x_continuous(expand = c(0.012, 0.012)) +
-    facet_grid(. ~ Sex)
+    facet_grid(. ~ Sex) +
+    theme_bw()
   p_female <- data %>%
     filter(Sex == "Female") %>%
     ggplot(aes(x = Age, y = Population, group = Year)) +
@@ -26,7 +27,8 @@ pyramid <- function(history, future) {
       axis.ticks.y.left = element_blank()
     ) +
     scale_x_continuous(position = "top", sec.axis = sec_axis(~.), expand = c(0.012, 0.012)) +
-    facet_grid(. ~ Sex)
+    facet_grid(. ~ Sex) +
+    theme_bw()
 
   (p_male | p_female)
 }
